### 2015-11-25 document/ms.tex
First commit of the document

\documentclass[revtex4]{emulateapj}
\usepackage[usenames,dvipsnames]{color}
\usepackage{natbib,graphicx,latexsym,lscape}

\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{url}
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\begin{document}

\citestyle{aa}
\slugcomment{\bf November 25, 2015 draft}
\shortauthors{Gully-Santiago \emph{et al.}}
\shorttitle{Welter}

\title{Welter is an ongoing analysis of a young star in Taurus}

\author{M.~A.~Gully-Santiago}
\affil{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing, P. R. China}

\author{G. Herczeg}
\affil{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing, P. R. China}

\maketitle

%------------------------------------------------------------------------------------------
\section{Introduction}
%------------------------------------------------------------------------------------------

Hello world.

See \citet{2011ARA&A..49...67W} for a review about circumstellar disks.
%------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------
%Bibliography
%------------------------------------------------------------------------------------------
\bibliographystyle{apj}
\bibliography{ms}

\end{document}

### 2015-12-04 document/ms.tex
Work on Issue #4: Brackett Gamma line, make a fresh layout for the ApJ document.

@@
+\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
+%\documentclass[onecolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
+%\documentclass[preprint]{aastex}
+
+%\usepackage{lineno}
+%\usepackage{blindtext}
+%\linenumbers
+
+\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
+%From: http://arxiv.org/format/1512.00483
+\input{setup}
+
+\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
+\providecommand{\adsurl}[1]{\href{#1}{ADS}}
+\newcommand{\name}{LkCa4}
+\def\vsini{$v\sin{i_*}$}
+
+\slugcomment{In preparation}
+
+\shorttitle{\name IGRINS spectroscopy}
+
+\shortauthors{Gully-Santiago et al.}
+
+\bibliographystyle{yahapj}
+
+\begin{document}
+
+\title{IGRINS spectra of \name}
+
+\author{Michael A. Gully-Santiago,\altaffilmark{1} Greg Herczeg,\altaffilmark{1} et al.}
+
+\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
+
+\begin{abstract}
+We interpret the high resolution near-IR spectra of \name.  We used the instrument IGRINS.
+\end{abstract}
+
+\keywords{stars: fundamental parameters --- stars: individual (\name) ---  stars: low-mass -- stars: statistics}
+
+\maketitle
+
+\section{Introduction}\label{sec:intro}
+
+\name is a weak lined \emph{T-Tauri} star.  In this short research note we provide the IGRINS spectrum of \name.
+
+\section{Observations}\label{sec:obs}
+
+\subsection{IGRINS Spectroscopy}\label{sec:igrins} 
+We acquired observations with IGRINS on the Harlan J.
+Smith Telescope at McDonald Observatory on XX UTC.
+The Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG}, is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
+The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.
+\section{Spectral properties}\label{sec:lines}
+
+Figure \ref{fig:BrG} shows the Br$\gamma$ line profile in the IGRINS spectrum of \name.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.95\columnwidth]{figures/Br_gamma_zoom} 
+	\caption{Line profile of Br$\gamma$ in the IGRINS spectrum of \name.  The spectrum has been normalized by the median of the spectral order surrounding the line.}
+	\label{fig:BrG}
+\end{figure}
+
+Figure \ref{fig:CO} shows the CO bandhead in the IGRINS spectrum of \name.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/CO_overview} 
+	\caption{CO bandhead in the IGRINS spectrum of \name.
+The spectrum shows instrumental artifacts attributable to imperfectly corrected echelle blaze function.
+Imperfect telluric correction is perceptible as conspicuous outliers present throughout the spectrum.
+The red line is the SpeX spectrum of K0 Ib supergiant HD~44391 shown to guide the eye to the location of typical CO absorption in a stellar photosphere.
+The emission in \name~  is seen \emph{in emission}.
+}
+	\label{fig:CO}
+\end{figure*}
+
+\acknowledgements
+The authors thank Gregory N. Mace and/or Kyle Kaplan for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.
+
+{\it Facilities:} \facility{Smith (IGRINS)}
+
+\clearpage
+
+\bibliographystyle{apj}
+\bibliography{ms}
+
+\end{document}
+
 \documentclass[revtex4]{emulateapj}

### 2015-12-04 document/ms.tex
reformat the paper following the style from Mann et al.

@@
 
+\subsection{Previous studies of \name}\label{sec:prev}
+
 \section{Observations}\label{sec:obs}
@@
 
-Figure \ref{fig:CO} shows the CO bandhead in the IGRINS spectrum of \name.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/CO_overview} 
-	\caption{CO bandhead in the IGRINS spectrum of \name.
-The spectrum shows instrumental artifacts attributable to imperfectly corrected echelle blaze function.
-Imperfect telluric correction is perceptible as conspicuous outliers present throughout the spectrum.
-The red line is the SpeX spectrum of K0 Ib supergiant HD~44391 shown to guide the eye to the location of typical CO absorption in a stellar photosphere.
-The emission in \name~  is seen \emph{in emission}.
-}
-	\label{fig:CO}
-\end{figure*}
-
 \acknowledgements
-The authors thank Gregory N. Mace and/or Kyle Kaplan for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.
+The authors thank Gregory N. Mace for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.
 
@@
 \end{document}
-
-\documentclass[revtex4]{emulateapj}
-\usepackage[usenames,dvipsnames]{color}
-\usepackage{natbib,graphicx,latexsym,lscape}
-
-\usepackage{amssymb}
-\usepackage{epstopdf}
-\usepackage{enumerate}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{longtable}
-\usepackage{url}
-\newcommand{\angstrom}{\mbox{\normalfont\AA}}
-\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
-
-\begin{document}
-
-\citestyle{aa}
-\slugcomment{\bf November 25, 2015 draft}
-\shortauthors{Gully-Santiago \emph{et al.}}
-\shorttitle{Welter}
-
-\title{Welter is an ongoing analysis of a young star in Taurus}
-
-\author{M.~A.~Gully-Santiago}
-\affil{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing, P. R. China}
-
-\author{G. Herczeg}
-\affil{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing, P. R. China}
-
-\maketitle
-
-%------------------------------------------------------------------------------------------
-\section{Introduction}
-%------------------------------------------------------------------------------------------
-
-Hello world.
-
-See \citet{2011ARA&A..49...67W} for a review about circumstellar disks.
-%------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------
-%Bibliography
-%------------------------------------------------------------------------------------------
-\bibliographystyle{apj}
-\bibliography{ms}
-
-\end{document}

### 2015-12-15 document/ms.tex
Add some prose about measuring Teff as a function of order

@@
 
-\subsection{Previous studies of \name}\label{sec:prev}
-
 \section{Observations}\label{sec:obs}
@@
 The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.
+
+\section{Analysis}
+We compared the IGRINS spectrum of \name to the emph{Phoenix} grid of pre-computed synthetic model spectra\citep{}.  We adapted the \emph{Starfish} code \citep{} in the following way.
+
+We added an instrument class for each of $H$ and $K$ bands of IGRINS.
+
+We ran the code in several different modes.
+First we ran the code as described in \citet{}, with XX orders in the $H$ band, covering XX-XX wavelengths.
+The stellar parameters derived in this mode are shared among the orders.
+In the second mode, we ran Starfish individually on each of XX orders.
+In this mode the stellar properties are derived separately for each order.
+Table XX lists the values of Teff derived from the two approaches.
+
+\subsection{Deriving $T_{eff}$ in each IGRINS order}
+
+We want to measure the derived effective temperature as a function of wavelength.
+The motivation for this strategy is as follows.
+We assume that LkCa4 has a significant fraction of its stellar disk covered by starspots \cite{XX}.
+Such a photosphere will have an emergent spectrum composed of superpositions of relatively cool patches and warm patches.
+The visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
+The infrared spectrum will have a lower overall spot contast, but with higher relative contribution attributable to the cool patches \citep[e.g.
+Prato]{XX}.
+
+The fit of a single-temperature forward-modeled spectrum to different regions of the spectrum could therefore conceivably yield different estimates for the effective temperature.
+
+In principle, one could estimate the effective temperature \emph{evaluated independently for each spectral line}.
+The line strength is often degenerate with other properties (\emph{e.g.} magnetic field, $\log{g}$, $[\mathrm{Fe}/\mathrm{H}]$, etc.), but \emph{on average} these correlations would be averaged over.
+
+We measured the effective temperature in \emph{each of the 43 spectral orders} of IGRINS.
+Figure \ref{XX} plots each derived effective temperature value and uncertainty at the center position of each order.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/teff_vs_order} 
+	\caption{Effective temperature as derived by different orders.}
+	\label{fig:teffOrder}
+\end{figure*}
+
 \section{Spectral properties}\label{sec:lines}

### 2015-12-30 document/ms.tex
Add a temporary table about the history of LkCa4

@@
 
+\appendix
+
+\section{Technical details}
+
+Here are some specifics about what we did.
+
+\section{Previous work}
+
+Table REF lists measurements of LkCa4 from previous studies.
+\input{tables/tbl_history.tex}
+
+In short, here is what we know about \name.
+It is a weak-lined \emph{T-Tauri} star.
+It exhibits a 3.36-3.37 day period \citep{1993AJ....106.1608V,1994IBVS.4042....1G}, as evinced by photometric monitoring in $BVRI$ bands.
+No periodic signal is detected at $U-$band.
+Section 5 of \citet{1993AJ....106.1608V}, ``More on the nature of CTT and WTT spots'' goes into detail about the whether the photometric variability is attributable to hot or cold patches.
+\name has no detected M-type-or-earlier binary companion down to $0.13''$ \citep{1993A&A...278..129L}.
+\name was demonstrates variability in X-rays with ROSAT \citep{1994ApJ...424..237S}, with $L_{x}=2.4$ ergs/s.
+
 \acknowledgements

### 2016-02-22 document/ms.tex
Revise text draft to include verbatim text from proposal.  Todo is to edit this down.

@@
-\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
-%\documentclass[onecolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
-%\documentclass[preprint]{aastex}
+%\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
+\documentclass[onecolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
+%\documentclass[12pt,preprint]{aastex}
 
@@
 %From: http://arxiv.org/format/1512.00483
-\input{setup}
+%\input{setup}
+\input{mgs_setup}
 
@@
 \providecommand{\adsurl}[1]{\href{#1}{ADS}}
-\newcommand{\name}{LkCa4}
-\def\vsini{$v\sin{i_*}$}
+\newcommand{\name}{LkCa4 }
+%\def\vsini{$v\sin{i_*}$}
 
@@
 
-\name is a weak lined \emph{T-Tauri} star.  In this short research note we provide the IGRINS spectrum of \name.
+Stars form by direct gravitational collapse of molecular cloud cores.
+By $\sim$1 Myr the envelopes of gas and dust have usually accreted onto the star, classical \emph{T-Tauri} stars).
+By $\sim$3-10 Myr the circumstellar disks are usually gone (Class III, weak-lined \emph{T-Tauri} stars).
+At some time in this process, gas giant planets form.
+Observations of young stars between 0 and 10 Myr anchor the overall ``cartoon picture'' understanding of star and planet formation.
+
+The understanding of the process is incomplete.
+Measurements for intrinsic stellar properties---luminosity, effective temperature, surface gravity---are known only coarsely.
+Their uncertainties flow down to uncertainties in the fundamental properties mass and age, which are estimated from positions on pre main-sequence HR diagrams.
+
+For a single presumably coeval stellar cluster, the pre main-sequence HR diagrams exhibit large ($\delta t_{\ast} \sim t_{\ast}$) apparent spreads in age \citep[e.g.][]{2011A&A...534A..83R}.
+The large spreads in these pre main-sequence HR diagrams is controversial: some take it as evidence for intrinsic age spreads, some take it as evidence for non static accretion history \citep{2009ApJ...702L..27B, 2010ARA&A..48..581S}.
+
+Still others take the large apparent age spreads in pre main-sequence HR diagrams as evidence for the limited physics included in the pre main-sequence evolutionary model isochrones.
+Most modern evolutionary models do not yet include the effects of starspots or magnetic fields, despite observations betraying their presence, \emph{e.g.} optical monitoring and Zeeman doppler imaging \citep{2008A&A...479..827G,2014MNRAS.444.3220D}.
+
+Sunspots are probably responsible for biases in stellar effective temperatures derived by different methods.
+For example, the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) measured effective temperatures for 3493 young stars finding offsets in $\teff$ of typically 200$-$500 K and as high as 1000 K compared to previous studies \citep{2014ApJ...794..125C}.
+Low resolution optical spectroscopy shows a typical spread of 200 K in the spectral type-to-effective-temperature conversion scale \citep{2014ApJ...786...97H}.
+Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses.
+The observations of sunspots are lagging behind the theory \citep{2015ApJ...807..174S}.
+
+The importance of starspots needs to be empirically evaluated to assess systematic biases of pre-main sequence stellar evolutionary models.
+
+In this paper we characterize the starspot coverage and temperature contrast of \name using full spectrum fitting.
+We demonstrate the constraining power of full spectrum fitting with panchromatic optical and near-IR echelle spectroscopy.
+We show that relatively small starspot filling factors can be detected due to the large spectral grasp of IGRINS.
 
@@
 \section{Analysis}
-We compared the IGRINS spectrum of \name to the emph{Phoenix} grid of pre-computed synthetic model spectra\citep{}.  We adapted the \emph{Starfish} code \citep{} in the following way.
+We compared the IGRINS spectrum of \name to the emph{Phoenix} grid of pre-computed synthetic model spectra citeXX.  We adapted the \emph{Starfish} code citeXX in the following way.
 
@@
 We ran the code in several different modes.
-First we ran the code as described in \citet{}, with XX orders in the $H$ band, covering XX-XX wavelengths.
+First we ran the code as described in citeXX, with XX orders in the $H$ band, covering XX-XX wavelengths.
 The stellar parameters derived in this mode are shared among the orders.
@@
 
+On November 15, 2015 we acquired IGRINS miniqueue observations of LkCa4, a weak-lined \emph{T-Tauri} star.
+We targeted this source for its likelihood of large areal coverage of starspots, as evinced by large-amplitude photometric variability  detected in $BVRI$ bands.
+Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G}.
+Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.
+The source has little or no accretion ($\log{\dot M} < 8.1$), no detection of mid-infrared nor mm excess, and no stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.
+This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.
+
+We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA.
+Our analysis procedure involves fitting the entire spectrum with pre-computed stellar model grids \citep{2013A&A...553A...6H}, and employing a new flexible likelihood function for spectroscopic inference \citep{2015ApJ...812..128C}.
+The existing implementation \emph{simultaneously} fits both the intrinsic stellar parameters, $\vt_{\ast} = \{\teff, \logg, \Z \}$, and extrinsic stellar parameters, $\vt_{\rm ext} = \{\sigma_v, \vsini, v_r, \Omega, A_V\}$, with all $N_{\mathrm{ord}}$ spectral orders sharing the same stellar parameters\footnote{The implementation \emph{also} simultaneously fits a small-amplitude polynomial to each spectral order to adjust for slight imperferfections in the continuum shape left over from the blaze correction in the IGRINS pipeline.
+The coefficients of the polynomials are treated as nuisance parameters.
+This strategy makes us resilient against the pitfalls of pseudo-continuum-fitting, and effortlessly propagates the uncertainty attributable to the continuum level into the uncertainty in the astrophysically interesting stellar parameters.}.
+We modified the default implementation by chunking the spectrum into 58 of its cleanest spectral orders and deriving the stellar parameters $\vt_{\ast,m}$ \emph{independently} in each $m^{\mathrm{th}}$ order.
+We therefore have 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.
+The figure shows a dramatic effect: \textbf{The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.}
+
+We interpret the cooler temperatures derived at $K-$band as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
+Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.
+We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).
+
+We further performed a plausibility check to constrain the effect size of starspots.
+We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.
+We coadded the spectra in a mixture model:  $ \mathsf{M}_{mix} = c \cdot \mathsf{M}_A(T_\textrm{eff,A}) + (1-c) \cdot \mathsf{M}_B(T_\textrm{eff,B})$.
+We chose a fill factor of starspots of 30\%.
+We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters one would na\"{\i}vely derive.
+The noised-up optical data yields $\teff \sim 4100$ K, close to that of the A component.
+We are awaiting the results from $K-$ band at the time of writing.
+
+Our ongoing work is focused on several improvements to the whole-spectrum fitting procedure.
+First we are adding support for directly fitting a mixture model, $\mathsf{M}_{mix}$.
+This will provide a \emph{measurement} of the star spot temperature and areal coverage fraction.
+Mixture model fitting capability will enable true whole-spectrum fitting, a more powerful on-label use of the fitting machinery.
+
 \subsection{Deriving $T_{eff}$ in each IGRINS order}
@@
 The motivation for this strategy is as follows.
-We assume that LkCa4 has a significant fraction of its stellar disk covered by starspots \cite{XX}.
+We assume that LkCa4 has a significant fraction of its stellar disk covered by starspots citeXX.
 Such a photosphere will have an emergent spectrum composed of superpositions of relatively cool patches and warm patches.
 The visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
-The infrared spectrum will have a lower overall spot contast, but with higher relative contribution attributable to the cool patches \citep[e.g.
-Prato]{XX}.
+The infrared spectrum will have a lower overall spot contast, but with higher relative contribution attributable to the cool patches citeXX.
 
@@
 \name has no detected M-type-or-earlier binary companion down to $0.13''$ \citep{1993A&A...278..129L}.
-\name was demonstrates variability in X-rays with ROSAT \citep{1994ApJ...424..237S}, with $L_{x}=2.4$ ergs/s.
+\name demonstrates variability in X-rays with ROSAT \citep{1994ApJ...424..237S}, with $L_{x}=2.4$ ergs/s.
 

### 2016-02-22 sf/analysis.py
All all .py scripts from Phuket.  These are important!

@@ -1,0 +1,17 @@
+#!/usr/bin/env python
+import os
+import yaml
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+for i in range(0,25):
+    output_dir = 'eo{:03d}/output/LkCa4_so{:03d}/run03'.format(i,i)
+    os.chdir(output_dir)
+    
+    #os.system('star.py --generate')
+    #os.system('splot.py s0_o0spec.json --matplotlib')
+    os.system('last_mc.py --last20k yes')
+    #os.system('chain.py --files mc.hdf5 --chain')
+    #os.system('mv walkers.png /home/gully/GitHub/welter/sf/plts/walkers_{}.png'.format(mdir))
+    #os.system('mv plots/s0_o0spec.json.png /home/gully/GitHub/welter/sf/plts/spec_{}.png'.format(mdir))
+    os.chdir('/home/gully/GitHub/welter/sf/')

### 2016-02-22 sf/batch_config.py

@@ -1,0 +1,31 @@
+#!/usr/bin/env python
+
+
+import os
+import yaml
+
+ms = range(98, 125+1)
+
+mdirs = ['m{:03d}'.format(m) for m in ms]
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+os.getcwd()
+
+for mdir in mdirs:
+    os.chdir(mdir)
+    print(os.getcwd())
+    
+    f = open("config.yaml")
+    config = yaml.load(f)
+    f.close()
+
+    val = config['data']['files']
+    if type(val) != list:
+        config['data']['files'] = [val]
+
+    with open("config.yaml", mode='w') as outfile:
+        outfile.write(yaml.dump(config))
+        print('Revised the config.yaml file: data file is 1 element list.')
+    os.chdir('..')
+

### 2016-02-22 sf/batch_config_K.py

@@ -1,0 +1,36 @@
+#!/usr/bin/env python
+
+import os
+import yaml
+import h5py
+import numpy as np
+
+for o in range(26):
+    m = o + 71
+    dat_name = '../data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)
+    path_out = 'm{:03d}/'.format(m)
+    sf_out = 'm{:03d}/config.yaml'.format(m)
+    
+    f = open("config.yaml")
+    config = yaml.load(f)
+    f.close()
+    
+    f=h5py.File(dat_name, "r")
+    wls = f['wls'][:]
+    f.close()
+    
+    config['data']['files'] = ['/home/gully/GitHub/welter/data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)]
+    config['grid']['hdf5_path'] = '/home/gully/GitHub/welter/sf/m113/libraries/PHOENIX_IGRINS_m{:03d}.hdf5'.format(m)
+    lb, ub = int(np.floor(wls[0])), int(np.ceil(wls[-1]))
+
+    config['grid']['wl_range'] = [lb, ub]
+    config['PCA']['path'] = '/home/gully/GitHub/welter/sf/m{:03d}/PHOENIX_IGRINS_H_PCA.hdf5'.format(m)
+    config['name'] = 'LkCa4_m{:03d}'.format(m)
+    config['Comments'] = 'LkCa4 single order: m = {}, autogenerated config file.'.format(m)
+    config['data']['instruments'] =['IGRINS_K']
+
+    print("{:03d}: {:.0f}  -  {:.0f}   {}".format(m, wls[0], wls[-1], dat_name))
+    
+    #os.makedirs(path_out, exist_ok=True)
+    with open(sf_out, mode='w') as outfile:
+        outfile.write(yaml.dump(config))

### 2016-02-22 sf/batch_startup.py

@@ -1,0 +1,23 @@
+#!/usr/bin/env python
+
+import os
+import yaml
+
+ms = range(98, 125+1)
+
+mdirs = ['m{:03d}'.format(m) for m in ms]
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+
+for mdir in mdirs:
+    os.chdir(mdir)
+    print(os.getcwd())
+
+    if os.path.isfile('eparams_emcee.npy'):
+        print('Skipping mdir')
+    else:
+        os.system('startup1.sh')
+        #os.system('echo "Dry run"')
+
+    os.chdir('..')

### 2016-02-22 sf/batch_synth.py

@@ -1,0 +1,31 @@
+#!/usr/bin/env python
+
+import os
+import yaml
+
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+for i in range(76, 91):
+    print(i)
+    os.chdir('m{:03d}/'.format(i))
+
+    with open('config.yaml', mode='r') as f:
+        config = yaml.load(f)    
+    
+    #These will be our initial guesses.
+    config['Comments'] = "SYNTHETIC DATA simulating two-Temps: 3300 and 4100. The 4100 filling factor is 70 percent."
+    config['Theta']['grid'] = [4000.0, 3.7, 0.0]
+    config['Theta']['logOmega'] = -0.22
+    config['Theta']['vsini'] = 30.0
+    config['Theta']['vz'] = 92.0
+    config['name'] = "LkCa4_sm{:03d}".format(i)
+    config['data']['files'] = ["/home/gully/GitHub/welter/data/synthetic/LkCa4_Synthetic_sm{:03d}.hdf5".format(i)]
+    config['grid']['hdf5_path'] = "/home/gully/GitHub/welter/sf/m{:03d}/libraries/PHOENIX_IGRINS_m{:03d}.hdf5".format(i,i)
+    config['Phi'] = {"l": 25.0, "logAmp": -2.7, "sigAmp": 0.3}
+    with open('config.yaml', mode='w') as f:
+        f.write(yaml.dump(config))
+
+    os.system('star.py --run_index 3')
+
+    os.chdir('/home/gully/GitHub/welter/sf/')

### 2016-02-22 sf/meta_batch.py

@@ -1,0 +1,39 @@
+#!/usr/bin/env python
+
+
+import os
+import yaml
+
+ms = range(76, 91+1)
+
+mdirs = ['m{:03d}'.format(m) for m in ms]
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+os.getcwd()
+
+for mdir in mdirs:
+    os.chdir(mdir)
+    
+    print('----------------------------')
+    print(os.getcwd())
+    print(' ')
+
+    #print("Running startup1.sh: ")    
+    #print("startup1.sh")
+    #os.system('startup1.sh')
+    #print("Completed startup1.sh")
+    #print(' ')
+
+    print("Starting the MCMC run.")
+    out_dir = "output/LkCa4_{}/run02/".format(mdir)
+    print("os.chdir(out_dir)")
+    print("Spawning a screen")
+    screen_command = 'screen -d -m bash -c ' + '"cd /home/gully/GitHub/welter/sf/{}/output/LkCa4_{}/run02/'.format(mdir, mdir)+'; run.sh"' 
+    print(screen_command)
+    os.system(screen_command)
+    print(' ')
+
+    print('Back to the start')
+    os.chdir('/home/gully/GitHub/welter/sf/')
+    print('----------------------------')

### 2016-02-22 sf/meta_batch_eo.py

@@ -1,0 +1,37 @@
+#!/usr/bin/env python
+
+
+import os
+import yaml
+
+ms = range(0, 35)
+
+mdirs = ['eo{:03d}'.format(m) for m in ms]
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+for mdir in mdirs:
+    os.chdir(mdir)
+    
+    print('----------------------------')
+    print(os.getcwd())
+    print(' ')
+
+    print("Running startup1.sh: ")    
+    print("startup1.sh")
+    os.system('startup1.sh')
+    print("Completed startup1.sh")
+    print(' ')
+
+    print("Starting the MCMC run.")
+    out_dir = "output/LkCa4_{}/run01/".format(mdir)
+    print("os.chdir(out_dir)")
+    print("Spawning a screen")
+    screen_command = 'screen -d -m bash -c ' + '"cd /home/gully/GitHub/welter/sf/{}/output/LkCa4_{}/run01/'.format(mdir, mdir)+'; run.sh"' 
+    print(screen_command)
+    os.system(screen_command)
+    print(' ')
+
+    print('Back to the start')
+    os.chdir('/home/gully/GitHub/welter/sf/')
+    print('----------------------------')

### 2016-02-22 sf/meta_batch_sm.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python
+
+import os
+import yaml
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+for i in range(76, 91):
+    os.chdir("m{:03d}".format(i))
+    
+    print('----------------------------')
+    print("Starting the MCMC run.")
+    print("Spawning a screen")
+    screen_command = 'screen -d -m bash -c ' + '"cd /home/gully/GitHub/welter/sf/m{:03d}/output/LkCa4_sm{:03d}/run03/'.format(i, i)+'; run.sh"' 
+    print(screen_command)
+    os.system(screen_command)
+    print(' ')
+
+    print('Back to the start')
+    os.chdir('/home/gully/GitHub/welter/sf/')
+    print('----------------------------')

### 2016-02-22 sf/meta_batch_so.py

@@ -1,0 +1,22 @@
+#!/usr/bin/env python
+
+import os
+import yaml
+
+os.chdir('/home/gully/GitHub/welter/sf/')
+
+for i in range(0, 25):
+    os.chdir("eo{:03d}".format(i))
+    
+    print('----------------------------')
+    print("Starting the MCMC run.")
+    out_dir = "output/LkCa4_so{:03d}/run03/".format(i)
+    print("Spawning a screen")
+    screen_command = 'screen -d -m bash -c ' + '"cd /home/gully/GitHub/welter/sf/eo{:03d}/output/LkCa4_so{:03d}/run03/'.format(i, i)+'; run.sh"' 
+    print(screen_command)
+    os.system(screen_command)
+    print(' ')
+
+    print('Back to the start')
+    os.chdir('/home/gully/GitHub/welter/sf/')
+    print('----------------------------')

### 2016-03-14 document/ms.tex
We will use a methodology section first, then observations.  Some edits to the dummy prose.

@@
 
-Stars form by direct gravitational collapse of molecular cloud cores.
-By $\sim$1 Myr the envelopes of gas and dust have usually accreted onto the star, classical \emph{T-Tauri} stars).
-By $\sim$3-10 Myr the circumstellar disks are usually gone (Class III, weak-lined \emph{T-Tauri} stars).
-At some time in this process, gas giant planets form.
-Observations of young stars between 0 and 10 Myr anchor the overall ``cartoon picture'' understanding of star and planet formation.
-
-The understanding of the process is incomplete.
-Measurements for intrinsic stellar properties---luminosity, effective temperature, surface gravity---are known only coarsely.
-Their uncertainties flow down to uncertainties in the fundamental properties mass and age, which are estimated from positions on pre main-sequence HR diagrams.
-
-For a single presumably coeval stellar cluster, the pre main-sequence HR diagrams exhibit large ($\delta t_{\ast} \sim t_{\ast}$) apparent spreads in age \citep[e.g.][]{2011A&A...534A..83R}.
+For a single presumably coeval stellar cluster, pre main-sequence HR diagrams exhibit large ($\delta t_{\ast} \sim t_{\ast}$) apparent spreads in age \citep[e.g.][]{2011A&A...534A..83R}.
 The large spreads in these pre main-sequence HR diagrams is controversial: some take it as evidence for intrinsic age spreads, some take it as evidence for non static accretion history \citep{2009ApJ...702L..27B, 2010ARA&A..48..581S}.
@@
 
-Sunspots are probably responsible for biases in stellar effective temperatures derived by different methods.
+Meanwhile, sunspots are probably responsible for biases in stellar effective temperatures derived by different methods.
 For example, the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) measured effective temperatures for 3493 young stars finding offsets in $\teff$ of typically 200$-$500 K and as high as 1000 K compared to previous studies \citep{2014ApJ...794..125C}.
@@
 In this paper we characterize the starspot coverage and temperature contrast of \name using full spectrum fitting.
+We chose \name for its likelihood of large areal coverage of starspots, as evinced by large-amplitude photometric variability  detected in $BVRI$ bands.
+Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G}.
+Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.
+The source has little or no accretion ($\log{\dot M} < 8.1$), no detection of mid-infrared nor mm excess, and no stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.
+This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.
+
+We extend a new spectral forward modeling framework to include two-temperature photosphere models.
 We demonstrate the constraining power of full spectrum fitting with panchromatic optical and near-IR echelle spectroscopy.
 We show that relatively small starspot filling factors can be detected due to the large spectral grasp of IGRINS.
+
+\section{Methodology}\label{sec:methods}
 
@@
 We acquired observations with IGRINS on the Harlan J.
-Smith Telescope at McDonald Observatory on XX UTC.
+Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
 The Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG}, is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
@@
 
+We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.
+
 \section{Analysis}
-We compared the IGRINS spectrum of \name to the emph{Phoenix} grid of pre-computed synthetic model spectra citeXX.  We adapted the \emph{Starfish} code citeXX in the following way.
+We compared the IGRINS spectrum of \name to the \PHOENIX grid of pre-computed synthetic model spectra \citep{2013A&A...553A...6H}.
 
-We added an instrument class for each of $H$ and $K$ bands of IGRINS.
+We use the \texttt{Starfish} code \citep{2015ApJ...812..128C}.  In this Section we describe our modifications to to the code.
 
-We ran the code in several different modes.
-First we ran the code as described in citeXX, with XX orders in the $H$ band, covering XX-XX wavelengths.
-The stellar parameters derived in this mode are shared among the orders.
-In the second mode, we ran Starfish individually on each of XX orders.
-In this mode the stellar properties are derived separately for each order.
-Table XX lists the values of Teff derived from the two approaches.
-
-On November 15, 2015 we acquired IGRINS miniqueue observations of LkCa4, a weak-lined \emph{T-Tauri} star.
-We targeted this source for its likelihood of large areal coverage of starspots, as evinced by large-amplitude photometric variability  detected in $BVRI$ bands.
-Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G}.
-Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.
-The source has little or no accretion ($\log{\dot M} < 8.1$), no detection of mid-infrared nor mm excess, and no stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.
-This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.
-
-We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA.
-Our analysis procedure involves fitting the entire spectrum with pre-computed stellar model grids \citep{2013A&A...553A...6H}, and employing a new flexible likelihood function for spectroscopic inference \citep{2015ApJ...812..128C}.
-The existing implementation \emph{simultaneously} fits both the intrinsic stellar parameters, $\vt_{\ast} = \{\teff, \logg, \Z \}$, and extrinsic stellar parameters, $\vt_{\rm ext} = \{\sigma_v, \vsini, v_r, \Omega, A_V\}$, with all $N_{\mathrm{ord}}$ spectral orders sharing the same stellar parameters\footnote{The implementation \emph{also} simultaneously fits a small-amplitude polynomial to each spectral order to adjust for slight imperferfections in the continuum shape left over from the blaze correction in the IGRINS pipeline.
+The existing \texttt{Starfish} implementation \emph{simultaneously} fits both the intrinsic stellar parameters, $\vt_{\ast} = \{\teff, \logg, \Z \}$, and extrinsic stellar parameters, $\vt_{\rm ext} = \{\sigma_v, \vsini, v_r, \Omega, A_V\}$, with all $N_{\mathrm{ord}}$ spectral orders sharing the same stellar parameters\footnote{The implementation \emph{also} simultaneously fits a small-amplitude polynomial to each spectral order to adjust for slight imperferfections in the continuum shape left over from the blaze correction in the IGRINS pipeline.
 The coefficients of the polynomials are treated as nuisance parameters.
@@
 
+\section{Results}
 We interpret the cooler temperatures derived at $K-$band as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
@@
 
-Our ongoing work is focused on several improvements to the whole-spectrum fitting procedure.
-First we are adding support for directly fitting a mixture model, $\mathsf{M}_{mix}$.
-This will provide a \emph{measurement} of the star spot temperature and areal coverage fraction.
-Mixture model fitting capability will enable true whole-spectrum fitting, a more powerful on-label use of the fitting machinery.
-
-\subsection{Deriving $T_{eff}$ in each IGRINS order}
+\subsection{Deriving $\teff$ in each IGRINS order}
 
@@
 We measured the effective temperature in \emph{each of the 43 spectral orders} of IGRINS.
-Figure \ref{XX} plots each derived effective temperature value and uncertainty at the center position of each order.
+Figure \ref{fig:teffOrder} plots each derived effective temperature value and uncertainty at the center position of each order.
 
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/teff_vs_order} 
+	\includegraphics[width=0.95\textwidth]{figures/teff_v_wl_example} 
 	\caption{Effective temperature as derived by different orders.}
@@
 \section{Spectral properties}\label{sec:lines}
-
-Figure \ref{fig:BrG} shows the Br$\gamma$ line profile in the IGRINS spectrum of \name.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.95\columnwidth]{figures/Br_gamma_zoom} 
-	\caption{Line profile of Br$\gamma$ in the IGRINS spectrum of \name.  The spectrum has been normalized by the median of the spectral order surrounding the line.}
-	\label{fig:BrG}
-\end{figure}
 

### 2016-03-14 document/ms.tex
Add a table of labels/parameters to the methodology section, start on writing equations.

@@
 \input{mgs_setup}
+
+\newcommand{\iancze}{{\sc C15}}
 
@@
 \section{Methodology}\label{sec:methods} 
+We extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{2015ApJ...812..128C}.
+We briefly summarize the model here for carity of notation, but see \iancze for more details.
+We follow and expand the notation from \iancze, all summarized in Table \ref{table:params}.
+
+The main idea is that \iancze define a pixel-level forward model $\vM$ of the data.
+A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR$.
+The model encapsulates the major intrinstic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:
+
+\begin{eqnarray} \label{eqn:scaling}
+\vM(\vT) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
+         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
+\end{eqnarray}
+
+The $\vt_{\ast}$ are comprised of the dimensions of the pre-computed stellar model grid.
+\iancze used the \PHOENIX model grid \citep{2013A&A...553A...6H}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
+
+\subsection{Mixture model extension to \citet{2015ApJ...812..128C}}
+
+Our two component photosphere mixture model extension modifies equation \ref{eqn:scaling} in the following way.
+
+\begin{eqnarray} \label{eqn:mix_model}
+\vM(\vT) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
+         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
+\end{eqnarray}
+
+\begin{deluxetable}{clcc}[!bh]
+\tablecaption{\label{table:params} Definition of symbols and parameters used}
+\tablehead{
+\colhead{Label} &
+\colhead{Description} & 
+\colhead{Shared?} &
+\colhead{Source}
+}
+\startdata
+$\vM$ & Pixel-level model & - & \iancze \\
+$\vT$ & Stellar parameters in the model & - & \iancze \\
+$q_o(\vt_{\ast})$ & Absolute mean flux ratio in order $o$  & N & This Work \\
+\hline
+ \multicolumn{4}{c}{$\vt_{\ast}$} \\
+\hline
+$\teffa$ & Effective temperature of component A & N & This Work \\
+$\teffb$ & Effective temperature of component B & N & This Work \\
+$\Delta \teff$ & Spot temperature contrast $\teffa - \teffb $ & - & This Work \\
+$\logg$ & Stellar surface gravity & Y & \iancze \\
+$\Z$ & Metallicity & Y & \iancze \\
+\hline
+\multicolumn{4}{c}{$\vt_{\rm ext}$} \\
+\hline
+$v\sin{i}$ & Projected stellar rotation & Y$^a$ & \iancze \\
+$\sigma_v$ & Instrumental resolution & Y & \iancze \\
+$\Omega_a$ & Solid angle subtended by component A & N & This Work \\
+$\Omega_b$ & Solid angle subtended by component B & N & This Work \\
+$c$ & Spot fill factor ($\Omega_b / \Omega_a$) & N & This Work \\
+$A_{\lambda}$ & Extinction towards the source 2 & Y & \iancze \\
+\enddata
+\tablecomments{\emph{a}- In principle, star spots could have non-uniform latitudinal distributions, resulting in slight differences in $v\sin{i}$ between the components CITE XX-McDonald Obs.
+We ignore this effect for now, but it could be an interesting line of study for future work.}
+\end{deluxetable}
+
+The existing \texttt{Starfish} implementation \emph{simultaneously} fits both the intrinsic stellar parameters, $\vt_{\ast} = \{\teff, \logg, \Z \}$, and extrinsic stellar parameters, $\vt_{\rm ext} = \{\sigma_v, \vsini, v_r, \Omega, A_V\}$, with all $N_{\mathrm{ord}}$ spectral orders sharing the same stellar parameters\footnote{The implementation \emph{also} simultaneously fits a small-amplitude polynomial to each spectral order to adjust for slight imperferfections in the continuum shape left over from the blaze correction in the IGRINS pipeline.
+The coefficients of the polynomials are treated as nuisance parameters.
+This strategy makes us resilient against the pitfalls of pseudo-continuum-fitting, and effortlessly propagates the uncertainty attributable to the continuum level into the uncertainty in the astrophysically interesting stellar parameters.}.
 
@@
 
-We use the \texttt{Starfish} code \citep{2015ApJ...812..128C}.  In this Section we describe our modifications to to the code.
-
-The existing \texttt{Starfish} implementation \emph{simultaneously} fits both the intrinsic stellar parameters, $\vt_{\ast} = \{\teff, \logg, \Z \}$, and extrinsic stellar parameters, $\vt_{\rm ext} = \{\sigma_v, \vsini, v_r, \Omega, A_V\}$, with all $N_{\mathrm{ord}}$ spectral orders sharing the same stellar parameters\footnote{The implementation \emph{also} simultaneously fits a small-amplitude polynomial to each spectral order to adjust for slight imperferfections in the continuum shape left over from the blaze correction in the IGRINS pipeline.
-The coefficients of the polynomials are treated as nuisance parameters.
-This strategy makes us resilient against the pitfalls of pseudo-continuum-fitting, and effortlessly propagates the uncertainty attributable to the continuum level into the uncertainty in the astrophysically interesting stellar parameters.}.
 We modified the default implementation by chunking the spectrum into 58 of its cleanest spectral orders and deriving the stellar parameters $\vt_{\ast,m}$ \emph{independently} in each $m^{\mathrm{th}}$ order.

### 2016-03-15 document/ms.tex
Write methodology section of the paper, with many equations to describe changes needed for the mixture model.

@@
 
-Our two component photosphere mixture model extension modifies equation \ref{eqn:scaling} in the following way.
+We construct a mixture model spectrum of the form:
 
-\begin{eqnarray} \label{eqn:mix_model}
-\vM(\vT) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
-         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
+\begin{eqnarray} \label{eqn:simple_mix}
+\flam(\vt_{\ast, \mathrm{mix}}) = (1-c) \flam(\teffa, ...) + c \flam(\teffb, ...)
 \end{eqnarray}
+
+Where $c, \teffa, \teffb$ are the mixture model fill factor and two-temperature photosphere components respectively.
+All other stellar intrinsic and extrinsic parameters, and instrumental nuisance calibration parameters are shared among the two components, as chronicled in Table \ref{table:params}.
+
+If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:simple_mix}.  However \iancze employ \emph{normalized} $\flam$:
+
+\begin{eqnarray} \label{eqn:normalization}
+\bar \flam = \frac{\flam}{\int_{\lambda_0}^{\lambda_1} \flam d\lambda} = \frac{\flam}{f}
+\end{eqnarray}
+
+The reason for normalizing is a matter of practicality: the number of PCA eigenspectra components scales steeply with the pixel-to-pixel variance of $f_{\lambda}(\{\vt_{\ast}\}^\textrm{grid})$.
+The choice to normalize makes no difference for modeling a single photospheric component.
+But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $c$.
+More flux comes from the hotter component per solid angle.
+So we scale the mixture model in the following way:
+
+\begin{eqnarray} \label{eqn:norm_scaling}
+f_{\lambda, \mathrm{mix}} &=& (1-c) f_{\mathrm{a}}\bar f_{\lambda, \mathrm{a}} + c f_{\mathrm{b}} \bar f_{\lambda, \mathrm{b}} \\
+q &=& q(\vt_{\ast})\equiv \frac{f_{\mathrm{b}}(\teffb, ...)}{f_{\mathrm{a}}(\teffa, ...)} \\
+f_{\lambda, \mathrm{mix}}^{\prime} &=& \bar f_{\lambda, \mathrm{a}} + \frac{c}{1-c} q \bar f_{\lambda, \mathrm{b}} 
+\end{eqnarray}
+
+where the prime symbol in the final line indicates a rescaled mixture model flux.
+
+We are now tasked with computing an estimator, $\hat f(\vt_{\ast})$.
+The Right Thing to Do would be to follow \iancze by training a Gaussian process on the $f(\{\vt_{\ast}\}^\textrm{grid})$.
+What We Actually Did was simple interpolation between the model grid-points.
+Interpolation can cause pile-up near model grid-points, as noted in \citet{2014ApJ...794..125C}, which motivated the spectral emulation procedure in \iancze.
+In this case, we assumed the interpolation of $\hat f$ was smooth enough that we would not see such pileups, and if present, the pileup would mostly be discernable in the distribution of samples in the starpost areal coverage fraction $c$.
+One drawback of our estimator method compared to the Gaussian Process regression method is that we do not propagate the uncertainty associated with the absolute flux ratio interpolation into our estimate of $c$.
+We assume this uncertainty is relatively small and can be ignored.
+
+The mixture model is a linear operation and the mixture model components share all the same extrinsic parameters, so we can re-use all the same post-processed eigenspectra $\widetilde{\mathbf{\Xi}}$, mean spectrum $\widetilde{\xi}_\mu$, and variance spectrum $\widetilde{\xi}_\sigma$, but calulate two sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{a}, \mathrm{b})}$, and their associated mean and covariances:
+
+\begin{equation}
+  \mathsf{M}_{\mathrm{mix}}^\prime = \widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{a}} + \frac{c}{1-c} q (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{b}})
+\end{equation}
+
+\begin{equation}
+  \mathsf{C}_{\mathrm{mix}}^\prime = \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{a}} \mathbf{X}^T + \frac{c}{1-c} q \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{b}} \mathbf{X}^T + \mathsf{C}
+  \label{eqn:modC}
+\end{equation}
 
@@
 \end{deluxetable}
-
-The existing \texttt{Starfish} implementation \emph{simultaneously} fits both the intrinsic stellar parameters, $\vt_{\ast} = \{\teff, \logg, \Z \}$, and extrinsic stellar parameters, $\vt_{\rm ext} = \{\sigma_v, \vsini, v_r, \Omega, A_V\}$, with all $N_{\mathrm{ord}}$ spectral orders sharing the same stellar parameters\footnote{The implementation \emph{also} simultaneously fits a small-amplitude polynomial to each spectral order to adjust for slight imperferfections in the continuum shape left over from the blaze correction in the IGRINS pipeline.
-The coefficients of the polynomials are treated as nuisance parameters.
-This strategy makes us resilient against the pitfalls of pseudo-continuum-fitting, and effortlessly propagates the uncertainty attributable to the continuum level into the uncertainty in the astrophysically interesting stellar parameters.}.
 

### 2016-03-15 document/ms.tex
Add pedantic blurb about tuning parameters for Metropolis Hastings covariance that will probably end up on the chopping block, but will live on forever in this git commit.

@@
 
+\subsection{Tuning the transition probability matrix for the highly degenerate mixture model}
+
+Once we had the mixture model in hand, we could apply the blocked Gibbs MCMC sampling framework from \iancze.
+We have added 2 more parameters ($c, \teffb$) to the model, expanding from 6 to 8 total stellar parameters.
+Unfortunately this increase in dimensionality adds considerable complexity to tuning the model.
+The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$, so our 2 new parameters increased the tuning parameters from 15 to 36!
+The tuning parameters are covariances between dimensions in your proposal distribution.
+Luckily, most of the covariances are negligibly small.
+However the $c, \teffb, \Omega$ terms were all highly correlated, suggesting an affine transformation of the parameters would accelerate the convergence of the MCMC chains.
+
 \section{Observations}\label{sec:obs}

### 2016-03-24 document/ms.tex
The manuscript sections now comport with the outline framework.

@@
 
+\subsection{Pre Main Sequence HR diagram spread}
+
 For a single presumably coeval stellar cluster, pre main-sequence HR diagrams exhibit large ($\delta t_{\ast} \sim t_{\ast}$) apparent spreads in age \citep[e.g.][]{2011A&A...534A..83R}.
@@
 Most modern evolutionary models do not yet include the effects of starspots or magnetic fields, despite observations betraying their presence, \emph{e.g.} optical monitoring and Zeeman doppler imaging \citep{2008A&A...479..827G,2014MNRAS.444.3220D}.
+
+\subsection{Previous studies of Starspots}
 
@@
 The importance of starspots needs to be empirically evaluated to assess systematic biases of pre-main sequence stellar evolutionary models.
+
+\subsection{Previous studies of \name}
 
@@
 \section{Methodology}\label{sec:methods}
+
+\subsection{Full-spectrum fitting framework}
+% Motivation for sampling- the questions we want to answer
+
 We extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{2015ApJ...812..128C}.
@@
 
-\subsection{Mixture model extension to \citet{2015ApJ...812..128C}}
+\subsection{Approach 1: Deriving unique Teff in each order}
+
+% Description of this approach
+
+\subsection{Approach 2: Two component photosphere mixture model}
 
@@
 
-\subsection{Tuning the transition probability matrix for the highly degenerate mixture model}
+\subsection{Challenges: Tuning the transition probability matrix}
 
@@
 
+\subsection{ESPaDOnS Spectroscopy}
 We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.
 
-\section{Analysis}
+\subsection{At what phase of variability were the spectra acquired?}
+
+\section{Results}
+
+\subsection{Result 1: Signal from deriving $\teff$ in each IGRINS order}
+
 We compared the IGRINS spectrum of \name to the \PHOENIX grid of pre-computed synthetic model spectra \citep{2013A&A...553A...6H}.
@@
 
-\section{Results}
 We interpret the cooler temperatures derived at $K-$band as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
@@
 We are awaiting the results from $K-$ band at the time of writing.
-
-\subsection{Deriving $\teff$ in each IGRINS order}
 
@@
 
-\section{Spectral properties}\label{sec:lines}
+\subsection{Result 2: Effect size from fitting synthetic data order-by-order}
+
+\subsection{Result 3: Direct measurement of spot properties with mixture model}
+
+\section{Discussion}
+
+\subsection{Interpretation of distribution of stellar properties from Results 1 + 2}
+
+\subsection{Interpretation of star spot properties from Result 3}
+
+\subsection{Longitudinal / latitudinal spot distributions and phase}
+
+\subsection{Addressing limitations of assumptions in the methodology}
 
@@
 
-\section{Technical details}
+\section{Testing and runing the mixture model}
 
@@
 \acknowledgements
-The authors thank Gregory N. Mace for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.
+The authors thank Gregory N. Mace and Kyle Kaplan for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.
 

### 2016-03-24 document/ms.tex
Add prose about the Approach 1

@@
 \subsection{Full-spectrum fitting framework}
-% Motivation for sampling- the questions we want to answer
+% Motivation: The questions we want to answer
+Modeling the periodic light curves of spotted stars can answer these questions: ``What evidence is there to support the existence of starspots.
+What constraint can be placed on the effective temperature contrast and areal coverage of the starspots?
+What is the longitudinal assymetry of the spots?
+''.
+As pointed out by CITE XX, cyclical light curve variations indicate only the longitudinally assymetric component of the star spots.
+Photometric modeling of the light curve produces degenerate estimates in the temperature contrast and areal coverage fraction.
+For example, CITE XX achieved XX.
 
-We extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{2015ApJ...812..128C}.
+By modeling the composite \emph{spectrum} of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.
+A stellar spectrum with a longitudinaly symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating star would all show zero amplitude of photometric variability, yet they all contain star spots.
+Spectroscopic modeling can still measure the starspot properties in these cases.
+
+In principle, more advanced questions could be asked about the properties of the spots: ``How many distinct spot groups are there?
+Is there evidence for both hot spots and cool spots?
+What is the longitudinal distribution of the spots?
+What is the (co-)latitudinal distribution of the spots?
+What is the distribution of effective temperature within a spot or spot group?
+What are the morphologies of the spots?''.
+Solving these questions would require a complex model comparison framework, combining all available data and lines of evidence from photometric, spectroscopic, and spectropolarimetric monitoring.
+We seek to answer the much easier questions about the aggregate properties of the stellar photosphere, assuming the star is well described by two distinct photospheric components.
+
+% Motivation:  Why sampling?  Why full spectrum fitting?
+
+A main motivating factor in designing our methodology was our wish to adress this question for a given spectrum: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the detection of starspots be reported?''.
+In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy.
+For example, we expect the best fit effective temperature contrast will be partially degenerate with the areal coverage fraction: a slightly cooler, smaller sunspot can masquerade as a larger, warmer spot.
+This degeneracy should be lessened in spectroscopic methods compared to photometric methods.
+The desire to reveal these intra-parameter correlations motivated the choice of \emph{sampling} from the posterior probability density distribution function.
+
+% Overview and summary of existing model
+
+We adopted and extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{2015ApJ...812..128C}.
 We briefly summarize the model here for carity of notation, but see \iancze for more details.
@@
 The main idea is that \iancze define a pixel-level forward model $\vM$ of the data.
-A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR$.
+A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.
 The model encapsulates the major intrinstic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:
@@
 The $\vt_{\ast}$ are comprised of the dimensions of the pre-computed stellar model grid.
-\iancze used the \PHOENIX model grid \citep{2013A&A...553A...6H}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
+We use the \PHOENIX model grid \citep{2013A&A...553A...6H}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
 
@@
 
-% Description of this approach
+The model $\vM(\vT)$ as it stands only models a single set of stellar parameters for the entire wavelength range of interest.
+This model is the desired beavior for most applications involving a single stellar photospheric component.
+In our case, however, we \emph{know} that a single stellar photospheric component is a poor model for the data: there are \emph{two} components lurking in the composite spectrum.
 

### 2016-03-24 document/ms.tex
more prose on methodology approach 1

@@
 
-The model $\vM(\vT)$ as it stands only models a single set of stellar parameters for the entire wavelength range of interest.
-This model is the desired beavior for most applications involving a single stellar photospheric component.
-In our case, however, we \emph{know} that a single stellar photospheric component is a poor model for the data: there are \emph{two} components lurking in the composite spectrum.
+The model $\vM(\vT)$ was intended to apply a single set of stellar parameters to the entire wavelength range of interest, presumably the entire available spectrum.
+For a spectrum from a multi-order echelle spectrograph, this means each spectral order is fit with the same stellar parameters.
+Simultaneous fitting is the desired behavior for most applications involving a single stellar photospheric component.
+In our case, however, we know that a single stellar photospheric component is a poor model for the data: there are \emph{two} components lurking in the composite spectrum.
+But depending on the star spot properties, a single stellar photosphere component might fit the composite spectrum satisfactorily, like if the flux contrast of the starspot is simply too low compared to the noise.
+
+The starspot contrast depends on wavelength, roughly as the ratio of blackbodies.
+Figure XX shows a plot of the flux ratio of two stellar photospheres with identical stellar properties except for different effective temperatures.
+So a sufficiently large bandwidth spectrum could exhibit differing levels of fit quality as a function of wavelength, if a single temperature photosphere fit is naively applied to different chunks of wavelengths.
+
+We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.
+This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.
+The naive single-component fit to different wavelength chunks conveys information about
+
+\begin{eqnarray} \label{eqn:scaling}
+\vM(\vT_o) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
+         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
+\end{eqnarray}
+
+star spot areal coverage fraction is very small, then the signal associated with the
 

### 2016-03-25 document/ms.tex
A notebook to trim the ends of IGRINS spectral orders.

@@
 A main motivating factor in designing our methodology was our wish to adress this question for a given spectrum: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the detection of starspots be reported?''.
-In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy.
+In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy among themselves.
 For example, we expect the best fit effective temperature contrast will be partially degenerate with the areal coverage fraction: a slightly cooler, smaller sunspot can masquerade as a larger, warmer spot.
 This degeneracy should be lessened in spectroscopic methods compared to photometric methods.
-The desire to reveal these intra-parameter correlations motivated the choice of \emph{sampling} from the posterior probability density distribution function.
+The desire to reveal these intra-parameter degeneracies motivated the choice of \emph{sampling} from the posterior probability density distribution function.
 
@@
 This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.
-The naive single-component fit to different wavelength chunks conveys information about
+The na\"ive single-component fit to different wavelength could provide a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.
+It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect on the spectrum.
+For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.
+For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = {T_{\mathrm{eff},o}, \logg_o, \feh_o, \sigma_{v, o}, v\sin{i}_o, v_{r,o}}$ to vary by order.
+In principle, one could refine the inference in an \emph{empirical Bayes'} strategy CITE (XX, astroML book?), in which we re-evaluate $\vT_o$ by setting priors on all the stellar parameters except $T_{\mathrm{eff},o}$.
+We elected not to pursue an empirical Bayes' approach.
 
-\begin{eqnarray} \label{eqn:scaling}
-\vM(\vT_o) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
-         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
-\end{eqnarray}
-
-star spot areal coverage fraction is very small, then the signal associated with the
+As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on our instrumental calibration.
+If the stellar parameters in one order is routinely off, we can examine and refine our instrumental calibration.
+For example, the radial velocity $v_r$ could be systematically offset in one order due to instrumental calibration problems.
+Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework assumes the spectral resolution is a fixed across all wavelengths, but in fact there is a small dependence on wavelength.
+This spectral-order granularity in fit quality is not available in a fit that includes \emph{all} $N_{order}$ spectral orders.
+In fact, the benefits of spectral chunking could be made even-more-granular by chunking the spectrum into individual spectral lines or line-groups.
+The fit quality could then be assessed on a line-by-line basis, even taking into account systematic effects like individual elemental abundance patterns beyond the coarse $\feh$ estimates.
+Future improvements to the spectral inference framework are directed at this spectral-line chunking strategy.
 

### 2016-03-25 document/ms.tex
Some improvements to the manuscript, Approach 1 section of Methodology.

--- 2016-03-24 document/ms.tex
@@
 
-\newcommand{\iancze}{{\sc C15}}
+\newcommand{\iancze}{{\sc C15 }}
 
@@
 This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.
-The naive single-component fit to different wavelength chunks conveys information about
+The na\"ive single-component fit to different wavelength provide a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.
+It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect of \emph{e.g.} $\logg$ on the spectrum.
+For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.
+For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \sigma_{v, o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.
 
-\begin{eqnarray} \label{eqn:scaling}
-\vM(\vT_o) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
-         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
-\end{eqnarray}
+In principle, one could refine the inference on $T_{\mathrm{eff},o}$ in an \emph{empirical Bayes'} strategy CITE (XX, astroML book?), in which we re-evaluate $\vT_o$ by setting priors on all the stellar parameters except $T_{\mathrm{eff},o}$.
+We elected not to pursue an empirical Bayes' approach.
 
-star spot areal coverage fraction is very small, then the signal associated with the
+As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on our instrumental calibration.
+If the stellar parameters in one order are routinely discrepant, we can examine and refine our instrumental calibration for that spectral order.
+For example, the radial velocity $v_r$ could be systematically offset in one order due to instrumental calibration problems.
+Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework from \iancze assumes the spectral resolution is fixed across all wavelengths, but typical spectrographs exhibit a small dependence of spectral resolution on wavelength.
+
+Spectral-order level granularity in fit quality is not available in a fit that includes all $N_{order}$ spectral orders.
+In fact, the benefits of spectral chunking could be made \emph{even more granular} by chunking the spectrum into individual spectral lines or line-groups.
+The fit quality could then be assessed on a line-by-line basis, even taking into account systematic effects like individual elemental abundance patterns beyond the coarse $\Z$ estimates.
+Future improvements to the spectral inference framework are directed at implementing this spectral-line chunking strategy.
 

### 2016-03-25 document/ms.tex
Redo all the equations to use Omegas instead of c.  Verify the accuracy of the equations.

@@
 For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.
-For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \sigma_{v, o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.
+For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \Omega_{o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.
 
@@
 
-\begin{eqnarray} \label{eqn:simple_mix}
-\flam(\vt_{\ast, \mathrm{mix}}) = (1-c) \flam(\teffa, ...) + c \flam(\teffb, ...)
+\begin{eqnarray} \label{eqn:mix_M}
+\vM_{\mathrm{mix}}(\vT) = \vM(\teffa, ...) \times \Omega_a + \vM(\teffb, ...) \times \Omega_b
 \end{eqnarray}
 
-Where $c, \teffa, \teffb$ are the mixture model fill factor and two-temperature photosphere components respectively.
+Where $\teffa, \teffb, \Omega_a, \Omega_b$ are temperatures and solid angles of two photospheric components respectively.
 All other stellar intrinsic and extrinsic parameters, and instrumental nuisance calibration parameters are shared among the two components, as chronicled in Table \ref{table:params}.
 
-If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:simple_mix}.  However \iancze employ \emph{normalized} $\flam$:
+If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.
+However \iancze employ \emph{standardized} $\flam$ when constructing the forward model $\vM$:
 
 \begin{eqnarray} \label{eqn:normalization}
-\bar \flam = \frac{\flam}{\int_{\lambda_0}^{\lambda_1} \flam d\lambda} = \frac{\flam}{f}
+\bar \flam = \frac{\flam}{\int_{0}^{\infty} \flam d\lambda} = \frac{\flam}{f}
 \end{eqnarray}
 
-The reason for normalizing is a matter of practicality: the number of PCA eigenspectra components scales steeply with the pixel-to-pixel variance of $f_{\lambda}(\{\vt_{\ast}\}^\textrm{grid})$.
-The choice to normalize makes no difference for modeling a single photospheric component.
-But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $c$.
-More flux comes from the hotter component per solid angle.
+The reason for normalizing is a matter of practicality: the number of PCA eigenspectra components in the spectral emulator scales steeply with the pixel-to-pixel variance of $f_{\lambda}(\{\vt_{\ast}\}^\textrm{grid})$, increasing the computational cost of spectral emulation.
+The choice to standardize fluxes makes no difference for modeling a single photospheric component.
+But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $c \equiv \Omega_b/(\Omega_a+\Omega_b)$.
 So we scale the mixture model in the following way:
@@
 \begin{eqnarray} \label{eqn:norm_scaling}
-f_{\lambda, \mathrm{mix}} &=& (1-c) f_{\mathrm{a}}\bar f_{\lambda, \mathrm{a}} + c f_{\mathrm{b}} \bar f_{\lambda, \mathrm{b}} \\
+f_{\lambda, \mathrm{mix}} &=& f_{\mathrm{a}} \bar f_{\lambda, \mathrm{a}} \times \Omega_a + f_{\mathrm{b}} \bar f_{\lambda, \mathrm{b}} \times \Omega_b \\
 q &=& q(\vt_{\ast})\equiv \frac{f_{\mathrm{b}}(\teffb, ...)}{f_{\mathrm{a}}(\teffa, ...)} \\
-f_{\lambda, \mathrm{mix}}^{\prime} &=& \bar f_{\lambda, \mathrm{a}} + \frac{c}{1-c} q \bar f_{\lambda, \mathrm{b}} 
+f_{\lambda, \mathrm{mix}}^{\prime} &=& \bar f_{\lambda, \mathrm{a}} \times \Omega_a + q \bar f_{\lambda, \mathrm{b}} \times \Omega_b
 \end{eqnarray}
 
-where the prime symbol in the final line indicates a rescaled mixture model flux.
+where the prime symbol in the final line indicates a re-standarized mixture model flux, where the relative fluxes of the model components are now correctly scaled.
 
-We are now tasked with computing an estimator, $\hat f(\vt_{\ast})$.
+We are then tasked with computing an estimator, $\hat f(\vt_{\ast})$, for estimating the scale factor $q$ in-between model gridpoints.
 The Right Thing to Do would be to follow \iancze by training a Gaussian process on the $f(\{\vt_{\ast}\}^\textrm{grid})$.
-What We Actually Did was simple interpolation between the model grid-points.
+What We Actually Did was linearly interpolate between the model grid-points.
 Interpolation can cause pile-up near model grid-points, as noted in \citet{2014ApJ...794..125C}, which motivated the spectral emulation procedure in \iancze.
-In this case, we assumed the interpolation of $\hat f$ was smooth enough that we would not see such pileups, and if present, the pileup would mostly be discernable in the distribution of samples in the starpost areal coverage fraction $c$.
+We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable in the distribution of samples in the starspot areal coverage fraction $c$.
 One drawback of our estimator method compared to the Gaussian Process regression method is that we do not propagate the uncertainty associated with the absolute flux ratio interpolation into our estimate of $c$.
@@
 
-The mixture model is a linear operation and the mixture model components share all the same extrinsic parameters, so we can re-use all the same post-processed eigenspectra $\widetilde{\mathbf{\Xi}}$, mean spectrum $\widetilde{\xi}_\mu$, and variance spectrum $\widetilde{\xi}_\sigma$, but calulate two sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{a}, \mathrm{b})}$, and their associated mean and covariances:
+The mixture model is a linear operation with all the same stellar extrinsic parameters, so we can re-use all the same post-processed eigenspectra $\widetilde{\mathbf{\Xi}}$, mean spectrum $\widetilde{\xi}_\mu$, and variance spectrum $\widetilde{\xi}_\sigma$, with the tildes representing all post processing \emph{except} the $\Omega$ scaling.
+We calulate \emph{two} sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{a}, \mathrm{b})}$, and their associated mean and covariances following the Appendix of \iancze, and yielding:
 
 \begin{equation}
-  \mathsf{M}_{\mathrm{mix}}^\prime = \widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{a}} + \frac{c}{1-c} q (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{b}})
+  \mathsf{M}_{\mathrm{mix}}^\prime = \Omega_a (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{a}}) + q \Omega_b (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{b}})
 \end{equation}
@@
 \begin{equation}
-  \mathsf{C}_{\mathrm{mix}}^\prime = \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{a}} \mathbf{X}^T + \frac{c}{1-c} q \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{b}} \mathbf{X}^T + \mathsf{C}
+  \mathsf{C}_{\mathrm{mix}}^\prime = \Omega_a^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{a}} \mathbf{X}^T + q \Omega_b^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{b}} \mathbf{X}^T + \mathsf{C}
   \label{eqn:modC}

### 2016-03-25 document/ms.tex
Minor additions and tweaks to the prose in Methodology.

@@
 
-The reason for normalizing is a matter of practicality: the number of PCA eigenspectra components in the spectral emulator scales steeply with the pixel-to-pixel variance of $f_{\lambda}(\{\vt_{\ast}\}^\textrm{grid})$, increasing the computational cost of spectral emulation.
+The reason for standardizing the flux is a matter of practicality: the number of PCA eigenspectra components in the spectral emulator scales steeply with the pixel-to-pixel variance of $f_{\lambda}(\{\vt_{\ast}\}^\textrm{grid})$, increasing the computational cost of spectral emulation.
 The choice to standardize fluxes makes no difference for modeling a single photospheric component.
@@
 $\vT$ & Stellar parameters in the model & - & \iancze \\
-$q_o(\vt_{\ast})$ & Absolute mean flux ratio in order $o$  & N & This Work \\
+$q(\vt_{\ast})$ & Absolute mean flux ratio in order $o$  & N & This Work \\
 \hline
@@
 $\sigma_v$ & Instrumental resolution & Y & \iancze \\
+$v_r$ & Radial Velocity & Y & \iancze \\
 $\Omega_a$ & Solid angle subtended by component A & N & This Work \\
 $\Omega_b$ & Solid angle subtended by component B & N & This Work \\
-$c$ & Spot fill factor ($\Omega_b / \Omega_a$) & N & This Work \\
-$A_{\lambda}$ & Extinction towards the source 2 & Y & \iancze \\
+$c$ & Spot fill factor, $\Omega_b / (\Omega_a+\Omega_b)$ & N & This Work \\
+$A_{\lambda}$ & Extinction towards the source & Y & \iancze \\
 \enddata
@@
 
-Once we had the mixture model in hand, we could apply the blocked Gibbs MCMC sampling framework from \iancze.
-We have added 2 more parameters ($c, \teffb$) to the model, expanding from 6 to 8 total stellar parameters.
+Once we have the mixture model in hand, we can apply the blocked Gibbs MCMC sampling framework from \iancze.
+We have added 2 more parameters ($\Omega_b, \teffb$) to the model, expanding from 6 to 8 total stellar parameters.
 Unfortunately this increase in dimensionality adds considerable complexity to tuning the model.
-The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$, so our 2 new parameters increased the tuning parameters from 15 to 36!
-The tuning parameters are covariances between dimensions in your proposal distribution.
+The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$ CITE XX, so our 2 new parameters increased the tuning parameters from 15 to 36!
+The tuning parameters are covariances between dimensions in the proposal distribution.
 Luckily, most of the covariances are negligibly small.
-However the $c, \teffb, \Omega$ terms were all highly correlated, suggesting an affine transformation of the parameters would accelerate the convergence of the MCMC chains.
+However the $\teffa, \teffb, \Omega_a, \Omega_b$ terms are likely to be correlated, suggesting an affine transformation of the parameters would accelerate the convergence of the MCMC chains.
+We experimented with some of these transformations and found that the existing sampling was best, although still correlated.
 

### 2016-05-01 code/batch_grid_pca.py
batch script for running all the grid.py and pca.py steps

@@ -1,0 +1,24 @@
+#!/usr/bin/env python
+import os
+import yaml
+import numpy as np 
+import h5py
+
+ms = range(98, 125)
+
+os.chdir(os.path.expandvars('$WELTER/sf/'))
+
+os.getcwd()
+
+for m in ms:
+
+    dat_name = '../../data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)
+    path_out = 'm{:03d}/'.format(m)
+    os.chdir(path_out)
+
+    # Do all the grid.py and pca.py setup.
+    os.system('grid.py --create')
+    os.system('pca.py --create')
+    os.system('pca.py --optimize=emcee --samples=30')
+    os.system('pca.py --store --params=emcee')
+    os.chdir(os.path.expandvars('$WELTER/sf/'))

### 2016-05-04 document/ms.tex
Write club outcome with Katelyn from Monay, May 2, preparing for the next formatting write club.

@@
 
+Modeling the periodic light curves of spotted stars can answer these questions: ``What evidence is there to support the existence of starspots?
+What constraint can be placed jointly upon the effective temperature contrast and areal coverage of the starspots?
+What is the longitudinal asymmetry of the spots?
+''.
+As pointed out by CITE XX, cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots.
+Photometric modeling of the light curve produces degenerate estimates in the temperature contrast and areal coverage fraction.
+For example, CITE XX achieved XX.
+
+By modeling the composite \emph{spectrum} of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.
+A stellar spectrum with a longitudinally symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating star would all show zero amplitude of photometric variability, yet they all contain star spots.
+Spectroscopic modeling can still measure the starspot properties in these cases.
+
+In principle, more advanced questions could be asked about the properties of the spots: ``How many distinct spot groups are there?
+Is there evidence for both hot spots and cool spots?
+What is the longitudinal distribution of the spots?
+What is the (co-)latitudinal distribution of the spots?
+What is the distribution of effective temperature within a spot or spot group?
+What are the morphologies of the spots?''.
+Solving these questions would require a complex model comparison framework, combining all available data and lines of evidence from photometric, spectroscopic, and spectropolarimetric monitoring.
+We seek to answer the much easier questions about the aggregate properties of the stellar photosphere, assuming the star is well described by two distinct photospheric components.
+
 \subsection{Previous studies of \name}
@@
 \subsection{Full-spectrum fitting framework}
-% Motivation: The questions we want to answer
-Modeling the periodic light curves of spotted stars can answer these questions: ``What evidence is there to support the existence of starspots.
-What constraint can be placed on the effective temperature contrast and areal coverage of the starspots?
-What is the longitudinal assymetry of the spots?
-''.
-As pointed out by CITE XX, cyclical light curve variations indicate only the longitudinally assymetric component of the star spots.
-Photometric modeling of the light curve produces degenerate estimates in the temperature contrast and areal coverage fraction.
-For example, CITE XX achieved XX.
-
-By modeling the composite \emph{spectrum} of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.
-A stellar spectrum with a longitudinaly symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating star would all show zero amplitude of photometric variability, yet they all contain star spots.
-Spectroscopic modeling can still measure the starspot properties in these cases.
-
-In principle, more advanced questions could be asked about the properties of the spots: ``How many distinct spot groups are there?
-Is there evidence for both hot spots and cool spots?
-What is the longitudinal distribution of the spots?
-What is the (co-)latitudinal distribution of the spots?
-What is the distribution of effective temperature within a spot or spot group?
-What are the morphologies of the spots?''.
-Solving these questions would require a complex model comparison framework, combining all available data and lines of evidence from photometric, spectroscopic, and spectropolarimetric monitoring.
-We seek to answer the much easier questions about the aggregate properties of the stellar photosphere, assuming the star is well described by two distinct photospheric components.
 
@@
 
-A main motivating factor in designing our methodology was our wish to adress this question for a given spectrum: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the detection of starspots be reported?''.
+A main motivating factor in designing our methodology was our wish to address for a given spectrum, the question: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the properties of starspots be measured?''.
 In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy among themselves.
@@
 A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.
-The model encapsulates the major intrinstic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:
+The model encapsulates the major intrinsic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:
 
@@
 
-\subsection{Approach 1: Deriving unique Teff in each order}
+\subsection{Model design and implementation considerations}
 
+\subsubsection{Approach 11: Whole spectrum with a single photospheric component (Czekala et al. 2015)}
+
+Approach 11 is identical to the strategy in \iancze.
 The model $\vM(\vT)$ was intended to apply a single set of stellar parameters to the entire wavelength range of interest, presumably the entire available spectrum.
@@
 Simultaneous fitting is the desired behavior for most applications involving a single stellar photospheric component.
-In our case, however, we know that a single stellar photospheric component is a poor model for the data: there are \emph{two} components lurking in the composite spectrum.
-But depending on the star spot properties, a single stellar photosphere component might fit the composite spectrum satisfactorily, like if the flux contrast of the starspot is simply too low compared to the noise.
+In our case, however, we know that a single stellar photospheric component is a poor model for the data: there are \emph{two or more components} lurking in the composite spectrum.
+We anticipate that these fits would be too uninformative, so we did not implement Approach 11 on the whole spectrum.
+
+\textbf{Other things to say: Optical and IR will have slightly different RV, perhaps different vsini based on erroneous spectral resolution.
+This method could work with liberal assignment of local kernels, and the development of new kernels that deal with line-width mis-matches.}
+
+\subsubsection{Approach 12: Deriving unique Teff in each order}
+
+In local chunks of wavelength, a single stellar photosphere component might fit the composite spectrum satisfactorily.
+Some wavelength chunks will fit the warm photosphere lines better and other wavelength chunks will fit prominent lines from cool spots better.
+Wavelength chunks possessing lines that are present in both cool and warm stars will yield mixed results.
 
@@
 We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.
-This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.
-The na\"ive single-component fit to different wavelength provide a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.
+
+This change does not represent reality: by definition, the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.
+The na\"ive single-component fit to different wavelength chunks merely provides a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.
+
 It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect of \emph{e.g.} $\logg$ on the spectrum.
@@
 
-As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on our instrumental calibration.
+As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on instrumental calibration.
 If the stellar parameters in one order are routinely discrepant, we can examine and refine our instrumental calibration for that spectral order.
@@
 Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework from \iancze assumes the spectral resolution is fixed across all wavelengths, but typical spectrographs exhibit a small dependence of spectral resolution on wavelength.
+(cite the SICK paper)
 
@@
 
-\subsection{Approach 2: Two component photosphere mixture model}
+\subsubsection{Approach 21: Whole spectrum with two components}
+
+Ideally what we want to do is fit the entire spectrum with a two (or three, or $N_c-$component photosphere).
+If we believe our model, the entire emergent spectrum of the star should be described by a single set of stellar parameters.
+If nature had truly delivered a noisy version of this model, the large wavelength coverage of the
+
+\subsubsection{Approach 22: Order-by-order with two components}
+
+\subsection{Implementation}
+
+\subsubsection{Mixture model definitions}
 

### 2016-05-04 document/ms.tex
Some editing of the prose, but mostly add a new framework for the table for Teff as a function of order for both models, related to Issue #17

@@
 
-A main motivating factor in designing our methodology was our wish to address for a given spectrum, the question: ``Is the spectrum consistent with the non-detection of starspots, and to what level of confidence can the properties of starspots be measured?''.
+A main motivating factor in designing our methodology was our wish to address the question: ``Is a given spectrum consistent with the non-detection of starspots, and to what level of confidence can the properties of starspots be measured given uncertain stellar properties?''.
 In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy among themselves.
@@
 
-Ideally what we want to do is fit the entire spectrum with a two (or three, or $N_c-$component photosphere).
+Ideally, we want to fit the entire spectrum with a two component photosphere.
 If we believe our model, the entire emergent spectrum of the star should be described by a single set of stellar parameters.
-If nature had truly delivered a noisy version of this model, the large wavelength coverage of the
+In other words, if nature had truly delivered a noisy version of this model, the ability to measure starspot properties would scale with the number of spectral channels (to some power).
+
+Unfortunately there are two main limitations of Approach 21.
+First, the Metropolis-Hastings Gibbs sampling is dramatically complicated by increasing from 6 to 8 stellar parameters: $theta-original to theta-multicomponent$.
+The details of the problem are summarized in Section \ref{sec:MC-challenges}.
 
 \subsubsection{Approach 22: Order-by-order with two components}
+
+Finally, Approach 22 is two sample each spectral order with a unique two-component photosphere model:
+
+$$ theta by order$$.
+
+In this case we altered the \iancze framework from a blocked Gibbs sampler with Metropolis-Hastings proposals to an affine invariant ensemble sampler with all stellar and nuisance parameters sampled simultaneously.
+
+This strategy has the \emph{disadvantage} that there is no statistically principled way to combine the $N_{ord}$ inferences from the set of $\theta$ at the end.
+There are many \emph{heuristic} ways to estimate the inferences at the end.
 
@@
 \subsection{Challenges: Tuning the transition probability matrix}
+\label{sec:MC-challenges}
 
@@
 Unfortunately this increase in dimensionality adds considerable complexity to tuning the model.
-The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$ CITE XX, so our 2 new parameters increased the tuning parameters from 15 to 36!
+The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$ CITE XX, so our 2 new parameters increased the tuning parameters from 15 to 36.
 The tuning parameters are covariances between dimensions in the proposal distribution.
@@
 However the $\teffa, \teffb, \Omega_a, \Omega_b$ terms are likely to be correlated, suggesting an affine transformation of the parameters would accelerate the convergence of the MCMC chains.
-We experimented with some of these transformations and found that the existing sampling was best, although still correlated.
+We experimented with some of these transformations and found that the existing stellar parameters were best, although still unacceptably correlated.
 
@@
 
-\subsection{Result 1: Signal from deriving $\teff$ in each IGRINS order}
+\subsection{Result 12: Signal from deriving $\teff$ in each IGRINS order}
 
@@
 We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).
+
+Table \ref{tbl_order_results} lists the values of Teff for all orders.
+
+\input{tables/tbl_order_results.tex}
 
@@
 
-\subsection{Result 2: Effect size from fitting synthetic data order-by-order}
-
-\subsection{Result 3: Direct measurement of spot properties with mixture model}
+\subsection{Result 22: Direct measurement of spot properties with mixture model}
 
@@
 \subsection{Interpretation of distribution of stellar properties from Results 1 + 2}
-
-\subsection{Interpretation of star spot properties from Result 3}
 

### 2016-05-04 document/ms.tex
Framework for answering the question: At what phase of variability were the spectra acquired? Issue #18

@@
 
+Figure XX shows the data of XX plotted from the interval X-Y.
+Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.
+The ESPaDoNs spectra were at a phase of Z, indicating...
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/V_phot_phase.pdf}
+	\caption{Estimated $V$-band photometry phase during the times of observations.}
+	\label{fig:PhotPhase}
+\end{figure*}
+
 \section{Results}

### 2016-05-04 document/ms.tex
Add a table showing the 4 approaches with full spectrum vs order-by-order, and one or two components.  Issue #19

@@
 
-\subsection{Model design and implementation considerations}
+\begin{tabular}{ r| p{5cm} | p{5cm} | }
+\multicolumn{1}{r}{}
+ &  \multicolumn{1}{c}{Whole spectrum (Gibbs Sampling)}
+ & \multicolumn{1}{c}{Order-by-order (emcee)} \\
+\cline{2-3}
+Single component photosphere & \citet{2015ApJ...812..128C}: Poor model for spotted stars & Sec. \ref{sec:approach12}- plausible evidence for starspots if $\teff$ varies with order \\
+\cline{2-3}
+Two component photosphere & \ref{sec:approach21}- Statistically principled inference on starspot properties given the whole spectrum.
+But strongly correlated dimensions impose challenge on MCMC tuning.
+& \ref{sec:approach22}- Multiple independent posteriors of starspot properties.
+But combining inferences is heuristic.
+\\
+\cline{2-3}
+\end{tabular}
 
-\subsubsection{Approach 11: Whole spectrum with a single photospheric component (Czekala et al. 2015)}
+\subsection{Approach 11: Whole spectrum with a single photospheric component (Czekala et al. 2015)}
 
@@
 
-\subsubsection{Approach 12: Deriving unique Teff in each order}
+\subsection{Approach 12: Deriving unique Teff in each order}
+\label{sec:approach12}
 
@@
 
-\subsubsection{Approach 21: Whole spectrum with two components}
+\subsection{Approach 21: Whole spectrum with two components}
+\label{sec:approach21}
 
@@
 
-\subsubsection{Approach 22: Order-by-order with two components}
+\subsection{Approach 22: Order-by-order with two components}
+\label{sec:approach22}
 

### 2016-05-05 document/ms.tex
Write club with Katelyn on Thursday May 5: ticking off outline items.

@@
 
-\subsection{Challenges: Tuning the transition probability matrix}
-\label{sec:MC-challenges}
-
-Once we have the mixture model in hand, we can apply the blocked Gibbs MCMC sampling framework from \iancze.
-We have added 2 more parameters ($\Omega_b, \teffb$) to the model, expanding from 6 to 8 total stellar parameters.
-Unfortunately this increase in dimensionality adds considerable complexity to tuning the model.
-The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$ CITE XX, so our 2 new parameters increased the tuning parameters from 15 to 36.
-The tuning parameters are covariances between dimensions in the proposal distribution.
-Luckily, most of the covariances are negligibly small.
-However the $\teffa, \teffb, \Omega_a, \Omega_b$ terms are likely to be correlated, suggesting an affine transformation of the parameters would accelerate the convergence of the MCMC chains.
-We experimented with some of these transformations and found that the existing stellar parameters were best, although still unacceptably correlated.
-
 \section{Observations}\label{sec:obs}
@@
 
-Figure XX shows the data of XX plotted from the interval X-Y.
+Figure XX shows the ASASSN X-band monitoring plotted from the interval X-Y.
 Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.
 The ESPaDoNs spectra were at a phase of Z, indicating...
+
+We fit all the data in the interval X to Z in the following way:
 
@@
 
+\subsection{Result 11}
+We expect that applying approach 11 (single component to all orders , \iancze) is a poor model for our multicomponent stellar data and would therefore yield a poor quality fit.
+Nevertheless we experimented with a single temperature fit to $N_{ord}=X$ IGRINS spectral orders with X samples sampling Theta and Phi parameters in the blocked Gibbs sampler identically to \iancze.
+We found relatively poor fit quality, with large typical residuals of X.
+The poor fit is exemplified in the top panel of Figure X which shows the observed spectrum in the region of the X line.
+The best fit model with theta = [x, y, z] does not achieve a good fit of the X line.
+
 \subsection{Result 12: Signal from deriving $\teff$ in each IGRINS order}
 
-We compared the IGRINS spectrum of \name to the \PHOENIX grid of pre-computed synthetic model spectra \citep{2013A&A...553A...6H}.
-
-We modified the default implementation by chunking the spectrum into 58 of its cleanest spectral orders and deriving the stellar parameters $\vt_{\ast,m}$ \emph{independently} in each $m^{\mathrm{th}}$ order.
-We therefore have 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.
+We chunked the IGRINS spectrum into $N_{ord}=$58 of its cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.
+We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.
 The figure shows a dramatic effect: \textbf{The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.}
-
-We interpret the cooler temperatures derived at $K-$band as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
-Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.
-We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).
 
@@
 
+Figure XX shows the joint posterior probability density distribution of $\teffb$ versus $f$ calculated independently for $N_{ord}=25$ IGRINS orders.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/Star_spot_measurement} 
+	\caption{Effective temperature as derived by different orders.}
+	\label{fig:StarspotProperties}
+\end{figure*}
+
 \section{Discussion}
@@
 \subsection{Interpretation of distribution of stellar properties from Results 1 + 2}
+
+We interpret the cooler temperatures derived at $K-$band in Approach 12 as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
+Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.
+We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).
+
+The systematically different teffs seen in Approach 12 could also be attributable to magnetic fields (cite XX).
 
@@
 
+\section{Challenges: Tuning the transition probability matrix}
+\label{sec:MC-challenges}
+
+Once we have the mixture model in hand, we can apply the blocked Gibbs MCMC sampling framework from \iancze.
+We have added 2 more parameters ($\Omega_b, \teffb$) to the model, expanding from 6 to 8 total stellar parameters.
+Unfortunately this increase in dimensionality adds considerable complexity to tuning the model.
+The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$ CITE XX, so our 2 new parameters increased the tuning parameters from 15 to 36.
+The tuning parameters are covariances between dimensions in the proposal distribution.
+Luckily, most of the covariances are negligibly small.
+However the $\teffa, \teffb, \Omega_a, \Omega_b$ terms are likely to be correlated, suggesting an affine transformation of the parameters would accelerate the convergence of the MCMC chains.
+We experimented with some of these transformations and found that the existing stellar parameters were best, although still unacceptably correlated.
+
 \acknowledgements

### 2016-05-13 code/batch_config_K.py
Batch scripts for K-Band mixture model

@@ -25,23 +25,20 @@ for m in ms:
     f.close()
     
     config['data']['files'] = ['$WELTER/data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)]
-    config['grid']['hdf5_path'] = '$WELTER/sf/m{:03d}/libraries/PHOENIX_IGRINS_m{:03d}.hdf5'.format(m,m)
+    config['grid']['hdf5_path'] = '$WELTER/sf/m{:03d}/libraries/PHX_IGR_2700-4500_m{:03d}.hdf5'.format(m,m)
     lb, ub = int(np.floor(wls[0])), int(np.ceil(wls[-1]))
 
     config['grid']['wl_range'] = [lb, ub]
-    config['PCA']['path'] = '$WELTER/sf/m{:03d}/PHOENIX_IGRINS_K_PCA.hdf5'.format(m)
-    config['name'] = 'LkCa4_m{:03d}'.format(m)
-    config['Comments'] = 'LkCa4 single order: m = {}, autogenerated config file.'.format(m)
+    config['PCA']['path'] = '$WELTER/sf/m{:03d}/PHX_IGR_2700-4500_K_PCA.hdf5'.format(m)
     config['data']['instruments'] =['IGRINS_K']
-    print("{:03d}: {:.0f}  -  {:.0f}   {}".format(m, wls[0], wls[-1], dat_name))
     
     os.makedirs(path_out, exist_ok=True)
     with open(sf_out, mode='w') as outfile:
         outfile.write(yaml.dump(config))
         print('wrote to {}'.format(path_out))
 
-for m in ms:
-    os.chdir("m{:03d}".format(m))
-    os.system('mkdir libraries &')
-    os.system('grid.py --create > grid.out &')
-    os.chdir("..")
+#for m in ms:
+#    os.chdir("m{:03d}".format(m))
+#    os.system('mkdir libraries &')
+#    os.system('grid.py --create > grid.out &')
+#    os.chdir("..")

### 2016-05-13 code/batch_grid_pca.py

@@ -4,7 +4,8 @@ import yaml
 import numpy as np 
 import h5py
 
-ms = range(98, 125)
+#ms = range(98, 125)
+ms = range(71, 96+1)
 
 os.chdir(os.path.expandvars('$WELTER/sf/'))
 
@@ -12,7 +13,6 @@ os.getcwd()
 
 for m in ms:
 
-    dat_name = '../../data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)
     path_out = 'm{:03d}/'.format(m)
     os.chdir(path_out)
 

### 2016-05-13 code/batch_grid_pca.py
Need to have libraries directory before performing grid.py --create

@@ -17,6 +17,7 @@ for m in ms:
     os.chdir(path_out)
 
     # Do all the grid.py and pca.py setup.
+    os.makedirs('libraries', exist_ok=True)
     os.system('grid.py --create')
     os.system('pca.py --create')
     os.system('pca.py --optimize=emcee --samples=30')

### 2016-05-16 code/batch_mix_emcee.py
Simplify the batch processing preparation for mix_emcee runs, it was too complicated before.

@@ -4,7 +4,7 @@ import yaml
 import numpy as np 
 import h5py
 
-ms = range(98, 125)
+ms = range(71, 96+1)
 
 os.chdir(os.path.expandvars('$WELTER/sf/'))
 
@@ -12,38 +12,11 @@ os.getcwd()
 
 for m in ms:
 
-    dat_name = '../../data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)
     path_out = 'm{:03d}/'.format(m)
     os.chdir(path_out)
-    sf_out = 'output/mix_emcee/run01/config.yaml'.format(m)
     
-    f = open("../m115/output/mix_emcee/run01/config.yaml")
-    config = yaml.load(f)
-    f.close()
-    
-    f=h5py.File(dat_name, "r")
-    wls = f['wls'][:]
-    f.close()
-    
-    config['data']['files'] = ['$WELTER/data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)]
-    config['grid']['hdf5_path'] = '$WELTER/sf/m{:03d}/libraries/PHOENIX_IGRINS_m{:03d}.hdf5'.format(m,m)
-    lb, ub = int(np.floor(wls[0])), int(np.ceil(wls[-1]))
-
-    config['grid']['wl_range'] = [lb, ub]
-    config['PCA']['path'] = '$WELTER/sf/m{:03d}/PHOENIX_IGRINS_H_PCA.hdf5'.format(m)
-    config['name'] = 'mix_emcee'
-    config['Comments'] = 'Mixture model single order designed for use with star_mix.py'
-    config['data']['instruments'] =['IGRINS_H']
-    
-    os.makedirs('output/mix_emcee', exist_ok=True)
-    os.makedirs('output/mix_emcee/run01', exist_ok=True)
-    with open(sf_out, mode='w') as outfile:
-        outfile.write(yaml.dump(config))
-        print('wrote to {}'.format(path_out))
-
     # Also initialize the nuissance parameter json file.
-    os.chdir('output/mix_emcee/run01/')
-    #os.system('star.py --initPhi')
-    #os.system('git add -f config.yaml')
-    os.system('git add -f s0_o0phi.json')
+    os.system('star.py -r 1')
+    os.chdir('output/mix_emcee/run01')
+    os.system('star.py --initPhi')
     os.chdir(os.path.expandvars('$WELTER/sf/'))

### 2016-05-16 code/batch_star_mix.py
First commit of a batch routine to submit sbatch jobs of star_mix.py for many spectral orders.

@@ -1,0 +1,21 @@
+#!/usr/bin/env python
+
+import os
+import yaml
+import numpy as np 
+import h5py
+
+ms = range(71, 96+1)
+
+os.chdir(os.path.expandvars('$WELTER/sf/'))
+
+os.getcwd()
+
+for m in ms:
+
+    path_out = 'm{:03d}/output/mix_emcee/run01/'.format(m)
+    os.chdir(path_out)
+
+    # Use sbatch.
+    os.system('sbatch --job-name=m{:03d} star_mix.py --samples=5000 --incremental_save=50'.format(m))
+    os.chdir(os.path.expandvars('$WELTER/sf/'))

### 2016-06-01 document/ms.tex
Some new and updated notebooks include results from all of H-band
GJH adds new content to the manuscript including low res spectra and photometry, some prose.

@@
 
-\author{Michael A. Gully-Santiago,\altaffilmark{1} Greg Herczeg,\altaffilmark{1} et al.}
+\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} et al.}
 
@@
 We chose \name for its likelihood of large areal coverage of starspots, as evinced by large-amplitude photometric variability  detected in $BVRI$ bands.
-Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G}.
+Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G,grankin08,xiao12}.
 Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/V_phot_phase.pdf}
-	\caption{Estimated $V$-band photometry phase during the times of observations.}
+	\includegraphics[width=0.95\textwidth]{figures/phase_folded_lightcurve.pdf}
+	\caption{Phase of photometry at the time of IGRINS measurement}
 	\label{fig:PhotPhase}
@@
 
+\section{Monitoring the Spots of LkCa 4}
+
+The previous sections established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
+In this section, we will demonstrate that this same model explains the broadband spectral energy distribution and flux-calibrated optical/near-IR spectra of LkCa 4.
+Periodic variability in photometry and spectral indices are reproduced by modest changes in the visible fraction of the hot spot.
+
+\subsection{Reproducing the Spectral Energy Distribution}
+
+\subsection{Reproducing the flux-calibrated low resolution}
+
+Figure~\ref{fig:lores}...
+
+\subsection{TiO Variability}
+
+The depth of TiO and other molecular bands are a common diagnostic of spectral type (and temperature) in optical spectra.
+In the 12 ESPaDOnS spectra of \name\ obtained over 14 days \citep{2014MNRAS.444.3220D}, the depth of the TiO bands vary.
+
+Each of the TiO spectral index is correlated with the other indices.
+The line depths also correlate with the V-band magnitude, as estimated from the ASAS-SN photometry and the V-band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.
+
+Needs a lot more.
+
+\subsection{Phased colors}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{lkca4_lores} 
+	\vspace{-100mm}
+	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+	\label{fig:lores}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{tiovar} 
+	\vspace{-100mm}
+	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
+The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
+The main panel shows a correlation between V-band magnitude and the TiO-7140 index, while the inset shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
+	\label{fig:tiovar}
+\end{figure*}
+
 \section{Discussion}

### 2016-06-20 code/batch_plot_mix.py
Batch scripts for making plots; ignore the rsync batch script for now.

@@ -1,0 +1,25 @@
+#!/usr/bin/env python
+import os
+import yaml
+import numpy as np 
+import h5py
+
+ms = range(99, 119)
+#ms = range(72, 94+1)
+
+os.chdir(os.path.expandvars('$WELTER/sf/'))
+
+os.getcwd()
+
+for m in ms:
+
+    dat_name = '../../data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)
+    path_out = 'm{:03d}/output/mix_emcee/run01'.format(m)
+    os.chdir(path_out)
+
+    print('Plotting results from m{:03d}'.format(m))
+    # Do all the grid.py and pca.py setup.
+    os.system('plot_many_mix_models.py --static')
+    os.system('cp mix_model.png '+
+    	os.path.expandvars('$WELTER/results/fig/mix_models/mix_model_m{:03d}.png'.format(m)))
+    os.chdir(os.path.expandvars('$WELTER/sf/'))

### 2016-06-20 document/ms.tex
Writing and revising the intro and methods section, move the detailed methods to the Appendix

@@
 
-\title{IGRINS spectra of \name}
+\title{Measuring starspot properties by forward modeling IGRINS spectra of \name}
 
@@
 
-\subsection{Pre Main Sequence HR diagram spread}
+%\subsection{Pre Main Sequence HR diagram spread}
 
 For a single presumably coeval stellar cluster, pre main-sequence HR diagrams exhibit large ($\delta t_{\ast} \sim t_{\ast}$) apparent spreads in age \citep[e.g.][]{2011A&A...534A..83R}.
-The large spreads in these pre main-sequence HR diagrams is controversial: some take it as evidence for intrinsic age spreads, some take it as evidence for non static accretion history \citep{2009ApJ...702L..27B, 2010ARA&A..48..581S}.
+The cause of the large spread in pre main-sequence HR diagrams is controversial: some take it as evidence for intrinsic age spreads, some take it as evidence for non static accretion history \citep{2009ApJ...702L..27B, 2010ARA&A..48..581S}.
 
@@
 
-\subsection{Previous studies of Starspots}
+%\subsection{Previous studies of Starspots}
 
-Meanwhile, sunspots are probably responsible for biases in stellar effective temperatures derived by different methods.
+Sunspots are probably responsible for biases in stellar effective temperatures derived by different methods.
 For example, the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) measured effective temperatures for 3493 young stars finding offsets in $\teff$ of typically 200$-$500 K and as high as 1000 K compared to previous studies \citep{2014ApJ...794..125C}.
 Low resolution optical spectroscopy shows a typical spread of 200 K in the spectral type-to-effective-temperature conversion scale \citep{2014ApJ...786...97H}.
-Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses.
-The observations of sunspots are lagging behind the theory \citep{2015ApJ...807..174S}.
+These discrepancies in $\teff$ could be attributable to measurements of spectral features steming from patches of stellar photosphere with different effective temperatures than the bulk photosphere.
+Single temperature photospheres are not realistic approximations for complex young photospheres possessing large areal coverage fractions of starspots.
 
+Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses \citep{2015ApJ...807..174S}.
 The importance of starspots needs to be empirically evaluated to assess systematic biases of pre-main sequence stellar evolutionary models.
+%...develop this point more
 
 Modeling the periodic light curves of spotted stars can answer these questions: ``What evidence is there to support the existence of starspots?
-What constraint can be placed jointly upon the effective temperature contrast and areal coverage of the starspots?
-What is the longitudinal asymmetry of the spots?
-''.
-As pointed out by CITE XX, cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots.
-Photometric modeling of the light curve produces degenerate estimates in the temperature contrast and areal coverage fraction.
-For example, CITE XX achieved XX.
+What joint constraint can be placed upon the effective temperature contrast and areal coverage of the starspots?
+What is the longitudinal asymmetry of the spots?''.
+Cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots \citep{2012AJ....143....4H}.
+Photometric modeling of the light curve taken alone can only yield degenerate estimates in the temperature contrast and areal coverage fraction.
+A star possessing longitudinally symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating (or very slowly rotating) star would all show zero or secular amplitude of photometric variability, yet they all contain star spots.
 
 By modeling the composite \emph{spectrum} of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.
-A stellar spectrum with a longitudinally symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating star would all show zero amplitude of photometric variability, yet they all contain star spots.
-Spectroscopic modeling can still measure the starspot properties in these cases.
+Spectroscopic modeling can still measure the starspot properties in pole-on stars, stars with longitudinally symmetric stars, and non-rotating stars.
 
@@
 
-\subsection{Previous studies of \name}
+%\subsection{Previous studies of \name}
 
@@
 Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G,grankin08,xiao12}.
+
 Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.  
+%This statement needs to be fact-checked, maybe some more supporting info.
+
 The source has little or no accretion ($\log{\dot M} < 8.1$), no detection of mid-infrared nor mm excess, and no stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.
 This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.
+% These claims need references.
 
@@
 We demonstrate the constraining power of full spectrum fitting with panchromatic optical and near-IR echelle spectroscopy.
-We show that relatively small starspot filling factors can be detected due to the large spectral grasp of IGRINS.
+% Consider putting in Section references here
 
 \section{Methodology}\label{sec:methods}
+
+The details of the methodology are contained in Appendix \ref{methods-details}.  Here we overview the salient concepts needed to follow the results and discussion.
+
+We extended the modular framework for spectral inference described in \iancze \footnote{The open source codebase and its full revision history is available at https://github.com/iancze/Starfish.
+The experimental fork discussed in this paper is at https://github.com/gully/Starfish}.
+The \iancze technique forward models emulated synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
+We use the \PHOENIX~ model grid.
+We made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
+We discuss these two changes below.
+
+Following and extending the notation of \iancze, we can write down the mixture model as:
+
+\begin{eqnarray} \label{eqn:mix_M}
+\vM_{\mathrm{mix}}(\vT) = \vM(\teffa, ...) \times \Omega_a + \vM(\teffb, ...) \times \Omega_b
+\end{eqnarray}
+
+where $\vM$ is the pixel-level forward model of a spectrum, and we assume the stellar photosphere is characterized as two photospheric components with different effective temperatures, $\teff$ and solid angular coverages $\Omega$, but sharing all the same intrinisic and extrinsic stellar parameters otherwise.
+The observed filling factor of photosphere $b$ is simply the ratio:
+
+\begin{eqnarray} \label{eqn:mix_M}
+f = \frac{\Omega_b}{\Omega_a + \Omega_b}
+\end{eqnarray}
+
+The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{2013PASP..125..306F}.
+The affine-invariant ensemble sampler is more resilient to correlations expected among starspot temperature and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
+The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
+There is no principled way to combine the $N_{\rm ord}$ sets of inferences on $\vT_{o}$, but there are ample heuristics like taking the weighted average of the $o$ sets of marginalized posterior distributions functions.
+
+\section{Observations}\label{sec:obs}
+
+\subsection{IGRINS Spectroscopy}\label{sec:igrins} 
+We acquired observations with IGRINS on the Harlan J.
+Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
+The Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG}, is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
+The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.
+
+\subsection{ESPaDOnS Spectroscopy}
+We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.
+
+\subsection{At what phase of variability were the spectra acquired?}
+
+Figure XX shows the ASASSN X-band monitoring plotted from the interval X-Y.
+Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.
+The ESPaDoNs spectra were at a phase of Z, indicating...
+
+We fit all the data in the interval X to Z in the following way:
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/phase_folded_lightcurve.pdf}
+	\caption{Phase of photometry at the time of IGRINS measurement}
+	\label{fig:PhotPhase}
+\end{figure*}
+
+\section{Results}
+
+\subsection{Result 11}
+We expect that applying approach 11 (single component to all orders , \iancze) is a poor model for our multicomponent stellar data and would therefore yield a poor quality fit.
+Nevertheless we experimented with a single temperature fit to $N_{ord}=X$ IGRINS spectral orders with X samples sampling Theta and Phi parameters in the blocked Gibbs sampler identically to \iancze.
+We found relatively poor fit quality, with large typical residuals of X.
+The poor fit is exemplified in the top panel of Figure X which shows the observed spectrum in the region of the X line.
+The best fit model with theta = [x, y, z] does not achieve a good fit of the X line.
+
+\subsection{Result 12: Signal from deriving $\teff$ in each IGRINS order}
+
+We chunked the IGRINS spectrum into $N_{ord}=$58 of its cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.
+We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.
+The figure shows a dramatic effect: \textbf{The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.}
+
+Table \ref{tbl_order_results} lists the values of Teff for all orders.
+
+\input{tables/tbl_order_results.tex}
+
+We further performed a plausibility check to constrain the effect size of starspots.
+We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.
+We coadded the spectra in a mixture model:  $ \mathsf{M}_{mix} = c \cdot \mathsf{M}_A(T_\textrm{eff,A}) + (1-c) \cdot \mathsf{M}_B(T_\textrm{eff,B})$.
+We chose a fill factor of starspots of 30\%.
+We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters one would na\"{\i}vely derive.
+The noised-up optical data yields $\teff \sim 4100$ K, close to that of the A component.
+We are awaiting the results from $K-$ band at the time of writing.
+
+We want to measure the derived effective temperature as a function of wavelength.
+The motivation for this strategy is as follows.
+We assume that LkCa4 has a significant fraction of its stellar disk covered by starspots citeXX.
+Such a photosphere will have an emergent spectrum composed of superpositions of relatively cool patches and warm patches.
+The visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
+The infrared spectrum will have a lower overall spot contast, but with higher relative contribution attributable to the cool patches citeXX.
+
+The fit of a single-temperature forward-modeled spectrum to different regions of the spectrum could therefore conceivably yield different estimates for the effective temperature.
+
+In principle, one could estimate the effective temperature \emph{evaluated independently for each spectral line}.
+The line strength is often degenerate with other properties (\emph{e.g.} magnetic field, $\log{g}$, $[\mathrm{Fe}/\mathrm{H}]$, etc.), but \emph{on average} these correlations would be averaged over.
+
+We measured the effective temperature in \emph{each of the 43 spectral orders} of IGRINS.
+Figure \ref{fig:teffOrder} plots each derived effective temperature value and uncertainty at the center position of each order.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/teff_v_wl_example} 
+	\caption{Effective temperature as derived by different orders.}
+	\label{fig:teffOrder}
+\end{figure*}
+
+\subsection{Result 22: Direct measurement of spot properties with mixture model}
+
+Figure XX shows the joint posterior probability density distribution of $\teffb$ versus $f$ calculated independently for $N_{ord}=25$ IGRINS orders.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/Star_spot_measurement} 
+	\caption{Effective temperature as derived by different orders.}
+	\label{fig:StarspotProperties}
+\end{figure*}
+
+\section{Monitoring the Spots of LkCa 4}
+
+The previous sections established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
+In this section, we will demonstrate that this same model explains the broadband spectral energy distribution and flux-calibrated optical/near-IR spectra of LkCa 4.
+Periodic variability in photometry and spectral indices are reproduced by modest changes in the visible fraction of the hot spot.
+
+\subsection{Reproducing the Spectral Energy Distribution}
+
+\subsection{Reproducing the flux-calibrated low resolution}
+
+Figure~\ref{fig:lores}...
+
+\subsection{TiO Variability}
+
+The depth of TiO and other molecular bands are a common diagnostic of spectral type (and temperature) in optical spectra.
+In the 12 ESPaDOnS spectra of \name\ obtained over 14 days \citep{2014MNRAS.444.3220D}, the depth of the TiO bands vary.
+
+Each of the TiO spectral index is correlated with the other indices.
+The line depths also correlate with the V-band magnitude, as estimated from the ASAS-SN photometry and the V-band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.
+
+Needs a lot more.
+
+\subsection{Phased colors}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
+	\vspace{-100mm}
+	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+	\label{fig:lores}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/tiovar} 
+	\vspace{-100mm}
+	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
+The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
+The main panel shows a correlation between V-band magnitude and the TiO-7140 index, while the inset shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
+	\label{fig:tiovar}
+\end{figure*}
+
+\section{Discussion}
+
+\subsection{Interpretation of distribution of stellar properties from Results 1 + 2}
+
+We interpret the cooler temperatures derived at $K-$band in Approach 12 as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
+Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.
+We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).
+
+The systematically different teffs seen in Approach 12 could also be attributable to magnetic fields (cite XX).
+
+\subsection{Longitudinal / latitudinal spot distributions and phase}
+
+\subsection{Addressing limitations of assumptions in the methodology}
+
+\appendix
+
+\section{Methodological details}
+\label{methods-details}
 
@@
 
-\section{Observations}\label{sec:obs}
-
-\subsection{IGRINS Spectroscopy}\label{sec:igrins} 
-We acquired observations with IGRINS on the Harlan J.
-Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
-The Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG}, is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
-The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.
-
-\subsection{ESPaDOnS Spectroscopy}
-We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.
-
-\subsection{At what phase of variability were the spectra acquired?}
-
-Figure XX shows the ASASSN X-band monitoring plotted from the interval X-Y.
-Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.
-The ESPaDoNs spectra were at a phase of Z, indicating...
-
-We fit all the data in the interval X to Z in the following way:
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/phase_folded_lightcurve.pdf}
-	\caption{Phase of photometry at the time of IGRINS measurement}
-	\label{fig:PhotPhase}
-\end{figure*}
-
-\section{Results}
-
-\subsection{Result 11}
-We expect that applying approach 11 (single component to all orders , \iancze) is a poor model for our multicomponent stellar data and would therefore yield a poor quality fit.
-Nevertheless we experimented with a single temperature fit to $N_{ord}=X$ IGRINS spectral orders with X samples sampling Theta and Phi parameters in the blocked Gibbs sampler identically to \iancze.
-We found relatively poor fit quality, with large typical residuals of X.
-The poor fit is exemplified in the top panel of Figure X which shows the observed spectrum in the region of the X line.
-The best fit model with theta = [x, y, z] does not achieve a good fit of the X line.
-
-\subsection{Result 12: Signal from deriving $\teff$ in each IGRINS order}
-
-We chunked the IGRINS spectrum into $N_{ord}=$58 of its cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.
-We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.
-The figure shows a dramatic effect: \textbf{The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.}
-
-Table \ref{tbl_order_results} lists the values of Teff for all orders.
-
-\input{tables/tbl_order_results.tex}
-
-We further performed a plausibility check to constrain the effect size of starspots.
-We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.
-We coadded the spectra in a mixture model:  $ \mathsf{M}_{mix} = c \cdot \mathsf{M}_A(T_\textrm{eff,A}) + (1-c) \cdot \mathsf{M}_B(T_\textrm{eff,B})$.
-We chose a fill factor of starspots of 30\%.
-We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters one would na\"{\i}vely derive.
-The noised-up optical data yields $\teff \sim 4100$ K, close to that of the A component.
-We are awaiting the results from $K-$ band at the time of writing.
-
-We want to measure the derived effective temperature as a function of wavelength.
-The motivation for this strategy is as follows.
-We assume that LkCa4 has a significant fraction of its stellar disk covered by starspots citeXX.
-Such a photosphere will have an emergent spectrum composed of superpositions of relatively cool patches and warm patches.
-The visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
-The infrared spectrum will have a lower overall spot contast, but with higher relative contribution attributable to the cool patches citeXX.
-
-The fit of a single-temperature forward-modeled spectrum to different regions of the spectrum could therefore conceivably yield different estimates for the effective temperature.
-
-In principle, one could estimate the effective temperature \emph{evaluated independently for each spectral line}.
-The line strength is often degenerate with other properties (\emph{e.g.} magnetic field, $\log{g}$, $[\mathrm{Fe}/\mathrm{H}]$, etc.), but \emph{on average} these correlations would be averaged over.
-
-We measured the effective temperature in \emph{each of the 43 spectral orders} of IGRINS.
-Figure \ref{fig:teffOrder} plots each derived effective temperature value and uncertainty at the center position of each order.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/teff_v_wl_example} 
-	\caption{Effective temperature as derived by different orders.}
-	\label{fig:teffOrder}
-\end{figure*}
-
-\subsection{Result 22: Direct measurement of spot properties with mixture model}
-
-Figure XX shows the joint posterior probability density distribution of $\teffb$ versus $f$ calculated independently for $N_{ord}=25$ IGRINS orders.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/Star_spot_measurement} 
-	\caption{Effective temperature as derived by different orders.}
-	\label{fig:StarspotProperties}
-\end{figure*}
-
-\section{Monitoring the Spots of LkCa 4}
-
-The previous sections established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
-In this section, we will demonstrate that this same model explains the broadband spectral energy distribution and flux-calibrated optical/near-IR spectra of LkCa 4.
-Periodic variability in photometry and spectral indices are reproduced by modest changes in the visible fraction of the hot spot.
-
-\subsection{Reproducing the Spectral Energy Distribution}
-
-\subsection{Reproducing the flux-calibrated low resolution}
-
-Figure~\ref{fig:lores}...
-
-\subsection{TiO Variability}
-
-The depth of TiO and other molecular bands are a common diagnostic of spectral type (and temperature) in optical spectra.
-In the 12 ESPaDOnS spectra of \name\ obtained over 14 days \citep{2014MNRAS.444.3220D}, the depth of the TiO bands vary.
-
-Each of the TiO spectral index is correlated with the other indices.
-The line depths also correlate with the V-band magnitude, as estimated from the ASAS-SN photometry and the V-band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.
-
-Needs a lot more.
-
-\subsection{Phased colors}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{lkca4_lores} 
-	\vspace{-100mm}
-	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
-	\label{fig:lores}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{tiovar} 
-	\vspace{-100mm}
-	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
-The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
-The main panel shows a correlation between V-band magnitude and the TiO-7140 index, while the inset shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
-	\label{fig:tiovar}
-\end{figure*}
-
-\section{Discussion}
-
-\subsection{Interpretation of distribution of stellar properties from Results 1 + 2}
-
-We interpret the cooler temperatures derived at $K-$band in Approach 12 as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
-Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.
-We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).
-
-The systematically different teffs seen in Approach 12 could also be attributable to magnetic fields (cite XX).
-
-\subsection{Longitudinal / latitudinal spot distributions and phase}
-
-\subsection{Addressing limitations of assumptions in the methodology}
-
-\appendix
-
-\section{Testing and runing the mixture model}
-
-Here are some specifics about what we did.
-
 \section{Previous work}

### 2016-06-24 document/ms.tex
Discussion of photometry and two new photometric plots

@@
 The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{2013PASP..125..306F}.
-The affine-invariant ensemble sampler is more resilient to correlations expected among starspot temperature and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
+The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among starspot temperature and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
 The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
@@
 
-\section{Observations}\label{sec:obs}
+\section{Observations and data mining}\label{sec:obs}
 
 \subsection{IGRINS Spectroscopy}\label{sec:igrins} 
-We acquired observations with IGRINS on the Harlan J.
+We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG} on the Harlan J.
 Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
-The Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG}, is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
+IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
 The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.
+The data were reduced with the Pipeline Package (citeXX).
+We performed telluric correction by dividing the spectrum of \name by an A0V star observed near-contemporaneously at similar air-mass.
+The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of \name.
+No effort was made to remove these flux excesses, which affect several spectral orders.
+%List the spectral orders these lines affect.
 
@@
 We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.
+There are 12 spectra observed over the 13 days between JD 2456665.72 and 2456678.90.
 
-\subsection{At what phase of variability were the spectra acquired?}
+\subsection{Photometric monitoring from ASASSN and \citet{grankin08}}
 
-Figure XX shows the ASASSN X-band monitoring plotted from the interval X-Y.
-Our IGRINS observation dates of Z and Q show that the spectra were probably acquired during a phase of XX.
-The ESPaDoNs spectra were at a phase of Z, indicating...
+We retrieved $V-$band monitoring from the ASASSN survey (citeXX).
+This data covered 2012 January - 2016 March.
+The 777 raw data points included near-contemporaneous measurements from repeated observations during the same visits, which lasted typically $<10$ minutes.
+We grouped datapoints by these visits yielding 186 data points, assigning a mean value and standard deviation when there was more than 1 observation per visit, enforcing a floor uncertainty of 0.01, the native quoted uncertainty of the data points.
+We assigned the native uncertainty of 0.01 when there was only a single observation per visit.
 
-We fit all the data in the interval X to Z in the following way:
+We also retrieved $V-$band monitoring from \citet{grankin08} which covers 1992 August - 2004 October with 284 data points.
+Of those, 278 have $B-V$, 268 have $V-R$, and 18 have $U-B$.
+We also compiled the 10 additional $V-$band photometric data points provided in \citet{2014MNRAS.444.3220D}.
+
+Figure \ref{fig:PhotTime} assembles the \citet{grankin08} and ASASSN $V-$band monitoring plotted over the interval 1992-2016.
+The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
 
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/phase_folded_lightcurve.pdf}
-	\caption{Phase of photometry at the time of IGRINS measurement}
+	\includegraphics[width=0.95\textwidth]{figures/LkCa4_phot1992-2016.pdf}
+	\caption{\name $V-$band photometric monitoring from 1992-2016.}
+	\label{fig:PhotTime}
+\end{figure*}
+
+Figure \ref{fig:PhotPhase} shows the phase-folded lightcurve of all available $V-$band data grouped by the 17 available observing seasons.
+We folded the phase by a period $P=3.375$ days, which is the median position of the peaks of the multiterm ($M_{\rm max} = 4$) Lomb-Scargle periodogram derived separately from each of the 17 observing seasons.
+The standard deviation of the 17 periodogram peaks was 0.003 days.
+The general appearance of the phase-folded lightcurves do not change with perturbations to the period on the scale of 0.003 days.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/all_LCs_phase.pdf}
+	\caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.
+The blue solid lines show a multi-term periodic fit keeping the first $M_{\rm max}=4$ Fourier components.
+The vertical lines show the epochs of observations for available spectroscopy.
+The unchanged vertical scale highlights the secular drift of the light curve amplitude and morphology.}
 	\label{fig:PhotPhase}

### 2016-06-27 document/ms.tex
Add Table of estimated V-band values, overhaul outline, some new text

@@
 
-Figure \ref{fig:PhotPhase} shows the phase-folded lightcurve of all available $V-$band data grouped by the 17 available observing seasons.
+Figure \ref{fig:PhotPhase} shows the phase-folded lightcurve of all available $V-$band data grouped by the 17 observing seasons.
 We folded the phase by a period $P=3.375$ days, which is the median position of the peaks of the multiterm ($M_{\rm max} = 4$) Lomb-Scargle periodogram derived separately from each of the 17 observing seasons.
 The standard deviation of the 17 periodogram peaks was 0.003 days.
-The general appearance of the phase-folded lightcurves do not change with perturbations to the period on the scale of 0.003 days.
+The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
+We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from the multiterm fit shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.
 
@@
 
+\input{tables/tbl_estV_atObsEpoch.tex}
+
 \section{Results}
-
-\subsection{Result 11}
-We expect that applying approach 11 (single component to all orders , \iancze) is a poor model for our multicomponent stellar data and would therefore yield a poor quality fit.
-Nevertheless we experimented with a single temperature fit to $N_{ord}=X$ IGRINS spectral orders with X samples sampling Theta and Phi parameters in the blocked Gibbs sampler identically to \iancze.
-We found relatively poor fit quality, with large typical residuals of X.
-The poor fit is exemplified in the top panel of Figure X which shows the observed spectrum in the region of the X line.
-The best fit model with theta = [x, y, z] does not achieve a good fit of the X line.
 
@@
 
-We chunked the IGRINS spectrum into $N_{ord}=$58 of its cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.
+We combined the IGRINS spectrum with the fourth ESPaDoNs spectrum from Table \ref{tbl_estimated_V}.
+These spectra have comparable $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
+We chunked the spectra into $N_{ord}=$58 of their cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.
 We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.
-The figure shows a dramatic effect: \textbf{The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.}
+The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.
 

### 2016-06-28 document/ms.tex
Table of of Stellar properties as a function of order, closes #17

@@
 We chunked the spectra into $N_{ord}=$58 of their cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.
-We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.
-The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.
+We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:SingleTeffvsOrder}.
+The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical or short-wavelength end of $H-$band.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/single_Teff_v_order}
+	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum assuming a single component photosphere.
+}
+	\label{fig:SingleTeffvsOrder}
+\end{figure*}
 
@@
 Figure \ref{fig:teffOrder} plots each derived effective temperature value and uncertainty at the center position of each order.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/teff_v_wl_example} 
-	\caption{Effective temperature as derived by different orders.}
-	\label{fig:teffOrder}
-\end{figure*}
 

### 2016-07-01 document/ms.tex
Add new Figures about Two Temp results and fill factor, many-panel figure of spectra for all orders, Table content

@@
 
-\subsection{Result 12: Signal from deriving $\teff$ in each IGRINS order}
+\subsection{Na\"ieve Single Component spectral fit to each spectral order}
 
@@
 
-\subsection{Result 22: Direct measurement of spot properties with mixture model}
+\subsection{Two-temperature photophere model fit to each spectral order}
 
-Figure XX shows the joint posterior probability density distribution of $\teffb$ versus $f$ calculated independently for $N_{ord}=25$ IGRINS orders.
+Figure \ref{fig:TwoTempResults} shows the starspot and photospheric temperature derived independently for 43 IGRINS orders.
+%% Things to say:
+% - Range of allowed temperatures and assumptions for each run
+% - H-band is tight
+% - Scatter in $K-Band$
+% - Telluric lines and other artifacts in the data
+% - Metal lines affected
 
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/Star_spot_measurement} 
-	\caption{Effective temperature as derived by different orders.}
-	\label{fig:StarspotProperties}
+	\includegraphics[width=0.95\textwidth]{figures/LkCa4_HK_mixTeff_by_order} 
+	\caption{Two-temperature model properties, $\teffa$ and $\teffb$, derived independently from full-spectrum fitting 43 IGRINS orders.
+The top panel denotes typical telluric transmission for all of the possible 54 IGRINS orders.
+The derived effective temperatures show enhanced scatter in $K-$band.}
+	\label{fig:TwoTempResults}
 \end{figure*}
+
+%% Plot of all spectra (vis-a-vis the poster)
+%(In the appendix for now)
+%% Things to say:
+% - Systematics-dominated traps
+% - Metal lines, and derived [Fe/H]
+% - Calibration artifacts
+% - Nice agreement
+% - Not every order has strongly temperature-sensitive lines
+% - Orders with very strong lines at one temperature will dominate
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.39\textwidth]{figures/LkCa4_fill_vs_Teff2} 
+	\caption{Joint constraint on the temperature of starspots $\teffb$, and their observed solid-angular filling factor $f$.
+Each data point and error bar are taken from Table \ref{tbl_order_results}, with the error bars therefore representing 2$\sigma$ errors.}
+	\label{fig:TwoTempResults}
+\end{figure*}
+
+%% Plot of starspot fill factor vs. Teff2
+%% Things to say:
+% - Many ways to combine the posteriors
+% - "Observed" fill factor
+% - Scatter
+% - Large range in fill factor is like adding a DC component and renormalizing
 
@@
 \appendix
+
+\section{Examples of full spectrum fitting}
+
+Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} show spectra from 42 IGRINS orders.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
+	\caption{IGRINS Orders 94 and $99-119$.  Note that the $y-$axis is on a logarithmic scale.  }
+	\label{fig:Hband3x7}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
+	\caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  }
+	\label{fig:Kband3x7}
+\end{figure*}
 

### 2016-07-04 code/batch_plot_mix.py
New Jupyter notebooks generate Latex tables and multi panel spectra figures

@@ -4,8 +4,9 @@ import yaml
 import numpy as np 
 import h5py
 
-ms = range(99, 119)
+#ms = range(99, 119)
 #ms = range(72, 94+1)
+ms = list(range(72, 94+1)) + list(range(99, 119))
 
 os.chdir(os.path.expandvars('$WELTER/sf/'))
 

### 2016-07-05 document/ms.tex
Overhaul the single-component fitting prose, add some references and text to the photometry section.

@@
 
+% Previous efforts to derive starspot properties via spectroscopy:
+
+%% Put in text here!
+
 In principle, more advanced questions could be asked about the properties of the spots: ``How many distinct spot groups are there?
@@
 The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{2013PASP..125..306F}.
-The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among starspot temperature and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
+The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
 The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
@@
 
-We retrieved $V-$band monitoring from the ASASSN survey (citeXX).
+We retrieved $V-$band monitoring from the ASASSN survey \citep{2014ApJ...788...48S}.
 This data covered 2012 January - 2016 March.
@@
 
-Figure \ref{fig:PhotTime} assembles the \citet{grankin08} and ASASSN $V-$band monitoring plotted over the interval 1992-2016.
+Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{2014MNRAS.444.3220D}, and ASASSN $V-$band monitoring plotted over the interval 1992-2016.
 The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
@@
 Figure \ref{fig:PhotPhase} shows the phase-folded lightcurve of all available $V-$band data grouped by the 17 observing seasons.
-We folded the phase by a period $P=3.375$ days, which is the median position of the peaks of the multiterm ($M_{\rm max} = 4$) Lomb-Scargle periodogram derived separately from each of the 17 observing seasons.
+We folded the phase by a period $P=3.375$ days, which is the median position of the peaks of the multiterm ($M_{\rm max} = 4$) Lomb-Scargle periodogram derived separately from each of the 17 observing seasons \citep{2014sdmm.book.....I}.
 The standard deviation of the 17 periodogram peaks was 0.003 days.
 The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from the multiterm fit shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{2015ApJ...812...18V, Jake Vanderplas_2015} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
 Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.
@@
 
-\subsection{Na\"ieve Single Component spectral fit to each spectral order}
+\subsection{Single Component spectral fit to each spectral order}
 
-We combined the IGRINS spectrum with the fourth ESPaDoNs spectrum from Table \ref{tbl_estimated_V}.
+We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth spectrum from Table \ref{tbl_estimated_V}.
+We chunked the spectrum into a subset of $N_{ord}=$26 spectral orders and performed full-spectrum fitting separately on each of these 26 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
+We employed the \PHOENIX model grid with a search range of $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and $\teff \in [3500, 4200]$ and trained a spectral emulator as described in \iancze.
+
+We tuned the Metropolis-Hasting step sizes with several iterations of burn-in procedure and visually checked the final chains for convergence.
+Our number of samples was generally much longer than the estimated integrated autocorrelation length.
+We spot-checked full-spectrum fits in comparison with the observed spectrum, finding modest agreement with the exception of spectral line outliers.
+No attempt was made to downweight spectral-line outliers as described in \iancze.
+
+We computed the median value and 5$^{th}$ and $95^{th}$ percentiles of a burned-in subset of the samples.
+Overall these 26 sets of point estimates for $\vt_{\ast,m}$ show relatively good agreement, with exceptions.
+We have little constraint on $\logg$ and $\Z$ since full-spectrum fitting tends to wash out the weak signal contained in line wings for spectra with a finite level of random noise and systematic error.
+Meanwhile, strong metal lines can bias estimates of $\Z$ at the expense of estimates for $\teff$.
+We get consistent estimates for $v_z \sim 15.6 \pm 0.6$ and $\vsini \sim 28.0 \pm 0.9$, with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$.
+These two outlying spectral orders converged to unreasonably large values for $\vsini$ and $a_{\rm G}$, the amplitude of the Gaussian process covariance kernel, and one of these orders has an unusually small value for effective temperature, $\teff\sim3500$, comparable to the lower limit of the employed model grid.
+Visual comparison of the observed spectrum for a range of fits for these orders shows that no single emulated spectrum could reasonably fit these discrepant spectral orders because there are several large spectral outliers.
+The other spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
+Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates, with the 5$^{th}$ and $95^{th}$ percentile error bars, placed at the central wavelength of each of the 26 spectral orders for the subset of ESPaDoNs orders that received full-spectrum fitting.
+Full spectrum fitting was attempted for some of the other available ESPaDoNs orders, but many of these orders did not achieve convergence in the MCMC chains.
+
+% Comparing the single-component results from Optical to Infrared
 These spectra have comparable $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
-We chunked the spectra into $N_{ord}=$58 of their cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.
-We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:SingleTeffvsOrder}.
-The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical or short-wavelength end of $H-$band.
+
+The effective temperature derived from the optical spectral orders shows some scatter in the range 3500 K - 4250, with a median   is about The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical or short-wavelength end of $H-$band.
 

### 2016-07-05 document/ms.tex
More prose for the results section-- single temperature results

@@
 
-We extended the modular framework for spectral inference described in \iancze \footnote{The open source codebase and its full revision history is available at https://github.com/iancze/Starfish.
+We experimented with several extensions to the modular framework for spectral inference described in \iancze \footnote{The open source codebase and its full revision history is available at https://github.com/iancze/Starfish.
 The experimental fork discussed in this paper is at https://github.com/gully/Starfish}.
-The \iancze technique forward models emulated synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
+The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
 We use the \PHOENIX~ model grid.
-We made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
+After experimenting with the base model from \iancze, we made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
 We discuss these two changes below.
@@
 
-\begin{eqnarray} \label{eqn:mix_M}
+\begin{eqnarray} \label{eqn:fill_factor}
 f = \frac{\Omega_b}{\Omega_a + \Omega_b}
@@
 The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{2015ApJ...812...18V, Jake Vanderplas_2015} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{2015ApJ...812...18V} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
 Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.
@@
 
-\subsection{Single Component spectral fit to each spectral order}
+\subsection{Single temperature fitting to the ESPaDoNs spectrum}
 
@@
 No attempt was made to downweight spectral-line outliers as described in \iancze.
+We attempted fits to 9 more of the 35 spectral orders available for this ESPaDoNs spectrum, but the MCMC computations for these orders failed to converge, possibly due to numerical artifacts arising from poor model fits.
 
-We computed the median value and 5$^{th}$ and $95^{th}$ percentiles of a burned-in subset of the samples.
-Overall these 26 sets of point estimates for $\vt_{\ast,m}$ show relatively good agreement, with exceptions.
+We computed the median value and 5$^{th}$ and $95^{th}$ percentiles of burned-in subsets of the MCMC samples described above.
+Overall these 26 sets of point estimates for $\vT_{m}$, $\vP_m$ show relatively good agreement, with exceptions.
 We have little constraint on $\logg$ and $\Z$ since full-spectrum fitting tends to wash out the weak signal contained in line wings for spectra with a finite level of random noise and systematic error.
 Meanwhile, strong metal lines can bias estimates of $\Z$ at the expense of estimates for $\teff$.
-We get consistent estimates for $v_z \sim 15.6 \pm 0.6$ and $\vsini \sim 28.0 \pm 0.9$, with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$.
-These two outlying spectral orders converged to unreasonably large values for $\vsini$ and $a_{\rm G}$, the amplitude of the Gaussian process covariance kernel, and one of these orders has an unusually small value for effective temperature, $\teff\sim3500$, comparable to the lower limit of the employed model grid.
-Visual comparison of the observed spectrum for a range of fits for these orders shows that no single emulated spectrum could reasonably fit these discrepant spectral orders because there are several large spectral outliers.
-The other spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
-Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates, with the 5$^{th}$ and $95^{th}$ percentile error bars, placed at the central wavelength of each of the 26 spectral orders for the subset of ESPaDoNs orders that received full-spectrum fitting.
-Full spectrum fitting was attempted for some of the other available ESPaDoNs orders, but many of these orders did not achieve convergence in the MCMC chains.
-
-% Comparing the single-component results from Optical to Infrared
-These spectra have comparable $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
-
-The effective temperature derived from the optical spectral orders shows some scatter in the range 3500 K - 4250, with a median   is about The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical or short-wavelength end of $H-$band.
+We get consistent estimates for\footnote{Note, $v_z$ is an uncorrected recessional velocity, not a proper radial velocity} $v_z \sim 15.6 \pm 0.6$ km/s and $\vsini \sim 28.0 \pm 0.9$ km/s, with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$.
+These two outlying spectral orders converged to unreasonably large values for $\vsini$ and $a_{\rm G}$, the amplitude of the Gaussian process covariance kernel.
+One of these orders has an unusually small value for effective temperature, $\teff\sim3500$, comparable to the lower limit of the employed model grid.
+Visual comparison of the observed spectrum for a range of fits for these orders shows that no single emulated spectrum could reasonably fit their spectrum because there are numerous large spectral outliers.
+The more-well-behaved spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
+Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each of the 26 spectral orders for the subset of ESPaDoNs orders that received full-spectrum fitting.
 
@@
 
-Table \ref{tbl_order_results} lists the values of Teff for all orders.
+\subsection{Single temperature fitting to the IGRINS spectrum}
 
-\input{tables/tbl_order_results.tex}
+We performed full-spectrum fitting on 32 of the 54 available IGRINS spectral orders, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $m$.
+We used the same analysis procedure as described for the ESPaDoNs spectra, with one exception.
+For the IGRINS $K-$band, we employed an expanded search range for the effective temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.
+No effort was made to shift the wavelength scales of the IGRINS data and $\PHOENIX$ model into the same system, so the absolute values of $v_z$ are arbitrary shifted.
 
-We further performed a plausibility check to constrain the effect size of starspots.
+We find a larger dispersion in the point estimates for the stellar parameters derived from the IGRINS data with single temperature fits.
+The most conspicuous trend is in the derived effective temperature as a function of wavelength shown in Figure \ref{fig:SingleTeffvsOrder}.
+Here we see dramatic result that the effective temperature peaks at a values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
+The $K-$band shows even lower derived effective temperatures of $\sim3300$ K.
+
+\subsection{Interpretation of the single temperature fitting results}
+
+There is a $\Delta \teff \sim 800$ K difference in the effective temperature derived at different wavelength intervals for the same stellar spectrum.
+To put this level of effective temperature in context, authors using 4200 K and 3300 K values would conclude evolutionary model derived masses of XX or YY as shown in Figure XX.
+\todo{Put in the numbers and HR diagram figure here.}
+
+It is clear that the single-temperature model is a poor fit to the data.
+Our model assumptions were incorrect: no single temperature can describe all the spectral lines present in the spectra.
+This discrepancy is circumstantial evidence for the direct detection of spectral lines attributable to starspots.
+This circumstantial evidence should not be surprising, given the previous evidence that \name possesses a large coverage fraction of starspots \citep{2014MNRAS.444.3220D}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase}.
+
+% Comparing the single-component results from Optical to Infrared
+Note that some care should be taken when directly comparing results between the ESPaDoNs and IGRINS spectra since they were not taken at the same time.
+These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
+If we assume the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, we can derive the result that the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
+
+We can understand the heightened sensitivity to starspot spectral lines as wavelength increases in the following way.
+The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission.
+So the ratio flux density as function of wavelength will generally increase with wavelength.
+In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
+The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K with solar metalicity and $\logg=3.5$.
+The flux density ratio is the flux per solid angle, so the delivered flux ratio will depend on (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.
+
+\todo{Put in the flux density ratio plot.}
+
+\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  These would end up being closer to the best fit values.}
+
+We performed a further plausibility check to constrain the effect size of starspots.
 We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.
@@
 The noised-up optical data yields $\teff \sim 4100$ K, close to that of the A component.
-We are awaiting the results from $K-$ band at the time of writing.
+\comm{I don't think I ever put together a figure for this, should we just skip it?  I think so.}
 
@@
 
-\subsection{Two-temperature photophere model fit to each spectral order}
+\subsection{Two-temperature fitting to IGRINS spectra}
 
@@
 % - Metal lines affected
+
+Table \ref{tbl_order_results} lists the values of $\teff$ for all IGRINS orders.
+\input{tables/tbl_order_results.tex}
 

### 2016-07-06 document/ms.tex
Some edits to the results section, some new text to results, moving on to the two temperature results

@@
 This discrepancy is circumstantial evidence for the direct detection of spectral lines attributable to starspots.
-This circumstantial evidence should not be surprising, given the previous evidence that \name possesses a large coverage fraction of starspots \citep{2014MNRAS.444.3220D}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase}.
-
-% Comparing the single-component results from Optical to Infrared
-Note that some care should be taken when directly comparing results between the ESPaDoNs and IGRINS spectra since they were not taken at the same time.
-These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
-If we assume the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, we can derive the result that the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
-
-We can understand the heightened sensitivity to starspot spectral lines as wavelength increases in the following way.
-The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission.
-So the ratio flux density as function of wavelength will generally increase with wavelength.
-In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
-The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K with solar metalicity and $\logg=3.5$.
-The flux density ratio is the flux per solid angle, so the delivered flux ratio will depend on (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.
-
-\todo{Put in the flux density ratio plot.}
-
-\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  These would end up being closer to the best fit values.}
+This circumstantial evidence should not be surprising given the previous evidence that \name possesses a large coverage fraction of starspots \citep{2014MNRAS.444.3220D}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase} and discussed previously by \citet{grankin08}.
 
@@
 We chose a fill factor of starspots of 30\%.
-We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters one would na\"{\i}vely derive.
-The noised-up optical data yields $\teff \sim 4100$ K, close to that of the A component.
+We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters our full-spectrum fitting procedure would na\"{\i}vely derive.
 \comm{I don't think I ever put together a figure for this, should we just skip it?  I think so.}
 
-We want to measure the derived effective temperature as a function of wavelength.
-The motivation for this strategy is as follows.
-We assume that LkCa4 has a significant fraction of its stellar disk covered by starspots citeXX.
-Such a photosphere will have an emergent spectrum composed of superpositions of relatively cool patches and warm patches.
-The visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
-The infrared spectrum will have a lower overall spot contast, but with higher relative contribution attributable to the cool patches citeXX.
+\subsection{Heightened sensitivity to starspot spectral lines in the infrared}
 
-The fit of a single-temperature forward-modeled spectrum to different regions of the spectrum could therefore conceivably yield different estimates for the effective temperature.
+Some care should be taken when directly comparing results between the ESPaDoNs and IGRINS spectra since they were not taken at the same time.
+These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
+If we assume the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, we can derive the result that the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
+The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.
 
-In principle, one could estimate the effective temperature \emph{evaluated independently for each spectral line}.
-The line strength is often degenerate with other properties (\emph{e.g.} magnetic field, $\log{g}$, $[\mathrm{Fe}/\mathrm{H}]$, etc.), but \emph{on average} these correlations would be averaged over.
+We can understand the heightened sensitivity to starspot spectral lines as wavelength increases in the following way.
+The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission, according to Wein's displacement law.
+So the ratio of flux density between starspot and bulk photosphere as function of wavelength will generally increase with wavelength until it assymptotes to a fixed value in the Rayleigh-Jeans tail.
+In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
+The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K with solar metalicity and $\logg=3.5$.
+The flux density ratio is the flux per solid angle, so the delivered flux ratio for a finite sized starspot will depend on the (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.
 
-We measured the effective temperature in \emph{each of the 43 spectral orders} of IGRINS.
-Figure \ref{fig:teffOrder} plots each derived effective temperature value and uncertainty at the center position of each order.
+\todo{Put in the flux density ratio plot.}
+
+\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  -These would end up being closer to the best fit values.}
+
+In summary, the visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
+The infrared spectrum will have a lower overall spot contast, but will have higher relative contribution attributable to the cool patches.
+This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{2008ApJ...687L.103P}.
+\comm{This blurb should probably go in the introduction.}
 
 \subsection{Two-temperature fitting to IGRINS spectra}
+
+Motivated by the failure of single-temperature model full-spectrum fitting, we added two new model parameters our forward model: a starspot temperature and a fill factor, as described by Equation \ref{eqn:Mix_M}.
+We also altered the model as described in Section \ref{sec:methods} and detailed in Appendix \ref{methods-details}.
 

### 2016-07-06 document/ms.tex
Two temperature results writeup and some experimenting with violin plots

@@
 
-Motivated by the failure of single-temperature model full-spectrum fitting, we added two new model parameters our forward model: a starspot temperature and a fill factor, as described by Equation \ref{eqn:Mix_M}.
-We also altered the model as described in Section \ref{sec:methods} and detailed in Appendix \ref{methods-details}.
+Motivated by the failure of single-temperature spectral fits, we added two new model parameters to our forward model: a starspot temperature and a fill factor, as described by Equation \ref{eqn:Mix_M}.
+For computational complexity reasons, we altered the model framework as described in Section \ref{sec:methods} and detailed in Appendix \ref{methods-details}.
+
+We computed full-spectrum fitting to 43 of 54 IGRINS spectral orders.
+We fit all 14 stellar and nuissance parameters simultaneously.
+We ran the fits for 5000 steps with 40 walkers in \texttt{emcee}.
+The stellar parameter ranges were $\logg \in [-3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [3000, 4300]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.
+We used the same priors for stellar and nuissance parameters as \iancze.
+We enforced $\teffb < \teffa$ to limit the combinatoric degeneracy and mode-mixing that's possible if MCMC samples with $\teffa \approx \teffb$ arise.
+This false mode mixing matters for the \texttt{emcee} algorithm since the step size distribution would be artificially inflated if some walkers mixed modes with $\teffa \Leftrightarrow \teffb$.
+The MCMC chains all appeared to converge after about 1500 steps.
+\footnote{We spot-checked a few of the MCMC chains for convergence by computing the integrated autocorrelation times.
+Most of the parameters had integrated autocorrelation times much less than our number of steps, except for the $\log{\Omega}$ terms.
+This makes sense because the $\log{\Omega_1}$ and $\log{\Omega_2}$ are strongly correlated, so it takes many steps for each walker to explore the joint probability space.
+We have a strong constraint on the filling factor with all 40 walkers combined.}
+
+We computed point estimates for each parameter by selecting the final 200 $\times$ 40 walkers = 8000 samples and computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
+
+%
+We assessed the fit quality by both overplotting models to data, and examining the distribution of the derived stellar parameters.
+The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
+We find median point estimates and standard deviations of all 43 orders of $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
+Spectral orders $m=91 \mathrm{ and }94$ had exceptionally large uncertainties on their values for $v_z$ and $\vsini$, which makes sense since these two orders are badly affected by telluric absorption artifacts.
+
+As noted previously, our full-spectrum fitting method does not have much constraining power on $\logg$, and $\Z$ can be biased in the face of systematic spectral line outliers.
+We find a preference for values of $\logg$ on the high end of our search range, $3.5 <\logg <4.0$, finding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{2014MNRAS.444.3220D}.
+For $\Z$ we find a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metalicity, while the shorter wavelength values prefer
+
+Table \ref{tbl_order_results} lists the values of $\teff$ for all IGRINS orders.
 
@@
 
-Table \ref{tbl_order_results} lists the values of $\teff$ for all IGRINS orders.
 \input{tables/tbl_order_results.tex}

### 2016-07-12 document/ms.tex
More text in the Results section

@@
 The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.
-The data were reduced with the Pipeline Package (citeXX).
+The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.
 We performed telluric correction by dividing the spectrum of \name by an A0V star observed near-contemporaneously at similar air-mass.
@@
 The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission, according to Wein's displacement law.
-So the ratio of flux density between starspot and bulk photosphere as function of wavelength will generally increase with wavelength until it assymptotes to a fixed value in the Rayleigh-Jeans tail.
+So the ratio of flux density between starspot and bulk photosphere as a function of wavelength will generally increase with wavelength until it assymptotes to a fixed value in the Rayleigh-Jeans tail.
 In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
-The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K with solar metalicity and $\logg=3.5$.
+The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K, solar metalicity, and $\logg=3.5$.
 The flux density ratio is the flux per solid angle, so the delivered flux ratio for a finite sized starspot will depend on the (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.
@@
 
-We computed full-spectrum fitting to 43 of 54 IGRINS spectral orders.
+We computed full-spectrum fitting of 43 of 54 IGRINS spectral orders.
 We fit all 14 stellar and nuissance parameters simultaneously.
@@
 
-We computed point estimates for each parameter by selecting the final 200 $\times$ 40 walkers = 8000 samples and computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
+We computed point estimates for each parameter by selecting the final 200 $\times$ 40 walkers = 8000 samples, and computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
 
-%
-We assessed the fit quality by both overplotting models to data, and examining the distribution of the derived stellar parameters.
+We assessed the fit quality by examining the consistency of the point estimates across the spectral orders.
 The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
@@
 
-As noted previously, our full-spectrum fitting method does not have much constraining power on $\logg$, and $\Z$ can be biased in the face of systematic spectral line outliers.
+As noted previously, our full-spectrum fitting method offers little constraining power on $\logg$, and $\Z$ can be biased in the face of systematic spectral line outliers.
 We find a preference for values of $\logg$ on the high end of our search range, $3.5 <\logg <4.0$, finding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{2014MNRAS.444.3220D}.
-For $\Z$ we find a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metalicity, while the shorter wavelength values prefer
+For $\Z$ we find a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metalicity, while the shorter wavelength values prefer slightly sub-solar metalicity.
+Orders 79, 81, 90, and to a lesser extent 78 and 76 showed aritificially tight constraints on $\Z$, biased to large values.
+Similarly, orders 86, 101, 102, 104, 106, all had $\Z$ estimates biased to extremely low values.
+Visual inspection of these orders indicates that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metalicity estimate alone.
+These spectral line outlier orders also tend to bias estimates of effective temperature.
+The interpretation of these lines will be addressed in the discussion section.
 
-Table \ref{tbl_order_results} lists the values of $\teff$ for all IGRINS orders.
+Finally, the posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.
+At first sight, the $H-$ band estimates show remarkably tight distributions centered near $\teffa\sim4100$ K and $\teffb\sim3000$ K, with the exception of a few spectral order outliers- $m=$ 107, 108, 109.
+The apparent tight constraint is an illusion from pileup near our effective temperature search range for $H-$band.
+So the point estimates for $\teffa$ and $\teffb$ should really be considered lower- and upper- limits respectively.
+Orders 107, 108, and 109 converged on solutions with nearly equal effective tempatures for starspot and photosphere, $\teffa \sim \teffb$.
+These nearly-equal solutions could be explained by vanishingly weak spectral lines in one or the other of the effective temperature ranges, in which case the method offers little constraint on $\teffb$, but improves the fit around $\teffa$.
 
-Figure \ref{fig:TwoTempResults} shows the starspot and photospheric temperature derived independently for 43 IGRINS orders.
-%% Things to say:
-% - Range of allowed temperatures and assumptions for each run
-% - H-band is tight
-% - Scatter in $K-Band$
-% - Telluric lines and other artifacts in the data
-% - Metal lines affected
+We experimented on the $K-$band spectra with expanded effective temperature search ranges.
+Here we see much more scatter, with no single photospheric temperature sticking out as strongly favored, but with values of $\teffa \sim 3900$ K and $\teffb \sim 2800$ K consistent with many orders.
+The $K-$band spectra possess strongly correlated residuals from poor telluric correction, as well as uncorrected hydrogen line features that appear as flux excessess after division by telluric standard spectrum.
+These instrumental afflictions degraded fits to several orders.
 
@@
 
-%% Plot of all spectra (vis-a-vis the poster)
-%(In the appendix for now)
-%% Things to say:
-% - Systematics-dominated traps
-% - Metal lines, and derived [Fe/H]
-% - Calibration artifacts
-% - Nice agreement
-% - Not every order has strongly temperature-sensitive lines
-% - Orders with very strong lines at one temperature will dominate
-
 \begin{figure*}
@@
 
-%% Plot of starspot fill factor vs. Teff2
-%% Things to say:
-% - Many ways to combine the posteriors
-% - "Observed" fill factor
-% - Scatter
-% - Large range in fill factor is like adding a DC component and renormalizing
+Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} show the 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
+The red and blue lines show the hot photosphere and cool spot spectra respectively.
+We inspected the quality of the fits, generally finding remarkable agreement with most spectral orders.
+Many orders demonstrated spectral line outliers, as noted in \iancze.
+Most of the gross spectral features are captured by the composite model.
+There are many examples of spectral lines that are present only in the hot photosphere model, or only in the cool photosphere model.
+
+%% Examples of selected regions.
+For example...
+
+\todo{Compile a list of Line IDs, and maybe little postage stamp figures for each line with a range of fits.}
+
+The most compelling results from the full spectrum fitting method come from orders for which there exist strongly temperature-sensitive spectral lines.
+We spot-checked each spectrum, flagging the orders that possessed these types of lines.
+We then computed the weighted mean of the stellar parameter point statistics only for these effective temperatures and fill factors.
+We arrived at best fit values for the stellar parameters summarized in Table XY.
+We adopt these parameters as the stellar properties at the epoch of the IGRINS observations.
+We find a large filling factor of cool starspots, with a best value of $f=XX\pm yy$.
+\todo{Table of best fit parameters.}
 
@@
 Each of the TiO spectral index is correlated with the other indices.
-The line depths also correlate with the V-band magnitude, as estimated from the ASAS-SN photometry and the V-band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.
+The line depths also correlate with the $V-$band magnitude, as estimated from the ASAS-SN photometry and the $V-$band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.
 
@@
 
-\subsection{Interpretation of distribution of stellar properties from Results 1 + 2}
-
-We interpret the cooler temperatures derived at $K-$band in Approach 12 as the presence of sunspots contributing more flux at longer wavelengths, as shown in the bottom panel of Figure \ref{fig:teffOrder}.
-Here we show the absolute flux ratio, $f_{\lambda, B} / f_{\lambda, A}$ at two different temperatures: $T_\textrm{eff,A} = 4100$ and $T_\textrm{eff,B} = 3300$.
-We present the ratio of two synthetic spectra from Phoenix (blue solid line), and the black body ratio (red dashed line).
-
-The systematically different teffs seen in Approach 12 could also be attributable to magnetic fields (cite XX).
+\subsection{Interpretation of distribution of stellar properties}
 

### 2016-07-12 code/batch_config.py
Revise the config files for an expanded Teff range, related to Issue #27

@@ -2,7 +2,7 @@
 import os
 import yaml
 import numpy as np 
-import h5py
+#import h5py
 
 ms = range(98, 126)
 
@@ -12,7 +12,6 @@ os.getcwd()
 
 for m in ms:
 
-    dat_name = '../data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)
     path_out = 'm{:03d}/'.format(m)
     sf_out = 'm{:03d}/config.yaml'.format(m)
     
@@ -20,28 +19,20 @@ for m in ms:
     config = yaml.load(f)
     f.close()
     
-    f=h5py.File(dat_name, "r")
-    wls = f['wls'][:]
-    f.close()
-    
-    config['data']['files'] = ['$WELTER/data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)]
-    config['grid']['hdf5_path'] = '$WELTER/sf/m{:03d}/libraries/PHOENIX_IGRINS_m{:03d}.hdf5'.format(m,m)
-    lb, ub = int(np.floor(wls[0])), int(np.ceil(wls[-1]))
+    config['grid']['hdf5_path'] = '$WELTER/sf/m{:03d}/libraries/PHOENIX_IGRINS_m{:03d}_Teff2700-4500.hdf5'.format(m,m)
 
-    config['grid']['wl_range'] = [lb, ub]
-    config['PCA']['path'] = '$WELTER/sf/m{:03d}/PHOENIX_IGRINS_H_PCA.hdf5'.format(m)
-    config['name'] = 'LkCa4_m{:03d}'.format(m)
-    config['Comments'] = 'LkCa4 single order: m = {}, autogenerated config file.'.format(m)
-    config['data']['instruments'] =['IGRINS_H']
-    print("{:03d}: {:.0f}  -  {:.0f}   {}".format(m, wls[0], wls[-1], dat_name))
+    config['grid']['parrange'] = [[2700, 4500], [3.5, 4.0], [-0.5, 0.5]]
+    config['PCA']['path'] = '$WELTER/sf/m{:03d}/PHOENIX_IGRINS_H_PCA_Teff2700-4500.hdf5'.format(m)
+    print("{}".format(sf_out))
     
     os.makedirs(path_out, exist_ok=True)
     with open(sf_out, mode='w') as outfile:
         outfile.write(yaml.dump(config))
         print('wrote to {}'.format(path_out))
 
-for m in ms:
-    os.chdir("m{:03d}".format(m))
[…]

### 2016-07-12 code/batch_config.py
Previous commit contained an error.  This is the correct batch.

@@ -14,8 +14,9 @@ for m in ms:
 
     path_out = 'm{:03d}/'.format(m)
     sf_out = 'm{:03d}/config.yaml'.format(m)
-    
-    f = open("m112/config.yaml")
+
+    # Presuppose that the file exists...    
+    f = open("m{:03d}/config.yaml".format(m))
     config = yaml.load(f)
     f.close()
     

### 2016-07-12 document/ms.tex
Addressing limitations of assumptions in the methodology

@@
 
-Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} show the 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
+Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
 The red and blue lines show the hot photosphere and cool spot spectra respectively.
@@
 We then computed the weighted mean of the stellar parameter point statistics only for these effective temperatures and fill factors.
-We arrived at best fit values for the stellar parameters summarized in Table XY.
+We arrived at best fit values for the stellar parameters summarized in Table \ref{tbl_adopted_props}.
 We adopt these parameters as the stellar properties at the epoch of the IGRINS observations.
-We find a large filling factor of cool starspots, with a best value of $f=XX\pm yy$.
-\todo{Table of best fit parameters.}
+We find a large filling factor of cool starspots, with a best value of $f=75\pm 10 \% $.
+
+\input{tables/tbl_best_fit.tex}
 
@@
 
-\subsection{Interpretation of distribution of stellar properties}
-
 \subsection{Longitudinal / latitudinal spot distributions and phase}
@@
 \subsection{Addressing limitations of assumptions in the methodology}
+
+\emph{Number of photospheric components-}  Our full spectrum fitting method assumed \emph{only} two temperature components present in the photosphere.
+In reality, starspots are probably described by a range of effective temperatures like umbra, penumbra, and plages on the sun's surface.
+A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can.
+Computational infeasibility limited our ability to rerun new multi-temperature models and compute model comparison diagnostics like AIC, BIC, or cross validation \citep{2014sdmm.book.....I}.
+Such investigations could be considered in future works, but we suspect systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
+High-precision polychromatic planetary transit photometry could offer an avenue to measure the morphologies and temperatures of starspots for the subset of transiting exoplanet host stars.
+% The fact that we get consistent estimates for Teff tells us something.
+% The fits are pretty good, also tells us something.
+% Coarsely sampled models + spectral emulator acts as a smoother in Teff, as does the GP global covariance kernel.
+%(cite Charlotte Norris CS19 poster?)
+
+\emph{Suitability of pre-computed \PHOENIX model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX synthetic spectra are a good representation to our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
+Furthermore, cool sunspots are associated with heightened magnetic fields on the sun.
+Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.
+The former effect will differentially impact lines with high Lande-g factors (cite XX, fix the g formatting).
+The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants (cite XX Saar and collaborators).
+Our tacit assumption has been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures and 2) there exist many orders and lines that are not affected at all.
+We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
+Strong metal lines demonstrate large departures in their best fit $\Z$ due to Zeeman broadening.
+No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
+% Note that these two effects would differently affect the spectra
+
+We also assumed that the spectral pattern of metallicity can be captured by a single coarse metric, $\Z$.
+In reality, the low temperature starspot spectrum of \name could exhibit $\A \neq 0$, resulting in a greater amplitude of residual spectrum correlations, and/or biased estimates for other parameters.
+Our Gaussian process inference framework yields some resilence to the former problem.
+For the latter, nonzero $\A$ would only impact a subset of all lines, and only to at a magnitude of typical departures of $\A$ in the solar neighborhood.
+The large number of IGRINS orders and spectral lines offers us some resilience to isolated orders badly affected by spectral line outliers.
+
+\subsection{Interpretation of the large filling factor of cool starspots}
+
+\subsection{Is \name an extreme source?}
+
+\subsection{What would APOGEE have derived for this source with single temperature fitting?}
 

### 2016-07-15 document/ms.tex
Include or mark todos for comments from Greg Herczeg

@@
 
+\todo{Overhaul the introduction: 1. Move discussion about age spreads later,  2. }
+
 For a single presumably coeval stellar cluster, pre main-sequence HR diagrams exhibit large ($\delta t_{\ast} \sim t_{\ast}$) apparent spreads in age \citep[e.g.][]{2011A&A...534A..83R}.
 The cause of the large spread in pre main-sequence HR diagrams is controversial: some take it as evidence for intrinsic age spreads, some take it as evidence for non static accretion history \citep{2009ApJ...702L..27B, 2010ARA&A..48..581S}.
-
 Still others take the large apparent age spreads in pre main-sequence HR diagrams as evidence for the limited physics included in the pre main-sequence evolutionary model isochrones.
-Most modern evolutionary models do not yet include the effects of starspots or magnetic fields, despite observations betraying their presence, \emph{e.g.} optical monitoring and Zeeman doppler imaging \citep{2008A&A...479..827G,2014MNRAS.444.3220D}.
+Most modern evolutionary models do not yet include the effects of starspots or magnetic fields, despite observations revealing their presence, \emph{e.g.} optical monitoring and Zeeman doppler imaging \citep{2008A&A...479..827G,2014MNRAS.444.3220D}.
 
@@
 Sunspots are probably responsible for biases in stellar effective temperatures derived by different methods.
-For example, the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) measured effective temperatures for 3493 young stars finding offsets in $\teff$ of typically 200$-$500 K and as high as 1000 K compared to previous studies \citep{2014ApJ...794..125C}.
-Low resolution optical spectroscopy shows a typical spread of 200 K in the spectral type-to-effective-temperature conversion scale \citep{2014ApJ...786...97H}.
+For example, the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) measured effective temperatures for 3493 young stars finding offsets in $\teff$ of typically 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) compared to previous studies \citep{2014ApJ...794..125C}.
+Low resolution optical spectroscopy scales between that of \citet{2003ApJ...593.1093L} and those of \citet{2013ApJS..208....9P} and \citet{2014ApJ...786...97H}, showing about 200 K in the spectral type-to-effective-temperature conversion scale.
 These discrepancies in $\teff$ could be attributable to measurements of spectral features steming from patches of stellar photosphere with different effective temperatures than the bulk photosphere.
@@
 
+\comm{From GH regarding the next paragraph: Starspots (or magnetic activity, or whatever) doesn't cause a spread in ages/evolution.
+A \emph{range} in starspots may cause a \emph{range} in evolution, but that paper requires a sample.
+I think we can refer to this sort of thing, but we shouldn't focus on it.}
 Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses \citep{2015ApJ...807..174S}.
 The importance of starspots needs to be empirically evaluated to assess systematic biases of pre-main sequence stellar evolutionary models.
-%...develop this point more
 
-Modeling the periodic light curves of spotted stars can answer these questions: ``What evidence is there to support the existence of starspots?
-What joint constraint can be placed upon the effective temperature contrast and areal coverage of the starspots?
-What is the longitudinal asymmetry of the spots?''.
+\todo{Discuss limitations and capabilities of photometry alone: presence or absence of starspots, joint constraint on areal coverage and temperature, longitudinal asymmetry.}
 Cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots \citep{2012AJ....143....4H}.
@@
 
-By modeling the composite \emph{spectrum} of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.
+By modeling the composite spectrum of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.
 Spectroscopic modeling can still measure the starspot properties in pole-on stars, stars with longitudinally symmetric stars, and non-rotating stars.
 
-% Previous efforts to derive starspot properties via spectroscopy:
+\todo{Cite previous efforts to derive starspot properties via spectroscopy}
 
-%% Put in text here!
-
-In principle, more advanced questions could be asked about the properties of the spots: ``How many distinct spot groups are there?
+\todo{More advanced approaches to understanding stellar surface properties.
+How many distinct spot groups are there?
 Is there evidence for both hot spots and cool spots?
@@
 What is the distribution of effective temperature within a spot or spot group?
-What are the morphologies of the spots?''.
+What are the morphologies of the spots?}
+In principle, more advanced questions could be asked about the properties of the spots....
+
 Solving these questions would require a complex model comparison framework, combining all available data and lines of evidence from photometric, spectroscopic, and spectropolarimetric monitoring.
@@
 
-%\subsection{Previous studies of \name}
+\todo{Previous studies of \name}
 
@@
 
-The source has little or no accretion ($\log{\dot M} < 8.1$), no detection of mid-infrared nor mm excess, and no stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.
+The source has no detected accretion, no detection of mid-infrared nor mm excess, and no detected stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.
 This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.
-% These claims need references.
+\todo{These claims need references.}
 
@@
 
-The details of the methodology are contained in Appendix \ref{methods-details}.  Here we overview the salient concepts needed to follow the results and discussion.
+\iancze developed a modular framework to infer stellar properties from high resolution spectra.
+In this section, we describe how we extended this framework to include spots in a 2-temperature fit to spectra.
+Further details of this methodology are described in Appendix \ref{methods-details}.
 
@@
 The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
-We use the \PHOENIX~ model grid.
-After experimenting with the base model from \iancze, we made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
+We use the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest\citep{2013A&A...553A...6H}.
+\todo{Put in a hyperlink?} After experimenting with the base model from \iancze, we made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
 We discuss these two changes below.
 
+We assume the stellar photosphere is characterized as two photospheric components with different effective temperatures, $\teffa$ and $\teffb$, and scalar solid angular coverages $\Omega_a$ and $\Omega_b$, but sharing all the same intrinisic and extrinsic stellar parameters otherwise.
 Following and extending the notation of \iancze, we can write down the mixture model as:
@@
 \begin{eqnarray} \label{eqn:mix_M}
-\vM_{\mathrm{mix}}(\vT) = \vM(\teffa, ...) \times \Omega_a + \vM(\teffb, ...) \times \Omega_b
+\vM_{\mathrm{mix}} = \Omega_a \vM(\teffa)  + \Omega_b \vM(\teffb)
 \end{eqnarray}
 
-where $\vM$ is the pixel-level forward model of a spectrum, and we assume the stellar photosphere is characterized as two photospheric components with different effective temperatures, $\teff$ and solid angular coverages $\Omega$, but sharing all the same intrinisic and extrinsic stellar parameters otherwise.
 The observed filling factor of photosphere $b$ is simply the ratio:
@@
 The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
-There is no principled way to combine the $N_{\rm ord}$ sets of inferences on $\vT_{o}$, but there are ample heuristics like taking the weighted average of the $o$ sets of marginalized posterior distributions functions.
+We combine the $N_{\rm ord}$ sets of inferences on $\vT_{o}$ with heuristics like taking the weighted average of point estimates of parameter distributions of the most reliable subsets of orders.
+We assume that these lossy heuristics offer a regression to the mean with a large number of spectral orders.
 
@@
 \subsection{ESPaDOnS Spectroscopy}
-We combined our IGRINS spectroscopy with existing ESPaDOnS panchromatic optical echelle spectra to provide 88 spectral orders between 5100 and 25000 \AA \citep{2014MNRAS.444.3220D}.
-There are 12 spectra observed over the 13 days between JD 2456665.72 and 2456678.90.
+We retrieved twelve existing ESPaDOnS spectra from \citet{2014MNRAS.444.3220D}.
+\todo{Say some more about the spectra- what wavelength range used, chunking.}
 
@@
 
-There is a $\Delta \teff \sim 800$ K difference in the effective temperature derived at different wavelength intervals for the same stellar spectrum.
+The effective temperature derived at different wavelength intervals exhibit a $\Delta \teff \sim 800$ K spread.
 To put this level of effective temperature in context, authors using 4200 K and 3300 K values would conclude evolutionary model derived masses of XX or YY as shown in Figure XX.
@@
 \emph{Suitability of pre-computed \PHOENIX model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX synthetic spectra are a good representation to our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
-Furthermore, cool sunspots are associated with heightened magnetic fields on the sun.
+Cool sunspots are associated with heightened magnetic fields on the sun.
 Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.
@@
 
-\begin{tabular}{ r| p{5cm} | p{5cm} | }
-\multicolumn{1}{r}{}
- &  \multicolumn{1}{c}{Whole spectrum (Gibbs Sampling)}
- & \multicolumn{1}{c}{Order-by-order (emcee)} \\
-\cline{2-3}
-Single component photosphere & \citet{2015ApJ...812..128C}: Poor model for spotted stars & Sec. \ref{sec:approach12}- plausible evidence for starspots if $\teff$ varies with order \\
-\cline{2-3}
-Two component photosphere & \ref{sec:approach21}- Statistically principled inference on starspot properties given the whole spectrum.
-But strongly correlated dimensions impose challenge on MCMC tuning.
-& \ref{sec:approach22}- Multiple independent posteriors of starspot properties.
-But combining inferences is heuristic.
-\\
-\cline{2-3}
-\end{tabular}
+\todo{Simplify this discussion to what matters here.}
 

### 2016-07-15 document/ms.tex
Text contributed by Greg Herczeg by email on Friday July 15.

@@
 
-The previous sections established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
-In this section, we will demonstrate that this same model explains the broadband spectral energy distribution and flux-calibrated optical/near-IR spectra of LkCa 4.
-Periodic variability in photometry and spectral indices are reproduced by modest changes in the visible fraction of the hot spot.
+In the previous sections we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
+These results have testable predictions for the spectral energy distribution (SED) and rotational modulation of features of the SED.
 
-\subsection{Reproducing the Spectral Energy Distribution}
+% quantify the spot fraction versus rotation period, and then
 
-\subsection{Reproducing the flux-calibrated low resolution}
+In \S 4.1 we describe how the two components of the photosphere fit low resolution spectra and optical photometry.
+The spectral features and colors should change as the spot rotates around the star, so that the visible fraction of hot and cool spot changes.
+While the variability in optical brightness is well documented and motivatet this study, in \S 4.2-4.3 we convert the $V$ band brightness to a spot filling factor and then quantify spectroscopic and color variability caused by changes in the spot filling factor.
 
-Figure~\ref{fig:lores}...
+\begin{figure}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
+	\vspace{-100mm}
+	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+	\label{fig:lores}
+\end{figure}
 
-\subsection{TiO Variability}
+\subsection{The Spectral Energy Distribution}
 
-The depth of TiO and other molecular bands are a common diagnostic of spectral type (and temperature) in optical spectra.
-In the 12 ESPaDOnS spectra of \name\ obtained over 14 days \citep{2014MNRAS.444.3220D}, the depth of the TiO bands vary.
+Figure~\ref{fig:lores} shows that the two-component photosphere matches flux-calibrated spectra well from $\sim 6000-2.5$ $\mu$m.
+The two components have fixed temperatures of 4200 K covering 30\% of the visible surface and 3000 K covering 70\% of the visible surface area.
+The flux and extinction are then scaled to match the spectrum.
 
-Each of the TiO spectral index is correlated with the other indices.
-The line depths also correlate with the $V-$band magnitude, as estimated from the ASAS-SN photometry and the $V-$band photometry provided in \citep{2014MNRAS.444.3220D} that were obtained within 6 months of the ESPaDOnS observations.
+The value for the extinction depends on XXX...
 
-Needs a lot more.
+\subsection{Rotational modulation of the hot spot}
+
+Since 1992 the $V$ band brightness has varied from $12.3$ to $13.2$ mag, with a typical range of $0.5$ mag in any single epoch.
+In a two-temperature atmosphere, this brightness corresponds directly to a filling factor for both components.
+
+We model the rotational modulation of LkCa 4 in different photometric bands by fixing the two temperatures to 4200 and 3000 K and setting the 70\% covering fraction of the cool component to $V_{est}=12.85$, as estimated at the time of the IGRINS spectrum.
+The colors for the two components are obtained from the main sequence colors compiled by \citet{kenyon95}.
+The colors from dwarfs stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
+
+In these simple models, the blue emission is dominated by the hotter component, while both components contribute to the red and infrared emission.   
+The $0.5$ mag range in $V$-band brightness requires at least a factor of 1.6 change in the visible surface area of hot component.  Figure~\ref{fig:spotcolors} shows the
+
+\subsection{Rotational Modulation of TiO Depth}
+
+The depths of TiO and other molecular bands are common diagnostics of spectral type (and therefore temperature) in optical spectra \citep[e.g.][]{kirkpatrick91}.
+In a 2-temperature photosphere, the depth of observed TiO bands will depend on the fractional coverage of the components.
+In this subsection, we demonstrate that the TiO band depths vary with spot coverage.
+
+\citet{donati14} spectroscopically monitored LkCa 4 with 12 spectra obtained over 14 days, covering $\sim 4$ rotation periods.
+The top panel Figure~\ref{fig:tiovar} shows two of these spectra obtained at the estimated maximum and minimum optical brightness.
+Small but significant changes are seen in the TiO bands.
+The blue spectrum does not change.
+
+The TiO variability is quantified through TiO indices listed in Table~\ref{tab:tiO}.  The TiO indices are also combined into a single index by calculating by 
+calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.
+Both the raw TiO 7140 index and this combined TiO index correlate strongly with the optical brightness.
+In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).
+
+0 New
+
+Reply
+
+BundleData Science (9)
 

### 2016-07-15 code/batch_config.py
Redo the batch configurations for H-band

@@ -19,21 +19,30 @@ for m in ms:
     f = open("m{:03d}/config.yaml".format(m))
     config = yaml.load(f)
     f.close()
+
+    # Stellar parameters
+    config['Theta']['grid'] = [4250.0, 3.8, 0.0]
+    config['Theta']['teff2'] = 2900.0
+    config['Theta']['logOmega'] = -0.2
+    config['Theta']['logOmega2'] = -0.6
+    config['Theta']['vsini'] = 29.0
+    config['Theta']['vz'] = 11.0
+
+    config['Theta_jump']['grid'] = [3.0, 0.003, 0.001]
+    config['Theta_jump']['teff2'] = 3.0
+    config['Theta_jump']['logOmega'] = 0.003
+    config['Theta_jump']['logOmega2'] = 0.003
+    config['Theta_jump']['vsini'] = 0.05
+    config['Theta_jump']['vz'] = 0.05
+
+    config['Theta_priors'] = '$WELTER/code/priors/user_prior.py'
+    config['name'] = 'mix_emcee'
     
     config['grid']['hdf5_path'] = '$WELTER/sf/m{:03d}/libraries/PHOENIX_IGRINS_m{:03d}_Teff2700-4500.hdf5'.format(m,m)
-
     config['grid']['parrange'] = [[2700, 4500], [3.5, 4.0], [-0.5, 0.5]]
     config['PCA']['path'] = '$WELTER/sf/m{:03d}/PHOENIX_IGRINS_H_PCA_Teff2700-4500.hdf5'.format(m)
-    print("{}".format(sf_out))
-    
-    os.makedirs(path_out, exist_ok=True)
+
+    #os.makedirs(path_out, exist_ok=True)
     with open(sf_out, mode='w') as outfile:
         outfile.write(yaml.dump(config))
-        print('wrote to {}'.format(path_out))
-
-#for m in ms:
-    #os.chdir("m{:03d}".format(m))
-    #os.system('mkdir libraries &')
-    #os.system('grid.py --create > grid.out &')
-    #os.chdir("..")
-
+        print('wrote to {}'.format(sf_out))

### 2016-07-15 code/batch_mix_emcee.py

@@ -4,11 +4,10 @@ import yaml
 import numpy as np 
 import h5py
 
-ms = range(71, 96+1)
+#ms = range(71, 96+1)
+ms = range(98, 126)
 
 os.chdir(os.path.expandvars('$WELTER/sf/'))
-
-os.getcwd()
 
 for m in ms:
 
@@ -16,7 +15,7 @@ for m in ms:
     os.chdir(path_out)
     
     # Also initialize the nuissance parameter json file.
-    os.system('star.py -r 1')
-    os.chdir('output/mix_emcee/run01')
+    os.system('star.py -r 2')
+    os.chdir('output/mix_emcee/run02')
     os.system('star.py --initPhi')
     os.chdir(os.path.expandvars('$WELTER/sf/'))

### 2016-07-15 code/priors/user_prior.py
Add user defined lnprior that will be used in the mixture model

@@ -1,0 +1,21 @@
+import numpy as np
+
+def user_defined_lnprior(p):
+    '''
+    Takes a vector of stellar parameters and returns the ln prior.
+    '''
+    if not ( (p[11] > 0) and (p[6] < p[0]) ):
+    	return -np.inf
+    
+    # Solar metalicity to within +/- 0.05 dex
+    lnp_FeH = -p[2]**2/(2.0*0.05**2)
+    # Logg 3.8 to within +/- 0.1 dex, Donati+ 2014
+    lnp_logg = -(p[1] - 3.8)**2/(2.0*0.1**2)
+    # vsini of 29.0 +/- 5 from previous experiments
+    lnp_vsini = -(p[4] - 29.0)**2/(2.0*5.0**2)
+    # No prior on v_z.
+
+    ln_prior_out = lnp_FeH + lnp_logg + lnp_vsini
+
+    return ln_prior_out
+

### 2016-07-15 code/batch_grid_pca.py
Run the PCA and grid steps for H-band

@@ -4,12 +4,12 @@ import yaml
 import numpy as np 
 import h5py
 
-#ms = range(98, 125)
-ms = range(71, 96+1)
+ms = range(98, 126)
+#ms = range(71, 96+1)
 
 os.chdir(os.path.expandvars('$WELTER/sf/'))
 
-os.getcwd()
+#os.getcwd()
 
 for m in ms:
 

### 2016-07-18 document/ms_18jul_gjh.tex
Create ms_18jul_gjh.tex

--- 2016-07-15 document/ms.tex
@@
 %\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
-\documentclass[onecolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
+\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
 %\documentclass[12pt,preprint]{aastex}
@@
 
-\title{Measuring starspot properties by forward modeling IGRINS spectra of \name}
+\title{Placing the spotted T Tauri star LkCa 4 on an HR diagram}
 
@@
 
-\todo{Overhaul the introduction: 1. Move discussion about age spreads later,  2. }
+Pre-main sequence stellar evolution is an unsolved problem \citep[see review by][]{soderblom14}.
+Systematic uncertainties in ages of pre-main sequence stars lead to uncertainties in dissipation timescales of envelopes and protoplanetary disks as evaluated in global studies.
+All clusters have large spreads in luminosity at any given temperature \citep[e.g.][]{reggiani11}, which frustrates the interpretation of individual star/disk properties as related to age.
 
-For a single presumably coeval stellar cluster, pre main-sequence HR diagrams exhibit large ($\delta t_{\ast} \sim t_{\ast}$) apparent spreads in age \citep[e.g.][]{2011A&A...534A..83R}.
-The cause of the large spread in pre main-sequence HR diagrams is controversial: some take it as evidence for intrinsic age spreads, some take it as evidence for non static accretion history \citep{2009ApJ...702L..27B, 2010ARA&A..48..581S}.
-Still others take the large apparent age spreads in pre main-sequence HR diagrams as evidence for the limited physics included in the pre main-sequence evolutionary model isochrones.
-Most modern evolutionary models do not yet include the effects of starspots or magnetic fields, despite observations revealing their presence, \emph{e.g.} optical monitoring and Zeeman doppler imaging \citep{2008A&A...479..827G,2014MNRAS.444.3220D}.
+The causes of global age uncertainties and of large luminosity spreads in individual clusters are controversial.
+Observationally, \citet{hartmann01} and \citet{slesnick08} argue that measurement uncertainties may mask any real differences in ages within a cluster.
+In models, \citet{hartmann97} and \citet{baraffe09} describe how non-static accretion histories change the stellar contraction at early times.
+Contraction rates also depend on the prescription for convection, which may vary with mass.
 
-%\subsection{Previous studies of Starspots}
+Magnetic activity is a likely source of significant uncertainty in both the models and observations of young low-mass stars. 
+Convection at these young ages generate strong magnetic fields, as measured in Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}, which cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14}.
+Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (Somers et al.~2015, Feiden 2016; see also Baraffe et al.~2015 for an updated treatment of convection without introducing magnetic fields).
+Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses \citep{somers15}.
 
-Sunspots are probably responsible for biases in stellar effective temperatures derived by different methods.
-For example, the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) measured effective temperatures for 3493 young stars finding offsets in $\teff$ of typically 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) compared to previous studies \citep{2014ApJ...794..125C}.
-Low resolution optical spectroscopy scales between that of \citet{2003ApJ...593.1093L} and those of \citet{2013ApJS..208....9P} and \citet{2014ApJ...786...97H}, showing about 200 K in the spectral type-to-effective-temperature conversion scale.
-These discrepancies in $\teff$ could be attributable to measurements of spectral features steming from patches of stellar photosphere with different effective temperatures than the bulk photosphere.
-Single temperature photospheres are not realistic approximations for complex young photospheres possessing large areal coverage fractions of starspots.
+Starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
+For example, effective temperatures for 3493 young stars measured using the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) are offset by 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) relative to previous measurements, usually from optical \citep{cottaar14}.
+Jackson \& Jeffries 2014ab needs to go somewhere.
 
-\comm{From GH regarding the next paragraph: Starspots (or magnetic activity, or whatever) doesn't cause a spread in ages/evolution.
-A \emph{range} in starspots may cause a \emph{range} in evolution, but that paper requires a sample.
-I think we can refer to this sort of thing, but we shouldn't focus on it.}
-Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses \citep{2015ApJ...807..174S}.
-The importance of starspots needs to be empirically evaluated to assess systematic biases of pre-main sequence stellar evolutionary models.
+...The importance of starspots needs to be empirically evaluated to assess systematic biases of pre-main sequence stellar evolutionary models.
 
 \todo{Discuss limitations and capabilities of photometry alone: presence or absence of starspots, joint constraint on areal coverage and temperature, longitudinal asymmetry.}
-Cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots \citep{2012AJ....143....4H}.
+Cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots \citep{harrison12}.
 Photometric modeling of the light curve taken alone can only yield degenerate estimates in the temperature contrast and areal coverage fraction.
@@
 
-In this paper we characterize the starspot coverage and temperature contrast of \name using full spectrum fitting.
-We chose \name for its likelihood of large areal coverage of starspots, as evinced by large-amplitude photometric variability  detected in $BVRI$ bands.
-Its period is 3.37$\pm$0.01 days \citep{1993AJ....106.1608V,1994IBVS.4042....1G,grankin08,xiao12}.
+In this paper we characterize the starspot coverage and temperature contrast of \name by fitting photospheric models to high-resolution optical and near-IR spectra.
+We chose \name for its likelihood of large areal coverage of starspots, as seen in large-amplitude photometric variability  detected in $BVRI$ bands with a period is 3.37$\pm$0.01 days \citep{vrba93,grankin94,grankin08,xiao12}.
+Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{donati14}.
 
-Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{2014MNRAS.444.3220D}.  
 %This statement needs to be fact-checked, maybe some more supporting info.
 
-The source has no detected accretion, no detection of mid-infrared nor mm excess, and no detected stellar companion, so its spectrum should be devoid of complicating factors like near-IR excess veiling and accretion excess.
-This source is the ideal candidate for direct measurement of two-temperature photosphere due to starspots.
-\todo{These claims need references.}
+Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
+\name does not have any mid-IR or mm excess \citep[e.g.][]{furlan06}, is not actively accreting (ref?), and does not have any known companion (some Kraus?
+paper).
+The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
 
@@
 The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
-We use the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest\citep{2013A&A...553A...6H}.
+We use the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest\citep{husser13}.
 \todo{Put in a hyperlink?} After experimenting with the base model from \iancze, we made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
@@
 
-The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{2013PASP..125..306F}.
+The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{foreman13.
 The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
@@
 
-\section{Observations and data mining}\label{sec:obs}
+\section{Observations}\label{sec:obs}
 
 \subsection{IGRINS Spectroscopy}\label{sec:igrins} 
-We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{2014SPIE.9147E..1DP,2012SPIE.8450E..2SG} on the Harlan J.
+We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{park14,gully12} on the Harlan J.
 Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
@@
 \subsection{ESPaDOnS Spectroscopy}
-We retrieved twelve existing ESPaDOnS spectra from \citet{2014MNRAS.444.3220D}.
-\todo{Say some more about the spectra- what wavelength range used, chunking.}
+We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.
+These spectra cover 3900-10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.
+The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.
+In this paper we concentrate on the intensity spectrum.
 
-\subsection{Photometric monitoring from ASASSN and \citet{grankin08}}
+Chunking, estimate flux calibration...
 
-We retrieved $V-$band monitoring from the ASASSN survey \citep{2014ApJ...788...48S}.
-This data covered 2012 January - 2016 March.
-The 777 raw data points included near-contemporaneous measurements from repeated observations during the same visits, which lasted typically $<10$ minutes.
-We grouped datapoints by these visits yielding 186 data points, assigning a mean value and standard deviation when there was more than 1 observation per visit, enforcing a floor uncertainty of 0.01, the native quoted uncertainty of the data points.
+\subsection{Low-resolution optical and near-IR spectra}
+
+Palomar/DBSP \citep{herczeg14}
+
+APO/TripleSpec (Covey)
+
+\subsection{Photometric monitoring from ASAS-SN and \citet{grankin08}}
+
+We retrieved $V-$band monitoring from the ASAS-SN survey \citep{shappee14}, obtained from 2012 January -- 2016 March in 186 visits.
+We also retrieved optical photometry of \name\ obtained in 284 visits in $V$-band (278 with $B$ and 268 with $R$ from 1992 August - 2004 October \citep{grankin08}, and 10 additional $BVR$ epochs obtained by \citet{donati14}.
+Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{donati14}, and ASAS-SN $V-$band monitoring plotted over the interval 1992-2016.
+The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
+
+%The 777 raw data points included near-contemporaneous measurements from repeated observations during the same visits, which lasted typically $<10$ minutes.
+We group these near-simultaneous observations by assigning
+% datapoints by these visits yielding 186 data points, assigning a mean value and standard deviation when there was more than 1 observation per visit, enforcing a floor uncertainty of 0.01, the native quoted uncertainty of the data points.
 We assigned the native uncertainty of 0.01 when there was only a single observation per visit.
-
-We also retrieved $V-$band monitoring from \citet{grankin08} which covers 1992 August - 2004 October with 284 data points.
-Of those, 278 have $B-V$, 268 have $V-R$, and 18 have $U-B$.
-We also compiled the 10 additional $V-$band photometric data points provided in \citet{2014MNRAS.444.3220D}.
-
-Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{2014MNRAS.444.3220D}, and ASASSN $V-$band monitoring plotted over the interval 1992-2016.
-The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
 
@@
 Figure \ref{fig:PhotPhase} shows the phase-folded lightcurve of all available $V-$band data grouped by the 17 observing seasons.
-We folded the phase by a period $P=3.375$ days, which is the median position of the peaks of the multiterm ($M_{\rm max} = 4$) Lomb-Scargle periodogram derived separately from each of the 17 observing seasons \citep{2014sdmm.book.....I}.
+We folded the phase by a period $P=3.375$ days, which is the median position of the peaks of the multiterm ($M_{\rm max} = 4$) Lomb-Scargle periodogram derived separately from each of the 17 observing seasons \citep{ivezic14}.
 The standard deviation of the 17 periodogram peaks was 0.003 days.
 The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{2015ApJ...812...18V} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
 Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.
@@
 
-\section{Results}
+\section{FITS TO HIGH RESOLUTION SPECTRA}
+
+Provide overview of section...
 
@@
 This discrepancy is circumstantial evidence for the direct detection of spectral lines attributable to starspots.
-This circumstantial evidence should not be surprising given the previous evidence that \name possesses a large coverage fraction of starspots \citep{2014MNRAS.444.3220D}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase} and discussed previously by \citet{grankin08}.
+This circumstantial evidence should not be surprising given the previous evidence that \name possesses a large coverage fraction of starspots \citep{donati14}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase} and discussed previously by \citet{grankin08}.
 
@@
 The infrared spectrum will have a lower overall spot contast, but will have higher relative contribution attributable to the cool patches.
-This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{2008ApJ...687L.103P}.
+This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{prato08}.
 \comm{This blurb should probably go in the introduction.}
@@
 As noted previously, our full-spectrum fitting method offers little constraining power on $\logg$, and $\Z$ can be biased in the face of systematic spectral line outliers.
-We find a preference for values of $\logg$ on the high end of our search range, $3.5 <\logg <4.0$, finding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{2014MNRAS.444.3220D}.
+We find a preference for values of $\logg$ on the high end of our search range, $3.5 <\logg <4.0$, finding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{donati14}.
 For $\Z$ we find a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metalicity, while the shorter wavelength values prefer slightly sub-solar metalicity.
@@
 
-0 New
-
-Reply
-
-BundleData Science (9)
-
 \subsection{Phased colors}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
-	\vspace{-100mm}
-	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
-	\label{fig:lores}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/tiovar} 
+	\includegraphics[width=0.95\textwidth]{figures/lkca4_tio_forpaper} 
 	\vspace{-100mm}
@@
 
+\begin{table*}
+\begin{tabular}{lccccc}
+Method & $T_{eff}$ & $A_V$ & $M$ & $\log$ Age \\
+\hline
+Blue, high resolution & 4100 & 0.68 \\
+Low resolution optical & 3670 & 0.35 & \\
+\hline
+\multicolumn{5}{c}{Simulated}
+GAIA-ESO\\
+APOGEE \\
+\hline
+This work & 3525 & \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Placing LkCa 4 on an HR Diagram}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.95\textwidth]{lkca4_hrdiag}
+	\caption{Placeholder for HR Diagram Figure}
+	\label{fig:hrdiag}
+\end{figure}
+
+The spectrum of LkCa 4 is well reproduced by a cool component of $3000$ K covering 75\% of the surface and a $4200$ K component covering 25\% of the surface.
+The effective temperature of these two components is 3525 K, based on the average surface flux.
+Decreasing the cool spot size to 60\% would increase the effective temperature to 3670 K, while increasing the spot size to 85\% would decrease the effective temperature to 3370 K.
+{\bf GJH note:  holy crap!!!}  Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc based the parallax distance of the nearest Taurus member \citep{torres12}.
+
+This improved characterization of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
+However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models.
+This age is uncomfortably young.
+LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
+The inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection and slowing the contraction rate.
+
+Comparisons to other results (both real and simulated):  APOGEE, GAIA-ESO,
+
 \subsection{Longitudinal / latitudinal spot distributions and phase}
@@
 A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can.
-Computational infeasibility limited our ability to rerun new multi-temperature models and compute model comparison diagnostics like AIC, BIC, or cross validation \citep{2014sdmm.book.....I}.
+Computational infeasibility limited our ability to rerun new multi-temperature models and compute model comparison diagnostics like AIC, BIC, or cross validation \citep{ivezic14}.
 Such investigations could be considered in future works, but we suspect systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
@@
 
-\subsection{What would APOGEE have derived for this source with single temperature fitting?}
+\clearpage
+\pagebreak
 
@@
 
-We adopted and extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{2015ApJ...812..128C}.
+We adopted and extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{czekala15}.
 We briefly summarize the model here for carity of notation, but see \iancze for more details.
@@
 The $\vt_{\ast}$ are comprised of the dimensions of the pre-computed stellar model grid.
-We use the \PHOENIX model grid \citep{2013A&A...553A...6H}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
+We use the \PHOENIX model grid \citep{husser13}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
 
@@
 What We Actually Did was linearly interpolate between the model grid-points.
-Interpolation can cause pile-up near model grid-points, as noted in \citet{2014ApJ...794..125C}, which motivated the spectral emulation procedure in \iancze.
+Interpolation can cause pile-up near model grid-points, as noted in \citet{cottaar14}, which motivated the spectral emulation procedure in \iancze.
 We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable in the distribution of samples in the starspot areal coverage fraction $c$.
@@
 It is a weak-lined \emph{T-Tauri} star.
-It exhibits a 3.36-3.37 day period \citep{1993AJ....106.1608V,1994IBVS.4042....1G}, as evinced by photometric monitoring in $BVRI$ bands.
+It exhibits a 3.36-3.37 day period \citep{vrba93,grankin94}, as seen in photometric monitoring in $BVRI$ bands.
 No periodic signal is detected at $U-$band.
-Section 5 of \citet{1993AJ....106.1608V}, ``More on the nature of CTT and WTT spots'' goes into detail about the whether the photometric variability is attributable to hot or cold patches.
-\name has no detected M-type-or-earlier binary companion down to $0.13''$ \citep{1993A&A...278..129L}.
-\name demonstrates variability in X-rays with ROSAT \citep{1994ApJ...424..237S}, with $L_{x}=2.4$ ergs/s.
+Section 5 of \citet{vrba93}, ``More on the nature of CTT and WTT spots'' goes into detail about the whether the photometric variability is attributable to hot or cold patches.
+\name has no detected M-type-or-earlier binary companion down to $0.13''$ (Kraus, plus Nguyen for SBs?).
+\name demonstrates variability in X-rays with ROSAT \citep{strom94}, with $L_{x}=2.4$ ergs/s.
 
@@
 \acknowledgements
-The authors thank Gregory N. Mace and Kyle Kaplan for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.
+The authors thank Gregory N. Mace and Kyle Kaplan for carrying out the IGRINS observations.
+
+MG-S and GJH are supported by general grant 11473005 awarded by the National
+Science Foundation of China.
+The ESPaDOnS observations are supported by the contribution to the MATYSSE Large Project on CFHT obtained  through the Telescope Access Program (TAP), which has been funded by the ``the Strategic Priority Research Program---The Emergence of Cosmological Structures'' of the Chinese Academy of Sciences (Grant No.11 XDB09000000) and the Special Fund for Astronomy from the Ministry of Finance.
+
+This research has made use of NASA's Astrophysics Data System.
 
@@
 \bibliographystyle{apj}
-\bibliography{ms}
+\bibliography{msv1}
 

### 2016-07-21 document/ms.tex
Edits from Greg Herczeg now directly included in main manuscript

@@
 
-The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{2013PASP..125..306F}.
+The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{foreman13}.
 The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
@@
 
-\begin{figure}
+\begin{figure*}
+    	\vspace{-60mm}
 	\centering
@@
 	\label{fig:lores}
-\end{figure}
+\end{figure*}
 
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
-	\vspace{-100mm}
-	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
-	\label{fig:lores}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/tiovar} 
-	\vspace{-100mm}
+	\vspace{-60mm}
+	\includegraphics[width=0.95\textwidth]{figures/lkca4_tio_forpaper} 
+    	\vspace{-30mm}
 	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
@@
 
+\begin{table}
+\begin{tabular}{lccccc}
+Method & $T_{eff}$ & $A_V$ & $M$ & $\log$ Age \\
+\hline
+Blue, high resolution & 4100 & 0.68 \\
+Low resolution optical & 3670 & 0.35 & \\
+\hline
+\multicolumn{5}{c}{Simulated}
+GAIA-ESO\\
+APOGEE \\
+\hline
+This work & 3525 & \\
+\hline
+\end{tabular}
+\end{table}
+
+\subsection{Placing LkCa 4 on an HR Diagram}
+
+\begin{figure}
+	\centering
+    	\vspace{-30mm}
+	\includegraphics[width=0.95\textwidth]{figures/lkca4_hrdiag}
+    	\vspace{-30mm}
+	\caption{Placeholder for HR Diagram Figure}
+	\label{fig:hrdiag}
+\end{figure}
+
+The spectrum of LkCa 4 is well reproduced by a cool component of $3000$ K covering 75\% of the surface and a $4200$ K component covering 25\% of the surface.
+The effective temperature of these two components is 3525 K, based on the average surface flux.
+Decreasing the cool spot size to 60\% would increase the effective temperature to 3670 K, while increasing the spot size to 85\% would decrease the effective temperature to 3370 K.
+{\bf GJH note:  holy crap!!!}  Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc based the parallax distance of the nearest Taurus member \citep{torres12}.
+
+This improved characterization of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
+However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models.
+This age is uncomfortably young.
+LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
+The inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection and slowing the contraction rate.
+
+Comparisons to other results (both real and simulated):  APOGEE, GAIA-ESO,
+
 \subsection{Longitudinal / latitudinal spot distributions and phase}

### 2016-07-21 code/priors/user_prior.py
User defined lnprior for constraining logg and [Fe/H] during MCMC sampling

@@ -1,5 +1,3 @@
-import numpy as np
-
 def user_defined_lnprior(p):
     '''
     Takes a vector of stellar parameters and returns the ln prior.

### 2016-07-21 document/ms.tex
Some residual comments from GJH draft

@@
 The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
-We use the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest\citep{husser13}.
-\todo{Put in a hyperlink?} After experimenting with the base model from \iancze, we made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
+We use the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
+\todo{Put in a hyperlink?} We made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
 We discuss these two changes below.
@@
 \begin{eqnarray} \label{eqn:mix_M}
-\vM_{\mathrm{mix}} = \Omega_a \vM(\teffa)  + \Omega_b \vM(\teffb)
+\f_{\mathrm{mix}} = \Omega_a f(\teffa)  + \Omega_b f(\teffb)
 \end{eqnarray}
 
-The observed filling factor of photosphere $b$ is simply the ratio:
+The observed filling factor of photosphere $c$ is simply the ratio:
 
 \begin{eqnarray} \label{eqn:fill_factor}
-f = \frac{\Omega_b}{\Omega_a + \Omega_b}
+c = \frac{\Omega_b}{\Omega_a + \Omega_b}
 \end{eqnarray}
 
-The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \cite{foreman13}.
+The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
 The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
@@
 We retrieved $V-$band monitoring from the ASAS-SN survey \citep{shappee14}, obtained from 2012 January -- 2016 March in 186 visits.
-We also retrieved optical photometry of \name\ obtained in 284 visits in $V$-band (278 with $B$ and 268 with $R$ from 1992 August - 2004 October \citep{grankin08}, and 10 additional $BVR$ epochs obtained by \citet{donati14}.
+We also retrieved optical photometry of \name\ obtained in 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 additional $BVR$ epochs obtained by \citet{donati14}.
 Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{donati14}, and ASAS-SN $V-$band monitoring plotted over the interval 1992-2016.
 The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
-
-%The 777 raw data points included near-contemporaneous measurements from repeated observations during the same visits, which lasted typically $<10$ minutes.
-We group these near-simultaneous observations by assigning
-% datapoints by these visits yielding 186 data points, assigning a mean value and standard deviation when there was more than 1 observation per visit, enforcing a floor uncertainty of 0.01, the native quoted uncertainty of the data points.
-We assigned the native uncertainty of 0.01 when there was only a single observation per visit.
 
@@
 
-Figure \ref{fig:PhotPhase} shows the phase-folded lightcurve of all available $V-$band data grouped by the 17 observing seasons.
-We folded the phase by a period $P=3.375$ days, which is the median position of the peaks of the multiterm ($M_{\rm max} = 4$) Lomb-Scargle periodogram derived separately from each of the 17 observing seasons \citep{ivezic14}.
-The standard deviation of the 17 periodogram peaks was 0.003 days.
+Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 17 observing seasons and phase-folded by period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
 The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-We estimated $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+We estimate $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
 Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.

### 2016-07-23 document/ms.tex
Reformat tables and figures with full-page width asterisks, add content to introduction

@@
 Convection at these young ages generate strong magnetic fields, as measured in Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}, which cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14}.
-Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (Somers et al.~2015, Feiden 2016; see also Baraffe et al.~2015 for an updated treatment of convection without introducing magnetic fields).
+Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (\citet{somers15}, \citet{feiden16}; see also \citet{baraffe15} for an updated treatment of convection without introducing magnetic fields).
 Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses \citep{somers15}.
@@
 For example, effective temperatures for 3493 young stars measured using the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) are offset by 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) relative to previous measurements, usually from optical \citep{cottaar14}.
-Jackson \& Jeffries 2014ab needs to go somewhere.
 
-...The importance of starspots needs to be empirically evaluated to assess systematic biases of pre-main sequence stellar evolutionary models.
+%Jackson \& Jeffries 2014ab needs to go somewhere.
+
+Starspots have recently been observed with few parts per million photometric precision from monitoring surveys targeting exoplanet transits (Harrison, Davenport, etc.).
+Contemporaneous or near-contemporaneous panchromatic photometric monitoring (Grankin, etc.) can break the degeneracy between starspot areal filling factor and starspot temperature.
+Photometric measurements are limited to detecting the largest longitudinally asymmetric starspots.
+Transiting planets or eclipsing binaries passing in front of starspots (cite XX) can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.
+Zeeman Doppler Imaging (ZDI, cite XX) suffers from the same longitudinally-asymmetric limitation as photometry, but yields information on the latitudinal distribution of starspots.
+All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g.
+bands), or stars with an isotropic distribution of small starspots.
+
+Spectroscopic strategies have the power to measure both the average areal coverage and the area-weighted average starspot temperature contrast in any geometric configuration.
+At low resolution, SED modeling (Wolk and Walker) has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).
+At high resolution, line depth ratio analysis (Neff, etc) has historically been demonstrated in isolated regions of spectrum, namely the TiO bands (cite O'Neal, Neff, etc), OH 1.5 micron feature (O'Neal, etc.), and others.
+
+The WTTS \name is an ideal exemplar for a spotted pre-MS star because it has no close companion (cite Kraus, etc.), demonstrates large amplitude sinusoidal photometric variability indicative of spots (cite Grankin), has recently been examined with ZDI (cite Donati), and has large (dTeff~500 K) disagreement about its effective temperature (cite Herczeg and Hillenbrand).
+In this work we constrain the starspot properties of \name with 4 complementary techniques.
+Section 2 and Appendix YY describe a spectral inference technique aimed at generalizing line depth ratio analysis.
+Section 3 applies the spectral inference technique to a high resolution panchromatic near-IR spectrum of \name.
+Sections 4.1, 4.2, and 4.3 show results from polychromatic photometric monitoring analysis, SED fitting, and optical TiO line-depth ratio fitting.
+All lines of evidence are ultimately combined to build a (in?)harmonious picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
 
@@
 \begin{eqnarray} \label{eqn:mix_M}
-\f_{\mathrm{mix}} = \Omega_a f(\teffa)  + \Omega_b f(\teffb)
+f_{\mathrm{mix}} = \Omega_a f(\teffa)  + \Omega_b f(\teffb)
 \end{eqnarray}
@@
 \begin{figure*}
-    	\vspace{-60mm}
+    	%\vspace{-60mm}
 	\centering
 	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
-	\vspace{-100mm}
+	%\vspace{-100mm}
 	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
@@
 	\centering
-	\vspace{-60mm}
+	%\vspace{-60mm}
 	\includegraphics[width=0.95\textwidth]{figures/lkca4_tio_forpaper} 
-    	\vspace{-30mm}
+    %	\vspace{-30mm}
 	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
-    	\vspace{-30mm}
+    %	\vspace{-30mm}
 	\includegraphics[width=0.95\textwidth]{figures/lkca4_hrdiag}
-    	\vspace{-30mm}
+    %	\vspace{-30mm}
 	\caption{Placeholder for HR Diagram Figure}
 	\label{fig:hrdiag}
-\end{figure}
+\end{figure*}
 

### 2016-07-23 document/ms.tex
Overhual the introduction, still in progress, add references

@@
 
-%Jackson \& Jeffries 2014ab needs to go somewhere.
+% Theory of starspots
+% Jackson \& Jeffries 2014ab needs to go somewhere.
 
-Starspots have recently been observed with few parts per million photometric precision from monitoring surveys targeting exoplanet transits (Harrison, Davenport, etc.).
-Contemporaneous or near-contemporaneous panchromatic photometric monitoring (Grankin, etc.) can break the degeneracy between starspot areal filling factor and starspot temperature.
+Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep{harrison11,davenport15}.
+Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{bouvier95,grankin07} can break the degeneracy between starspot areal filling factor and starspot temperature.
 Photometric measurements are limited to detecting the largest longitudinally asymmetric starspots.
-Transiting planets or eclipsing binaries passing in front of starspots (cite XX) can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.
-Zeeman Doppler Imaging (ZDI, cite XX) suffers from the same longitudinally-asymmetric limitation as photometry, but yields information on the latitudinal distribution of starspots.
+Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.
+Zeeman Doppler Imaging (ZDI, \emph{e.g.} \citet{donati14}) suffers from the same longitudinally-asymmetric limitation as photometry, but yields information on the latitudinal distribution of starspots.
 All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g.
@@
 
-Spectroscopic strategies have the power to measure both the average areal coverage and the area-weighted average starspot temperature contrast in any geometric configuration.
-At low resolution, SED modeling (Wolk and Walker) has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).
-At high resolution, line depth ratio analysis (Neff, etc) has historically been demonstrated in isolated regions of spectrum, namely the TiO bands (cite O'Neal, Neff, etc), OH 1.5 micron feature (O'Neal, etc.), and others.
+Spectroscopic strategies have the power to measure both the starspot areal coverage and temperature in any geometric configuration.
+At low resolution, SED modeling \citep{wolk96} has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).
+At high resolution, line depth ratio analysis has historically been demonstrated in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
 

### 2016-07-23 document/ms.tex
Add copious references to the previous studies of LkCa4 paragraph of the introduction, maybe too many references.

@@
 Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.
-Zeeman Doppler Imaging (ZDI, \emph{e.g.} \citet{donati14}) suffers from the same longitudinally-asymmetric limitation as photometry, but yields information on the latitudinal distribution of starspots.
+Zeeman Doppler Imaging (ZDI, \emph{e.g.} \citet{donati14}) suffers from the same longitudinal asymmetry limitation as photometry, but can yield information on the latitudinal distribution of starspots.
 All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g.
@@
 
-The WTTS \name is an ideal exemplar for a spotted pre-MS star because it has no close companion (cite Kraus, etc.), demonstrates large amplitude sinusoidal photometric variability indicative of spots (cite Grankin), has recently been examined with ZDI (cite Donati), and has large (dTeff~500 K) disagreement about its effective temperature (cite Herczeg and Hillenbrand).
+Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
+The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep{hartigan95,kenyon98,edwards06,cauley12,yang12,ardila13,castro13,loyd14,martinez15}, has no evidence for a close companion \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11}}, demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}, has recently been examined with ZDI \citep{donati14}, and has large ($\delta \teff \sim$500 K) disagreement about its effective temperature \citep{herczeg14}.
+The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
+
 In this work we constrain the starspot properties of \name with 4 complementary techniques.
@@
 Section 3 applies the spectral inference technique to a high resolution panchromatic near-IR spectrum of \name.
-Sections 4.1, 4.2, and 4.3 show results from polychromatic photometric monitoring analysis, SED fitting, and optical TiO line-depth ratio fitting.
-All lines of evidence are ultimately combined to build a (in?)harmonious picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
-
-\todo{Discuss limitations and capabilities of photometry alone: presence or absence of starspots, joint constraint on areal coverage and temperature, longitudinal asymmetry.}
-Cyclical light curve variations indicate only the longitudinally asymmetric component of the star spots \citep{harrison12}.
-Photometric modeling of the light curve taken alone can only yield degenerate estimates in the temperature contrast and areal coverage fraction.
-A star possessing longitudinally symmetric distribution of starspots, or a pole-on star with a single spot, or a non-rotating (or very slowly rotating) star would all show zero or secular amplitude of photometric variability, yet they all contain star spots.
-
-By modeling the composite spectrum of a spotted star, it is possible to directly measure the collective areal coverage and effective temperature contrast.
-Spectroscopic modeling can still measure the starspot properties in pole-on stars, stars with longitudinally symmetric stars, and non-rotating stars.
-
-\todo{Cite previous efforts to derive starspot properties via spectroscopy}
-
-\todo{More advanced approaches to understanding stellar surface properties.
-How many distinct spot groups are there?
-Is there evidence for both hot spots and cool spots?
-What is the longitudinal distribution of the spots?
-What is the (co-)latitudinal distribution of the spots?
-What is the distribution of effective temperature within a spot or spot group?
-What are the morphologies of the spots?}
-In principle, more advanced questions could be asked about the properties of the spots....
-
-Solving these questions would require a complex model comparison framework, combining all available data and lines of evidence from photometric, spectroscopic, and spectropolarimetric monitoring.
-We seek to answer the much easier questions about the aggregate properties of the stellar photosphere, assuming the star is well described by two distinct photospheric components.
-
-\todo{Previous studies of \name}
-
-In this paper we characterize the starspot coverage and temperature contrast of \name by fitting photospheric models to high-resolution optical and near-IR spectra.
-We chose \name for its likelihood of large areal coverage of starspots, as seen in large-amplitude photometric variability  detected in $BVRI$ bands with a period is 3.37$\pm$0.01 days \citep{vrba93,grankin94,grankin08,xiao12}.
-Recent optical spectro-polarimetry showed evidence for hot or cool starspots covering an estimated $25\%$ of the stellar surface \citep{donati14}.
-
-%This statement needs to be fact-checked, maybe some more supporting info.
-
-Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
-\name does not have any mid-IR or mm excess \citep[e.g.][]{furlan06}, is not actively accreting (ref?), and does not have any known companion (some Kraus?
-paper).
-The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
-
-We extend a new spectral forward modeling framework to include two-temperature photosphere models.
-We demonstrate the constraining power of full spectrum fitting with panchromatic optical and near-IR echelle spectroscopy.
-% Consider putting in Section references here
+Sections 4.1, 4.2, and 4.3 show results from polychromatic photometric monitoring, SED fitting, and optical TiO line-depth ratio fitting.
+All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
 

### 2016-07-25 document/ms.tex
Some edits through the results sections, trim some extraneous paragraphs

@@
 
-\newcommand{\iancze}{{\sc C15 }}
+\newcommand{\iancze}{{\sc C15}}
 
@@
 Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{bouvier95,grankin07} can break the degeneracy between starspot areal filling factor and starspot temperature.
-Photometric measurements are limited to detecting the largest longitudinally asymmetric starspots.
+Photometric measurements are limited to detecting large longitudinally asymmetric starspots.
 Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.
-Zeeman Doppler Imaging (ZDI, \emph{e.g.} \citet{donati14}) suffers from the same longitudinal asymmetry limitation as photometry, but can yield information on the latitudinal distribution of starspots.
-All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots (e.g.
-bands), or stars with an isotropic distribution of small starspots.
+Zeeman Doppler Imaging \citep[ZDI]{donati14} suffers from the same longitudinal asymmetry limitation as photometry, but can yield information on the latitudinal distribution of starspots.
+All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots, or stars with an isotropic distribution of small starspots.
 
@@
 At low resolution, SED modeling \citep{wolk96} has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).
-At high resolution, line depth ratio analysis has historically been demonstrated in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
+At high resolution, line depth ratio analysis has historically been demonstrated on evolved stars in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
 
@@
 In this work we constrain the starspot properties of \name with 4 complementary techniques.
-Section 2 and Appendix YY describe a spectral inference technique aimed at generalizing line depth ratio analysis.
+Section 2 and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis.
 Section 3 applies the spectral inference technique to a high resolution panchromatic near-IR spectrum of \name.
@@
 
-\iancze developed a modular framework to infer stellar properties from high resolution spectra.
-In this section, we describe how we extended this framework to include spots in a 2-temperature fit to spectra.
-Further details of this methodology are described in Appendix \ref{methods-details}.
+\citet[hereafter \iancze]{czekala15} developed a modular framework\footnote{The open source codebase and its full revision history is available at \url{https://github.com/iancze/Starfish}.
+The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}} to infer stellar properties from high resolution spectra.
+The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
+We employed the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
+The modular framework was altered to accommodate starspot measurements in two ways.
+First, the single photospheric component was updated to includes a starspot spectrum.
+Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added in the starspot model.
 
-We experimented with several extensions to the modular framework for spectral inference described in \iancze \footnote{The open source codebase and its full revision history is available at https://github.com/iancze/Starfish.
-The experimental fork discussed in this paper is at https://github.com/gully/Starfish}.
-The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
-We use the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
-\todo{Put in a hyperlink?} We made two principal changes to the modular framework: 1) the introduction of a starspot mixture model characterized by a second $\teff$ and areal fill factor $f$, and 2) the switch from Gibbs sampling to ensemble sampling with chunking by spectral order.
-We discuss these two changes below.
-
-We assume the stellar photosphere is characterized as two photospheric components with different effective temperatures, $\teffa$ and $\teffb$, and scalar solid angular coverages $\Omega_a$ and $\Omega_b$, but sharing all the same intrinisic and extrinsic stellar parameters otherwise.
-Following and extending the notation of \iancze, we can write down the mixture model as:
+The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_b$ and $\Omega_a$, respectively.
+Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, and they share the same average intrinisic and extrinsic stellar parameters otherwise; that is $(\vsini, \logg, \Z, v_z)$ are indentical for starspots and ambient photosphere.
+The composite mixture model for observed flux density can be written down as:
 
@@
 
-The observed filling factor of photosphere $c$ is simply the ratio:
+The observed filling factor of starspots $c$ is simply the ratio:
 
@@
 
-The second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
-The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations expected among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
-The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
+The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $c$.
+The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degnerate over small changes in effective temperature.
+So the second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
+The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
+The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
 We combine the $N_{\rm ord}$ sets of inferences on $\vT_{o}$ with heuristics like taking the weighted average of point estimates of parameter distributions of the most reliable subsets of orders.
-We assume that these lossy heuristics offer a regression to the mean with a large number of spectral orders.
+These lossy heuristics should regress to the mean with a large number of spectral orders, assuming each order delivers unbiased estimates of stellar parameters.
+
+Further details of the spectral inference methodology are described in Appendix \ref{methods-details}.
 
@@
 \subsection{IGRINS Spectroscopy}\label{sec:igrins} 
-We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{park14,gully12} on the Harlan J.
+We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{gully12,park14} on the Harlan J.
 Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
 IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
-The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-band$.
+The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band.
 The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.
-We performed telluric correction by dividing the spectrum of \name by an A0V star observed near-contemporaneously at similar air-mass.
+Telluric correction was performed by dividing the spectrum of \name by a spectrum of HR 1237, an A0V star observed immediately before \name, both at airmass 1.1.
 The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of \name.
 No effort was made to remove these flux excesses, which affect several spectral orders.
-%List the spectral orders these lines affect.
 
@@
 We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.
-These spectra cover 3900-10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.
+These spectra cover 3900$-$10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.
 The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.
 In this paper we concentrate on the intensity spectrum.
-
-Chunking, estimate flux calibration...
+We apportioned the spectrum into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
+\todo{Flux calibration?}
 
@@
 We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth spectrum from Table \ref{tbl_estimated_V}.
-We chunked the spectrum into a subset of $N_{ord}=$26 spectral orders and performed full-spectrum fitting separately on each of these 26 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
-We employed the \PHOENIX model grid with a search range of $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and $\teff \in [3500, 4200]$ and trained a spectral emulator as described in \iancze.
+Full-spectrum fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
+The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and $\teff \in [3500, 4200]$.
 
-We tuned the Metropolis-Hasting step sizes with several iterations of burn-in procedure and visually checked the final chains for convergence.
-Our number of samples was generally much longer than the estimated integrated autocorrelation length.
-We spot-checked full-spectrum fits in comparison with the observed spectrum, finding modest agreement with the exception of spectral line outliers.
+The Metropolis-Hastings step sizes were tuned with several iterations of burn-in procedure and the final chains were visually checked for convergence.
+Nine of the 35 available spectral orders failed to converge, possibly due to numerical artifacts arising from poor model fits.
+For the other 26 spectral orders, the number of samples was generally much longer than the estimated integrated autocorrelation length.
+Overlays of models with observed spectra show modest agreement, with the exception of conspicuous spectral line outliers.
 No attempt was made to downweight spectral-line outliers as described in \iancze.
-We attempted fits to 9 more of the 35 spectral orders available for this ESPaDoNs spectrum, but the MCMC computations for these orders failed to converge, possibly due to numerical artifacts arising from poor model fits.
 
@@
 Meanwhile, strong metal lines can bias estimates of $\Z$ at the expense of estimates for $\teff$.
-We get consistent estimates for\footnote{Note, $v_z$ is an uncorrected recessional velocity, not a proper radial velocity} $v_z \sim 15.6 \pm 0.6$ km/s and $\vsini \sim 28.0 \pm 0.9$ km/s, with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$.
+We get consistent estimates for $v_z \sim 15.6 \pm 0.6$ km/s and $\vsini \sim 28.0 \pm 0.9$ km/s, with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$.
 These two outlying spectral orders converged to unreasonably large values for $\vsini$ and $a_{\rm G}$, the amplitude of the Gaussian process covariance kernel.
@@
 The more-well-behaved spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
-Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each of the 26 spectral orders for the subset of ESPaDoNs orders that received full-spectrum fitting.
+Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each of the 26 spectral orders.
 
@@
 The effective temperature derived at different wavelength intervals exhibit a $\Delta \teff \sim 800$ K spread.
-To put this level of effective temperature in context, authors using 4200 K and 3300 K values would conclude evolutionary model derived masses of XX or YY as shown in Figure XX.
-\todo{Put in the numbers and HR diagram figure here.}
+No single temperature can describe all the spectral lines present in the high resolution optical and IR spectra.
+This discrepancy is circumstantial evidence for the detection of spectral lines attributable to starspots.
+This circumstantial evidence should not be surprising given the previous evidence that \name possesses a large coverage fraction of starspots \citep{grankin08,donati14}.
 
-It is clear that the single-temperature model is a poor fit to the data.
-Our model assumptions were incorrect: no single temperature can describe all the spectral lines present in the spectra.
-This discrepancy is circumstantial evidence for the direct detection of spectral lines attributable to starspots.
-This circumstantial evidence should not be surprising given the previous evidence that \name possesses a large coverage fraction of starspots \citep{donati14}, along with its large amplitude of photometric variations, as shown in Figure \ref{fig:PhotPhase} and discussed previously by \citet{grankin08}.
-
-We performed a further plausibility check to constrain the effect size of starspots.
+%We performed a further plausibility check to constrain the effect size of starspots.
 We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.
@@
 We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters our full-spectrum fitting procedure would na\"{\i}vely derive.
-\comm{I don't think I ever put together a figure for this, should we just skip it?  I think so.}
 
@@
 These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
-If we assume the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, we can derive the result that the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
+Assuming the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
 The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.
 
-We can understand the heightened sensitivity to starspot spectral lines as wavelength increases in the following way.
+The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
 The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission, according to Wein's displacement law.
-So the ratio of flux density between starspot and bulk photosphere as a function of wavelength will generally increase with wavelength until it assymptotes to a fixed value in the Rayleigh-Jeans tail.
-In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
+So the ratio of flux density between starspot and bulk photosphere as a function of wavelength will generally increase with wavelength until it assymptotes to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
+
+%In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
 The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K, solar metalicity, and $\logg=3.5$.
 The flux density ratio is the flux per solid angle, so the delivered flux ratio for a finite sized starspot will depend on the (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.
-
-\todo{Put in the flux density ratio plot.}
+%\todo{Put in the flux density ratio plot.}
 

### 2016-07-25 document/ms.tex
Overhaul the results from IGRINS data and clean up some errors in the text.

@@
 Section 3 applies the spectral inference technique to a high resolution panchromatic near-IR spectrum of \name.
-Sections 4.1, 4.2, and 4.3 show results from polychromatic photometric monitoring, SED fitting, and optical TiO line-depth ratio fitting.
+Sections 5.1, 5.2, and 5.3 show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
 All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
@@
 The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_b$ and $\Omega_a$, respectively.
-Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, and they share the same average intrinisic and extrinsic stellar parameters otherwise; that is $(\vsini, \logg, \Z, v_z)$ are indentical for starspots and ambient photosphere.
+Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, and they share the same average intrinsic and extrinsic stellar parameters otherwise; that is $(\vsini, \logg, \Z, v_z)$ are identical for starspots and ambient photosphere.
 The composite mixture model for observed flux density can be written down as:
@@
 The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $c$.
-The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degnerate over small changes in effective temperature.
+The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in effective temperature.
 So the second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
 The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
-The practical effect of this switch is that we obtain unique stellar parameter estimates $\vT_{o}$ for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
-We combine the $N_{\rm ord}$ sets of inferences on $\vT_{o}$ with heuristics like taking the weighted average of point estimates of parameter distributions of the most reliable subsets of orders.
-These lossy heuristics should regress to the mean with a large number of spectral orders, assuming each order delivers unbiased estimates of stellar parameters.
+The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order.
+So stellar parameter estimates $\vT_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
+The $N_{\rm ord}$ sets of inferences on $\vT_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or clear model mismatches.
+This process can be thought of as a course approximation to the much more sophisticated spectral line outlier rejection described in \iancze.
 
@@
 
-Provide overview of section...
+\todo{Provide overview of section...}
 
@@
 The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
-The effective temperature of a starspot is, by definition, cooler than its surrounding photosphere, and will therefore have a longer wavelength of peak emission, according to Wein's displacement law.
-So the ratio of flux density between starspot and bulk photosphere as a function of wavelength will generally increase with wavelength until it assymptotes to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
+Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission, according to Wein's displacement law.
+The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
 
@@
 %\todo{Put in the flux density ratio plot.}
-
-\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  -These would end up being closer to the best fit values.}
+%\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  -These would end up being closer to the best fit values.}
 
@@
 This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{prato08}.
-\comm{This blurb should probably go in the introduction.}
+%\comm{This blurb should probably go in the introduction.}
 
@@
 
-Motivated by the failure of single-temperature spectral fits, we added two new model parameters to our forward model: a starspot temperature and a fill factor, as described by Equation \ref{eqn:Mix_M}.
-For computational complexity reasons, we altered the model framework as described in Section \ref{sec:methods} and detailed in Appendix \ref{methods-details}.
+Full-spectrum fitting was performed for 43 of the 54 available IGRINS spectral orders as described in Sectrion \ref{sec:methods} and Appendix \ref{methods-details}.
+The MCMC samples had 5000 steps with 40 walkers.
+The stellar parameter ranges were $\logg \in [-3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [2700, 4500]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.
+The MCMC chains all appeared to converge after about 1500 steps.
 
-We computed full-spectrum fitting of 43 of 54 IGRINS spectral orders.
-We fit all 14 stellar and nuissance parameters simultaneously.
-We ran the fits for 5000 steps with 40 walkers in \texttt{emcee}.
-The stellar parameter ranges were $\logg \in [-3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [3000, 4300]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.
-We used the same priors for stellar and nuissance parameters as \iancze.
-We enforced $\teffb < \teffa$ to limit the combinatoric degeneracy and mode-mixing that's possible if MCMC samples with $\teffa \approx \teffb$ arise.
-This false mode mixing matters for the \texttt{emcee} algorithm since the step size distribution would be artificially inflated if some walkers mixed modes with $\teffa \Leftrightarrow \teffb$.
-The MCMC chains all appeared to converge after about 1500 steps.
-\footnote{We spot-checked a few of the MCMC chains for convergence by computing the integrated autocorrelation times.
-Most of the parameters had integrated autocorrelation times much less than our number of steps, except for the $\log{\Omega}$ terms.
-This makes sense because the $\log{\Omega_1}$ and $\log{\Omega_2}$ are strongly correlated, so it takes many steps for each walker to explore the joint probability space.
-We have a strong constraint on the filling factor with all 40 walkers combined.}
+Marginalized point estimates were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
+The fit quality was assessed by examining the consistency of the point estimates across the spectral orders.
+The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
+The range for all 43 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
+Spectral orders $m=91$ and $94$ had exceptionally large uncertainties on their values for $v_z$ and $\vsini$, which makes sense since these two orders are badly affected by telluric absorption artifacts.
 
-We computed point estimates for each parameter by selecting the final 200 $\times$ 40 walkers = 8000 samples, and computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
-
-We assessed the fit quality by examining the consistency of the point estimates across the spectral orders.
-The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
-We find median point estimates and standard deviations of all 43 orders of $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
-Spectral orders $m=91 \mathrm{ and }94$ had exceptionally large uncertainties on their values for $v_z$ and $\vsini$, which makes sense since these two orders are badly affected by telluric absorption artifacts.
-
-As noted previously, our full-spectrum fitting method offers little constraining power on $\logg$, and $\Z$ can be biased in the face of systematic spectral line outliers.
-We find a preference for values of $\logg$ on the high end of our search range, $3.5 <\logg <4.0$, finding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{donati14}.
-For $\Z$ we find a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metalicity, while the shorter wavelength values prefer slightly sub-solar metalicity.
+As noted previously, the full-spectrum fitting method offers little constraining power on $\logg$, and $\Z$ can be biased in the face of systematic spectral line outliers.
+Estimates of $\logg$ appeared the high end of our search range, $3.5 <\logg <4.0$, yielding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{donati14}.
+The estimates for $\Z$ yield a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metalicity, while the shorter wavelength values prefer slightly sub-solar metalicity.
 Orders 79, 81, 90, and to a lesser extent 78 and 76 showed aritificially tight constraints on $\Z$, biased to large values.
@@
 These spectral line outlier orders also tend to bias estimates of effective temperature.
-The interpretation of these lines will be addressed in the discussion section.
+These metal lines can also be biased by Zeeman broadening, which would explain the heightened effect size with wavelength.
 
 Finally, the posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.
-At first sight, the $H-$ band estimates show remarkably tight distributions centered near $\teffa\sim4100$ K and $\teffb\sim3000$ K, with the exception of a few spectral order outliers- $m=$ 107, 108, 109.
-The apparent tight constraint is an illusion from pileup near our effective temperature search range for $H-$band.
-So the point estimates for $\teffa$ and $\teffb$ should really be considered lower- and upper- limits respectively.
-Orders 107, 108, and 109 converged on solutions with nearly equal effective tempatures for starspot and photosphere, $\teffa \sim \teffb$.
-These nearly-equal solutions could be explained by vanishingly weak spectral lines in one or the other of the effective temperature ranges, in which case the method offers little constraint on $\teffb$, but improves the fit around $\teffa$.
+\todo{insert results from re-run of H-band spectra here}
+Nearly-equal solutions could be explained by vanishingly weak spectral lines in one or the other of the effective temperature ranges, in which case the method offers little constraint on $\teffb$, but improves the fit around $\teffa$.
 
-We experimented on the $K-$band spectra with expanded effective temperature search ranges.
-Here we see much more scatter, with no single photospheric temperature sticking out as strongly favored, but with values of $\teffa \sim 3900$ K and $\teffb \sim 2800$ K consistent with many orders.
+The $K-$band orders demonstrate much more scatter than $H-$band, with no single photospheric temperature sticking out as strongly favored, but with values of $\teffa \sim 3900$ K and $\teffb \sim 2800$ K consistent with many orders.
 The $K-$band spectra possess strongly correlated residuals from poor telluric correction, as well as uncorrected hydrogen line features that appear as flux excessess after division by telluric standard spectrum.
@@
 There are many examples of spectral lines that are present only in the hot photosphere model, or only in the cool photosphere model.
+For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.
 
-%% Examples of selected regions.
-For example...
-
-\todo{Compile a list of Line IDs, and maybe little postage stamp figures for each line with a range of fits.}
-
-The most compelling results from the full spectrum fitting method come from orders for which there exist strongly temperature-sensitive spectral lines.
-We spot-checked each spectrum, flagging the orders that possessed these types of lines.
-We then computed the weighted mean of the stellar parameter point statistics only for these effective temperatures and fill factors.
-We arrived at best fit values for the stellar parameters summarized in Table \ref{tbl_adopted_props}.
-We adopt these parameters as the stellar properties at the epoch of the IGRINS observations.
-We find a large filling factor of cool starspots, with a best value of $f=75\pm 10 \% $.
+Best fit values for the stellar parameters summarized are listen in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $c=75\pm 10 \% $.
 

### 2016-07-25 document/ms.tex
Remove lots of content from the previously-bloated appendix.  Focus on the implementation facts and reproducibility.  Some content slated for removal or move to Discussion.

@@
 
-% Motivation:  Why sampling?  Why full spectrum fitting?
-
-A main motivating factor in designing our methodology was our wish to address the question: ``Is a given spectrum consistent with the non-detection of starspots, and to what level of confidence can the properties of starspots be measured given uncertain stellar properties?''.
-In order to answer this question, we need some way to gauge the uncertainty in the derived stellar properties, which we assumed would have some level of degeneracy among themselves.
-For example, we expect the best fit effective temperature contrast will be partially degenerate with the areal coverage fraction: a slightly cooler, smaller sunspot can masquerade as a larger, warmer spot.
-This degeneracy should be lessened in spectroscopic methods compared to photometric methods.
-The desire to reveal these intra-parameter degeneracies motivated the choice of \emph{sampling} from the posterior probability density distribution function.
-
-% Overview and summary of existing model
-
-We adopted and extended an existing modular framework for spectral inference \citep[][hereafter \iancze]{czekala15}.
-We briefly summarize the model here for carity of notation, but see \iancze for more details.
-We follow and expand the notation from \iancze, all summarized in Table \ref{table:params}.
-
-The main idea is that \iancze define a pixel-level forward model $\vM$ of the data.
+\iancze define a pixel-level forward model $\vM$ of the data.
 A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.
@@
 
-\todo{Simplify this discussion to what matters here.}
+\todo{Remove the matrix/approach jargon and simplify}
 
-\subsection{Approach 11: Whole spectrum with a single photospheric component (Czekala et al. 2015)}
-
-Approach 11 is identical to the strategy in \iancze.
-The model $\vM(\vT)$ was intended to apply a single set of stellar parameters to the entire wavelength range of interest, presumably the entire available spectrum.
-For a spectrum from a multi-order echelle spectrograph, this means each spectral order is fit with the same stellar parameters.
-Simultaneous fitting is the desired behavior for most applications involving a single stellar photospheric component.
-In our case, however, we know that a single stellar photospheric component is a poor model for the data: there are \emph{two or more components} lurking in the composite spectrum.
-We anticipate that these fits would be too uninformative, so we did not implement Approach 11 on the whole spectrum.
-
-\textbf{Other things to say: Optical and IR will have slightly different RV, perhaps different vsini based on erroneous spectral resolution.
-This method could work with liberal assignment of local kernels, and the development of new kernels that deal with line-width mis-matches.}
-
-\subsection{Approach 12: Deriving unique Teff in each order}
+\subsection{Discussion of deriving unique Teff in each order}
 \label{sec:approach12}
 
-In local chunks of wavelength, a single stellar photosphere component might fit the composite spectrum satisfactorily.
-Some wavelength chunks will fit the warm photosphere lines better and other wavelength chunks will fit prominent lines from cool spots better.
-Wavelength chunks possessing lines that are present in both cool and warm stars will yield mixed results.
-
-The starspot contrast depends on wavelength, roughly as the ratio of blackbodies.
-Figure XX shows a plot of the flux ratio of two stellar photospheres with identical stellar properties except for different effective temperatures.
-So a sufficiently large bandwidth spectrum could exhibit differing levels of fit quality as a function of wavelength, if a single temperature photosphere fit is naively applied to different chunks of wavelengths.
-
-We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.
+\todo{Move or delete this section}
 
@@
 For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \Omega_{o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.
-
-In principle, one could refine the inference on $T_{\mathrm{eff},o}$ in an \emph{empirical Bayes'} strategy CITE (XX, astroML book?), in which we re-evaluate $\vT_o$ by setting priors on all the stellar parameters except $T_{\mathrm{eff},o}$.
-We elected not to pursue an empirical Bayes' approach.
-
-As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on instrumental calibration.
-If the stellar parameters in one order are routinely discrepant, we can examine and refine our instrumental calibration for that spectral order.
-For example, the radial velocity $v_r$ could be systematically offset in one order due to instrumental calibration problems.
-Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework from \iancze assumes the spectral resolution is fixed across all wavelengths, but typical spectrographs exhibit a small dependence of spectral resolution on wavelength.
-(cite the SICK paper)
-
-Spectral-order level granularity in fit quality is not available in a fit that includes all $N_{order}$ spectral orders.
-In fact, the benefits of spectral chunking could be made \emph{even more granular} by chunking the spectrum into individual spectral lines or line-groups.
-The fit quality could then be assessed on a line-by-line basis, even taking into account systematic effects like individual elemental abundance patterns beyond the coarse $\Z$ estimates.
-Future improvements to the spectral inference framework are directed at implementing this spectral-line chunking strategy.
-
-\subsection{Approach 21: Whole spectrum with two components}
-\label{sec:approach21}
-
-Ideally, we want to fit the entire spectrum with a two component photosphere.
-If we believe our model, the entire emergent spectrum of the star should be described by a single set of stellar parameters.
-In other words, if nature had truly delivered a noisy version of this model, the ability to measure starspot properties would scale with the number of spectral channels (to some power).
-
-Unfortunately there are two main limitations of Approach 21.
-First, the Metropolis-Hastings Gibbs sampling is dramatically complicated by increasing from 6 to 8 stellar parameters: $theta-original to theta-multicomponent$.
-The details of the problem are summarized in Section \ref{sec:MC-challenges}.
-
-\subsection{Approach 22: Order-by-order with two components}
-\label{sec:approach22}
-
-Finally, Approach 22 is two sample each spectral order with a unique two-component photosphere model:
-
-$$ theta by order$$.
-
-In this case we altered the \iancze framework from a blocked Gibbs sampler with Metropolis-Hastings proposals to an affine invariant ensemble sampler with all stellar and nuisance parameters sampled simultaneously.
-
-This strategy has the \emph{disadvantage} that there is no statistically principled way to combine the $N_{ord}$ inferences from the set of $\theta$ at the end.
-There are many \emph{heuristic} ways to estimate the inferences at the end.
 
@@
 
-\begin{deluxetable}{clcc}[!bh]
-\tablecaption{\label{table:params} Definition of symbols and parameters used}
-\tablehead{
-\colhead{Label} &
-\colhead{Description} & 
-\colhead{Shared?} &
-\colhead{Source}
-}
-\startdata
-$\vM$ & Pixel-level model & - & \iancze \\
-$\vT$ & Stellar parameters in the model & - & \iancze \\
-$q(\vt_{\ast})$ & Absolute mean flux ratio in order $o$  & N & This Work \\
-\hline
- \multicolumn{4}{c}{$\vt_{\ast}$} \\
-\hline
-$\teffa$ & Effective temperature of component A & N & This Work \\
-$\teffb$ & Effective temperature of component B & N & This Work \\
-$\Delta \teff$ & Spot temperature contrast $\teffa - \teffb $ & - & This Work \\
-$\logg$ & Stellar surface gravity & Y & \iancze \\
-$\Z$ & Metallicity & Y & \iancze \\
-\hline
-\multicolumn{4}{c}{$\vt_{\rm ext}$} \\
-\hline
-$v\sin{i}$ & Projected stellar rotation & Y$^a$ & \iancze \\
-$\sigma_v$ & Instrumental resolution & Y & \iancze \\
-$v_r$ & Radial Velocity & Y & \iancze \\
-$\Omega_a$ & Solid angle subtended by component A & N & This Work \\
-$\Omega_b$ & Solid angle subtended by component B & N & This Work \\
-$c$ & Spot fill factor, $\Omega_b / (\Omega_a+\Omega_b)$ & N & This Work \\
-$A_{\lambda}$ & Extinction towards the source & Y & \iancze \\
-\enddata
-\tablecomments{\emph{a}- In principle, star spots could have non-uniform latitudinal distributions, resulting in slight differences in $v\sin{i}$ between the components CITE XX-McDonald Obs.
-We ignore this effect for now, but it could be an interesting line of study for future work.}
-\end{deluxetable}
-
 \section{Previous work}
@@
 \input{tables/tbl_history.tex}
-
-In short, here is what we know about \name.
-It is a weak-lined \emph{T-Tauri} star.
-It exhibits a 3.36-3.37 day period \citep{vrba93,grankin94}, as seen in photometric monitoring in $BVRI$ bands.
-No periodic signal is detected at $U-$band.
-Section 5 of \citet{vrba93}, ``More on the nature of CTT and WTT spots'' goes into detail about the whether the photometric variability is attributable to hot or cold patches.
-\name has no detected M-type-or-earlier binary companion down to $0.13''$ (Kraus, plus Nguyen for SBs?).
-\name demonstrates variability in X-rays with ROSAT \citep{strom94}, with $L_{x}=2.4$ ergs/s.
-
-\section{Challenges: Tuning the transition probability matrix}
-\label{sec:MC-challenges}
-
-Once we have the mixture model in hand, we can apply the blocked Gibbs MCMC sampling framework from \iancze.
-We have added 2 more parameters ($\Omega_b, \teffb$) to the model, expanding from 6 to 8 total stellar parameters.
-Unfortunately this increase in dimensionality adds considerable complexity to tuning the model.
-The number of possible tuning parameters in a conventional Metropolis Hastings MCMC sampler scales as $N(N+1)/2$ CITE XX, so our 2 new parameters increased the tuning parameters from 15 to 36.
-The tuning parameters are covariances between dimensions in the proposal distribution.
-Luckily, most of the covariances are negligibly small.
-However the $\teffa, \teffb, \Omega_a, \Omega_b$ terms are likely to be correlated, suggesting an affine transformation of the parameters would accelerate the convergence of the MCMC chains.
-We experimented with some of these transformations and found that the existing stellar parameters were best, although still unacceptably correlated.
 

### 2016-07-27 document/ms.tex
This commit was posted to Overleaf.com as ms_25jul_mgs.tex, along with some updated tables and updated ms.bib.
Prose added by GJH on the Overleaf on July 27, several new figures for his section.

@@
 
-\section{Monitoring the Spots of LkCa 4}
+\section{Spots at Low Spectral Resolution}
 
@@
 
-In \S 4.1 we describe how the two components of the photosphere fit low resolution spectra and optical photometry.
-The spectral features and colors should change as the spot rotates around the star, so that the visible fraction of hot and cool spot changes.
-While the variability in optical brightness is well documented and motivatet this study, in \S 4.2-4.3 we convert the $V$ band brightness to a spot filling factor and then quantify spectroscopic and color variability caused by changes in the spot filling factor.
+In \S 4.1 we describe how the two components of the photosphere fit low resolution spectra and optical/near-IR photometry.
+The brightness, colors, spectral features should change as the spot rotates around the star.
+In \S 4.2, we convert the $V$ brightness to a filling factor of the cool spot, and then in \S 4.2-4.3 we compare how the expected rotational modulation of photometry and spectral indices compares with observed measurements.
 
 \begin{figure*}
-    	%\vspace{-60mm}
 	\centering
+    	\vspace{-120mm}
 	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
-	%\vspace{-100mm}
 	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
@@
 
+\begin{figure*}
+	\centering
+    	\vspace{-120mm}
+	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores_twopanel} 
+	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+	\label{fig:lores_twopanel}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+    	\vspace{-20mm}
+	\includegraphics[width=0.95\textwidth]{figures/vband_spot} 
+    	\vspace{-100mm}
+\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+\label{fig:vband_spot}
+\end{figure*}
+
 \subsection{The Spectral Energy Distribution}
 
-Figure~\ref{fig:lores} shows that the two-component photosphere matches flux-calibrated spectra well from $\sim 6000-2.5$ $\mu$m.
+Figure~\ref{fig:lores} shows that the two-component photosphere matches flux-calibrated spectra well from $\sim 0.6-2.5$ $\mu$m.
 The two components have fixed temperatures of 4200 K covering 30\% of the visible surface and 3000 K covering 70\% of the visible surface area.
@@
 
-The value for the extinction depends on XXX...
+The lower panels show photospheric spectra scaled separately to the observed red-optical and near-IR spectra.
+The single temperature spectra are unable to reproduce the observed emission.
+The $3900$ K component fits the TiO bands at reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
+The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
+On the best-fit photosphere from \S 3 fits both the optical and the near-IR bands well.
+
+SED...
+
+The value for the extinction depends on.
+
+Relative to main sequence colors, the $E(B-V)=0.24$ would yield.
+
+%Furlan:  K7, V-IC=1.92, E(V-I)=1.6 => 0.85 mag;  close enough to their 1.1 mag
+%V-K = 4.18  ; MS colors:  3.16 (KH95) => Av=1.1 mag
+
+%V-J:  2.8-3.8
+%J-K:  0.9-1.0
+
+ The upper limit may be estimated by comparing the observed $B-V$ color to main sequence $B-V$ colors.
+
+The $B-V$
+
+The $J-K=0.93$ color is equal to the expected color to within 0.05 => 0.3 mag (for T=3000, 4200)
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.49\textwidth]{figures/bv_kh95} 
+    \includegraphics[width=0.49\textwidth]{figures/vr_kh95} 
+\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+\vspace{-50mm}
+\label{fig:colors}
+\end{figure*}
 
@@
 Since 1992 the $V$ band brightness has varied from $12.3$ to $13.2$ mag, with a typical range of $0.5$ mag in any single epoch.
-In a two-temperature atmosphere, this brightness corresponds directly to a filling factor for both components.
+In a two-temperature atmosphere with fixed temperatures, this brightness corresponds directly to a filling factor for both components.
+Figure~\ref{vband_spot} shows this conversion for temperatures of 4200 K, 3000 K, and a 75\% filling factor for the 3000 K component at $V_{est}=12.83$, as estimated at the time of the IGRINS spectrum.
 
-We model the rotational modulation of LkCa 4 in different photometric bands by fixing the two temperatures to 4200 and 3000 K and setting the 70\% covering fraction of the cool component to $V_{est}=12.85$, as estimated at the time of the IGRINS spectrum.
-The colors for the two components are obtained from the main sequence colors compiled by \citet{kenyon95}.
-The colors from dwarfs stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
+The model photometry is obtained from the main sequence colors compiled by \citet{kenyon95}.
+Colors from dwarfs stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
+Synthetic spectra of $3000-4000$ K stars predict $B-V$ colors that are much bluer than observed and that become bluer at cooler temperatures, the opposite of what is observed.
+As a consequence, synthetic photometry also cannot be used here.
 
-In these simple models, the blue emission is dominated by the hotter component, while both components contribute to the red and infrared emission.   
-The $0.5$ mag range in $V$-band brightness requires at least a factor of 1.6 change in the visible surface area of hot component.  Figure~\ref{fig:spotcolors} shows the
+The optical emission is dominated by the hotter component while both components contribute to the red and infrared emission (see Figure \ref{fig:lores}).
+The $0.7$ mag range in $V$-band brightness requires at a factor of 1.9 change in the visible surface area of hot component in the limit that the cool component does not contribute any $V$-band emission.
+In the 2014-2015 ASAS-SN photometry, the minimum and maximum brightness correspond to cool spot coverage of 83\% and 68\%, respectively.
+LkCa 4 was brighter in past epochs, which corresponds to either a larger covering fraction for the hot component (as assumed here) or components with hotter temperatures.
+
+The rotational modulation leads to much smaller brightness changes at near-IR wavelengths than at optical wavelengths (see Table~\ref{tab:photrange}).
+The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller amplitude than LkCa 4 in $V$ band.
+Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller.
+The predicted colors from rotational modulation do not match the observed $V-R_J$ colors or the correlation with $V$, either because of changes in spot properties since the \citet{grankin08} data were obtained or because a two-temperature model for the photosphere is overly simplistic.
+
+\begin{table}
+\caption{Predicted Photometric Range - based on $V$, adapt for $A_V$}
+\label{tab:photrange}
+\begin{tabular}{cccc}
+\hline
+Band & Low Spot & High Spot & Range\\
+Cool Spot & 68\% & 83\% &\\
+\hline
+$B$ & 13.80 & 14.48 & 0.68\\
+$V$ & 12.56 & 13.23 & 0.67\\
+$R$ & 11.53 & 12.17 & 0.64 \\
+$I$ & 10.80 & 11.38 & 0.58\\
+$J$ & 9.79 & 10.00 & 0.21\\
+$K$ & 8.89 & 9.04 & 0.15\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-\subsection{Phased colors}
-
 \begin{figure*}
 	\centering
-	%\vspace{-60mm}
+	\vspace{-60mm}
 	\includegraphics[width=0.95\textwidth]{figures/lkca4_tio_forpaper} 
-    %	\vspace{-30mm}
+    	\vspace{-30mm}
 	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
@@
     %	\vspace{-30mm}
-	\includegraphics[width=0.95\textwidth]{figures/lkca4_hrdiag}
-    %	\vspace{-30mm}
-	\caption{Placeholder for HR Diagram Figure}
+	\includegraphics[width=0.95\textwidth]{figures/lkca4_hrdiag_forpaper}
+    	\vspace{-80mm}
+	\caption{HR Diagram Figure}
 	\label{fig:hrdiag}
@@
 
-Table REF lists measurements of LkCa4 from previous studies.
+Table \ref{tbl_history} lists measurements of LkCa4 from previous studies.
 \input{tables/tbl_history.tex}

### 2016-07-28 code/batch_plot_mix.py
spot check the most recent round of Starfish MCMC runs, orders 100-117

@@ -4,9 +4,9 @@ import yaml
 import numpy as np 
 import h5py
 
-#ms = range(99, 119)
+ms = range(100, 117)
 #ms = range(72, 94+1)
-ms = list(range(72, 94+1)) + list(range(99, 119))
+#ms = list(range(72, 94+1)) + list(range(99, 119))
 
 os.chdir(os.path.expandvars('$WELTER/sf/'))
 
@@ -14,13 +14,12 @@ os.getcwd()
 
 for m in ms:
 
-    dat_name = '../../data/reduced/LkCa4_IGRINS_m{:03d}.hdf5'.format(m)
-    path_out = 'm{:03d}/output/mix_emcee/run01'.format(m)
+    path_out = 'm{:03d}/output/mix_emcee/run02'.format(m)
     os.chdir(path_out)
 
     print('Plotting results from m{:03d}'.format(m))
-    # Do all the grid.py and pca.py setup.
+    os.system('cp temp_emcee_chain.npy emcee_chain.npy')
     os.system('plot_many_mix_models.py --static')
     os.system('cp mix_model.png '+
-    	os.path.expandvars('$WELTER/results/fig/mix_models/mix_model_m{:03d}.png'.format(m)))
+    	os.path.expandvars('$WELTER/results/fig/mix_models_run02/mix_model_m{:03d}.png'.format(m)))
     os.chdir(os.path.expandvars('$WELTER/sf/'))

### 2016-07-28 document/ms.tex
Some small edits from the Overleaf from GJH
Update the photometry figures
Merge section 2 to a subsection of the old Section 4 (now Section 3)

@@
 
+\section{Observations}\label{sec:obs}
+
+\subsection{IGRINS Spectroscopy}\label{sec:igrins} 
+We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{gully12,park14} on the Harlan J.
+Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
+IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
+The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band.
+The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.
+Telluric correction was performed by dividing the spectrum of \name by a spectrum of HR 1237, an A0V star observed immediately before \name, both at airmass 1.1.
+The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of \name.
+No effort was made to remove these flux excesses, which affect several spectral orders.
+
+\subsection{ESPaDOnS Spectroscopy}
+We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.
+These spectra cover 3900$-$10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.
+The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.
+In this paper we concentrate on the intensity spectrum.
+The spectrum was apportioned into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
+\todo{Flux calibration?}
+
+\subsection{Low-resolution optical and near-IR spectra}
+
+Palomar/DBSP \citep{herczeg14}
+
+APO/TripleSpec (Covey)
+
+\subsection{Photometric monitoring from ASAS-SN and \citet{grankin08}}
+
+We retrieved $V-$band monitoring from the ASAS-SN survey \citep{shappee14}, obtained from 2012 January -- 2016 March in 186 visits.
+We also retrieved optical photometry of \name\ obtained in 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 additional $BVR$ epochs obtained by \citet{donati14}.
+Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{donati14}, and ASAS-SN $V-$band monitoring plotted over the interval 1992-2016.
+The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
+	\caption{\name $V-$band photometric monitoring from 1992-2016.}
+	\label{fig:PhotTime}
+\end{figure*}
+
+Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 17 observing seasons and phase-folded by period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
+The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
+We estimate $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.95\textwidth]{figures/Vband_22s.pdf}
+	\caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.
+The blue solid lines show a multi-term periodic fit keeping the first $M_{\rm max}=4$ Fourier components.
+The vertical lines show the epochs of observations for available spectroscopy.
+The unchanged vertical scale highlights the secular drift of the light curve amplitude and morphology.}
+	\label{fig:PhotPhase}
+\end{figure*}
+
+\input{tables/tbl_estV_atObsEpoch.tex}
+
+\section{FITS TO HIGH RESOLUTION SPECTRA}
+
+\todo{Provide overview of section...}
+
 \section{Methodology}\label{sec:methods}
@@
 Further details of the spectral inference methodology are described in Appendix \ref{methods-details}.
-
-\section{Observations}\label{sec:obs}
-
-\subsection{IGRINS Spectroscopy}\label{sec:igrins} 
-We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{gully12,park14} on the Harlan J.
-Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
-IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
-The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band.
-The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.
-Telluric correction was performed by dividing the spectrum of \name by a spectrum of HR 1237, an A0V star observed immediately before \name, both at airmass 1.1.
-The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of \name.
-No effort was made to remove these flux excesses, which affect several spectral orders.
-
-\subsection{ESPaDOnS Spectroscopy}
-We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.
-These spectra cover 3900$-$10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.
-The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.
-In this paper we concentrate on the intensity spectrum.
-We apportioned the spectrum into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
-\todo{Flux calibration?}
-
-\subsection{Low-resolution optical and near-IR spectra}
-
-Palomar/DBSP \citep{herczeg14}
-
-APO/TripleSpec (Covey)
-
-\subsection{Photometric monitoring from ASAS-SN and \citet{grankin08}}
-
-We retrieved $V-$band monitoring from the ASAS-SN survey \citep{shappee14}, obtained from 2012 January -- 2016 March in 186 visits.
-We also retrieved optical photometry of \name\ obtained in 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 additional $BVR$ epochs obtained by \citet{donati14}.
-Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{donati14}, and ASAS-SN $V-$band monitoring plotted over the interval 1992-2016.
-The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/LkCa4_phot1992-2016.pdf}
-	\caption{\name $V-$band photometric monitoring from 1992-2016.}
-	\label{fig:PhotTime}
-\end{figure*}
-
-Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 17 observing seasons and phase-folded by period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
-The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-We estimate $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
-Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.95\textwidth]{figures/all_LCs_phase.pdf}
-	\caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.
-The blue solid lines show a multi-term periodic fit keeping the first $M_{\rm max}=4$ Fourier components.
-The vertical lines show the epochs of observations for available spectroscopy.
-The unchanged vertical scale highlights the secular drift of the light curve amplitude and morphology.}
-	\label{fig:PhotPhase}
-\end{figure*}
-
-\input{tables/tbl_estV_atObsEpoch.tex}
-
-\section{FITS TO HIGH RESOLUTION SPECTRA}
-
-\todo{Provide overview of section...}
 
@@
 
+\begin{figure}
+	\centering
+    	\vspace{-20mm}
+	\includegraphics[width=0.95\textwidth]{figures/phot1_paper} 
+    	\vspace{-100mm}
+\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+\label{fig:vband_spot}
+\end{figure}
+
 \subsection{The Spectral Energy Distribution}
@@
 \begin{table}
-\caption{Predicted Photometric Range - based on $V$, adapt for $A_V$}
+\caption{Predicted Photometric Range}
 \label{tab:photrange}
@@
 \hline
+\multicolumn{4}{c}{Based on $V$, adapt for $A_V$}\\
 $B$ & 13.80 & 14.48 & 0.68\\

### 2016-07-28 document/ms.tex
Update formatting of aliases C15 and PHOENIX; for some reason they skip spaces sometimes.

@@
 
-\section{Methodology}\label{sec:methods}
+\subsection{Methodology}\label{sec:methods}
 
@@
 The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}} to infer stellar properties from high resolution spectra.
-The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
-We employed the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
+The \iancze\ technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
+We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
 The modular framework was altered to accommodate starspot measurements in two ways.
@@
 For the IGRINS $K-$band, we employed an expanded search range for the effective temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.
-No effort was made to shift the wavelength scales of the IGRINS data and $\PHOENIX$ model into the same system, so the absolute values of $v_z$ are arbitrary shifted.
+No effort was made to shift the wavelength scales of the IGRINS data and \PHOENIX\ model into the same system, so the absolute values of $v_z$ are arbitrary shifted.
 
@@
 
-\emph{Suitability of pre-computed \PHOENIX model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX synthetic spectra are a good representation to our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
+\emph{Suitability of pre-computed \PHOENIX\ model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX\ synthetic spectra are a good representation to our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
 Cool sunspots are associated with heightened magnetic fields on the sun.
@@
 
-\iancze define a pixel-level forward model $\vM$ of the data.
+\iancze\ define a pixel-level forward model $\vM$ of the data.
 A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.
@@
 The $\vt_{\ast}$ are comprised of the dimensions of the pre-computed stellar model grid.
-We use the \PHOENIX model grid \citep{husser13}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
+We use the \PHOENIX\ model grid \citep{husser13}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
 
@@
 If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.
-However \iancze employ \emph{standardized} $\flam$ when constructing the forward model $\vM$:
+However \iancze\ employ \emph{standardized} $\flam$ when constructing the forward model $\vM$:
 

### 2016-07-28 document/ms.tex
Add descriptions of the new photometry-- ASAS, Integral-OMC, AAVSO.  Add ackwoledgements and facilities hat tips.

@@
 Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
-The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep{hartigan95,kenyon98,edwards06,cauley12,yang12,ardila13,castro13,loyd14,martinez15}, has no evidence for a close companion \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11}}, demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}, has recently been examined with ZDI \citep{donati14}, and has large ($\delta \teff \sim$500 K) disagreement about its effective temperature \citep{herczeg14}.
+The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep{hartigan95,kenyon98,edwards06,cauley12,yang12,ardila13,castro13,loyd14,martinez15}, has no evidence for a close companion \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11}}, demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}, has recently been examined with ZDI \citep{donati14}, and has large ($\Delta \teff \sim$500 K) disagreement about its effective temperature \citep{herczeg14}.
 The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
@@
 In this work we constrain the starspot properties of \name with 4 complementary techniques.
-Section 2 and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis.
-Section 3 applies the spectral inference technique to a high resolution panchromatic near-IR spectrum of \name.
-Sections 5.1, 5.2, and 5.3 show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
+Section \ref{sec:obs} quantifies the optical variability of \name over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
+Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution panchromatic near-IR spectrum of \name in Section \ref{sec:two_tempIGRINS} .
+Sections 4.1, 4.2, and 4.3 show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
 All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
@@
 Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
-IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48\um.
+IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48 \um.
 The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band.
@@
 In this paper we concentrate on the intensity spectrum.
-The spectrum was apportioned into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
-\todo{Flux calibration?}
+%\todo{Flux calibration?}
 
@@
 
-Palomar/DBSP \citep{herczeg14}
+The Palomar/DBSP data was previously described in \citet{herczeg14}.
 
 APO/TripleSpec (Covey)
+\todo{fill in details about TripleSpec data}
 
-\subsection{Photometric monitoring from ASAS-SN and \citet{grankin08}}
+\subsection{Photometric monitoring for 22 seasons over 31 years}
 
-We retrieved $V-$band monitoring from the ASAS-SN survey \citep{shappee14}, obtained from 2012 January -- 2016 March in 186 visits.
-We also retrieved optical photometry of \name\ obtained in 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 additional $BVR$ epochs obtained by \citet{donati14}.
-Figure \ref{fig:PhotTime} assembles the \citet{grankin08}, \citet{donati14}, and ASAS-SN $V-$band monitoring plotted over the interval 1992-2016.
-The dates of observations of the IGRINS spectra and ESPaDoNs spectra are demarcated as vertical lines.
+An archive of 1173 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
+Published data targeting \name\ is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
+ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002-2004.
+Integral-OMC obtained 138 $V-$band measurements from 2006-2008 \citep{garzon12}.
+The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.
+Finally, unpublished data from the ASAS-SN survey \citep{shappee14}, were obtained from 2012 January -- 2016 March in 186 visits.
+Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1986-2016.
 
@@
 	\includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
-	\caption{\name $V-$band photometric monitoring from 1992-2016.}
+	\caption{\name $V-$band photometric monitoring from 1986$-$2016.
+The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DoubleSpec, and TripleSpec.
+The near contemporaneous DoubleSpec and TripleSpec epochs lay on top of each other on this scale, as do the 12 ESPaDOnS epochs.
+The abscissa range is equal to the current lifespan of the first author of this paper.}
 	\label{fig:PhotTime}
@@
 
-\section{FITS TO HIGH RESOLUTION SPECTRA}
+\section{FITS TO HIGH RESOLUTION SPECTRA}\label{sec:Starfish}
 
@@
 We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth spectrum from Table \ref{tbl_estimated_V}.
+The spectrum was apportioned into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
 Full-spectrum fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
@@
 
-\subsection{Two-temperature fitting to IGRINS spectra}
+\subsection{Two-temperature fitting to IGRINS spectra}\label{sec:two_tempIGRINS}
 
@@
 
-{\it Facilities:} \facility{Smith (IGRINS)}
+Based on data from the OMC Archive at CAB (INTA-CSIC), pre-processed by ISDC.
+
+We acknowledge with thanks the variable star observations from the AAVSO International Database contributed by observers worldwide and used in this research.
+
+{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS},
 

### 2016-07-28 document/ms.tex
Small changes to photometry and observations discussion in preparation for a big text dump from GJH

@@
 
-\subsection{Photometric monitoring for 22 seasons over 31 years}
+\subsection{Photometric monitoring}
 
@@
 Published data targeting \name\ is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
-ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002-2004.
-Integral-OMC obtained 138 $V-$band measurements from 2006-2008 \citep{garzon12}.
+ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002$-$2004.
+Integral-OMC obtained 138 $V-$band measurements from 2006$-$2008 \citep{garzon12}.
 The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.
@@
 
-Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 17 observing seasons and phase-folded by period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
+Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 22 observing seasons and phase-folded by period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
 The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-We estimate $\hat V$, the $V-$band magnitude at the time of the spectral observations, from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
-Table \ref{tbl_estimated_V} lists $\hat V$ and the observing epoch for the spectral observations with ESPaDoNs and IGRINS.
+The estimated $BVR$ magnitudes at the time of the spectral observations are determined from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+Table \ref{tbl_estimated_V} lists the estimated $BVR$ photometry and the observing epoch for data from IGRINS, ESPaDOnS, 2MASS \citep{skrutskie06}, DoubleSpec, and TripleSpec.
 
@@
 	\caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.
-The blue solid lines show a multi-term periodic fit keeping the first $M_{\rm max}=4$ Fourier components.
-The vertical lines show the epochs of observations for available spectroscopy.
-The unchanged vertical scale highlights the secular drift of the light curve amplitude and morphology.}
+The blue solid lines show a multi-term regularized periodic fit keeping the first $M_{\rm max}=4$ Fourier components.
+The vertical lines show the epochs of observations for ancillary data, with the same line styles and colors as Figure \ref{fig:PhotTime}.
+The unchanged vertical and horizontal scales highlight the secular drift of the light curve amplitude and morphology.}
 	\label{fig:PhotPhase}
@@
 
+This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
+
 {\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS},

### 2016-07-28 document/ms.tex
Updated text from an email from GJH on July 28, subject: text

@@
 
+\begin{figure}
+	\centering
+    	\vspace{-20mm}
+	\includegraphics[width=0.95\textwidth]{figures/phot1_paper} 
+    	\vspace{-100mm}
+\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
+\label{fig:sed}
+\end{figure}
+
 \begin{figure*}
@@
 	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
-	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
+The inset shows that the 3000 K (red, 70\% fill factor) and 4200 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4200 K component dominates the blue emission.
+The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.}
 	\label{fig:lores}
@@
 	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores_twopanel} 
-	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+	\caption{The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere, and the two temperature photosphere that best fit the IGRINS spectrum.
+The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
+Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.
+Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
+The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
 	\label{fig:lores_twopanel}
@@
     	\vspace{-100mm}
-\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+\caption{The $V$-band magnitude in 2014--2015 {\bf check}, converted into fill factor for the cool component.
+The optical brightness depends mostly on the hot component.
+If we fix a 75\% filling factor, as measured in the IGRINS spectrum, to $V=12.83$ at the time of the observation, then the $V$-band amplitude  corresponds to filling factors of 67--83\%.
+The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\delta V=0.6$.
+}
 \label{fig:vband_spot}
@@
 
-\begin{figure}
-	\centering
-    	\vspace{-20mm}
-	\includegraphics[width=0.95\textwidth]{figures/phot1_paper} 
-    	\vspace{-100mm}
-\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
-\label{fig:vband_spot}
-\end{figure}
-
 \subsection{The Spectral Energy Distribution}
 
-Figure~\ref{fig:lores} shows that the two-component photosphere matches flux-calibrated spectra well from $\sim 0.6-2.5$ $\mu$m.
+Figures~\ref{fig:sed}-\ref{fig:lores} shows that the two-component photosphere matches the SED and flux-calibrated spectra well from $\sim 0.6-2.5$ $\mu$m.
 The two components have fixed temperatures of 4200 K covering 30\% of the visible surface and 3000 K covering 70\% of the visible surface area.
-The flux and extinction are then scaled to match the spectrum.
+The only free parameters are the luminosity and extinction, which are both scaled to match the spectrum.
 
@@
 
-SED...
-
-The value for the extinction depends on.
-
-Relative to main sequence colors, the $E(B-V)=0.24$ would yield.
+Extinction paragraph, needs overhaul...  Relative to main sequence colors, the $E(B-V)=0.24$ would yield $A_V=0.72$ mag....  
+The $J-K=0.93$ color is equal to the expected color to within 0.05 => 0.3 mag (for T=3000, 4200)...
+The $B-V$ is always dominated by the hot component and therefore does not depend on the filling factor of the hot component.
+The $V-R$ varies more with $V$, indicating a larger contribution from the cool component.
+The difference between observed and predicted $B-V$ color, $E(B-V)$, may correspond to the extinction.
+After accounting for extinction synthetic model underpredicts both the $V-R$...
 
@@
 
- The upper limit may be estimated by comparing the observed $B-V$ color to main sequence $B-V$ colors.
-
-The $B-V$
-
-The $J-K=0.93$ color is equal to the expected color to within 0.05 => 0.3 mag (for T=3000, 4200)
-
 \begin{figure*}
@@
     \includegraphics[width=0.49\textwidth]{figures/vr_kh95} 
-\caption{The low-resolution optical/near-IR spectrum of LkCa 4 is }
+\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions from converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{kenyon95} (purple lines).}
 \vspace{-50mm}
@@
 \hline
-\multicolumn{4}{c}{Based on $V$, adapt for $A_V$}\\
+\multicolumn{4}{c}{Based on $V$, need to adapt for $A_V$}\\
 $B$ & 13.80 & 14.48 & 0.68\\
@@
 
-\citet{donati14} spectroscopically monitored LkCa 4 with 12 spectra obtained over 14 days, covering $\sim 4$ rotation periods.
-The top panel Figure~\ref{fig:tiovar} shows two of these spectra obtained at the estimated maximum and minimum optical brightness.
+\citet{donati14} spectroscopically monitored LkCa 4 with 12 spectra obtained over 14 days covering $\sim 4$ rotation periods.
+The spectra obtained near the estimated maximum and minimum optical brightness are shown in the top panel of Figure~\ref{fig:tiovar}.
 Small but significant changes are seen in the TiO bands.
@@
 
-The TiO variability is quantified through TiO indices listed in Table~\ref{tab:tiO}.  The TiO indices are also combined into a single index by calculating by 
-calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.
+The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}.
+The TiO indices are also combined into a single index by calculating by  calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.
+
 Both the raw TiO 7140 index and this combined TiO index correlate strongly with the optical brightness.
 In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).
+These results are consistent with expectations from the rotational modulation of the hot spot.
+The TiO bands trace the cool component.
+When the hotter component has a larger filling fraction, the TiO bands are veiled by the hotter component and are therefore not as deep.
 
@@
     	\vspace{-80mm}
-	\caption{HR Diagram Figure}
+	\caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.
+The measured effective temperature and luminosity from this paper, based on the two-component fit and a median $V$-band magnitude, corresponds to the black asterisk.
+The yellow shaded region corresponds to the range of apparent effective temperatures that are would be measured as the hot component rotates into and out of our view.
+The blue circle corresponds to the measurement at blue-optical wavelengths by \citet{donati14}, the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to]{herczeg14}, while the red diamong corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
 	\label{fig:hrdiag}
@@
 
+Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc based the parallax distance of the nearest Taurus member \citep{torres12}.
 The spectrum of LkCa 4 is well reproduced by a cool component of $3000$ K covering 75\% of the surface and a $4200$ K component covering 25\% of the surface.
-The effective temperature of these two components is 3525 K, based on the average surface flux.
+The effective temperature of these two components is 3611 K, as calculated from the average surface flux at the median $V$ band magnitude.
+The apparent effective temperature in any single epoch would depend on the relative fractions of the hot and cool spot.
 Decreasing the cool spot size to 60\% would increase the effective temperature to 3670 K, while increasing the spot size to 85\% would decrease the effective temperature to 3370 K.
-{\bf GJH note:  holy crap!!!}  Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc based the parallax distance of the nearest Taurus member \citep{torres12}.
+{\bf GJH note:  holy crap!!!}.
+Since the Hayashi tracks are nearly vertical at this temperature and age, the temperature uncertainty leads directly to an uncertainty in inferred mass.
+Application of multi-temperature atmosphere is also likely to solve long-standing problems related to colors of young stars \citep[e.g.][]{stauffer03}
+
+{\bf GJH paragraph:}  The multi-temperature photosphere may also resolve some of the long-standing problems related to colors of young stars...
+\citet{tottle15}.
+I want to say something here, but I'm not sure exactly what.
+
+{\bf paragraph MG-S:}  Comparisons to other results (both real and simulated) from single-temperature fits to APOGEE, GAIA-ESO wavelengths.  Approximate is ok...
 
@@
 LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
-The inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection and slowing the contraction rate.
+Even though this is only a single data point, the inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection.
+As a result, the surface is cooler and releases less radiation.
+As a result, the contraction rate may be slower.
+The star would then appear more luminous and cooler than expected from tracks that do not consider magnetic fields.
 
-Comparisons to other results (both real and simulated):  APOGEE, GAIA-ESO,
+{\bf TBD:}  Discussion of Somers+, Feiden (2016)...
 
@@
 \acknowledgements
-The authors thank Gregory N. Mace and Kyle Kaplan for carrying out the IGRINS observations.
+The authors thank Gregory N. Mace for carrying out the IGRINS observations.
 
-MG-S and GJH are supported by general grant 11473005 awarded by the National
-Science Foundation of China.
+MG-S and GJH are supported by general grant 11473005 awarded by the National Science Foundation of China.
 The ESPaDOnS observations are supported by the contribution to the MATYSSE Large Project on CFHT obtained through the Telescope Access Program (TAP), which has been funded by the ``the Strategic Priority Research Program---The Emergence of Cosmological Structures'' of the Chinese Academy of Sciences (Grant No.11 XDB09000000) and the Special Fund for Astronomy from the Ministry of Finance.
@@
 This research has made use of NASA's Astrophysics Data System.  
-
 Based on data from the OMC Archive at CAB (INTA-CSIC), pre-processed by ISDC.
-
 We acknowledge with thanks the variable star observations from the AAVSO International Database contributed by observers worldwide and used in this research.
-
 This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.

### 2016-08-02 document/ms.tex
Small typos and additional text for figure caption for the manuscript

@@
 	\includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
-	\caption{\name $V-$band photometric monitoring from 1986$-$2016.
+	\caption{Overview of \name $V-$band photometric monitoring from 1986$-$2016.
 The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DoubleSpec, and TripleSpec.
@@
 So stellar parameter estimates $\vT_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
-The $N_{\rm ord}$ sets of inferences on $\vT_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or clear model mismatches.
-This process can be thought of as a course approximation to the much more sophisticated spectral line outlier rejection described in \iancze.
+The $N_{\rm ord}$ sets of inferences on $\vT_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or conspicuous model mismatches.
+This process can be thought of as a coarse approximation to the much more sophisticated spectral line outlier rejection described in \iancze.
 
@@
 
-We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth spectrum from Table \ref{tbl_estimated_V}.
-The spectrum was apportioned into a subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
+We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth ESPaDOnS spectrum from Table \ref{tbl_estimated_V}.
+The spectrum was apportioned into subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
 Full-spectrum fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/single_Teff_v_order}
-	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum assuming a single component photosphere.
-}
+	\includegraphics[width=0.8\textwidth]{figures/single_Teff_v_order}
+	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
+The top panel indicates the location and size of spectral chunks used to derive the values in the bottom panel.
+The IGRINS orders also show typical atmospheric transmission (red lines) in the infrared.
+Unused spectral chunks are lightened.
+The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.}
 	\label{fig:SingleTeffvsOrder}
@@
 The MCMC samples had 5000 steps with 40 walkers.
-The stellar parameter ranges were $\logg \in [-3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [2700, 4500]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.
+The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [2700, 4500]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.
 The MCMC chains all appeared to converge after about 1500 steps.

### 2016-08-02 document/ms.tex
Add violin plot, trim and clip the bounding boxes of the PDF latex figures made with EPS by GJH.

@@
 %In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
-The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K, solar metalicity, and $\logg=3.5$.
+The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K, solar metallicity, and $\logg=3.5$.
 The flux density ratio is the flux per solid angle, so the delivered flux ratio for a finite sized starspot will depend on the (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.
@@
 
-Full-spectrum fitting was performed for 43 of the 54 available IGRINS spectral orders as described in Sectrion \ref{sec:methods} and Appendix \ref{methods-details}.
+Full-spectrum fitting was performed for 43 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.
 The MCMC samples had 5000 steps with 40 walkers.
@@
 Estimates of $\logg$ appeared the high end of our search range, $3.5 <\logg <4.0$, yielding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{donati14}.
-The estimates for $\Z$ yield a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metalicity, while the shorter wavelength values prefer slightly sub-solar metalicity.
-Orders 79, 81, 90, and to a lesser extent 78 and 76 showed aritificially tight constraints on $\Z$, biased to large values.
+The estimates for $\Z$ yield a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metallicity, while the shorter wavelength values prefer slightly sub-solar metallicity.
+Orders 79, 81, 90, and to a lesser extent 78 and 76 showed artificially tight constraints on $\Z$, biased to large values.
 Similarly, orders 86, 101, 102, 104, 106, all had $\Z$ estimates biased to extremely low values.
-Visual inspection of these orders indicates that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metalicity estimate alone.
+Visual inspection of these orders indicates that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
 These spectral line outlier orders also tend to bias estimates of effective temperature.
@@
 The $K-$band orders demonstrate much more scatter than $H-$band, with no single photospheric temperature sticking out as strongly favored, but with values of $\teffa \sim 3900$ K and $\teffb \sim 2800$ K consistent with many orders.
-The $K-$band spectra possess strongly correlated residuals from poor telluric correction, as well as uncorrected hydrogen line features that appear as flux excessess after division by telluric standard spectrum.
+The $K-$band spectra possess strongly correlated residuals from poor telluric correction, as well as uncorrected hydrogen line features that appear as flux excesses after division by telluric standard spectrum.
 These instrumental afflictions degraded fits to several orders.
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/LkCa4_HK_mixTeff_by_order} 
-	\caption{Two-temperature model properties, $\teffa$ and $\teffb$, derived independently from full-spectrum fitting 43 IGRINS orders.
-The top panel denotes typical telluric transmission for all of the possible 54 IGRINS orders.
-The derived effective temperatures show enhanced scatter in $K-$band.}
-	\label{fig:TwoTempResults}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.39\textwidth]{figures/LkCa4_fill_vs_Teff2} 
-	\caption{Joint constraint on the temperature of starspots $\teffb$, and their observed solid-angular filling factor $f$.
-Each data point and error bar are taken from Table \ref{tbl_order_results}, with the error bars therefore representing 2$\sigma$ errors.}
+	\includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
+	\caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $c$, derived independently from full-spectrum fitting to 41 IGRINS orders.
+Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($m=111$) consistent with negligible starspot emission, and others ($m=104, 102, 100$) showing tight constraints on the filling factor of starspots.
+The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.
+$K-$band orders show lower estimates for the ambient photosphere, though some of these estimates are unreliable due to spectral line outliers}
 	\label{fig:TwoTempResults}
@@
 	\centering
-    	\vspace{-20mm}
-	\includegraphics[width=0.95\textwidth]{figures/phot1_paper} 
-    	\vspace{-100mm}
+	\includegraphics[trim=3.1cm 13cm 2.3cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot1_paper}
 \caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
@@
 	\centering
-    	\vspace{-120mm}
-	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores} 
+	\includegraphics[trim=2.1cm 13cm 2.5cm 3.1cm, clip=true, width=0.60\textwidth]{figures/lkca4_lores}
 	\caption{The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
 The inset shows that the 3000 K (red, 70\% fill factor) and 4200 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4200 K component dominates the blue emission.
-The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.}
+The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
+\todo{Fix the $x-$axis label to be micron instead of Angstrom.} }
 	\label{fig:lores}
@@
 	\centering
-    	\vspace{-120mm}
-	\includegraphics[width=0.95\textwidth]{figures/lkca4_lores_twopanel} 
+	\includegraphics[trim=2.3cm 2.3cm 1.8cm 13.9cm, clip=true, width=0.75\textwidth]{figures/lkca4_lores_twopanel}
 	\caption{The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere, and the two temperature photosphere that best fit the IGRINS spectrum.
@@
 	\centering
-    	\vspace{-20mm}
-	\includegraphics[width=0.95\textwidth]{figures/vband_spot} 
-    	\vspace{-100mm}
-\caption{The $V$-band magnitude in 2014--2015 {\bf check}, converted into fill factor for the cool component.
+	\fbox{\includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.75\textwidth]{figures/vband_spot} }
+\caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
 The optical brightness depends mostly on the hot component.
@@
 The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\delta V=0.6$.
-}
+\todo{Update with all available photometry or the derived multi-term fit} }
 \label{fig:vband_spot}
@@
 In reality, the low temperature starspot spectrum of \name could exhibit $\A \neq 0$, resulting in a greater amplitude of residual spectrum correlations, and/or biased estimates for other parameters.
-Our Gaussian process inference framework yields some resilence to the former problem.
+Our Gaussian process inference framework yields some resilience to the former problem.
 For the latter, nonzero $\A$ would only impact a subset of all lines, and only to at a magnitude of typical departures of $\A$ in the solar neighborhood.

### 2016-08-02 document/ms.tex
All figures are not trimmed to the correct bounding box using Latex clip and trim commands to includegraphics.  These will need to be updated if the figure shape changes.

@@
 	\centering
-	\fbox{\includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.75\textwidth]{figures/vband_spot} }
+	\includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot}
 \caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
@@
 	\centering
-	\includegraphics[width=0.49\textwidth]{figures/bv_kh95} 
-    \includegraphics[width=0.49\textwidth]{figures/vr_kh95} 
+	\begin{tabular}{ll}
+	\includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{figures/bv_kh95} 
+    &
+    \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{figures/vr_kh95}
+    \end{tabular}
 \caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions from converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{kenyon95} (purple lines).}
-\vspace{-50mm}
 \label{fig:colors}
@@
 	\centering
-	\vspace{-60mm}
-	\includegraphics[width=0.95\textwidth]{figures/lkca4_tio_forpaper} 
-    	\vspace{-30mm}
+	\includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{figures/lkca4_tio_forpaper}
 	\caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
@@
 	\centering
-    %	\vspace{-30mm}
-	\includegraphics[width=0.95\textwidth]{figures/lkca4_hrdiag_forpaper}
-    	\vspace{-80mm}
+	\includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag_forpaper}
 	\caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.

### 2016-08-02 document/ms.tex
Add Paw Robershawnnn citation and APOGEE reference

@@
 Magnetic activity is a likely source of significant uncertainty in both the models and observations of young low-mass stars.
-Convection at these young ages generate strong magnetic fields, as measured in Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}, which cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14}.
+Convection at these young ages generate strong magnetic fields, as measured in Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}, which cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14, robertson14}.
 Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (\citet{somers15}, \citet{feiden16}; see also \citet{baraffe15} for an updated treatment of convection without introducing magnetic fields).
@@
 Starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
-For example, effective temperatures for 3493 young stars measured using the APOGEE spectrograph ($1.5-1.70 \;\mu$m at $R=22,500$) are offset by 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) relative to previous measurements, usually from optical \citep{cottaar14}.
+For example, effective temperatures for 3493 young stars measured using the APOGEE spectrograph \citep[$1.5-1.70 \;\mu$m at $R=22,500$][]{wilson10} are offset by 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) relative to previous measurements, usually from optical \citep{cottaar14}.
 

### 2016-08-02 document/ms.tex
Add software references, but the software command requires AASTEX6

@@
 \newcommand{\name}{LkCa4 }
+\newcommand{\project}[1]{\textsl{#1}}
 %\def\vsini{$v\sin{i_*}$}
@@
 At low resolution, SED modeling \citep{wolk96} has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).
-At high resolution, line depth ratio analysis has historically been demonstrated on evolved stars in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
+At high resolution, line depth ratio analysis has been demonstrated mostly on evolved stars in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
 
@@
 Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution panchromatic near-IR spectrum of \name in Section \ref{sec:two_tempIGRINS} .
-Sections 4.1, 4.2, and 4.3 show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
+Sections \ref{sec:SED}, \ref{sec:rotSpot}, and \ref{sec:RotTiO} show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
 All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
@@
 Finally, unpublished data from the ASAS-SN survey \citep{shappee14}, were obtained from 2012 January -- 2016 March in 186 visits.
-Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1986-2016.
+Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1985-2016.
 
@@
 
-\subsection{The Spectral Energy Distribution}
+\subsection{The Spectral Energy Distribution}\label{sec:SED}
 
@@
 
-\subsection{Rotational modulation of the hot spot}
+\subsection{Rotational modulation of the hot spot}\label{sec:rotSpot}
 
@@
 
-\subsection{Rotational Modulation of TiO Depth}
+\subsection{Rotational Modulation of TiO Depth}\label{sec:RotTiO}
 
@@
 {\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, 
+{\it Software: } TBD
+	\project{pandas} \citep{mckinney10}
+    \project{emcee} \citep{foreman13},
+	\project{matplotlib} \citep{hunter07},
+	\project{numpy} \citep{vanderwalt11},
+	\project{scipy} \citep{jones01},
+	\project{ipython} \citep{perez07},
+	\project{gatspy} \citep{JakeVanderplas2015},
+	\project{starfish} \citep{czekala15}
+%\software{%
+%	\project{pandas} \citep{mckinney10}
+%    \project{emcee} \citep{foreman13},
+%	\project{matplotlib} \citep{hunter07},
+%	\project{numpy} \citep{vanderwalt11},
+%	\project{scipy} \citep{jones01},
+%	\project{ipython} \citep{perez07},
+%	\project{gatspy} \citep{JakeVanderplas2015},
+%	\project{starfish} \citep{czekala15}}.
 

### 2016-08-03 document/ms.tex
Settle on using f_Omega for the fill factor, add some text about observational fill factor

@@
 \providecommand{\adsurl}[1]{\href{#1}{ADS}}
-\newcommand{\name}{LkCa4 }
+\newcommand{\name}{LkCa 4 }
 \newcommand{\project}[1]{\textsl{#1}}
@@
 \begin{abstract}
-We interpret the high resolution near-IR spectra of \name.  We used the instrument IGRINS.
+We interpret the high resolution near-IR spectra of LkCa 4.  We used the instrument IGRINS.
 \end{abstract}
@@
 Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
-The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep{hartigan95,kenyon98,edwards06,cauley12,yang12,ardila13,castro13,loyd14,martinez15}, has no evidence for a close companion \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11}}, demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}, has recently been examined with ZDI \citep{donati14}, and has large ($\Delta \teff \sim$500 K) disagreement about its effective temperature \citep{herczeg14}.
+The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep{hartigan95,kenyon98,edwards06,cauley12,yang12,ardila13,castro13,loyd14,martinez15}, has no evidence for a close companion \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}}, demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}, has recently been examined with ZDI \citep{donati14}, and has large ($\Delta \teff \sim$500 K) disagreement about its effective temperature \citep{herczeg14}.
 The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
@@
 Telluric correction was performed by dividing the spectrum of \name by a spectrum of HR 1237, an A0V star observed immediately before \name, both at airmass 1.1.
-The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of \name.
+The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of LkCa 4.
 No effort was made to remove these flux excesses, which affect several spectral orders.
@@
 
-The Palomar/DBSP data was previously described in \citet{herczeg14}.
+The Palomar/DBSP data was previously described in \citet{herczeg14}.  Briefly, these flux-calibrated spectra cover 3000-8700 $\AA$ at a spectral resolution $R\sim500-700$.
 
@@
 An archive of 1173 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
-Published data targeting \name\ is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
+Published data targeting \name is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
 ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002$-$2004.
@@
 \begin{eqnarray} \label{eqn:mix_M}
-f_{\mathrm{mix}} = \Omega_a f(\teffa)  + \Omega_b f(\teffb)
+S_{\mathrm{mix}} = \Omega_a B(\teffa)  + \Omega_b B(\teffb)
 \end{eqnarray}
 
-The observed filling factor of starspots $c$ is simply the ratio:
+where $B$ is the spectral radiance from emulated model spectra.  The observed filling factor of starspots $f_{\Omega}$ is simply the ratio:
 
 \begin{eqnarray} \label{eqn:fill_factor}
-c = \frac{\Omega_b}{\Omega_a + \Omega_b}
+f_{\Omega} = \frac{\Omega_b}{\Omega_a + \Omega_b}
 \end{eqnarray}
 
-The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $c$.
+Note that $f_{\Omega}$ represents an instantaneous, observational fill factor seen on one hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
+In the limit of homogenously distributed spots, $f_{\Omega}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\Omega}$ can vary cyclicly though rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
+
+The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $f_{\Omega}$.
 The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in effective temperature.
@@
 The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order.
-So stellar parameter estimates $\vT_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vT$ that was based on all $N_{\rm ord}$ spectral orders.
-The $N_{\rm ord}$ sets of inferences on $\vT_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or conspicuous model mismatches.
+So stellar parameter estimates $\vt_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
+The $N_{\rm ord}$ sets of inferences on $\vt_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or conspicuous model mismatches.
 This process can be thought of as a coarse approximation to the much more sophisticated spectral line outlier rejection described in \iancze.
@@
 We computed the median value and 5$^{th}$ and $95^{th}$ percentiles of burned-in subsets of the MCMC samples described above.
-Overall these 26 sets of point estimates for $\vT_{m}$, $\vP_m$ show relatively good agreement, with exceptions.
+Overall these 26 sets of point estimates for $\vT_{o}$, $\vP_o$ show relatively good agreement, with exceptions.
 We have little constraint on $\logg$ and $\Z$ since full-spectrum fitting tends to wash out the weak signal contained in line wings for spectra with a finite level of random noise and systematic error.
@@
 
-We performed full-spectrum fitting on 32 of the 54 available IGRINS spectral orders, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $m$.
+We performed full-spectrum fitting on 32 of the 54 available IGRINS spectral orders, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $o$.
 We used the same analysis procedure as described for the ESPaDoNs spectra, with one exception.
@@
 The range for all 43 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
-Spectral orders $m=91$ and $94$ had exceptionally large uncertainties on their values for $v_z$ and $\vsini$, which makes sense since these two orders are badly affected by telluric absorption artifacts.
+Spectral orders $o=91$ and $94$ had exceptionally large uncertainties on their values for $v_z$ and $\vsini$, which makes sense since these two orders are badly affected by telluric absorption artifacts.
 
@@
 	\includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
-	\caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $c$, derived independently from full-spectrum fitting to 41 IGRINS orders.
-Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($m=111$) consistent with negligible starspot emission, and others ($m=104, 102, 100$) showing tight constraints on the filling factor of starspots.
+	\caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 41 IGRINS orders.
+Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=111$) consistent with negligible starspot emission, and others ($o=104, 102, 100$) showing tight constraints on the filling factor of starspots.
 The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.
@@
 The choice to standardize fluxes makes no difference for modeling a single photospheric component.
-But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $c \equiv \Omega_b/(\Omega_a+\Omega_b)$.
+But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $f_{\Omega} \equiv \Omega_b/(\Omega_a+\Omega_b)$.
 So we scale the mixture model in the following way:
@@
 Interpolation can cause pile-up near model grid-points, as noted in \citet{cottaar14}, which motivated the spectral emulation procedure in \iancze.
-We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable in the distribution of samples in the starspot areal coverage fraction $c$.
-One drawback of our estimator method compared to the Gaussian Process regression method is that we do not propagate the uncertainty associated with the absolute flux ratio interpolation into our estimate of $c$.
+We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable in the distribution of samples in the starspot areal coverage fraction $f_{\Omega}$.
+One drawback of our estimator method compared to the Gaussian Process regression method is that we do not propagate the uncertainty associated with the absolute flux ratio interpolation into our estimate of $f_{\Omega}$.
 We assume this uncertainty is relatively small and can be ignored.
@@
 
-Table \ref{tbl_history} lists measurements of LkCa4 from previous studies.
+Table \ref{tbl_history} lists measurements of \name from previous studies.
 \input{tables/tbl_history.tex}

### 2016-08-03 document/ms.tex
Provide overview of Section 3

@@
 
-The Palomar/DBSP data was previously described in \citet{herczeg14}.  Briefly, these flux-calibrated spectra cover 3000-8700 $\AA$ at a spectral resolution $R\sim500-700$.
-
-APO/TripleSpec (Covey)
-\todo{fill in details about TripleSpec data}
+The Palomar/DBSP \citep{oke82} data was previously described in \citet{herczeg14}.
+Briefly, these flux-calibrated spectra cover 3000$-$8700 $\AA$ at a spectral resolution $R\sim500-700$ in two epochs.
+The DBSP data were acquired near-contemporaneously with near-IR spectra from APO/TripleSpec \citep{wilson04}.
+\todo{(Covey) Fill in details about TripleSpec data}
 
@@
 
-An archive of 1173 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
+An archive of 1216 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
 Published data targeting \name is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
@@
 The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.
-Finally, unpublished data from the ASAS-SN survey \citep{shappee14}, were obtained from 2012 January -- 2016 March in 186 visits.
+Unpublished data from the ASAS-SN survey \citep{shappee14}, were obtained from 2012 January -- 2016 March in 186 visits.
+Finally, recent photometry from the ongoing Crimean Astrophysical Observatory (CrAO) ROTOR project \citep{grankin08} is presented here for the first time.
+The CrAO data includes 43 $BVR$ visits from August 2015 - March 2016.
 Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1985-2016.
@@
 
-\todo{Provide overview of section...}
+As noted previously, line depth ratio analysis has traditionally been limited to isolated portions of spectrum that possess spectral lines attributable only to starspots and spectral lines attributable only to ambient photosphere \citep[\emph{e.g.}][]{neff95, oneal01}.
+The apparent veiling of the lines and their respective temperature dependences can be combined to solve for the starspot and ambient photosphere temperatures and relative areal coverages.
+The line depth ratio method suffers from the need to identify portions of the spectrum that possess such strong lines, and also suffers from the need to assemble large atlases of observed spectral templates to which the spotted star spectrum can be compared.
+In this section we introduce a generalization of line depth ratio analysis which employs pixel-by-pixel modeling of spectral orders.
+By leveraging all the channels present in a spectrum, this strategy has the power to constrain starspot properties at relatively low fill-factors, and identify weak lines that originate from the starspot.
+
+We took two approaches to characterizing the effective temperature response from a spotted-star spectrum.
+First we measured a single effective temperature to unique spectral orders in the optical (\S \ref{sec:ESP_starfish}) and near-IR (\S \ref{sec:IGR_starfish}).
+Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to the near-IR spectra (\S \ref{sec:two_tempIGRINS}), which should show greater starspot flux density than optical(\S \ref{sec:whyNearIR}).
 
@@
 
-Note that $f_{\Omega}$ represents an instantaneous, observational fill factor seen on one hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
+Note that $f_{\Omega}$ represents an instantaneous, observational fill factor seen on one projected hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
 In the limit of homogenously distributed spots, $f_{\Omega}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\Omega}$ can vary cyclicly though rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
@@
 
-\subsection{Single temperature fitting to the ESPaDoNs spectrum}
+\subsection{Single temperature fitting to the ESPaDOnS spectrum}\label{sec:ESP_starfish}
 
-We performed spectral fitting on the ESPaDoNs spectrum acquired on 2014 January 11, the fourth ESPaDOnS spectrum from Table \ref{tbl_estimated_V}.
+We performed spectral fitting on the ESPaDOnS spectrum acquired on 2014 January 11, the fourth ESPaDOnS spectrum from Table \ref{tbl_estimated_V}.
 The spectrum was apportioned into subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
@@
 
-\subsection{Single temperature fitting to the IGRINS spectrum}
+\subsection{Single temperature fitting to the IGRINS spectrum}\label{sec:IGR_starfish}
 
 We performed full-spectrum fitting on 32 of the 54 available IGRINS spectral orders, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $o$.
-We used the same analysis procedure as described for the ESPaDoNs spectra, with one exception.
+We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
 For the IGRINS $K-$band, we employed an expanded search range for the effective temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.
@@
 
-\subsection{Heightened sensitivity to starspot spectral lines in the infrared}
+\subsection{Heightened sensitivity to starspot spectral lines in the infrared}\label{sec:whyNearIR}
 
-Some care should be taken when directly comparing results between the ESPaDoNs and IGRINS spectra since they were not taken at the same time.
-These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.
-Assuming the areal coverage fraction of spots was the same or greater during the ESPaDoNs spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
+Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.
+These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.
+Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
 The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.
@@
 
-{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, 
+{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}
 {\it Software: } TBD

### 2016-08-03 document/ms.tex
Closes #32-- shorten Section 3.2

@@
 Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1985-2016.
+HJD, BJD, and JD are simply refered to as JD, which is accurate to the precision of available data.
 
@@
 The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-The estimated $BVR$ magnitudes at the time of the spectral observations are determined from a regularized multiterm fit \citep{vanderplas15a} shown as the solid blue line in Figure \ref{fig:PhotPhase}.
+The estimated $BVR$ magnitudes at the time of the spectral observations are determined from regularized multiterm fits \citep{vanderplas15a} shown as the solid blue lines in Figure \ref{fig:PhotPhase}.
 Table \ref{tbl_estimated_V} lists the estimated $BVR$ photometry and the observing epoch for data from IGRINS, ESPaDOnS, 2MASS \citep{skrutskie06}, DoubleSpec, and TripleSpec.
@@
 The modular framework was altered to accommodate starspot measurements in two ways.
-First, the single photospheric component was updated to includes a starspot spectrum.
+First, the single photospheric component was updated to include a starspot spectrum.
 Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added in the starspot model.
@@
 The Metropolis-Hastings step sizes were tuned with several iterations of burn-in procedure and the final chains were visually checked for convergence.
-Nine of the 35 available spectral orders failed to converge, possibly due to numerical artifacts arising from poor model fits.
+Nine of the 35 available spectral orders failed to converge, due to numerical artifacts arising from poor model fits.
 For the other 26 spectral orders, the number of samples was generally much longer than the estimated integrated autocorrelation length.
@@
 We computed the median value and 5$^{th}$ and $95^{th}$ percentiles of burned-in subsets of the MCMC samples described above.
-Overall these 26 sets of point estimates for $\vT_{o}$, $\vP_o$ show relatively good agreement, with exceptions.
+Overall the 26 sets of point estimates for stellar parameters show relatively good agreement, with exceptions.
 We have little constraint on $\logg$ and $\Z$ since full-spectrum fitting tends to wash out the weak signal contained in line wings for spectra with a finite level of random noise and systematic error.
 Meanwhile, strong metal lines can bias estimates of $\Z$ at the expense of estimates for $\teff$.
-We get consistent estimates for $v_z \sim 15.6 \pm 0.6$ km/s and $\vsini \sim 28.0 \pm 0.9$ km/s, with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$.
-These two outlying spectral orders converged to unreasonably large values for $\vsini$ and $a_{\rm G}$, the amplitude of the Gaussian process covariance kernel.
-One of these orders has an unusually small value for effective temperature, $\teff\sim3500$, comparable to the lower limit of the employed model grid.
-Visual comparison of the observed spectrum for a range of fits for these orders shows that no single emulated spectrum could reasonably fit their spectrum because there are numerous large spectral outliers.
+Estimates for $v_z \sim 15.6 \pm 0.6$ km/s and $\vsini \sim 28.0 \pm 0.9$ km/s are consistent across all orders with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$ due to numerous large spectral outliers.
 The more-well-behaved spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
-Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each of the 26 spectral orders.
+Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each spectral order.
 
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{figures/single_Teff_v_order}
+	\includegraphics[width=0.65\textwidth]{figures/single_Teff_v_order}
 	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
@@
 For the IGRINS $K-$band, we employed an expanded search range for the effective temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.
-No effort was made to shift the wavelength scales of the IGRINS data and \PHOENIX\ model into the same system, so the absolute values of $v_z$ are arbitrary shifted.
 
-We find a larger dispersion in the point estimates for the stellar parameters derived from the IGRINS data with single temperature fits.
+We find a larger dispersion in the point estimates for the stellar parameters derived from the IGRINS data than those derived in optical.
 The most conspicuous trend is in the derived effective temperature as a function of wavelength shown in Figure \ref{fig:SingleTeffvsOrder}.
-Here we see dramatic result that the effective temperature peaks at a values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
-The $K-$band shows even lower derived effective temperatures of $\sim3300$ K.
-
-\subsection{Interpretation of the single temperature fitting results}
-
-The effective temperature derived at different wavelength intervals exhibit a $\Delta \teff \sim 800$ K spread.
+The effective temperature peaks at a values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
+The $K-$band shows even lower derived effective temperatures of $\sim3300$ K, a $Delta \teff \sim 700$ K spread from optical.
 No single temperature can describe all the spectral lines present in the high resolution optical and IR spectra.
-This discrepancy is circumstantial evidence for the detection of spectral lines attributable to starspots.
-This circumstantial evidence should not be surprising given the previous evidence that \name possesses a large coverage fraction of starspots \citep{grankin08,donati14}.
-
-%We performed a further plausibility check to constrain the effect size of starspots.
-We generated flux calibrated spectra at two temperatures, and forward-modeled them to resemble the LkCa4 IGRINS and ESPaDOnS spectra in all other ways (\emph{i.e.} $\logg, \Z, \vt_{\rm ext}$), including noise and calibration parameters.
-We coadded the spectra in a mixture model:  $ \mathsf{M}_{mix} = c \cdot \mathsf{M}_A(T_\textrm{eff,A}) + (1-c) \cdot \mathsf{M}_B(T_\textrm{eff,B})$.
-We chose a fill factor of starspots of 30\%.
-We then re-ran our single-temperature fitting procedure on the two-temperature, synthetic, noised-up data to see what stellar parameters our full-spectrum fitting procedure would na\"{\i}vely derive.
+This discrepancy is circumstantial evidence for the detection of spectral features attributable to starspots.
 
@@
 
-%In Figure XX we plot the ratio of black body flux density at temperatures 4100 K and 3300 K with a red line.
-The blue line is the ratio of two smoothed \PHOENIX model spectra with 4100 K and 3300 K, solar metallicity, and $\logg=3.5$.
-The flux density ratio is the flux per solid angle, so the delivered flux ratio for a finite sized starspot will depend on the (flux-weighted) solid angle of the starspot relative to the (flux-weighted) solid angle of the stellar disk, vis-a-vis Equations \ref{eqn:Mix_M} and \ref{eqn:fill_factor}.
-%\todo{Put in the flux density ratio plot.}
-%\comm{Should we change the plot numbers from 4100 and 3300 to 4200 and 3000?  -These would end up being closer to the best fit values.}
-
 In summary, the visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
-The infrared spectrum will have a lower overall spot contast, but will have higher relative contribution attributable to the cool patches.
+The infrared spectrum will have a lower overall spot contast, but will have more net starspot flux than optical.
 This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{prato08}.
-%\comm{This blurb should probably go in the introduction.}
 
@@
 The MCMC samples had 5000 steps with 40 walkers.
-The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range for $H-$ band was $\teffa, \teffb \in [2700, 4500]$, and was expanded to $\teffa, \teffb \in [2700, 4500]$ for $K-$band.
+The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.
+$H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$.
 The MCMC chains all appeared to converge after about 1500 steps.
 
-Marginalized point estimates were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
-The fit quality was assessed by examining the consistency of the point estimates across the spectral orders.
+Marginalized distributions were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
+The fit quality was first assessed by examining the consistency of the point estimates across the spectral orders.
 The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
 The range for all 43 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
-Spectral orders $o=91$ and $94$ had exceptionally large uncertainties on their values for $v_z$ and $\vsini$, which makes sense since these two orders are badly affected by telluric absorption artifacts.
+Two orders with poor telluric correction ($o=91$ and $94$) had exceptionally large uncertainties on their values for $v_z$ and $\vsini$.
 
-As noted previously, the full-spectrum fitting method offers little constraining power on $\logg$, and $\Z$ can be biased in the face of systematic spectral line outliers.
-Estimates of $\logg$ appeared the high end of our search range, $3.5 <\logg <4.0$, yielding a median value of the point estimates of 3.8 and a standard deviation of 0.1, consistent with previously published values from \citet{donati14}.
-The estimates for $\Z$ yield a slight trend with wavelength-- the longest wavelength orders tend to prefer higher metallicity, while the shorter wavelength values prefer slightly sub-solar metallicity.
-Orders 79, 81, 90, and to a lesser extent 78 and 76 showed artificially tight constraints on $\Z$, biased to large values.
-Similarly, orders 86, 101, 102, 104, 106, all had $\Z$ estimates biased to extremely low values.
-Visual inspection of these orders indicates that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
+Some orders indicates that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
 These spectral line outlier orders also tend to bias estimates of effective temperature.
@@
 	\project{starfish} \citep{czekala15}
+	\project{seaborn} \citep{waskom14}
 %\software{%

### 2016-08-03 document/ms.tex
Continuing on with Issue #33 with a goal of having a shareable draft soon.

@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
-	\includegraphics[width=0.65\textwidth]{figures/single_Teff_v_order}
+	\includegraphics[width=0.48\textwidth]{figures/single_Teff_v_order}
 	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
@@
 	\label{fig:SingleTeffvsOrder}
-\end{figure*}
+\end{figure}
 
@@
 Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.
-These spectra have comparable albeit different $\hat V$ of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.
+These spectra have comparable albeit different $V_{\rm est}$ of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.
 Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
@@
 
-Full-spectrum fitting was performed for 43 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.
+Full-spectrum fitting was performed for 48 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.
 The MCMC samples had 5000 steps with 40 walkers.
@@
 The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
-The range for all 43 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
+The range for all 48 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
 Two orders with poor telluric correction ($o=91$ and $94$) had exceptionally large uncertainties on their values for $v_z$ and $\vsini$.
 
-Some orders indicates that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
+The posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Appendix Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.
+
+Overplotting models with the observed spectra yielded insights on why some orders failed, and which orders can discriminate between starspots and ambient photospheric lines the best.
+Some orders indicate that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
 These spectral line outlier orders also tend to bias estimates of effective temperature.
@@
 
-Finally, the posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.
 \todo{insert results from re-run of H-band spectra here}
@@
 
-\input{tables/tbl_order_results.tex}
-
 \begin{figure*}
@@
 	\includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
-	\caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 41 IGRINS orders.
+	\caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 48 IGRINS orders.
 Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=111$) consistent with negligible starspot emission, and others ($o=104, 102, 100$) showing tight constraints on the filling factor of starspots.
@@
 
+\section{Full table of IGRINS best fits}
+
+Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
+\comm{It's not clear if we need this table...}
+\input{tables/tbl_order_results.tex}
+
 \acknowledgements

### 2016-08-03 document/ms.tex
Use Grammarly to find grammar and spelling mistakes.  Awkward with latex though.

@@
 
-In this work we constrain the starspot properties of \name with 4 complementary techniques.
+In this work, we constrain the starspot properties of \name with 4 complementary techniques.
 Section \ref{sec:obs} quantifies the optical variability of \name over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
@@
 The Zeeman Doppler Imaging obtained from these observations were analyzed by \citet{donati14}.
-In this paper we concentrate on the intensity spectrum.
+In this paper, we concentrate on the intensity spectrum.
 %\todo{Flux calibration?}
@@
 The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.
-Unpublished data from the ASAS-SN survey \citep{shappee14}, were obtained from 2012 January -- 2016 March in 186 visits.
+Unpublished data from the ASAS-SN survey \citep{shappee14} were obtained from 2012 January -- 2016 March in 186 visits.
 Finally, recent photometry from the ongoing Crimean Astrophysical Observatory (CrAO) ROTOR project \citep{grankin08} is presented here for the first time.
@@
 Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1985-2016.
-HJD, BJD, and JD are simply refered to as JD, which is accurate to the precision of available data.
+HJD, BJD, and JD are simply referred to as JD, which is accurate to the precision of available data.
 
@@
 The line depth ratio method suffers from the need to identify portions of the spectrum that possess such strong lines, and also suffers from the need to assemble large atlases of observed spectral templates to which the spotted star spectrum can be compared.
-In this section we introduce a generalization of line depth ratio analysis which employs pixel-by-pixel modeling of spectral orders.
-By leveraging all the channels present in a spectrum, this strategy has the power to constrain starspot properties at relatively low fill-factors, and identify weak lines that originate from the starspot.
+In this section, we introduce a generalization of line depth ratio analysis which employs pixel-by-pixel modeling of spectral orders.
+By leveraging all the channels present in a spectrum, this strategy has the power to constrain starspot properties at relatively low fill-factors and identify weak lines that originate from the starspot.
 
@@
 Note that $f_{\Omega}$ represents an instantaneous, observational fill factor seen on one projected hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
-In the limit of homogenously distributed spots, $f_{\Omega}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\Omega}$ can vary cyclicly though rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
+In the limit of homogenously distributed spots, $f_{\Omega}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\Omega}$ can vary cyclically through rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
 
@@
 The most conspicuous trend is in the derived effective temperature as a function of wavelength shown in Figure \ref{fig:SingleTeffvsOrder}.
-The effective temperature peaks at a values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
+The effective temperature peaks at values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
 The $K-$band shows even lower derived effective temperatures of $\sim3300$ K, a $Delta \teff \sim 700$ K spread from optical.
@@
 The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
-Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission, according to Wein's displacement law.
+Starspots are cooler than their surrounding photosphere and will, therefore, have a longer wavelength of peak emission, according to Wein's displacement law.
 The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
@@
 In summary, the visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
-The infrared spectrum will have a lower overall spot contast, but will have more net starspot flux than optical.
+The infrared spectrum will have a lower overall spot contrast, but will have more net starspot flux than optical.
 This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{prato08}.
@@
 
-In the previous sections we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
+In the previous sections, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
 These results have testable predictions for the spectral energy distribution (SED) and rotational modulation of features of the SED.
@@
 The $B-V$ is always dominated by the hot component and therefore does not depend on the filling factor of the hot component.
-The $V-R$ varies more with $V$, indicating a larger contribution from the cool component.
+The $V-R$ varies more with $V$, indicating a larger contribution of the cool component.
 The difference between observed and predicted $B-V$ color, $E(B-V)$, may correspond to the extinction.
@@
 The optical emission is dominated by the hotter component while both components contribute to the red and infrared emission (see Figure \ref{fig:lores}).
-The $0.7$ mag range in $V$-band brightness requires at a factor of 1.9 change in the visible surface area of hot component in the limit that the cool component does not contribute any $V$-band emission.
+The $0.7$ mag range in $V$-band brightness requires a factor of 1.9 change in the visible surface area of the hot component in the limit that the cool component does not contribute any $V$-band emission.
 In the 2014-2015 ASAS-SN photometry, the minimum and maximum brightness correspond to cool spot coverage of 83\% and 68\%, respectively.
@@
 The yellow shaded region corresponds to the range of apparent effective temperatures that are would be measured as the hot component rotates into and out of our view.
-The blue circle corresponds to the measurement at blue-optical wavelengths by \citet{donati14}, the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to]{herczeg14}, while the red diamong corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
+The blue circle corresponds to the measurement at blue-optical wavelengths by \citet{donati14}, the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to]{herczeg14}, while the red diamond corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
  \label{fig:hrdiag}
@@
 A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can.
-Computational infeasibility limited our ability to rerun new multi-temperature models and compute model comparison diagnostics like AIC, BIC, or cross validation \citep{ivezic14}.
+Computational infeasibility limited our ability to rerun new multi-temperature models and compute model comparison diagnostics like AIC, BIC, or cross-validation \citep{ivezic14}.
 Such investigations could be considered in future works, but we suspect systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
@@
 
-\emph{Suitability of pre-computed \PHOENIX\ model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX\ synthetic spectra are a good representation to our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
+\emph{Suitability of pre-computed \PHOENIX\ model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX\ synthetic spectra are a good representation of our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
 Cool sunspots are associated with heightened magnetic fields on the sun.
@@
 We also assumed that the spectral pattern of metallicity can be captured by a single coarse metric, $\Z$.
-In reality, the low temperature starspot spectrum of \name could exhibit $\A \neq 0$, resulting in a greater amplitude of residual spectrum correlations, and/or biased estimates for other parameters.
+In reality, the low-temperature starspot spectrum of \name could exhibit $\A \neq 0$, resulting in a greater amplitude of residual spectrum correlations, and/or biased estimates for other parameters.
 Our Gaussian process inference framework yields some resilience to the former problem.
 For the latter, nonzero $\A$ would only impact a subset of all lines, and only to at a magnitude of typical departures of $\A$ in the solar neighborhood.
-The large number of IGRINS orders and spectral lines offers us some resilience to isolated orders badly affected by spectral line outliers.
+The large spectral grasp of IGRINS offers us some resilience to isolated orders badly affected by spectral line outliers.
 

### 2016-08-04 document/ms.tex
A few typo and miscellaneous corrections from a draft read through

@@
 The red and blue lines show the hot photosphere and cool spot spectra respectively.
-We inspected the quality of the fits, generally finding remarkable agreement with most spectral orders.
-Many orders demonstrated spectral line outliers, as noted in \iancze.
+We inspected the quality of the fits, generally finding good agreement with most spectral orders.
+Many orders demonstrated spectral line outliers.
 Most of the gross spectral features are captured by the composite model.
@@
 
-Best fit values for the stellar parameters summarized are listen in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $c=75\pm 10 \% $.
+Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $c=75\pm 10 \% $.
 
@@
 In \S 4.1 we describe how the two components of the photosphere fit low resolution spectra and optical/near-IR photometry.
-The brightness, colors, spectral features should change as the spot rotates around the star.
-In \S 4.2, we convert the $V$ brightness to a filling factor of the cool spot, and then in \S 4.2-4.3 we compare how the expected rotational modulation of photometry and spectral indices compares with observed measurements.
+The brightness, colors, and spectral features should change as the spot rotates around the star.
+In \S 4.2, we convert the $V$ brightness to a filling factor of the cool spot, and then in \S 4.2-4.3 we compare how the expected rotational modulation of photometry and spectral indices compare with observed measurements.
 
@@
 
-Figures~\ref{fig:sed}-\ref{fig:lores} shows that the two-component photosphere matches the SED and flux-calibrated spectra well from $\sim 0.6-2.5$ $\mu$m.
+Figures~\ref{fig:sed}-\ref{fig:lores} show that the two-component photosphere matches the SED and flux-calibrated spectra well from $\sim 0.6-2.5$ $\mu$m.
 The two components have fixed temperatures of 4200 K covering 30\% of the visible surface and 3000 K covering 70\% of the visible surface area.
@@
 
-The lower panels show photospheric spectra scaled separately to the observed red-optical and near-IR spectra.
+The two panels in Figure \ref{fig:lores_twopanel} show photospheric spectra scaled separately to the observed red-optical and near-IR spectra.
 The single temperature spectra are unable to reproduce the observed emission.
-The $3900$ K component fits the TiO bands at reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
+The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
 The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
@@
 
-Extinction paragraph, needs overhaul...  Relative to main sequence colors, the $E(B-V)=0.24$ would yield $A_V=0.72$ mag....  
+\todo{Extinction paragraph, needs overhaul...}  Relative to main sequence colors, the $E(B-V)=0.24$ would yield $A_V=0.72$ mag....  
 The $J-K=0.93$ color is equal to the expected color to within 0.05 => 0.3 mag (for T=3000, 4200)...
@@
 
-Since 1992 the $V$ band brightness has varied from $12.3$ to $13.2$ mag, with a typical range of $0.5$ mag in any single epoch.
+Since 1992 the $V$ band brightness has varied from $12.3$ to $13.2$ mag, with a typical range of $0.5$ mag in any single epoch (\emph{c.f} Figure \ref{fig:PhotPhase}).
 In a two-temperature atmosphere with fixed temperatures, this brightness corresponds directly to a filling factor for both components.
-Figure~\ref{vband_spot} shows this conversion for temperatures of 4200 K, 3000 K, and a 75\% filling factor for the 3000 K component at $V_{est}=12.83$, as estimated at the time of the IGRINS spectrum.
+Figure~\ref{fig:vband_spot} shows this conversion for temperatures of 4200 K, 3000 K, and a 75\% filling factor for the 3000 K component at $V_{\rm est}=12.83$, as estimated at the time of the IGRINS spectrum.
 
 The model photometry is obtained from the main sequence colors compiled by \citet{kenyon95}.
-Colors from dwarfs stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
+Colors from dwarf stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
 Synthetic spectra of $3000-4000$ K stars predict $B-V$ colors that are much bluer than observed and that become bluer at cooler temperatures, the opposite of what is observed.
@@
 The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller amplitude than LkCa 4 in $V$ band.
-Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller.
+Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller \comm{double check this statement}.
 The predicted colors from rotational modulation do not match the observed $V-R_J$ colors or the correlation with $V$, either because of changes in spot properties since the \citet{grankin08} data were obtained or because a two-temperature model for the photosphere is overly simplistic.
+\comm{We could check for seasonal variations in V-R.}
 
@@
 The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}.
-The TiO indices are also combined into a single index by calculating by  calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.
+The TiO indices are also combined into a single index by  calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.
+\comm{this is confusing!}
 
@@
 Since the Hayashi tracks are nearly vertical at this temperature and age, the temperature uncertainty leads directly to an uncertainty in inferred mass.
-Application of multi-temperature atmosphere is also likely to solve long-standing problems related to colors of young stars \citep[e.g.][]{stauffer03}
 
@@
 
-{\bf paragraph MG-S:}  Comparisons to other results (both real and simulated) from single-temperature fits to APOGEE, GAIA-ESO wavelengths.  Approximate is ok...
+{\bf paragraph MG-S:}  Comparisons to other results (both real and simulated) from single-temperature fits to APOGEE, GAIA-ESO wavelengths.  Approximate is ok... \todo{MGS provide text here}
 
@@
 
-We also assumed that the spectral pattern of metallicity can be captured by a single coarse metric, $\Z$.
-In reality, the low-temperature starspot spectrum of \name could exhibit $\A \neq 0$, resulting in a greater amplitude of residual spectrum correlations, and/or biased estimates for other parameters.
-Our Gaussian process inference framework yields some resilience to the former problem.
-For the latter, nonzero $\A$ would only impact a subset of all lines, and only to at a magnitude of typical departures of $\A$ in the solar neighborhood.
-The large spectral grasp of IGRINS offers us some resilience to isolated orders badly affected by spectral line outliers.
+%Our Gaussian process inference framework yields some resilience to the former problem.
 
@@
 {\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}
-{\it Software: } TBD
- \project{pandas} \citep{mckinney10}
+
+{\it Software: } 
+ \project{pandas} \citep{mckinney10},
  \project{emcee} \citep{foreman13},
@@
  \project{gatspy} \citep{JakeVanderplas2015},
- \project{starfish} \citep{czekala15}
+ \project{starfish} \citep{czekala15},
  \project{seaborn} \citep{waskom14}

### 2016-08-04 document/ms.tex
Add a condensed abstract

@@
 
-\shorttitle{\name IGRINS spectroscopy}
+\shorttitle{\name Starspots on LkCa 4}
 
@@
 \begin{abstract}
-We interpret the high resolution near-IR spectra of LkCa 4.  We used the instrument IGRINS.
+The weak-lined T-Tauri star LkCa 4 has no evidence for IR excess, accretion, or nearby companions, and shows exceptionally large photometric modulation attributable to star spots, making it an ideal testbed for measuring starspot properties.
+Infrared spectral features in high resolution data indicate that 70-80\% of the surface is covered in 2700$-$3000 K effective temperature regions at the epoch of the observation.
+The photometric phase curve is scaled to this filling factor to construct the fill-factor-as-a-function-of-phase.
+The SED, color variability, and low-resolution optical/IR spectroscopy are registered to filling factor at their epochs, confirming the large filling factor and temperature contrast of the starspots through time.
+The revised effective temperature and luminosity make LkCa4 appear much lower mass and much younger when placed on a pre-main sequence HR diagram, compared to previous estimates based only on optical spectroscopy and not taking into account the large coverage fraction of cool spots.
 \end{abstract}

### 2016-08-04 document/ms.tex
Trim extraneous text from the Appendix, fix a few miscellaneous place holders

@@
 The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller amplitude than LkCa 4 in $V$ band.
-Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller \comm{double check this statement}.
+Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller.
 The predicted colors from rotational modulation do not match the observed $V-R_J$ colors or the correlation with $V$, either because of changes in spot properties since the \citet{grankin08} data were obtained or because a two-temperature model for the photosphere is overly simplistic.
-\comm{We could check for seasonal variations in V-R.}
 
@@
 The TiO indices are also combined into a single index by  calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.
-\comm{this is confusing!}
 
@@
 
-\subsection{Full-spectrum fitting framework}
-
-\iancze\ define a pixel-level forward model $\vM$ of the data.
-A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.
-The model encapsulates the major intrinsic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:
-
-\begin{eqnarray} \label{eqn:scaling}
-\vM(\vT) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
-         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
-\end{eqnarray}
-
-The $\vt_{\ast}$ are comprised of the dimensions of the pre-computed stellar model grid.
-We use the \PHOENIX\ model grid \citep{husser13}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.
-
-\todo{Remove the matrix/approach jargon and simplify}
-
-\subsection{Discussion of deriving unique Teff in each order}
-\label{sec:approach12}
-
-\todo{Move or delete this section}
-
-This change does not represent reality: by definition, the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.
-The na\"ive single-component fit to different wavelength chunks merely provides a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.
-
-It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect of \emph{e.g.} $\logg$ on the spectrum.
-For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.
-For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \Omega_{o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.
-
-\subsection{Implementation}
-
-\subsubsection{Mixture model definitions}
-
-We construct a mixture model spectrum of the form:
-
-\begin{eqnarray} \label{eqn:mix_M}
-\vM_{\mathrm{mix}}(\vT) = \vM(\teffa, ...) \times \Omega_a + \vM(\teffb, ...) \times \Omega_b
-\end{eqnarray}
-
-Where $\teffa, \teffb, \Omega_a, \Omega_b$ are temperatures and solid angles of two photospheric components respectively.
-All other stellar intrinsic and extrinsic parameters, and instrumental nuisance calibration parameters are shared among the two components, as chronicled in Table \ref{table:params}.
-
+\subsection{Addressing absolute flux calibration}
 If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.
@@
 We are then tasked with computing an estimator, $\hat f(\vt_{\ast})$, for estimating the scale factor $q$ in-between model gridpoints.
-The Right Thing to Do would be to follow \iancze by training a Gaussian process on the $f(\{\vt_{\ast}\}^\textrm{grid})$.
+The Right Thing to Do would be to follow \iancze\ by training a Gaussian process on the $f(\{\vt_{\ast}\}^\textrm{grid})$.
 What We Actually Did was linearly interpolate between the model grid-points.
 Interpolation can cause pile-up near model grid-points, as noted in \citet{cottaar14}, which motivated the spectral emulation procedure in \iancze.
-We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable in the distribution of samples in the starspot areal coverage fraction $f_{\Omega}$.
+We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable as kinks in the distribution of samples in the starspot coverage fraction $f_{\Omega}$.
 One drawback of our estimator method compared to the Gaussian Process regression method is that we do not propagate the uncertainty associated with the absolute flux ratio interpolation into our estimate of $f_{\Omega}$.
@@
 
+\todo{Verify that the final term possesses a $q$ and not a $q^2$ term.}
+
 \section{Previous work}
@@
 Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
-\comm{It's not clear if we need this table...}
+\comm{It's not clear if we need this table.
+If we keep it, we should update it with a reliability index or note about which orders were used in deriving the final values.
+A better table might be a list of new spectral features attributable to the spot.}
 \input{tables/tbl_order_results.tex}

### 2016-08-10 document/ms.tex
Final round of edits to the draft before we set Version 0.5
Comments from GJH on the version 0.5 draft.

@@
 \begin{abstract}
-The weak-lined T-Tauri star LkCa 4 has no evidence for IR excess, accretion, or nearby companions, and shows exceptionally large photometric modulation attributable to star spots, making it an ideal testbed for measuring starspot properties.
-Infrared spectral features in high resolution data indicate that 70-80\% of the surface is covered in 2700$-$3000 K effective temperature regions at the epoch of the observation.
+Starspots temporarily increase the opacity in stellar photospheres, impacting both their instantaneous stellar flux and the duration and efficiency of their convective energy transport during pre-main sequence stellar evolution.
+The observational manifestation of local magnetic fields, starspots on young stars can cover a large fraction of the stellar surface, causing the incorrect assessment of both the effective temperature and the luminosity and therefore the placement of sources on HR diagrams.
+The singleton weak-lined T-Tauri star LkCa 4 shows exceptionally large photometric modulation attributable to star spots, making it an ideal testbed for measuring starspot properties.
+Infrared spectral features in high resolution IGRINS spectra indicate that 70-80\% of the surface is covered in $\teff \sim 2700-3000$ K patches of cool photosphere at the epoch of the observation.
+The rest of the $20-30\%$ of the stellar surface can be thought of as either ambient photosphere, or a hot spot of $\teff\sim4200$ K.
 The photometric phase curve is scaled to this filling factor to construct the fill-factor-as-a-function-of-phase.
-The SED, color variability, and low-resolution optical/IR spectroscopy are registered to filling factor at their epochs, confirming the large filling factor and temperature contrast of the starspots through time.
+The SED, color variability, and low-resolution optical/IR spectroscopy are registered to the filling factors at their epochs, strengthening the large filling factor and temperature contrast of the starspots through time.
 The revised effective temperature and luminosity make LkCa4 appear much lower mass and much younger when placed on a pre-main sequence HR diagram, compared to previous estimates based only on optical spectroscopy and not taking into account the large coverage fraction of cool spots.
+LkCa 4 represents the extreme end of starspot coverage, suggesting that many heavily spotted young stars have been misplaced on the observational HR diagram, leading to incorrect ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
 \end{abstract}
@@
 Magnetic activity is a likely source of significant uncertainty in both the models and observations of young low-mass stars.
-Convection at these young ages generate strong magnetic fields, as measured in Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}, which cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14, robertson14}.
+Convection at these young ages generates strong magnetic fields, as measured in Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}.
 Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (\citet{somers15}, \citet{feiden16}; see also \citet{baraffe15} for an updated treatment of convection without introducing magnetic fields).
@@
 
-Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep{harrison11,davenport15}.
+Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep[\emph{e.g}][]{harrison11,cody14,davenport15}.
 Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{bouvier95,grankin07} can break the degeneracy between starspot areal filling factor and starspot temperature.
@@
 At high resolution, line depth ratio analysis has been demonstrated mostly on evolved stars in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
+Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
 
-Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
-The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep{hartigan95,kenyon98,edwards06,cauley12,yang12,ardila13,castro13,loyd14,martinez15}, has no evidence for a close companion \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}}, demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}, has recently been examined with ZDI \citep{donati14}, and has large ($\Delta \teff \sim$500 K) disagreement about its effective temperature \citep{herczeg14}.
+The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep[\emph{e.g.}][]{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep[\emph{e.g.}]{kenyon98,edwards06,cauley12,yang12}, has no evidence for a close companion \citep{karr10,kraus11,nguyen12,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}}, and demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}.
 The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
+
+LkCa 4 has recently been examined with ZDI \citep{donati14}.  Unanswered questions about the large disagreement ($\Delta \teff \sim$500 K) in LkCa 4's effective temperature \citep{herczeg14} remain.
 
@@
 \subsection{IGRINS Spectroscopy}\label{sec:igrins} 
-We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{gully12,park14} on the Harlan J.
+We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{park14} on the Harlan J.
 Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
 IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48 \um.
-The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band.
+The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band \citep{gully12}.
 The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.
@@
 
-As noted previously, line depth ratio analysis has traditionally been limited to isolated portions of spectrum that possess spectral lines attributable only to starspots and spectral lines attributable only to ambient photosphere \citep[\emph{e.g.}][]{neff95, oneal01}.
+Starspots possess a spectrum distinct from the ambient photosphere.
+Spatially resolved spectra of starspots have not yet been observed for stars beyond the sun, though interferometric techniques \todo{cite} and planetary transits \todo{cite} are promising.
+Approaches like ZDI and line-bisector analysis \todo{cite} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.
+In contrast, the technique described in this Section detects and measures the spectral lines originating from starspots photospheric emission.
+
+Starspot line depth ratio analysis has traditionally been limited to isolated portions of spectrum that possess spectral lines attributable only to starspots and spectral lines attributable only to ambient photosphere \citep[\emph{e.g.}][]{neff95, oneal01}.
 The apparent veiling of the lines and their respective temperature dependences can be combined to solve for the starspot and ambient photosphere temperatures and relative areal coverages.
@@
 The \iancze\ technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
-We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
+We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
 The modular framework was altered to accommodate starspot measurements in two ways.
@@
 
-Note that $f_{\Omega}$ represents an instantaneous, observational fill factor seen on one projected hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
+The term $f_{\Omega}$ represents an instantaneous, observational fill factor seen on one projected hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
 In the limit of homogenously distributed spots, $f_{\Omega}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\Omega}$ can vary cyclically through rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
@@
 The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in effective temperature.
-So the second important change to the spectral inference framework involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
+This challenge motivated the second important change to the spectral inference framework, which involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
 The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
 The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order.
-So stellar parameter estimates $\vt_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
+Stellar parameter estimates $\vt_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
 The $N_{\rm ord}$ sets of inferences on $\vt_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or conspicuous model mismatches.
@@
 The effective temperature peaks at values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
-The $K-$band shows even lower derived effective temperatures of $\sim3300$ K, a $Delta \teff \sim 700$ K spread from optical.
+The $K-$band shows even lower derived effective temperatures of $\sim3300$ K, or 700 K cooloer than estimated from optical.
 No single temperature can describe all the spectral lines present in the high resolution optical and IR spectra.
@@
 The infrared spectrum will have a lower overall spot contrast, but will have more net starspot flux than optical.
-This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{prato08}.
 
@@
 The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.
-$H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$.
+$H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$ km/s.
 The MCMC chains all appeared to converge after about 1500 steps.
@@
 The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
-The range for all 48 orders was $v_z = 12.4 \pm 2.6$ and $\vsini = 28.8 \pm 2.0$.
+The range for all 48 orders was $v_z = 12.4 \pm 2.6$ km/s and $\vsini = 28.8 \pm 2.0$ km/s.
 Two orders with poor telluric correction ($o=91$ and $94$) had exceptionally large uncertainties on their values for $v_z$ and $\vsini$.
@@
 The posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Appendix Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.
+\todo{Explain this more.}
 
 Overplotting models with the observed spectra yielded insights on why some orders failed, and which orders can discriminate between starspots and ambient photospheric lines the best.
-Some orders indicate that their spectrum is dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
+Some orders are dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
 These spectral line outlier orders also tend to bias estimates of effective temperature.
@@
 There are many examples of spectral lines that are present only in the hot photosphere model, or only in the cool photosphere model.
-For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.
+\todo{Insert new figure and text here.} For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.
 
-Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.  Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $c=75\pm 10 \% $.
+Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.
+Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $f_{\Omega}=75\pm 10 \% $.
 
@@
 The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
-On the best-fit photosphere from \S 3 fits both the optical and the near-IR bands well.
+Only the best-fit photosphere from \S 3 fits both the optical and the near-IR bands well.
 
@@
 
-The model photometry is obtained from the main sequence colors compiled by \citet{kenyon95}.
+\comm{GJH: needs revision.}
+Photometry is obtained from the main sequence colors compiled by \citet{kenyon95}.
 Colors from dwarf stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
@@
 The rotational modulation leads to much smaller brightness changes at near-IR wavelengths than at optical wavelengths (see Table~\ref{tab:photrange}).
-The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller amplitude than LkCa 4 in $V$ band.
+The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
 Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller.
@@
 The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}.
-The TiO indices are also combined into a single index by  calculating how many standard deviations each point is from the median value of the index, and then averaging the standard deviation.
+The TiO indices are also combined into a single index by  calculating the number of standard deviations each point is from the median value of the index, and then averaging the standard deviation.
 
@@
 
-Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc based the parallax distance of the nearest Taurus member \citep{torres12}.
+Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
 The spectrum of LkCa 4 is well reproduced by a cool component of $3000$ K covering 75\% of the surface and a $4200$ K component covering 25\% of the surface.
@@
 
+\subsection{Umbra versus penumbra}
+Sunspots consist of cool penumbra enveloping much cooler and smaller umbra with temperature differences of X and Y respectively \todo{cite}.  We must be seeing the umbra of the star.
+
 \subsection{Interpretation of the large filling factor of cool starspots}
@@
 \subsection{Is \name an extreme source?}
+
+\subsection{Starspots as a source of RV Jitter}
+Starspots cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14, robertson14}.  \todo{Potentially expand on this topic, but not critical.}
+
+This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{prato08}.
 

### 2016-08-12 document/ms.tex
GJH changes from Overleaf on Friday Aug 12

@@
 
-In the previous sections, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a cool photosphere with a hot spot.
-These results have testable predictions for the spectral energy distribution (SED) and rotational modulation of features of the SED.
+In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.
+The rotation of the hot component around the star has testable predictions for the spectral energy distribution (SED) and its rotational modulation.
+In the following subsections, we use these results to reproduce the SED and low-resolution spectra (\S 4.2), rotational modulation of colors \S 4.3, and rotational modulation of spectral indices (\S 4.4).
+The tests presented in this section confirms that the two temperature solution is reasonable and explains features that cannot be explained with single temperature photospheres without any adjustment to the best-fit solution found in \S 3.
 
-% quantify the spot fraction versus rotation period, and then
+\subsection{Rotational Modulation in the $V$-band lightcurve}\label{sec:rotSpot1}
 
-In \S 4.1 we describe how the two components of the photosphere fit low resolution spectra and optical/near-IR photometry.
-The brightness, colors, and spectral features should change as the spot rotates around the star.
-In \S 4.2, we convert the $V$ brightness to a filling factor of the cool spot, and then in \S 4.2-4.3 we compare how the expected rotational modulation of photometry and spectral indices compare with observed measurements.
+The  $V$ brightness corresponds to a filling factor of the cool spot based on two temperatures fit from IGRINS spectra.
+Although our analysis is consistent with a range of acceptable temperatures and filling factors, we adopt components of 2800 K covering 80\% of the visible stellar surface and 4200 K covering 20\% of the stellar surface at the time of the IGRINS spectrum, with an estimated $V_{rm est}=12.84$.
+With these temperatures, the $V$-band emission is dominated by the hotter component.
+The $V$-band brightness is therefore a good proxy for the visible surface area of the hot component.
+
+Figure~\ref{fig:vband_spot} shows the recent ASAS-SN lightcurve, converted into a cool spot filling factor.
+In these epochs, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
+Since 1992 the $V$ band photometry has been as bright as $12.3$ mag, corresponding to a cool component fill factor of $65\%$, and as faint as $13.2$ mag, or a cool component fill factor of $87\%$.
+This drastic change in visible area of the hot spot (35\% to 13\%) is needed to explain the full $\sim 1$ mag range in brightness.
+
+\subsection{The Spectral Energy Distribution}\label{sec:SED}
+
+Figures~\ref{fig:sed}-\ref{fig:lores} compares synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
+The only free parameters are the luminosity and extinction, which are both scaled to match the spectrum.
+The optical-IR SED is obtained from estimating photometry from \citet{grankin08} during the 2MASS epoch.
+We also included mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.
+In the spectroscopic comparison, some minor discrepancies may be introduced because the spot coverage changed in the $\sim 5$ hrs between the optical and near-IR spectra.
+The synthetic spectrum is obtained from the Phoenix models, as in \S 3.
+
+These comparisons require extinction estimates.
+The $B-V$ color from \citet{grankin08} has an excess $E(B-V)=0.15$ mag relative to empirical colors of a 4200 K main sequence star and a $0.27$ mag excess for a pre-main sequence star \citep{kenyon95,pecaut13}.
+The main sequence colors are probably most appropriate in this analysis because they are more free of spots.
+Under this assumption, the $B-V$ color excess leads to an extinction $A_V=0.45\pm0.15$ mag, where the uncertainty range  corresponds to colors of 4100--4300 K temperature photospheres.
+This extinction is overestimated if cooler temperatures also contribute to optical emission in a multi-temperature photosphere.
+More accurate extinction estimates from the full SED are challenging because they depend on the areal distribution of temperatures in the photosphere, which in this work is simplied to two temperatures.
+J--K discussion.
+Bizarre V--R color note...
+
+The synthetic models match the full spectrum reasonably well.
+When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (Figure \ref{fig:lores_twopanel}).
+However, single temperature photospheres (two shown in Figure \ref{fig:lores_twopanel}) fail to reproduce large spectral features.
+The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
+The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
+A two temperature photosphere with the parameters from the best-fit calculated in \S 3 fits both the molecular bands in the optical and near-IR spectra.
+
+\subsection{Rotational Modulation of Colors}\label{sec:rotSpot}
+
+Photometry is obtained from the main sequence colors compiled by \citet{kenyon95}.
+Colors from dwarf stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
+Synthetic spectra of $3000-4000$ K stars predict $B-V$ colors that are much bluer than observed and that become bluer at cooler temperatures, the opposite of what is observed.
+As a consequence, synthetic photometry also cannot be used here.
+
+The optical emission is dominated by the hotter component while both components contribute to the red and infrared emission (see Figure \ref{fig:lores}).
+The $0.7$ mag range in $V$-band brightness requires a factor of 1.9 change in the visible surface area of the hot component in the limit that the cool component does not contribute any $V$-band emission.
+In the 2014-2015 ASAS-SN photometry, the minimum and maximum brightness correspond to cool spot coverage of 83\% and 68\%, respectively.
+LkCa 4 was brighter in past epochs, which corresponds to either a larger covering fraction for the hot component (as assumed here) or components with hotter temperatures.
+
+The rotational modulation leads to much smaller brightness changes at near-IR wavelengths than at optical wavelengths (see Table~\ref{tab:photrange}).
+The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
+Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller.
+The predicted colors from rotational modulation do not match the observed $V-R_J$ colors or the correlation with $V$, either because of changes in spot properties since the \citet{grankin08} data were obtained or because a two-temperature model for the photosphere is overly simplistic.
 
@@
 
-\subsection{The Spectral Energy Distribution}\label{sec:SED}
-
-Figures~\ref{fig:sed}-\ref{fig:lores} show that the two-component photosphere matches the SED and flux-calibrated spectra well from $\sim 0.6-2.5$ $\mu$m.
-The two components have fixed temperatures of 4200 K covering 30\% of the visible surface and 3000 K covering 70\% of the visible surface area.
-The only free parameters are the luminosity and extinction, which are both scaled to match the spectrum.
-
-The two panels in Figure \ref{fig:lores_twopanel} show photospheric spectra scaled separately to the observed red-optical and near-IR spectra.
-The single temperature spectra are unable to reproduce the observed emission.
-The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
-The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
-Only the best-fit photosphere from \S 3 fits both the optical and the near-IR bands well.
-
-\todo{Extinction paragraph, needs overhaul...}  Relative to main sequence colors, the $E(B-V)=0.24$ would yield $A_V=0.72$ mag....  
-The $J-K=0.93$ color is equal to the expected color to within 0.05 => 0.3 mag (for T=3000, 4200)...
-The $B-V$ is always dominated by the hot component and therefore does not depend on the filling factor of the hot component.
-The $V-R$ varies more with $V$, indicating a larger contribution of the cool component.
-The difference between observed and predicted $B-V$ color, $E(B-V)$, may correspond to the extinction.
-After accounting for extinction synthetic model underpredicts both the $V-R$...
-
 %Furlan:  K7, V-IC=1.92, E(V-I)=1.6 => 0.85 mag;  close enough to their 1.1 mag
@@
 \end{figure*}
-
-\subsection{Rotational modulation of the hot spot}\label{sec:rotSpot}
-
-Since 1992 the $V$ band brightness has varied from $12.3$ to $13.2$ mag, with a typical range of $0.5$ mag in any single epoch (\emph{c.f} Figure \ref{fig:PhotPhase}).
-In a two-temperature atmosphere with fixed temperatures, this brightness corresponds directly to a filling factor for both components.
-Figure~\ref{fig:vband_spot} shows this conversion for temperatures of 4200 K, 3000 K, and a 75\% filling factor for the 3000 K component at $V_{\rm est}=12.83$, as estimated at the time of the IGRINS spectrum.
-
-\comm{GJH: needs revision.}
-Photometry is obtained from the main sequence colors compiled by \citet{kenyon95}.
-Colors from dwarf stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
-Synthetic spectra of $3000-4000$ K stars predict $B-V$ colors that are much bluer than observed and that become bluer at cooler temperatures, the opposite of what is observed.
-As a consequence, synthetic photometry also cannot be used here.
-
-The optical emission is dominated by the hotter component while both components contribute to the red and infrared emission (see Figure \ref{fig:lores}).
-The $0.7$ mag range in $V$-band brightness requires a factor of 1.9 change in the visible surface area of the hot component in the limit that the cool component does not contribute any $V$-band emission.
-In the 2014-2015 ASAS-SN photometry, the minimum and maximum brightness correspond to cool spot coverage of 83\% and 68\%, respectively.
-LkCa 4 was brighter in past epochs, which corresponds to either a larger covering fraction for the hot component (as assumed here) or components with hotter temperatures.
-
-The rotational modulation leads to much smaller brightness changes at near-IR wavelengths than at optical wavelengths (see Table~\ref{tab:photrange}).
-The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
-Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller.
-The predicted colors from rotational modulation do not match the observed $V-R_J$ colors or the correlation with $V$, either because of changes in spot properties since the \citet{grankin08} data were obtained or because a two-temperature model for the photosphere is overly simplistic.
 
@@
 
-Scaling our composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
-The spectrum of LkCa 4 is well reproduced by a cool component of $3000$ K covering 75\% of the surface and a $4200$ K component covering 25\% of the surface.
+The spectrum of LkCa 4 is well reproduced by a cool component of $2800$ K covering 80\% of the surface and a $4200$ K component covering 20\% of the surface.
+Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming $A_V=0.5$ mag and a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
+Brief discussion of other datapoints, based on Somers comments...
+
 The effective temperature of these two components is 3611 K, as calculated from the average surface flux at the median $V$ band magnitude.
@@
 Decreasing the cool spot size to 60\% would increase the effective temperature to 3670 K, while increasing the spot size to 85\% would decrease the effective temperature to 3370 K.
-{\bf GJH note:  holy crap!!!}.
+
+This wide range of possible observed temperatures at any single epoch, when having the most possible information, underscores the difficulty in placing young stars on HR diagrams.
 Since the Hayashi tracks are nearly vertical at this temperature and age, the temperature uncertainty leads directly to an uncertainty in inferred mass.
+The discrepancies in temperature are even larger when spectral type/temperature estimates focus on features in either blue-optical or $H$ or $K$-band spectra, and may explain the severe differences in effective temperature between APOGEE and other (optical) methods \citep{cottaar14}.
+For LkCa 4, the spectral type measured from TiO depths is reasonably close to the median value \citep{herczeg14}, which supports the widespread use of red spectra for effective temperatures \citep[e.g.][]{luhman03}.
+The temperature uncertainties for young K and M dwarfs are likely larger than any formal uncertainties in the measurements.
 
-{\bf GJH paragraph:}  The multi-temperature photosphere may also resolve some of the long-standing problems related to colors of young stars...
-\citet{tottle15}.
-I want to say something here, but I'm not sure exactly what.
+The multi-temperature photosphere may also resolve some of the long-standing problems related to discrepancies between observed and model colors of young stars.
+Low mass young stars are redder than expected in the near-IR \citep[e.g.][]{tottle15}.
+As a consequence, extinctions are high when measured by comparing near-IR colors to colors expected for optical spectral types.
+For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $1.04$ mag for a 4200 K photosphere and \citep{pecaut13} colors.
+This extinction is consistent with the color and SED analysis of \citet{furlan06}.
+However, this near-IR extinction is overestimated because the emission is generated from a composite spectrum and not only the hot component.
+ Our analysis in \S 4 suggests that $A_V\approx0.5$ mag, similar to the $A_V=0.69$ mag from \citet{kenyon95}.
 
-{\bf paragraph MG-S:}  Comparisons to other results (both real and simulated) from single-temperature fits to APOGEE, GAIA-ESO wavelengths.  Approximate is ok... \todo{MGS provide text here}
+These issues likely explain why near-IR extinctions are often higher than optical extinctions for young stars, and our results here generally support the lower extinctions obtained at optical wavelengths \citep[see analysis in][]{herczeg14}.
+If the range in spot temperature/coverage in young stars is large, then extinctions measured from empirical pre-main sequence color scales may also be suspect.
+The hottest temperature component dominates emission at short wavelengths and may provide the most accurate extinction estimate for non-accretors.
+These color discrepancies are not problems with photospheric models or with the spectral type-effective temperature scale, although our results suggest that any single spectral type may be a misleading estimate of effective temperature.
 
@@
 However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models.
-This age is uncomfortably young.
+This age is uncomfortably young and the mass is uncomfortably low.
 LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
-Even though this is only a single data point, the inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection.
-As a result, the surface is cooler and releases less radiation.
-As a result, the contraction rate may be slower.
-The star would then appear more luminous and cooler than expected from tracks that do not consider magnetic fields.
-
-{\bf TBD:}  Discussion of Somers+, Feiden (2016)...
+Dynamical measurements of masses of young stars with similar optical properties suggest that LkCa 4 should have a mass of $\sim 0.6-1.0$ M$_\odot$ \citep[e.g.][]{guilloteau14,czekala16,rizzuto16}.
+Even though this is only a single data point, the inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection in LkCa 4.
+As a result, the surface is cooler and releases less radiation, slowing the contraction rate.
+LkCa 4 then appears more luminous and cooler than expected from tracks that do not consider magnetic fields.
+Inclusion of magnetic fields may help to resolve some of the age discrepancies between intermediate mass and low mass young stars \citep[e.g.][]{herczeg15}.
 

### 2016-08-12 document/ms.tex
GJH contributions from afternoon of Aug 12, some new figures added

@@
 
-\subsection{Rotational Modulation in the $V$-band lightcurve}\label{sec:rotSpot1}
+\begin{figure*}
+ \centering
+ \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2800k}
+\caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
+The optical brightness depends mostly on the hot component.
+If we fix a 75\% filling factor, as measured in the IGRINS spectrum, to $V=12.83$ at the time of the observation, then the $V$-band amplitude  corresponds to filling factors of 67--83\%.
+The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\delta V=0.6$.
+\todo{Update with all available photometry or the derived multi-term fit} }
+\label{fig:vband_spot}
+\end{figure*}
 
-The  $V$ brightness corresponds to a filling factor of the cool spot based on two temperatures fit from IGRINS spectra.
-Although our analysis is consistent with a range of acceptable temperatures and filling factors, we adopt components of 2800 K covering 80\% of the visible stellar surface and 4200 K covering 20\% of the stellar surface at the time of the IGRINS spectrum, with an estimated $V_{rm est}=12.84$.
-With these temperatures, the $V$-band emission is dominated by the hotter component.
-The $V$-band brightness is therefore a good proxy for the visible surface area of the hot component.
+\subsection{The $V$-band lightcurve and spot coverage}\label{sec:rotSpot1}
 
+The  $V$-band brightness corresponds to a filling factor of the cool spot based on two temperatures fit from IGRINS spectra.
+We adopt photosphere components of 2800 K covering 80\% of the visible stellar surface and 4200 K covering 20\% of the stellar surface at the time of the IGRINS spectrum, with an estimated $V_{rm est}=12.84$.
+These parameters are selected as roughly the median of the range of acceptable temperatures and filling factors from \S 3, and are selected blindly with respect to the ability to reproduce the broadband SED and spectra.
+
+The $V$-band emission is dominated by the hotter component and is therefore a good proxy for the visible surface area of the hot component.
 Figure~\ref{fig:vband_spot} shows the recent ASAS-SN lightcurve, converted into a cool spot filling factor.
@@
 
+\begin{figure}
+ \centering
+ \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot1_paper}
+\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
+\label{fig:sed}
+\end{figure}
+
+\begin{figure*}
+ \centering
+ \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_paper}
+ \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
+The inset shows that the 3000 K (red, 70\% fill factor) and 4200 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4200 K component dominates the blue emission.
+The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
+Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere, and the two temperature photosphere that best fit the IGRINS spectrum.
+The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
+Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.
+Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
+The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
+ \label{fig:lores}
+\end{figure*}
+
 \subsection{The Spectral Energy Distribution}\label{sec:SED}
@@
 Figures~\ref{fig:sed}-\ref{fig:lores} compares synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
-The only free parameters are the luminosity and extinction, which are both scaled to match the spectrum.
+The only free parameters are the luminosity and extinction, which are both scaled to match the spectrum as described below.
 The optical-IR SED is obtained from estimating photometry from \citet{grankin08} during the 2MASS epoch.
-We also included mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.
-In the spectroscopic comparison, some minor discrepancies may be introduced because the spot coverage changed in the $\sim 5$ hrs between the optical and near-IR spectra.
-The synthetic spectrum is obtained from the Phoenix models, as in \S 3.
+The SED also includes mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.
+In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations.
+The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) for calculating the bolometric luminosity.
 
-These comparisons require extinction estimates.
-The $B-V$ color from \citet{grankin08} has an excess $E(B-V)=0.15$ mag relative to empirical colors of a 4200 K main sequence star and a $0.27$ mag excess for a pre-main sequence star \citep{kenyon95,pecaut13}.
-The main sequence colors are probably most appropriate in this analysis because they are more free of spots.
-Under this assumption, the $B-V$ color excess leads to an extinction $A_V=0.45\pm0.15$ mag, where the uncertainty range  corresponds to colors of 4100--4300 K temperature photospheres.
-This extinction is overestimated if cooler temperatures also contribute to optical emission in a multi-temperature photosphere.
-More accurate extinction estimates from the full SED are challenging because they depend on the areal distribution of temperatures in the photosphere, which in this work is simplied to two temperatures.
-J--K discussion.
-Bizarre V--R color note...
+These comparisons require extinction estimates.  The $B-V$ color from \citet{grankin08} has an 
+excess $E(B-V)=0.15$ mag relative to empirical colors of a 4200 K main sequence star and a 
+$0.27$ mag excess for a pre-main sequence star \citep{kenyon95,pecaut13}.  The $B-V$ color 
+excess leads to an extinction $A_V=0.45\pm0.15$ mag, or $0.84\pm0.15$ mag relative to 
+pre-main sequence colors.   The listed uncertainty corresponds to colors of 
+4100--4300 K temperature photospheres.  The main sequence colors are probably most 
+appropriate in this analysis because they are more free of spots.    
+This extinction is overestimated if cooler temperatures also contribute to optical 
+emission in a multi-temperature photosphere.  In the near-IR, the estimated $V=12.61$ 
+at the time of the 2MASS observations leads to a template (main sequence) color 
+$J-K_s=0.85$, with a range of $\sim 0.04$ for acceptable solutions with other 
+temperatures and covering fractions. The observed $J-K=0.93$ leads to $A_V=0.47$ mag, 
+with a range of 0.23 to account for the range of other photospheric solutions.  
+The template near-IR color is more robust than optical colors to differences 
+in the main sequence/pre-main sequence temperature scales because the pre-main 
+sequence $J-K$ color is redder at 4200 K and bluer at 2800 K.  Baed on this 
+analysis, an $A_V=0.5$ mag is adopted throughout this paper.  More accurate 
+extinction estimates from the full SED are challenging because they depend on the 
+areal distribution of temperatures in the photosphere, which in this work is 
+simplified to two temperatures.  {\bf GJH note:  this last sentence and the 
+generic approach tells the reader that we don't know how to do SED fitting, 
+which sounds extremely embarrassing.  I think it's also correct.}
 
@@
 
-Photometry is obtained from the main sequence colors compiled by \citet{kenyon95}.
-Colors from dwarf stars should have minimal contribution from spots; measurements of pre-main sequence colors will include some unknown contribution of spots and cannot be used for this analysis.
-Synthetic spectra of $3000-4000$ K stars predict $B-V$ colors that are much bluer than observed and that become bluer at cooler temperatures, the opposite of what is observed.
-As a consequence, synthetic photometry also cannot be used here.
+The relative contributions from the hot and cool components change as LkCa 4 rotates, leading to rotational modulation of colors.
+We model this rotational modulation using the main sequence colors compiled by \citet{pecaut13}, which should have less contribution from spots than their pre-main sequence colors.
+Synthetic photometry obtained from Phoenix (or BT-Settl) spectra cannot be used here because the predicted $B-V$ colors are much bluer than observed.
 
-The optical emission is dominated by the hotter component while both components contribute to the red and infrared emission (see Figure \ref{fig:lores}).
-The $0.7$ mag range in $V$-band brightness requires a factor of 1.9 change in the visible surface area of the hot component in the limit that the cool component does not contribute any $V$-band emission.
-In the 2014-2015 ASAS-SN photometry, the minimum and maximum brightness correspond to cool spot coverage of 83\% and 68\%, respectively.
-LkCa 4 was brighter in past epochs, which corresponds to either a larger covering fraction for the hot component (as assumed here) or components with hotter temperatures.
-
-The rotational modulation leads to much smaller brightness changes at near-IR wavelengths than at optical wavelengths (see Table~\ref{tab:photrange}).
-The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
-Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, while the $V-R_J$ becomes slightly redder when $V$ is smaller.
+The optical emission is dominated by the hotter component while both components contribute equally to the infrared emission (see Figure \ref{fig:lores}).
+Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, which is consistent with expectations for a single hot component with no contributions from the cooler component.
+The range of 0.03 mag in $B-V$ color indicates that the spot temperature is stable to 60 K.
 The predicted colors from rotational modulation do not match the observed $V-R_J$ colors or the correlation with $V$, either because of changes in spot properties since the \citet{grankin08} data were obtained or because a two-temperature model for the photosphere is overly simplistic.
 
-\begin{figure}
- \centering
- \includegraphics[trim=3.1cm 13cm 2.3cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot1_paper}
-\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
-\label{fig:sed}
-\end{figure}
-
-\begin{figure*}
- \centering
- \includegraphics[trim=2.1cm 13cm 2.5cm 3.1cm, clip=true, width=0.60\textwidth]{figures/lkca4_lores}
- \caption{The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
-The inset shows that the 3000 K (red, 70\% fill factor) and 4200 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4200 K component dominates the blue emission.
-The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
-\todo{Fix the $x-$axis label to be micron instead of Angstrom.} }
- \label{fig:lores}
-\end{figure*}
-
-\begin{figure*}
- \centering
- \includegraphics[trim=2.3cm 2.3cm 1.8cm 13.9cm, clip=true, width=0.75\textwidth]{figures/lkca4_lores_twopanel}
- \caption{The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere, and the two temperature photosphere that best fit the IGRINS spectrum.
-The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
-Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.
-Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
-The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
- \label{fig:lores_twopanel}
-\end{figure*}
-
-\begin{figure*}
- \centering
- \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot}
-\caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
-The optical brightness depends mostly on the hot component.
-If we fix a 75\% filling factor, as measured in the IGRINS spectrum, to $V=12.83$ at the time of the observation, then the $V$-band amplitude  corresponds to filling factors of 67--83\%.
-The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\delta V=0.6$.
-\todo{Update with all available photometry or the derived multi-term fit} }
-\label{fig:vband_spot}
-\end{figure*}
-
-%Furlan:  K7, V-IC=1.92, E(V-I)=1.6 => 0.85 mag;  close enough to their 1.1 mag
-%V-K = 4.18  ; MS colors:  3.16 (KH95) => Av=1.1 mag
-
-%V-J:  2.8-3.8
-%J-K:  0.9-1.0
+Rotational modulation is expected to lead to much smaller brightness changes at near-IR wavelengths than at optical wavelengths (see Table~\ref{tab:photrange}).
+The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
 
@@
 \end{figure*}
+
+%Furlan:  K7, V-IC=1.92, E(V-I)=1.6 => 0.85 mag;  close enough to their 1.1 mag
+%V-K = 4.18  ; MS colors:  3.16 (KH95) => Av=1.1 mag
+
+%V-J:  2.8-3.8
+%J-K:  0.9-1.0
 
@@
 The depths of TiO and other molecular bands are common diagnostics of spectral type (and therefore temperature) in optical spectra \citep[e.g.][]{kirkpatrick91}.
-In a 2-temperature photosphere, the depth of observed TiO bands will depend on the fractional coverage of the components.
-In this subsection, we demonstrate that the TiO band depths vary with spot coverage.
+In a 2-temperature photosphere cool enough for molecules to form, the depth of observed TiO bands will depend on the fractional coverage of the components.
+In this subsection, we demonstrate that the TiO band depths vary with spot coverage using 12 epochs of CFHT/ESPaDOnS spectra obtained over 14 days ($\sim 4$ rotation periods) by \citet{donati14}.
 
-\citet{donati14} spectroscopically monitored LkCa 4 with 12 spectra obtained over 14 days covering $\sim 4$ rotation periods.
 The spectra obtained near the estimated maximum and minimum optical brightness are shown in the top panel of Figure~\ref{fig:tiovar}.
@@
 The blue spectrum does not change.
-
-The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}.
-The TiO indices are also combined into a single index by  calculating the number of standard deviations each point is from the median value of the index, and then averaging the standard deviation.
+The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}  {\bf GJH:  Is this needed?}.
+The TiO indices are also combined into a single TiO index by calculating the number of standard deviations each point is from the median value of the index and then averaging the standard deviation.
 
@@
 
+{\bf GJH note:  I think this gets pretty rambling}
+
 The multi-temperature photosphere may also resolve some of the long-standing problems related to discrepancies between observed and model colors of young stars.
@@
 However, this near-IR extinction is overestimated because the emission is generated from a composite spectrum and not only the hot component.
- Our analysis in \S 4 suggests that $A_V\approx0.5$ mag, similar to the $A_V=0.69$ mag from \citet{kenyon95}.
+Our analysis in \S 4 suggests that $A_V\approx0.5$ mag, similar to the $A_V=0.69$ mag from optical photometry \citet{kenyon95} and $A_V=0.35$ mag from optical spectroscopy \citet{herczeg14}.
 
-These issues likely explain why near-IR extinctions are often higher than optical extinctions for young stars, and our results here generally support the lower extinctions obtained at optical wavelengths \citep[see analysis in][]{herczeg14}.
-If the range in spot temperature/coverage in young stars is large, then extinctions measured from empirical pre-main sequence color scales may also be suspect.
+These issues likely explain why near-IR extinctions are often higher than optical extinctions for young stars \citep[see analysis in][]{herczeg14}.
+Our results tentatively support the lower extinctions obtained at optical wavelengths, although the template colors used to calculate extinction is unclear.
+In the \citet{pecaut13} conversions, late K spectral types lead to lower temperatures for pre-main sequence than main-sequence stars, and at the same temperature the B-V colors are redder.
+The extinction to LkCa 4 and similar objects depends on whether these differences are caused by spots or gravity.
+
+Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types, if spot coverage is also similar.
+However, if the range in spot temperature/coverage in young stars is large, then extinctions measured from empirical pre-main sequence color scales may also be suspect.
 The hottest temperature component dominates emission at short wavelengths and may provide the most accurate extinction estimate for non-accretors.
@@
 
-This improved characterization of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
+The improved characterization of the photospheric emission and radius of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
 However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models.
-This age is uncomfortably young and the mass is uncomfortably low.
+This age is uncomfortably young and this mass is uncomfortably low.
 LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.

### 2016-08-14 document/ms.tex
Add prose surrounding the violin plot, some other minor edits.

@@
 Full-spectrum fitting was performed for 48 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.
-The MCMC samples had 5000 steps with 40 walkers.
+The MCMC samples generally had 5000 steps with 40 walkers.
 The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.
@@
 Marginalized distributions were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
-The fit quality was first assessed by examining the consistency of the point estimates across the spectral orders.
-The distribution of $v_z$ and $\vsini$ were informative for finding extremely poor fits.
-The range for all 48 orders was $v_z = 12.4 \pm 2.6$ km/s and $\vsini = 28.8 \pm 2.0$ km/s.
-Two orders with poor telluric correction ($o=91$ and $94$) had exceptionally large uncertainties on their values for $v_z$ and $\vsini$.
+The fit quality was first assessed by examining the consistency of the point estimates of $v_z$ and $\vsini$ across the spectral orders.
+The distribution of $v_z$ and $\vsini$ exposed extremely poor fits in two orders ($o=91$ and $94$), with all other orders demonstrating $v_z = 12.4 \pm 2.6$ km/s and $\vsini = 28.8 \pm 2.0$ km/s.
 
-The posteriors on $\teffa$ and $\teffb$ show several trends- see Figure \ref{fig:TwoTempResults} and Appendix Table \ref{tbl_order_results} for the results of effective temperatures for all IGRINS orders.
-\todo{Explain this more.}
-
-Overplotting models with the observed spectra yielded insights on why some orders failed, and which orders can discriminate between starspots and ambient photospheric lines the best.
-Some orders are dominated by spectral line outliers--deep metal lines that cannot be described by a coarse metallicity estimate alone.
-These spectral line outlier orders also tend to bias estimates of effective temperature.
-These metal lines can also be biased by Zeeman broadening, which would explain the heightened effect size with wavelength.
-
-\todo{insert results from re-run of H-band spectra here}
-Nearly-equal solutions could be explained by vanishingly weak spectral lines in one or the other of the effective temperature ranges, in which case the method offers little constraint on $\teffb$, but improves the fit around $\teffa$.
+Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders performed better than others in assessing stellar properties.
+This model comparison is performed by sorting the 8000 samples by their fill factor estimates and examining random draws of the cool spectrum, hot spectrum, and composite spectrum, excluding the Gaussian process coveriance and white noise steps.
+Fitting defects were conspicuous.
+Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, were all excluded from our final stellar parameter compilation.
+Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.
+For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \todo{cite}.
+These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \todo{cite}.
+Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.
+What's left were the most informative orders relatively devoid of spectral line outliers.
+Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $\f_{\Omega}$ (yellow shading) for all of the spectral orders, but with the rejected orders grayed out, and the most reliable spectral orders shown in bold.
+The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.
 

### 2016-08-14 document/ms.tex
Add some descriptions of the Spectral feature postage stamps.

@@
 
-\shorttitle{\name Starspots on LkCa 4}
+\shorttitle{Starspots on LkCa 4}
 
@@
 Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.
-What's left were the most informative orders relatively devoid of spectral line outliers.
-Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $\f_{\Omega}$ (yellow shading) for all of the spectral orders, but with the rejected orders grayed out, and the most reliable spectral orders shown in bold.
+What's left were the most informative orders relatively devoid of spectral line outliers, referred to hereafter as the Reliable Order subset.
+Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\Omega}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the Reliable Orders shown in bold.
 The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.
-
-The $K-$band orders demonstrate much more scatter than $H-$band, with no single photospheric temperature sticking out as strongly favored, but with values of $\teffa \sim 3900$ K and $\teffb \sim 2800$ K consistent with many orders.
-The $K-$band spectra possess strongly correlated residuals from poor telluric correction, as well as uncorrected hydrogen line features that appear as flux excesses after division by telluric standard spectrum.
-These instrumental afflictions degraded fits to several orders.
 
@@
 
+The IGRINS spectrum demonstrates some features that are reproduced only in the hot photosphere model, or only in the cool photosphere model.
+Figure \todo{FigureRef} shows a selection of such spectral features for a range of fill factors.
+The temperature-sensitivity for the whole-order spectral fit is shown as a function of fill factor in the rightmost panels.
+The unshown portion of the spectral order dilutes the temperature-sensitivity of these distinctive features, but overall the fill factor correlates with effective temperature in order to reproduce the observed line-depth ratio.
+In some cases, featureless cool photosphere spectra veil isolated spectral lines predicted in the hot photosphere models.
+In other cases, the hot photosphere model veils sequences of shallow spectral features predicted in the cool photosphere model.
+The cool photosphere models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotationally broadening.
+This line blanketing has probably hampered efforts to isolate spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
+In comparison, the forward-modeling technique thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
+
+For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.
+
 Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
-The red and blue lines show the hot photosphere and cool spot spectra respectively.
-We inspected the quality of the fits, generally finding good agreement with most spectral orders.
-Many orders demonstrated spectral line outliers.
-Most of the gross spectral features are captured by the composite model.
-There are many examples of spectral lines that are present only in the hot photosphere model, or only in the cool photosphere model.
-\todo{Insert new figure and text here.} For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.
 

### 2016-08-14 document/ms.tex
Add the postage stamp figures and some text around them.

@@
 The cool photosphere models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotationally broadening.
-This line blanketing has probably hampered efforts to isolate spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
-In comparison, the forward-modeling technique thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
+This line blanketing has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
+One such feature has been previously identified in the near-IR: the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines, although the \PHOENIX\ models predict a non-negligible hot star contribution to the middle line at our range of effective temperatures.
+In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
+Similar forward-modelling strategies have successfully identified weak metal lines in the spectra of extremely low metallicity stars \todo{cite-Evan Kirby}.
+Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
 
-For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_01}
 
-Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
+ \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_02}
+
+ \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_03} 
+ \caption{Examples of spectral features in the observed IGRINS spectrum (thick gray line) that are present only in the hot (blue line) photosphere model (top panel), only in the cool (red line) photosphere model (middle panel), or in a mixture of hot and cool models (bottom panel).
+The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel spectrum) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
+The right-most panels show the temperature-fill factor correlation for these spectral orders, with a straight-line fit (dashed black line) through all the samples.
+The location of the samples used to make the synthetic spectra to the left are shown as solid black symbols.}
+ \label{fig:specPostageStamps}
+\end{figure*}
 

### 2016-08-14 document/ms.tex
GJH edits from an email at 9:57pm on Sunday August 14 titled editing.

@@
 
-\section{Spots at Low Spectral Resolution}
+\section{The Two Temperature Fit to the SED and Stellar Rotation}
 
 In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.
-The rotation of the hot component around the star has testable predictions for the spectral energy distribution (SED) and its rotational modulation.
-In the following subsections, we use these results to reproduce the SED and low-resolution spectra (\S 4.2), rotational modulation of colors \S 4.3, and rotational modulation of spectral indices (\S 4.4).
-The tests presented in this section confirms that the two temperature solution is reasonable and explains features that cannot be explained with single temperature photospheres without any adjustment to the best-fit solution found in \S 3.
+In this section, we use testable predictions from this fit to demonstrate that the fit reasonably matches spectral features and their rotational modulation.
+We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4200 K covering 20\% of the stellar surface.
+The IGRINS spectrum occurred when LkCa 4 had an estimated brightness of $V_{\rm est}=12.84$ mag.
+These parameters are selected  as roughly the median of the range of acceptable temperatures and filling factors from \S 3, blindly and without any adjustments to attempt to improve fits to the SED or broadband spectra.
+
+Figures~\ref{fig:sed}-\ref{fig:lores} compares synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
+The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum as described below.
+The optical-IR SED is obtained from estimating photometry from \citet{grankin08} during the 2MASS epoch.
+The SED also includes mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.
+In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations.
+The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) for calculating the bolometric luminosity.
+
+The synthetic models match the full spectrum reasonably well.
+When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (Figure \ref{fig:lores_twopanel}).
+However, single temperature photospheres (two shown in Figure \ref{fig:lores_twopanel}) fail to reproduce large spectral features.
+The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
+The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
+A two temperature photosphere with the parameters from the best-fit calculated in \S 3 fits both the molecular bands in the optical and near-IR spectra.
+
+The features in the SED and in spectra should be rotationally modulated as the filling factors of the hot and cool components change.
+In \S 4.1, we first use our fit to the IGRINS spectrum to convert the $V$-band brightness to the filling factor of the two components.
+We subsequently calculate the color changes expected based on this spot coverage and compare these results to historical data (\S 4.2), and confirm our basic approach by demonstrating that TiO band depths vary with rotation (\S 4.3).
 
@@
  \centering
- \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2800k}
+ %\includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2750k}
 \caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
@@
 
+\begin{figure*}
+ \centering
+ \begin{tabular}{ll}
+ %\includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{figures/bv_pec13} 
+    &
+  %  \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{figures/vr_pec13}
+    \end{tabular}
+\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions from converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{kenyon95} (purple lines).}
+\label{fig:colors}
+\end{figure*}
+
 \subsection{The $V$-band lightcurve and spot coverage}\label{sec:rotSpot1}
 
-The  $V$-band brightness corresponds to a filling factor of the cool spot based on two temperatures fit from IGRINS spectra.
-We adopt photosphere components of 2800 K covering 80\% of the visible stellar surface and 4200 K covering 20\% of the stellar surface at the time of the IGRINS spectrum, with an estimated $V_{rm est}=12.84$.
-These parameters are selected as roughly the median of the range of acceptable temperatures and filling factors from \S 3, and are selected blindly with respect to the ability to reproduce the broadband SED and spectra.
-
-The $V$-band emission is dominated by the hotter component and is therefore a good proxy for the visible surface area of the hot component.
-Figure~\ref{fig:vband_spot} shows the recent ASAS-SN lightcurve, converted into a cool spot filling factor.
-In these epochs, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
-Since 1992 the $V$ band photometry has been as bright as $12.3$ mag, corresponding to a cool component fill factor of $65\%$, and as faint as $13.2$ mag, or a cool component fill factor of $87\%$.
-This drastic change in visible area of the hot spot (35\% to 13\%) is needed to explain the full $\sim 1$ mag range in brightness.
-
-\begin{figure}
- \centering
- \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot1_paper}
-\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
-\label{fig:sed}
-\end{figure}
+The  $V$-band brightness corresponds to the filling factor of the cool and hot components.
+In the two-temperature photosphere, the $V$-band emission is dominated by the hotter component and is therefore a good proxy for the visible surface area of the hot component.
+Figure~\ref{fig:vband_spot} shows the 2015--2016 ASAS-SN lightcurve, converted into a cool spot filling factor.
+In this epochs, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
+Since 1992 the $V$ band photometry has been as bright as $12.3$ mag, which corresponds to a cool component fill factor of $65\%$, and as faint as $13.2$ mag, or a cool component fill factor of $87\%$.
+This drastic change in visible area of the hot spot (35\% to 13\%) is needed to explain the full $\sim 1$ mag range in brightness, assuming no temperature change in either component.
 
@@
  \centering
- \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_paper}
+ %\includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_2750k}
  \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
@@
 
-\subsection{The Spectral Energy Distribution}\label{sec:SED}
-
-Figures~\ref{fig:sed}-\ref{fig:lores} compares synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
-The only free parameters are the luminosity and extinction, which are both scaled to match the spectrum as described below.
-The optical-IR SED is obtained from estimating photometry from \citet{grankin08} during the 2MASS epoch.
-The SED also includes mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.
-In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations.
-The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) for calculating the bolometric luminosity.
-
-These comparisons require extinction estimates.  The $B-V$ color from \citet{grankin08} has an 
-excess $E(B-V)=0.15$ mag relative to empirical colors of a 4200 K main sequence star and a 
-$0.27$ mag excess for a pre-main sequence star \citep{kenyon95,pecaut13}.  The $B-V$ color 
-excess leads to an extinction $A_V=0.45\pm0.15$ mag, or $0.84\pm0.15$ mag relative to 
-pre-main sequence colors.   The listed uncertainty corresponds to colors of 
-4100--4300 K temperature photospheres.  The main sequence colors are probably most 
-appropriate in this analysis because they are more free of spots.    
-This extinction is overestimated if cooler temperatures also contribute to optical 
-emission in a multi-temperature photosphere.  In the near-IR, the estimated $V=12.61$ 
-at the time of the 2MASS observations leads to a template (main sequence) color 
-$J-K_s=0.85$, with a range of $\sim 0.04$ for acceptable solutions with other 
-temperatures and covering fractions. The observed $J-K=0.93$ leads to $A_V=0.47$ mag, 
-with a range of 0.23 to account for the range of other photospheric solutions.  
-The template near-IR color is more robust than optical colors to differences 
-in the main sequence/pre-main sequence temperature scales because the pre-main 
-sequence $J-K$ color is redder at 4200 K and bluer at 2800 K.  Baed on this 
-analysis, an $A_V=0.5$ mag is adopted throughout this paper.  More accurate 
-extinction estimates from the full SED are challenging because they depend on the 
-areal distribution of temperatures in the photosphere, which in this work is 
-simplified to two temperatures.  {\bf GJH note:  this last sentence and the 
-generic approach tells the reader that we don't know how to do SED fitting, 
-which sounds extremely embarrassing.  I think it's also correct.}
-
-The synthetic models match the full spectrum reasonably well.
-When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (Figure \ref{fig:lores_twopanel}).
-However, single temperature photospheres (two shown in Figure \ref{fig:lores_twopanel}) fail to reproduce large spectral features.
-The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
-The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
-A two temperature photosphere with the parameters from the best-fit calculated in \S 3 fits both the molecular bands in the optical and near-IR spectra.
-
 \subsection{Rotational Modulation of Colors}\label{sec:rotSpot}
@@
 We model this rotational modulation using the main sequence colors compiled by \citet{pecaut13}, which should have less contribution from spots than their pre-main sequence colors.
-Synthetic photometry obtained from Phoenix (or BT-Settl) spectra cannot be used here because the predicted $B-V$ colors are much bluer than observed.
+The Cousins $R$ photometry from \citet{pecaut13} is converted to Johnson $R$ for comparison with the \citet{grankin08} photometry, following the Grankin et al.~prescription obtained from \citet{landolt82}.
+Photometry from synthetic spectra produced by Phoenix and BT-Settl models cannot be used here because the predicted $B-V$ colors are much bluer than observed.
+Offsets between model and observed colors are attributed to extinction and are discussed in \S 5.1.
 
-The optical emission is dominated by the hotter component while both components contribute equally to the infrared emission (see Figure \ref{fig:lores}).
+The optical emission is dominated by the hotter component while both components contribute equally to the infrared emission (see inset in top panel of Figure \ref{fig:lores}).
 Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, which is consistent with expectations for a single hot component with no contributions from the cooler component.
-The range of 0.03 mag in $B-V$ color indicates that the spot temperature is stable to 60 K.
-The predicted colors from rotational modulation do not match the observed $V-R_J$ colors or the correlation with $V$, either because of changes in spot properties since the \citet{grankin08} data were obtained or because a two-temperature model for the photosphere is overly simplistic.
+The standard deviation of 0.03 mag in $B-V$ color, which includes a $\sim 0.01$ mag uncertainty in both $V$ and $B$, indicates that the spot temperature is stable to $\lesssim 50$ K.
+The stability of this temperature implies that this hotter component may be the ambient temperature of the photosphere.
+
+The correlation between $V$ and $V-R$ indicates that the star becomes redder when the cool spot is more dominant.
+While this relationship is easily understood, the correlation predicted in our simple model is much weaker than the observed relationship.
+Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ could could be reproduced with some contribution from intermediate temperature.
 
@@
 
-\begin{figure*}
+\begin{figure}
  \centering
- \begin{tabular}{ll}
- \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{figures/bv_kh95} 
-    &
-    \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{figures/vr_kh95}
-    \end{tabular}
-\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions from converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{kenyon95} (purple lines).}
-\label{fig:colors}
-\end{figure*}
+ %\includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot1_2750k}
+\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
+\label{fig:sed}
+\end{figure}
 
@@
 
+\section{DISCUSSION or something}
+
 \subsection{Rotational Modulation of TiO Depth}\label{sec:RotTiO}
@@
 The blue spectrum does not change.
-The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}  {\bf GJH:  Is this needed?}.
+The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}.
 The TiO indices are also combined into a single TiO index by calculating the number of standard deviations each point is from the median value of the index and then averaging the standard deviation.
@@
 
-\section{Discussion}
+\subsection{Extinction estimates to LkCa 4}
 
-\begin{table}
-\begin{tabular}{lccccc}
-Method & $T_{eff}$ & $A_V$ & $M$ & $\log$ Age \\
-\hline
-Blue, high resolution & 4100 & 0.68 \\
-Low resolution optical & 3670 & 0.35 & \\
-\hline
-\multicolumn{5}{c}{Simulated}
-GAIA-ESO\\
-APOGEE \\
-\hline
-This work & 3525 & \\
-\hline
-\end{tabular}
-\end{table}
+Multi-temperature photospheres may resolve some of the long-standing problems related to discrepancies between observed and model colors of young stars.
+Low mass young stars are redder than expected in the near-IR \citep[e.g.][]{tottle15}.
+As a consequence, extinctions are high when measured by comparing near-IR colors to colors expected for optical spectral types.
+For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $1.04$ mag for a 4200 K photosphere and \citep{pecaut13} colors.
+This extinction is consistent with the color and SED analysis of \citet{furlan06}, which adopted a K7 spectral type, and is significantly higher than extinctions of $A_V=0.69$ measured from optical photometry \citep{kenyon95} and $0.35$ mag measured by comparing optical spectra to young spectral templates \citep{herczeg14}.
+
+An accurate extinction estimate from the full SED is challenging because of a strong dependence on the areal distribution of temperatures in the photosphere, which in our work is simplified to a two temperature fit.
+However, isolating specific colors constrains the possible range of extinctions.
+The $B-V$ color is stable and not affected by cooler components, and may therefore be compared with the expected colors for the hotter (4100 K) temperature.  
+The average $B-V=1.41$ mag color from \citet{grankin08} has a color excess $E(B-V)=0.09$ mag relative to the empirical color expected for a main sequence star and $E(B-V)=0.20$ mag for colors of pre-main sequence stars, based on the temperature-color tables of \citep{pecaut13}.
+The main sequence colors are probably most
+appropriate in this analysis because they are more free of spots.  
+The $B-V$ color 
+excess leads to an extinction $A_V=0.28\pm0.15$ mag, or $0.62\pm0.15$ mag relative to 
+pre-main sequence colors, with the listed uncertainty calculated for similar estimates with a hot component of 4000 and 4200 K.
+The $V-R_J$ color excess leads to $A_V=0.48$ mag, which should be less affected by gravity (based on $V-I_C$ colors in Pecaut et al.) but may be overestimated because the affects of the cool component are underestimated in our two-temperature model (as seen in Fig.~X).
+In the near-IR, the estimated $V=12.61$ mag at the time of the 2MASS observations leads to a template (main sequence) color 
+$J-K_s=0.87$ mag, with a range of $\sim 0.05$ mag for acceptable solutions with other 
+temperatures and covering fractions. The observed $J-K=0.93$ mag leads to $A_V=0.35$ mag, 
+with a range of $0.29$ mag to account for the range of other acceptable photospheric solutions.  
+The template near-IR color is more robust than optical colors to differences 
+in the main sequence/pre-main sequence temperature scales because the pre-main 
+sequence $J-K$ color is redder at 4200 K and bluer at 2800 K.  Based on this 
+analysis, an $A_V=0.3$ mag is adopted throughout this paper.
+
+The near-IR extinctions of LkCa 4 may be overestimated if emission is generated from a composite spectrum but comparison colors come from the hotter component.
+This mismatch likely explains why near-IR extinctions are often higher than optical extinctions for young stars \citep[see analysis in][]{herczeg14}.
+Our results tentatively support the lower extinctions obtained at optical wavelengths, although the template colors used to calculate extinction are uncertain and will need revision.
+In the \citet{pecaut13} conversions, late K spectral types lead to lower temperatures for pre-main sequence than main-sequence stars, and at the same temperature the B-V colors are redder.
+The extinction to LkCa 4 and similar objects depends on whether these differences are caused by spots or gravity.
+Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types, if spot coverage is also similar.
 
@@
 The spectrum of LkCa 4 is well reproduced by a cool component of $2800$ K covering 80\% of the surface and a $4200$ K component covering 20\% of the surface.
-Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, assuming $A_V=0.5$ mag and a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
-Brief discussion of other datapoints, based on Somers comments...
+Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, adopting $A_V=0.3$ mag and a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
+The effective temperature of these two components is 3611 K, as calculated from the average surface flux at the median $V$ band magnitude.
 
-The effective temperature of these two components is 3611 K, as calculated from the average surface flux at the median $V$ band magnitude.
 The apparent effective temperature in any single epoch would depend on the relative fractions of the hot and cool spot.
 Decreasing the cool spot size to 60\% would increase the effective temperature to 3670 K, while increasing the spot size to 85\% would decrease the effective temperature to 3370 K.
+This wide range of possible observed effective temperatures at any single epoch, when accounting for the visible contributions of both hot and cool components, underscores the difficulty in placing young stars on HR diagrams.
+Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures that would be measured in any single epoch corresponds to a mass range of $\sim 0.27--0.4$ $M_\odot$.
 
-This wide range of possible observed temperatures at any single epoch, when having the most possible information, underscores the difficulty in placing young stars on HR diagrams.
-Since the Hayashi tracks are nearly vertical at this temperature and age, the temperature uncertainty leads directly to an uncertainty in inferred mass.
 The discrepancies in temperature are even larger when spectral type/temperature estimates focus on features in either blue-optical or $H$ or $K$-band spectra, and may explain the severe differences in effective temperature between APOGEE and other (optical) methods \citep{cottaar14}.
-For LkCa 4, the spectral type measured from TiO depths is reasonably close to the median value \citep{herczeg14}, which supports the widespread use of red spectra for effective temperatures \citep[e.g.][]{luhman03}.
-The temperature uncertainties for young K and M dwarfs are likely larger than any formal uncertainties in the measurements.
+For LkCa 4, the spectral type measured from TiO depths is reasonably close to the median value \citep{herczeg14}, which supports the widespread use of red spectra for effective temperatures of low mass young stars \citep[e.g.][]{luhman03}.
+The temperature uncertainties for young K and M dwarfs are larger than any formal uncertainties in the measurements.
 
-{\bf GJH note:  I think this gets pretty rambling}
-
-The multi-temperature photosphere may also resolve some of the long-standing problems related to discrepancies between observed and model colors of young stars.
-Low mass young stars are redder than expected in the near-IR \citep[e.g.][]{tottle15}.
-As a consequence, extinctions are high when measured by comparing near-IR colors to colors expected for optical spectral types.
-For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $1.04$ mag for a 4200 K photosphere and \citep{pecaut13} colors.
-This extinction is consistent with the color and SED analysis of \citet{furlan06}.
-However, this near-IR extinction is overestimated because the emission is generated from a composite spectrum and not only the hot component.
-Our analysis in \S 4 suggests that $A_V\approx0.5$ mag, similar to the $A_V=0.69$ mag from optical photometry \citet{kenyon95} and $A_V=0.35$ mag from optical spectroscopy \citet{herczeg14}.
-
-These issues likely explain why near-IR extinctions are often higher than optical extinctions for young stars \citep[see analysis in][]{herczeg14}.
-Our results tentatively support the lower extinctions obtained at optical wavelengths, although the template colors used to calculate extinction is unclear.
-In the \citet{pecaut13} conversions, late K spectral types lead to lower temperatures for pre-main sequence than main-sequence stars, and at the same temperature the B-V colors are redder.
-The extinction to LkCa 4 and similar objects depends on whether these differences are caused by spots or gravity.
-
-Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types, if spot coverage is also similar.
-However, if the range in spot temperature/coverage in young stars is large, then extinctions measured from empirical pre-main sequence color scales may also be suspect.
-The hottest temperature component dominates emission at short wavelengths and may provide the most accurate extinction estimate for non-accretors.
-These color discrepancies are not problems with photospheric models or with the spectral type-effective temperature scale, although our results suggest that any single spectral type may be a misleading estimate of effective temperature.
-
-The improved characterization of the photospheric emission and radius of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
+The improved characterization of the photospheric emission and radius of LkCa 4 is supposed to lead to more accurate estimates of mass and age from pre-main sequence tracks.
 However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models.
@@
 Dynamical measurements of masses of young stars with similar optical properties suggest that LkCa 4 should have a mass of $\sim 0.6-1.0$ M$_\odot$ \citep[e.g.][]{guilloteau14,czekala16,rizzuto16}.
-Even though this is only a single data point, the inferred age and low mass may instead be evidence that strong magnetic fields are inhibiting convection in LkCa 4.
+Even though LkCa 4 is only a single data point, the inferred age and low mass may be evidence that strong magnetic fields are inhibiting convection in LkCa 4.
 As a result, the surface is cooler and releases less radiation, slowing the contraction rate.
-LkCa 4 then appears more luminous and cooler than expected from tracks that do not consider magnetic fields.
-Inclusion of magnetic fields may help to resolve some of the age discrepancies between intermediate mass and low mass young stars \citep[e.g.][]{herczeg15}.
+LkCa 4 then appears more luminous and cooler than expected from evolutionary tracks that do not consider magnetic fields.
+This shift to lower temperature may also help to resolve some of the age discrepancies between intermediate mass and low mass young stars \citep[e.g.][]{herczeg15}.
+
+{\bf For Somers:  do we want a paragraph with a more explicit comparison to Somers \& Pinnsoneault (2015) and Feiden (2016)?}
+
+{\bf goes later?}
+
+Despite some evidence that LkCa 4 is an outlier, spots are likely broadly important in estimating the properties of young low-mass stars.
+As an example, the well-studied CTTS TW Hya has a $\sim 4000$ K photosphere measured from high resolution optical spectra \citep[e.g.][]{yang05}.
+However, the near-IR spectrum is consistent with $\sim M2$, when compared with main sequence dwarf stars \citep{vacca11}.
+\citet{debes13} reconciled this discrepancy by invoking spots, although the spectral contribution from continuum emission was uncertain.
+\citet{mcclure13} found that the TW Hya spectrum was well reproduced with near-IR spectra of stars with similar ($\sim$K7) optical spectral type, as long as the comparison spectra were young.
+\citet{herczeg14} found an intermediate spectral type for TW Hya and other TTSs by focusing on TiO bands at redder wavelengths than previous spectra, and also by using young stars as photospheric templates.
+The mismatch between near-IR spectra of dwarf stars and young stars, even with similar optical spectral types, is likely explained by the prevalence and importance of cool spots in low mass stars.
+
+{\bf For the conclusions}
+
+Our confusion in colors, spectral type/effective temperatures, and extinctions for TTSs is dominated by ignoring spots and is not a fundamental problem with either photospheric models or with spectral type-effective temperature scales.
+Any single spectral type from either optical or near-IR spectra will provide a misleading estimate of the effective temperature.
+
+{\bf GJH TO DO:  revise plots;  TiO Table; more citations for colors}
 

### 2016-08-15 document/ms.tex
Add lots of text for the discussion, related to issue #36

@@
 
-\subsection{Longitudinal / latitudinal spot distributions and phase}
+\subsection{Addressing limitations of assumptions in the spectral inference methodology}
 
-\subsection{Addressing limitations of assumptions in the methodology}
+The spectral inference method assumed only two temperature components present in the photosphere.
+In reality, starspots are probably described by a range of effective temperatures like umbra, penumbra, and plages on the sun's surface.
+A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better.
+The fit-quality of the existing two-temperature fits seems fairly strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
+Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.
+Most of these orders were flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.
+But some orders just showed mediocre fits where no permutation of hot and cool two-temperature models could describe all of the variance in the spectrum.
+These $K-$band orders could be examined for a penumbra-like temperature component.
+We suspect systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
+High-precision polychromatic planetary transit photometry could offer an avenue to measure the morphologies and temperatures of starspots for the subset of transiting exoplanet host stars.
 
-\emph{Number of photospheric components-}  Our full spectrum fitting method assumed \emph{only} two temperature components present in the photosphere.
-In reality, starspots are probably described by a range of effective temperatures like umbra, penumbra, and plages on the sun's surface.
-A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can.
-Computational infeasibility limited our ability to rerun new multi-temperature models and compute model comparison diagnostics like AIC, BIC, or cross-validation \citep{ivezic14}.
-Such investigations could be considered in future works, but we suspect systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
-High-precision polychromatic planetary transit photometry could offer an avenue to measure the morphologies and temperatures of starspots for the subset of transiting exoplanet host stars.
-% The fact that we get consistent estimates for Teff tells us something.
-% The fits are pretty good, also tells us something.
-% Coarsely sampled models + spectral emulator acts as a smoother in Teff, as does the GP global covariance kernel.
-%(cite Charlotte Norris CS19 poster?)
-
-\emph{Suitability of pre-computed \PHOENIX\ model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX\ synthetic spectra are a good representation of our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
+\emph{Suitability of pre-computed \PHOENIX\ model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
 Cool sunspots are associated with heightened magnetic fields on the sun.
 Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.
-The former effect will differentially impact lines with high Lande-g factors (cite XX, fix the g formatting).
-The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants (cite XX Saar and collaborators).
-Our tacit assumption has been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures and 2) there exist many orders and lines that are not affected at all.
+The former effect will differentially impact lines with high magnetic sensitivity \citep{2013AJ....146...51D}.
+The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
+Our tacit assumptions have been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model allows some resilience against unknown residual spectrum correlations.
 We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
@@
 No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
-% Note that these two effects would differently affect the spectra
-
-%Our Gaussian process inference framework yields some resilience to the former problem.
-
-\subsection{Umbra versus penumbra}
-Sunspots consist of cool penumbra enveloping much cooler and smaller umbra with temperature differences of X and Y respectively \todo{cite}.  We must be seeing the umbra of the star.
 
 \subsection{Interpretation of the large filling factor of cool starspots}
+We have shown that LkCa 4 exposes between 67\% and 83\% cool photosphere towards our viewing direction.
+This exceptionally large fraction of surface area covered by spots defies the conventional wisdom that starspots should not cover more than 50\% of a stellar surface, since the minority constituent of temperature is usually called the spot.
+The evidence for this derived fill factor has been shown in the SED, high-resolution spectral inference, direct spectral detection, and TiO variability modelling.
+Perhaps the strongest evidence for the large fill factor of cool photosphere is the large amplitude of $V-$band modulation, which cannot be explained with small spots, even if an effective temperature of absolute zero is assigned to the cool regions.
+
+One conceivable interpretation of the 67\% to 83\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere.
+The ambient hot photosphere would then be close to the equator, which could additionally be limb-darkened due to project effects.
+Local fingers of cool spots would reached down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
+\todo{Is this picture consistent with Donati et al.
+2014?}.
 
 \subsection{Is \name an extreme source?}
+LkCa 4 is an extreme source by several metrics.
+Mainly, its large amplitude of cyclical optical variability exceeds all other counterparts from long-term monitoring of WTTSs \citep{grankin08}.
+LkCa 4 has about 40 times the photometric amplitude of the typical young star towards Ophiuchus or Upper Sco (Gully-Santiago et al.
+in prep.).
 
-\subsection{Starspots as a source of RV Jitter}
-Starspots cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14, robertson14}.  \todo{Potentially expand on this topic, but not critical.}
+\subsection{Evidence for intra-spectrum RV jitter}
+Starspots cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14, robertson14}.
+The two-temperature model assumed that the hot and cool components shared the same $\vsini$ and $v_z$.
+This assumption is accurate for either homogeneously distributed spots, azimuthally symmetric bands of spots, or polar spots.
+However, LkCa 4 has clear optical line-profile variations \citep{nguyen12, donati14}.
+Interestingly, we should be able to detect anticorrelation between lines attributable to hot photosphere, and lines attributable to cool photosphere, since there is a zero-sum competition for solid-angle on the recessional and advancing stellar limbs.
+We found tentative, albeit weak, evidence for such anticorrelation in $v_z$ across spectral orders with dominated by cool photosphere and those dominated by hot photosphere.
+For example, the cool-photosphere dominstated spectral orders $o = 100, 102, and 104$ show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
 
-This observation has motivated precision radial velocity (RV) planet searches in the infrared, where the modulation of RV signals is lessened \citep{prato08}.
+Radial velocity (RV) planet searches in the infrared--where the modulation of RV signals is lessened \citep{prato08}-- could potentially reduce RV jitter by characterizing and constraining the effect of direct emission from starspots.
+
+\subsection{Comparison with APOGEE/IN-SYNC}
+The INfrared Spectra of Young Nebulous Clusters (IN-SYNC) project \citep{cottaar14} employs APOGEE, which has a $15100-17000 \;\AA$ bandwidth.
+The long-wavelength cutoff prevents APOGEE from detecting the most conspicuous cool star emission we detected in IGRINS spectral orders $o = 100, 101, 104$ at $17075-17990 \;\AA$.
+These spectral orders can be thought of as a ``sweet spot'' where the cool star spectrum is putting out ample flux, but still far-enough away from the $K-$band where problems like magnetic field-sensitive lines, and enhanced telluric absorption complicate the spectra.
+Additionally, veiling from mid-IR excess in classical T-Tauri stars will be lessened in $H-band$.
+
+\subsection{Addressing binarity}
+In principle, unresolved eclipsing binaries could mimic some of the data shown here.
+However, unresolved such a system would have had to evade detection in high-resolution imaging \citep{kraus11,daemgen15}...
 
@@
 Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
-\comm{It's not clear if we need this table.
-If we keep it, we should update it with a reliability index or note about which orders were used in deriving the final values.
-A better table might be a list of new spectral features attributable to the spot.}
+\comm{Update this with ``used/unused'' label and most recent values.}
 \input{tables/tbl_order_results.tex}

### 2016-08-15 document/ms.tex
some more text to the addressing binarity subsection in discussion

@@
 The IGRINS spectrum demonstrates some features that are reproduced only in the hot photosphere model, or only in the cool photosphere model.
-Figure \todo{FigureRef} shows a selection of such spectral features for a range of fill factors.
+Figure \ref{fig:specPostageStamp} shows a selection of such spectral features for a range of fill factors.
 The temperature-sensitivity for the whole-order spectral fit is shown as a function of fill factor in the rightmost panels.
@@
 The location of the samples used to make the synthetic spectra to the left are shown as solid black symbols.}
- \label{fig:specPostageStamps}
+ \label{fig:specPostageStamp}
 \end{figure*}
@@
 
-\emph{Suitability of pre-computed \PHOENIX\ model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
+We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
 Cool sunspots are associated with heightened magnetic fields on the sun.
@@
 The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
-Our tacit assumptions have been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model allows some resilience against unknown residual spectrum correlations.
+Our tacit assumptions have been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations.
 We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
@@
 No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
+
+Uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
+The reliability of the stellar model continuum opacities has been called into question (A.
+Mann, \emph{priv.
+comm.}).
+Erroneous bulk opacities could be responsible for some of the scatter of fill factor distributions seen across different spectral orders, as in Figures \ref{fig:TwoTempResults} and \ref{fig:specPostageStamp}.
 
@@
 This assumption is accurate for either homogeneously distributed spots, azimuthally symmetric bands of spots, or polar spots.
-However, LkCa 4 has clear optical line-profile variations \citep{nguyen12, donati14}.
-Interestingly, we should be able to detect anticorrelation between lines attributable to hot photosphere, and lines attributable to cool photosphere, since there is a zero-sum competition for solid-angle on the recessional and advancing stellar limbs.
-We found tentative, albeit weak, evidence for such anticorrelation in $v_z$ across spectral orders with dominated by cool photosphere and those dominated by hot photosphere.
-For example, the cool-photosphere dominstated spectral orders $o = 100, 102, and 104$ show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
+LkCa 4 has clear optical line-profile variations \citep{nguyen12, donati14}.
+Accordingly, we should be able to detect anticorrelation between lines attributable to hot photosphere, and lines attributable to cool photosphere, since there is a zero-sum competition for solid-angle on the recessional and advancing stellar limbs.
+We found tentative, albeit weak, evidence for such anticorrelation in $v_z$ across spectral orders dominated by cool photosphere and those dominated by hot photosphere.
+For example, the cool-photosphere dominated spectral orders $o = 100, 102, and 104$ show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
 
-Radial velocity (RV) planet searches in the infrared--where the modulation of RV signals is lessened \citep{prato08}-- could potentially reduce RV jitter by characterizing and constraining the effect of direct emission from starspots.
+Radial velocity (RV) planet searches in the infrared--where the modulation of RV signals is lessened \citep{prato08}-- could potentially reduce RV jitter by characterizing and constraining the effect of direct emission from starspots, in addition to the flux deficits imbued in optical line profiles.
+Direct spectral emission from cool starspots is likely much weaker in sources with less starspot coverage than LkCa 4.
 
@@
 \subsection{Addressing binarity}
-In principle, unresolved eclipsing binaries could mimic some of the data shown here.
-However, unresolved such a system would have had to evade detection in high-resolution imaging \citep{kraus11,daemgen15}...
+In principle, unresolved binarity could mimic aspects of the data shown here, like the near-IR SED.
+However, such a system would have had to evade detection in high-resolution imaging \citep{kraus11,daemgen15} and spectroscopic monitoring \citep{nguyen12,donati14}.
+The sources would need to be eclipsing in order to yield $V-$band variability, which does not indicate a regular eclipsing binary signal in the light-curve (\emph{c.f.} Figure \ref{fig:PhotPhase}).
+These hypothetical binaries would also need the same rotational broadening, since the IGRINS spectrum shows comparable estimates for $\vsini$ for both the cool and hot components.
+So all of these lines of evidence render a hypothetical close eclipsing binary unviable.
 

### 2016-08-15 document/ms.tex
Version of the paper GJH and MGS will review together in preparation to send to coauthors

@@
 
+\begin{figure}
+ \centering
+ \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot_2750}
+\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
+\label{fig:sed}
+\end{figure}
+
+\begin{figure*}
+ \centering
+ \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_2750k}
+ \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
+The inset shows that the 2750 K (red, 70\% fill factor) and 4100 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.
+The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
+Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere, and the two temperature photosphere that best fit the IGRINS spectrum.
+The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
+Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.
+Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
+The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
+ \label{fig:lores}
+\end{figure*}
+
 In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.
 In this section, we use testable predictions from this fit to demonstrate that the fit reasonably matches spectral features and their rotational modulation.
-We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4200 K covering 20\% of the stellar surface.
+We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface.
 The IGRINS spectrum occurred when LkCa 4 had an estimated brightness of $V_{\rm est}=12.84$ mag.
-These parameters are selected  as roughly the median of the range of acceptable temperatures and filling factors from \S 3, blindly and without any adjustments to attempt to improve fits to the SED or broadband spectra.
+These parameters are selected without any adjustments to attempt to improve fits to the SED or broadband spectra.
 
 Figures~\ref{fig:sed}-\ref{fig:lores} compares synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
-The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum as described below.
-The optical-IR SED is obtained from estimating photometry from \citet{grankin08} during the 2MASS epoch.
+The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum (see \S 5.1-5.2).
+The optical-IR SED is obtained from estimating photometry from \citet{grankin08} during the 2MASS epoch, with $V\sim12.61$ mag.
 The SED also includes mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.
-In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations.
+In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations ($\Delta V=0.08$ mag).
 The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) for calculating the bolometric luminosity.
@@
 The synthetic models match the full spectrum reasonably well.
-When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (Figure \ref{fig:lores_twopanel}).
-However, single temperature photospheres (two shown in Figure \ref{fig:lores_twopanel}) fail to reproduce large spectral features.
+When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (bottom panels of Figure \ref{fig:lores}).
+However, single temperature photospheres fail to reproduce large spectral features.
 The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
 The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
-A two temperature photosphere with the parameters from the best-fit calculated in \S 3 fits both the molecular bands in the optical and near-IR spectra.
+A two temperature photosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
 
-The features in the SED and in spectra should be rotationally modulated as the filling factors of the hot and cool components change.
+The spectral features should be rotationally modulated as the filling factors of the hot and cool components change.
 In \S 4.1, we first use our fit to the IGRINS spectrum to convert the $V$-band brightness to the filling factor of the two components.
@@
  \centering
- %\includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2750k}
+ \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2750k}
 \caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
@@
  \begin{tabular}{ll}
- %\includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{figures/bv_pec13} 
+ \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{figures/bv_pec13} 
     &
-  %  \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{figures/vr_pec13}
+   \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{figures/vr_pec13}
     \end{tabular}
@@
 
-\begin{figure*}
- \centering
- %\includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_2750k}
- \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
-The inset shows that the 3000 K (red, 70\% fill factor) and 4200 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4200 K component dominates the blue emission.
-The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
-Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere, and the two temperature photosphere that best fit the IGRINS spectrum.
-The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
-Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.
-Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
-The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
- \label{fig:lores}
-\end{figure*}
-
 \subsection{Rotational Modulation of Colors}\label{sec:rotSpot}
@@
 The relative contributions from the hot and cool components change as LkCa 4 rotates, leading to rotational modulation of colors.
-We model this rotational modulation using the main sequence colors compiled by \citet{pecaut13}, which should have less contribution from spots than their pre-main sequence colors.
-The Cousins $R$ photometry from \citet{pecaut13} is converted to Johnson $R$ for comparison with the \citet{grankin08} photometry, following the Grankin et al.~prescription obtained from \citet{landolt82}.
+We model this rotational modulation using the main sequence colors \citep[compiled by][]{pecaut13}, which should have less contribution from spots than  pre-main sequence colors.
+The Cousins $R$ photometry from \citet{pecaut13} is converted to Johnson $R$ for comparison with the \citet{grankin08} photometry, following the color transformation prescribed by \citet{landolt82} and applied by Grankin et al.
 Photometry from synthetic spectra produced by Phoenix and BT-Settl models cannot be used here because the predicted $B-V$ colors are much bluer than observed.
@@
 
-The correlation between $V$ and $V-R$ indicates that the star becomes redder when the cool spot is more dominant.
-While this relationship is easily understood, the correlation predicted in our simple model is much weaker than the observed relationship.
+The correlation between $V$ and $V-R$ indicates that the star becomes redder when the cool spot has a higher filling factor.
+Our simple model predicts that the correlation should be much weaker than is measured.
 Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ could could be reproduced with some contribution from intermediate temperature.
@@
 The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
-
-\begin{figure}
- \centering
- %\includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot1_2750k}
-\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
-\label{fig:sed}
-\end{figure}
 
@@
 
-\section{DISCUSSION or something}
-
 \subsection{Rotational Modulation of TiO Depth}\label{sec:RotTiO}
 
-The depths of TiO and other molecular bands are common diagnostics of spectral type (and therefore temperature) in optical spectra \citep[e.g.][]{kirkpatrick91}.
+The depths of TiO and other molecular bands are common diagnostics of spectral type and therefore temperature in optical spectra \citep[e.g.][]{kirkpatrick91}.
 In a 2-temperature photosphere cool enough for molecules to form, the depth of observed TiO bands will depend on the fractional coverage of the components.
@@
 
+\section{DISCUSSION or something}
+
+Some overview?
+
 \subsection{Extinction estimates to LkCa 4}
@@
 Multi-temperature photospheres may resolve some of the long-standing problems related to discrepancies between observed and model colors of young stars.
-Low mass young stars are redder than expected in the near-IR \citep[e.g.][]{tottle15}.
-As a consequence, extinctions are high when measured by comparing near-IR colors to colors expected for optical spectral types.
+Low mass young stars are redder than expected in the near-IR, when compared with expectations from optical spectral types \citep[e.g.][]{tottle15}.
 For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $1.04$ mag for a 4200 K photosphere and \citep{pecaut13} colors.
@@
 excess leads to an extinction $A_V=0.28\pm0.15$ mag, or $0.62\pm0.15$ mag relative to 
-pre-main sequence colors, with the listed uncertainty calculated for similar estimates with a hot component of 4000 and 4200 K.
-The $V-R_J$ color excess leads to $A_V=0.48$ mag, which should be less affected by gravity (based on $V-I_C$ colors in Pecaut et al.) but may be overestimated because the affects of the cool component are underestimated in our two-temperature model (as seen in Fig.~X).
+pre-main sequence colors.   The listed uncertainties are calculated from extinction estimates relative to colors of 4000 and 4200 K photospheres.
+The $V-R_J$ color excess leads to $A_V=0.48$ mag, which should be less affected by gravity (based on $V-I_C$ colors in Pecaut et al.) but is likely to be overestimated because the cool component contributes to the $R_J$-band emission, as seen in Fig.~\ref{fig:colors}.
 In the near-IR, the estimated $V=12.61$ mag at the time of the 2MASS observations leads to a template (main sequence) color 
@@
 in the main sequence/pre-main sequence temperature scales because the pre-main 
-sequence $J-K$ color is redder at 4200 K and bluer at 2800 K.  Based on this 
+sequence $J-K$ color is redder at 4100 K and bluer at 2750 K {\bf GJH: (just redo for Pec13 young colors)}.  Based on this 
 analysis, an $A_V=0.3$ mag is adopted throughout this paper.
 
-The near-IR extinctions of LkCa 4 may be overestimated if emission is generated from a composite spectrum but comparison colors come from the hotter component.
+The near-IR extinctions of LkCa 4, and perhaps other TTSs, will be overestimated if emission is generated from a multi-temperature spectrum but template colors are based on only the hotter component.
 This mismatch likely explains why near-IR extinctions are often higher than optical extinctions for young stars \citep[see analysis in][]{herczeg14}.
 Our results tentatively support the lower extinctions obtained at optical wavelengths, although the template colors used to calculate extinction are uncertain and will need revision.
-In the \citet{pecaut13} conversions, late K spectral types lead to lower temperatures for pre-main sequence than main-sequence stars, and at the same temperature the B-V colors are redder.
-The extinction to LkCa 4 and similar objects depends on whether these differences are caused by spots or gravity.
+Differences between main sequence and pre-main sequence temperature scales and colors in the \citet{pecaut13} tables are introduced by a combination of spots, in addition to any color differences caused by gravity differences.
 Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types, if spot coverage is also similar.
@@
 
-The apparent effective temperature in any single epoch would depend on the relative fractions of the hot and cool spot.
-Decreasing the cool spot size to 60\% would increase the effective temperature to 3670 K, while increasing the spot size to 85\% would decrease the effective temperature to 3370 K.
+The apparent effective temperature in any single epoch depends on the relative fractions of the hot and cool spot.
+Decreasing the cool spot size to 60\% increases the effective temperature to 3670 K, while increasing the spot size to 85\% decreases to the effective temperature to 3370 K.
 This wide range of possible observed effective temperatures at any single epoch, when accounting for the visible contributions of both hot and cool components, underscores the difficulty in placing young stars on HR diagrams.
-Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures that would be measured in any single epoch corresponds to a mass range of $\sim 0.27--0.4$ $M_\odot$.
+Since the Hayashi tracks are nearly vertical at this temperature and age, this range in effective temperatures corresponds to a mass range of $\sim 0.27-0.4$ $M_\odot$  {\bf (GJH: all numbers need revision for 2750 K)}.
 
@@
 
-Our confusion in colors, spectral type/effective temperatures, and extinctions for TTSs is dominated by ignoring spots and is not a fundamental problem with either photospheric models or with spectral type-effective temperature scales.
-Any single spectral type from either optical or near-IR spectra will provide a misleading estimate of the effective temperature.
+Discrepancies in colors, spectral type/effective temperatures, and extinctions for LkCa 4, and perhaps more broadly for TTSs, are dominated by ignoring spots and are not caused by fundamental problems in either photospheric models or in spectral type-effective temperature scales.
 
 {\bf GJH TO DO:  revise plots;  TiO Table; more citations for colors}
+
+0 New
+
+Reply
 

### 2016-08-15 document/ms.tex
Pair-reading with GJH, making some changes

@@
 \begin{abstract}
-Starspots temporarily increase the opacity in stellar photospheres, impacting both their instantaneous stellar flux and the duration and efficiency of their convective energy transport during pre-main sequence stellar evolution.
+Magnetic fields temporarily increase the opacity in stellar photospheres, impacting both their instantaneous stellar flux and the duration and efficiency of their convective energy transport during pre-main sequence stellar evolution.
 The observational manifestation of local magnetic fields, starspots on young stars can cover a large fraction of the stellar surface, causing the incorrect assessment of both the effective temperature and the luminosity and therefore the placement of sources on HR diagrams.
 The singleton weak-lined T-Tauri star LkCa 4 shows exceptionally large photometric modulation attributable to star spots, making it an ideal testbed for measuring starspot properties.
-Infrared spectral features in high resolution IGRINS spectra indicate that 70-80\% of the surface is covered in $\teff \sim 2700-3000$ K patches of cool photosphere at the epoch of the observation.
-The rest of the $20-30\%$ of the stellar surface can be thought of as either ambient photosphere, or a hot spot of $\teff\sim4200$ K.
+Infrared spectral features in high resolution IGRINS spectra indicate that 80\% of the surface is covered in $\teff \sim 2750$ K patches of cool photosphere at the epoch of the observation.
+The rest of the $20\%$ of the stellar surface can be thought of as either ambient photosphere or a hot spot of $\teff\sim4100$ K.
 The photometric phase curve is scaled to this filling factor to construct the fill-factor-as-a-function-of-phase.
-The SED, color variability, and low-resolution optical/IR spectroscopy are registered to the filling factors at their epochs, strengthening the large filling factor and temperature contrast of the starspots through time.
-The revised effective temperature and luminosity make LkCa4 appear much lower mass and much younger when placed on a pre-main sequence HR diagram, compared to previous estimates based only on optical spectroscopy and not taking into account the large coverage fraction of cool spots.
-LkCa 4 represents the extreme end of starspot coverage, suggesting that many heavily spotted young stars have been misplaced on the observational HR diagram, leading to incorrect ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
+The SED, color variability, rotational modulation, and low-resolution optical/IR spectroscopy are registered to the filling factors at their epochs, strengthening the case for a large starspot filling factor and temperature contrast through time.
+The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger when placed on a pre-main sequence HR diagram, compared to previous estimates based only on optical spectroscopy and not taking into account the large coverage fraction of cool spots.
+The derived starspot properties explain the extreme $V-$band photometric amplitude of 0.5$-$0.8 magnitudes.
+Geometric considerations of spot coverage suggest that other heavily spotted young stars have been misplaced on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
 \end{abstract}
@@
 Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses \citep{somers15}.
-
 Starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
@@
 
-LkCa 4 has recently been examined with ZDI \citep{donati14}.  Unanswered questions about the large disagreement ($\Delta \teff \sim$500 K) in LkCa 4's effective temperature \citep{herczeg14} remain.
+LkCa 4 has recently been examined with ZDI \citep{donati14}.
+Unanswered questions about the large disagreement ($\Delta \teff \sim$500 K) in LkCa 4's effective temperature \citep{herczeg14, donati14} remain.
 
@@
 IGRINS is a high resolution near-infrared echelle spectrograph providing simultaneous $R\simeq45,000$ spectra over 1.48-2.48 \um.
-The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band \citep{gully12}.
-The data were reduced with the Pipeline Package\footnote{\url{https://github.com/igrins/plp}}.
+The spectrograph has two arms with 28 orders in $H-$band and 25 orders in $K-$band.
+The data were reduced with the Pipeline Package \citep{jaejoonlee15}.
 Telluric correction was performed by dividing the spectrum of \name by a spectrum of HR 1237, an A0V star observed immediately before \name, both at airmass 1.1.
@@
 Starspots possess a spectrum distinct from the ambient photosphere.
-Spatially resolved spectra of starspots have not yet been observed for stars beyond the sun, though interferometric techniques \todo{cite} and planetary transits \todo{cite} are promising.
 Approaches like ZDI and line-bisector analysis \todo{cite} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.
-In contrast, the technique described in this Section detects and measures the spectral lines originating from starspots photospheric emission.
+In contrast, the technique described in this Section detects and measures the emergent spectrum originating from cool starspots.
 
@@
 
+\comm{From discussion with GJH about lifetime of spots:  Where to put the source on the observational HR diagram depends on what your assumptions for its evolutionary history are.}
+
 {\bf goes later?}

### 2016-08-15 document/ms.tex
Add some Comments from iancze, revise the best fit tables with the stabilized values.

@@
 
-The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep[\emph{e.g.}][]{hartigan95} or mid-IR or mm excess \citep{skrutskie90,andrews05,mccabe06,furlan06,luhman10,furlan11,harris12,marichalar12,howard13,buckle15}, is not actively accreting \citep[\emph{e.g.}]{kenyon98,edwards06,cauley12,yang12}, has no evidence for a close companion \citep{karr10,kraus11,nguyen12,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}}, and demonstrates large amplitude sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}.
-The spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
+The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep[\emph{e.g.}][]{hartigan95} or mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15}, and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
+LkCa 4 has no evidence for a close companion from both direct imaging searches\citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}} and RV searches \citep{nguyen12,donati14}.
+This single star demonstrates a large amplitude of sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}.
+All of these observations indicate that the spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
 
-LkCa 4 has recently been examined with ZDI \citep{donati14}.
+LkCa 4 has recently been examined with ZDI \citep{donati14}, revealing a dark spot over the magnetic pole and a bright region at mid-latitudes.
 Unanswered questions about the large disagreement ($\Delta \teff \sim$500 K) in LkCa 4's effective temperature \citep{herczeg14, donati14} remain.
@@
 Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution panchromatic near-IR spectrum of \name in Section \ref{sec:two_tempIGRINS} .
-Sections \ref{sec:SED}, \ref{sec:rotSpot}, and \ref{sec:RotTiO} show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
+Section \ref{sec:GJHsection4} shows results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
 All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
@@
 In this paper, we concentrate on the intensity spectrum.
-%\todo{Flux calibration?}
+To calculate TiO indices, the relative flux calibration was obtained from an approximate instrument sensitivity calculated from observations of 72 Tau.
+The spectral shapes match the flux calibrated low resolution spectra described in \S 2.3.
 
@@
 
-The Palomar/DBSP \citep{oke82} data was previously described in \citet{herczeg14}.
-Briefly, these flux-calibrated spectra cover 3000$-$8700 $\AA$ at a spectral resolution $R\sim500-700$ in two epochs.
-The DBSP data were acquired near-contemporaneously with near-IR spectra from APO/TripleSpec \citep{wilson04}.
-\todo{(Covey) Fill in details about TripleSpec data}
+A flux-calibrated low-resolution optical spectrum of LkCa 4 was obtained using Palomar/DBSP \citep{Oke1982} on 30 Dec.
+2008.
+These spectra cover 3200--8700 \AA\ at a spectral resolution $R\sim 500$.
+The data reduction and a spectral analysis are described by \citet{herczeg14} within the context of a larger survey.
+
+A low-resolution near-IR spectrum of LkCa 4 was obtained with APO/TripleSpec \citep{Wilson04} contemporaneous to the Palomar/DBSP optical spectrum.  {\bf Covey:  fill in reduction details.}
 
@@
 The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}} to infer stellar properties from high resolution spectra.
-The \iancze\ technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.
+The \iancze\ technique forward models observed spectra with synthetic spectral from pre-computed model grids.
+The intra-grid-point spectra are emulated, taking into account the information loss attributable to the coarsely sampled stellar intrinsic parameters.
+The forward model includes calibration parameters, line spread functions, and a Gaussian process noise model to account for correlations in the residual spectrum.
 We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
@@
 The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
-The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order.
-Stellar parameter estimates $\vt_{o}$ are unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
+The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order, making stellar parameter estimates $\vt_{o}$ unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
 The $N_{\rm ord}$ sets of inferences on $\vt_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or conspicuous model mismatches.
 This process can be thought of as a coarse approximation to the much more sophisticated spectral line outlier rejection described in \iancze.
+No attempt was made to downweight spectral-line outliers using local kernels.
 
@@
 Overlays of models with observed spectra show modest agreement, with the exception of conspicuous spectral line outliers.
-No attempt was made to downweight spectral-line outliers as described in \iancze.
 
@@
 
-In summary, the visible portion of the spectrum will be dominated by the warm patches, but the contrast with the starspots will be higher.
-The infrared spectrum will have a lower overall spot contrast, but will have more net starspot flux than optical.
+In summary, the visible portion of the spectrum will be dominated by the warm patches.
+The infrared spectrum will have a lower overall spot contrast, and will have more net starspot flux than optical.
 
@@
 
-\section{The Two Temperature Fit to the SED and Stellar Rotation}
+\section{The Two Temperature Fit to the SED and Stellar Rotation}\label{sec:GJHsection4}
 
@@
 If we fix a 75\% filling factor, as measured in the IGRINS spectrum, to $V=12.83$ at the time of the observation, then the $V$-band amplitude  corresponds to filling factors of 67--83\%.
-The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\delta V=0.6$.
+The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\Delta V=0.6$.
 \todo{Update with all available photometry or the derived multi-term fit} }
@@
 
-We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.
+We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of LkCa 4, a young star that possesses a strong magnetic field \citep{donati14}.
 Cool sunspots are associated with heightened magnetic fields on the sun.
@@
 We found tentative, albeit weak, evidence for such anticorrelation in $v_z$ across spectral orders dominated by cool photosphere and those dominated by hot photosphere.
-For example, the cool-photosphere dominated spectral orders $o = 100, 102, and 104$ show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
+For example, the cool-photosphere dominated spectral orders $o = 100, 102, 104$ show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
 
@@
 \subsection{Comparison with APOGEE/IN-SYNC}
-The INfrared Spectra of Young Nebulous Clusters (IN-SYNC) project \citep{cottaar14} employs APOGEE, which has a $15100-17000 \;\AA$ bandwidth.
+The INfrared Spectra of Young Nebulous Clusters (IN-SYNC) project \citep{cottaar14} employs APOGEE, which has a $15100-17000$ \AA\ bandwidth.
 The long-wavelength cutoff prevents APOGEE from detecting the most conspicuous cool star emission we detected in IGRINS spectral orders $o = 100, 101, 104$ at $17075-17990 \;\AA$.
 These spectral orders can be thought of as a ``sweet spot'' where the cool star spectrum is putting out ample flux, but still far-enough away from the $K-$band where problems like magnetic field-sensitive lines, and enhanced telluric absorption complicate the spectra.
-Additionally, veiling from mid-IR excess in classical T-Tauri stars will be lessened in $H-band$.
+Additionally, veiling from mid-IR excess in classical T-Tauri stars will be lessened in $H-$band.
 

### 2016-08-15 document/ms.tex
Get rid of all V est for simplicity

@@
 Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.
-These spectra have comparable albeit different $V_{\rm est}$ of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.
+These spectra have comparable albeit different estimated $V-$band magnitudes of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.
 Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
@@
 Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.
-Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $f_{\Omega}=75\pm 10 \% $.
+Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $f_{\Omega}=80\pm 5 \% $.
 
@@
 We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface.
-The IGRINS spectrum occurred when LkCa 4 had an estimated brightness of $V_{\rm est}=12.84$ mag.
+The IGRINS spectrum occurred when LkCa 4 had an estimated brightness of $V=12.84$ mag.
 These parameters are selected without any adjustments to attempt to improve fits to the SED or broadband spectra.

### 2016-08-15 document/ms.tex
Add footnote about possible Teff offsets, put in question for Donati

@@
 The improved characterization of the photospheric emission and radius of LkCa 4 is supposed to lead to more accurate estimates of mass and age from pre-main sequence tracks.
-However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models.
+However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard15}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
 This age is uncomfortably young and this mass is uncomfortably low.
@@
 Local fingers of cool spots would reached down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
-\todo{Is this picture consistent with Donati et al.
+\todo{Donati-- How does this compare to the reconstructed maps from ZDI in Donati et al.
 2014?}.

### 2016-08-15 document/ms.tex
Changing Figure 3 to the old style with flux ratio below.

@@
 This single star demonstrates a large amplitude of sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}.
-All of these observations indicate that the spectrum of \name should be devoid of complicating factors like near-IR excess veiling and accretion excess.
+The variability amplitude cannot arise from eclipsing binarity, since the large RV variations would have been seen in spectroscopic monitoring.
+All of these observations indicate that the spectrum of \name should be devoid of complicating factors like near-IR excess veiling, accretion excess, or close binaries.
 
@@
  \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
-The top panel indicates the location and size of spectral chunks used to derive the values in the bottom panel.
-The IGRINS orders also show typical atmospheric transmission (red lines) in the infrared.
-Unused spectral chunks are lightened.
-The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.}
+The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.
+The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.}
  \label{fig:SingleTeffvsOrder}
@@
 
-\subsection{Addressing binarity}
-In principle, unresolved binarity could mimic aspects of the data shown here, like the near-IR SED.
-However, such a system would have had to evade detection in high-resolution imaging \citep{kraus11,daemgen15} and spectroscopic monitoring \citep{nguyen12,donati14}.
-The sources would need to be eclipsing in order to yield $V-$band variability, which does not indicate a regular eclipsing binary signal in the light-curve (\emph{c.f.} Figure \ref{fig:PhotPhase}).
-These hypothetical binaries would also need the same rotational broadening, since the IGRINS spectrum shows comparable estimates for $\vsini$ for both the cool and hot components.
-So all of these lines of evidence render a hypothetical close eclipsing binary unviable.
-
 \clearpage
@@
  \includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
- \caption{IGRINS Orders 94 and $99-119$.  Note that the $y-$axis is on a logarithmic scale.  }
+ \caption{IGRINS Orders 94 and $99-119$.
+Note that the $y-$axis is on a logarithmic scale.
+The red line is the cool photosphere while the blue line is the hot photosphere.
+The purple line is the composite mixture model.}
  \label{fig:Hband3x7}
@@
  \includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
- \caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  }
+ \caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  Cools are the same as Figure \ref{fig:Hband3x7}}
  \label{fig:Kband3x7}

### 2016-08-15 document/ms.tex
Revised text from GJH based on new numbers for cool component.

@@
 
-The spectrum of LkCa 4 is well reproduced by a cool component of $2800$ K covering 80\% of the surface and a $4200$ K component covering 20\% of the surface.
-Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.2$ $R_\odot$ and $\log L/L_\odot=0.17$, adopting $A_V=0.3$ mag and a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
-The effective temperature of these two components is 3611 K, as calculated from the average surface flux at the median $V$ band magnitude.
+The spectrum of LkCa 4 is well reproduced by a cool component of $2750$ K covering 80\% of the surface and a $4100$ K component covering 20\% of the surface.
+Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=0.17$, adopting $A_V=0.3$ mag and a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
+The effective temperature of these two components is 3330 K, as calculated from the average surface flux at the median $V$ band magnitude.
+Figure~\ref{fig:hrdiag} and Table~4 shows that this effective temperature is much cooler than previous measurements from optical spectra, which are clustered around 4000 K.
+The luminosity does not change significantly because the broadband SED yields similar luminosities, independent of temperature.
 
 The apparent effective temperature in any single epoch depends on the relative fractions of the hot and cool spot.
-Decreasing the cool spot size to 60\% increases the effective temperature to 3670 K, while increasing the spot size to 85\% decreases to the effective temperature to 3370 K.
+Decreasing the cool spot size to 74\% increases the effective temperature to 3440 K, while increasing the spot size to 86\% decreases to the effective temperature to 3200 K.
 This wide range of possible observed effective temperatures at any single epoch, when accounting for the visible contributions of both hot and cool components, underscores the difficulty in placing young stars on HR diagrams.
-Since the Hayashi tracks are nearly vertical at this temperature and age, this range in effective temperatures corresponds to a mass range of $\sim 0.27-0.4$ $M_\odot$  {\bf (GJH: all numbers need revision for 2750 K)}.
+Since the Hayashi tracks are nearly vertical at this temperature and age, this range in effective temperatures corresponds to a mass range of $\sim 0.2-0.3$ $M_\odot$.
+Our IGRINS analysis is also consistent with a cool component of 3000 K instead of 2750 K, which would increase the effective temperature by $\sim 200$ K.
 
 The discrepancies in temperature are even larger when spectral type/temperature estimates focus on features in either blue-optical or $H$ or $K$-band spectra, and may explain the severe differences in effective temperature between APOGEE and other (optical) methods \citep{cottaar14}.
-For LkCa 4, the spectral type measured from TiO depths is reasonably close to the median value \citep{herczeg14}, which supports the widespread use of red spectra for effective temperatures of low mass young stars \citep[e.g.][]{luhman03}.
-The temperature uncertainties for young K and M dwarfs are larger than any formal uncertainties in the measurements.
+On the other hand, GAIA-ESO spectra \citep{frasca15} cover only a narrow wavelength around H$\alpha$ and would yield an effective temperature of 4000 K.
+Spectral types and effective temperatures measured from TiO depths \citep{herczeg14} are lower than those from blue spectra but still overestimate the effective temperature.
+Temperature uncertainties for young K and M dwarfs are larger than any formal uncertainties in individual measurements.
 

### 2016-08-16 document/ms.tex
Add some references and text to the discussion

@@
 The rest of the $20\%$ of the stellar surface can be thought of as either ambient photosphere or a hot spot of $\teff\sim4100$ K.
-The photometric phase curve is scaled to this filling factor to construct the fill-factor-as-a-function-of-phase.
-The SED, color variability, rotational modulation, and low-resolution optical/IR spectroscopy are registered to the filling factors at their epochs, strengthening the case for a large starspot filling factor and temperature contrast through time.
+The spectral energy distribution, color variability, rotational modulation, and low-resolution optical/IR spectroscopy-- when registered to the filling factors at the epochs of their observations--strengthen the case for a large starspot filling factor and temperature contrast through time.
 The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger when placed on a pre-main sequence HR diagram, compared to previous estimates based only on optical spectroscopy and not taking into account the large coverage fraction of cool spots.
@@
 
-Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep[\emph{e.g}][]{harrison11,cody14,davenport15}.
-Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{bouvier95,grankin07} can break the degeneracy between starspot areal filling factor and starspot temperature.
-Photometric measurements are limited to detecting large longitudinally asymmetric starspots.
-Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups.
-Zeeman Doppler Imaging \citep[ZDI]{donati14} suffers from the same longitudinal asymmetry limitation as photometry, but can yield information on the latitudinal distribution of starspots.
-All of these techniques would underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots, or stars with an isotropic distribution of small starspots.
+Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep[\emph{e.g}][]{harrison11,davenport15}.
+Monochromatic photometric monitoring cannot separate the relative areas and temperatures of the emitting regions, and therefore cannot yield estimates for the areal fill factor of spots without making assumptions about the relative temperature contrast.
+Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{petrov94,bouvier95,grankin07,cody14} can break the degeneracy between starspot areal filling factor and starspot temperature, but these measurements are still limited to detecting large longitudinally asymmetric starspots.
+Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups, but the number of such transiting systems and demands of high photometric precision limit wider application.
+Zeeman Doppler Imaging \citep[ZDI]{donati14} suffers from similar longitudinal asymmetry limitations as photometry, but can yield some information on the latitudinal distribution of starspots in reconstructed brightness maps based on models for spectro-polarimetric line shapes.
+All of these techniques would tend to underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots, or stars with an isotropic distribution of small starspots.
 
@@
 LkCa 4 has recently been examined with ZDI \citep{donati14}, revealing a dark spot over the magnetic pole and a bright region at mid-latitudes.
-Unanswered questions about the large disagreement ($\Delta \teff \sim$500 K) in LkCa 4's effective temperature \citep{herczeg14, donati14} remain.
+Unanswered questions about the large disagreement ($\Delta \teff \sim$ 500 K) in LkCa 4's effective temperature \citep{herczeg14, donati14} remain.
 
@@
 Starspots possess a spectrum distinct from the ambient photosphere.
-Approaches like ZDI and line-bisector analysis \todo{cite} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.
+Approaches like ZDI and line-bisector analysis \citep[\emph{e.g.}][]{prato08, donati14} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.
 In contrast, the technique described in this Section detects and measures the emergent spectrum originating from cool starspots.
@@
 Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.
-For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \todo{cite}.
-These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \todo{cite}.
+For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
+These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \citep{deen13}.
 Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.
@@
 In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
-Similar forward-modelling strategies have successfully identified weak metal lines in the spectra of extremely low metallicity stars \todo{cite-Evan Kirby}.
+Similar forward-modelling strategies have successfully identified patterns of metal lines in the line-blanketed spectra of low metallicity stars \citep{kirby11,kirby15}.
 Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
@@
 The blue spectrum does not change.
-The TiO band depths in these spectra are measured from spectral indices listed in Table~\ref{tab:tio}.
+The TiO band depths in these spectra are measured from spectral indices as described in \citet{herczeg14}.
 The TiO indices are also combined into a single TiO index by calculating the number of standard deviations each point is from the median value of the index and then averaging the standard deviation.
+% Could use a footnote to be more exact on the TiO indices.
 
@@
  \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{figures/lkca4_tio_forpaper}
- \caption{Variability in TiO bands measured with ESPaDOnS (see also Table X).
+ \caption{Variability in TiO bands measured with ESPaDOnS.
 The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
@@
  \centering
- \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag_forpaper}
+ \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag}
  \caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.
@@
 The improved characterization of the photospheric emission and radius of LkCa 4 is supposed to lead to more accurate estimates of mass and age from pre-main sequence tracks.
-However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard15}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
+However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
 This age is uncomfortably young and this mass is uncomfortably low.
@@
 Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.
-The former effect will differentially impact lines with high magnetic sensitivity \citep{2013AJ....146...51D}.
+The former effect will differentially impact lines with high magnetic sensitivity \citep{deen13}.
 The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
@@
 Uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
-The reliability of the stellar model continuum opacities has been called into question (A.
-Mann, \emph{priv.
-comm.}).
 Erroneous bulk opacities could be responsible for some of the scatter of fill factor distributions seen across different spectral orders, as in Figures \ref{fig:TwoTempResults} and \ref{fig:specPostageStamp}.
+The large number of spectral orders over which the fill factors are averaged offers some resilience against these anomalies.
 
 \subsection{Interpretation of the large filling factor of cool starspots}
-We have shown that LkCa 4 exposes between 67\% and 83\% cool photosphere towards our viewing direction.
-This exceptionally large fraction of surface area covered by spots defies the conventional wisdom that starspots should not cover more than 50\% of a stellar surface, since the minority constituent of temperature is usually called the spot.
+We have shown that LkCa 4 exposes between 67\% and 83\% cool photosphere towards our viewing direction in 2015-2016, the most recent season for which there is data.
+In previous seasons, like Fall 2004 (\emph{c.f.} Figures \ref{fig:PhotPhase} and \ref{fig:vband_spot}), the filling factor of cool spots could have exceeded 90\%.
+This exceptionally large fraction of surface area covered by spots defies the conventional wisdom that starspots are the minority constituent of the stellar surface.
 The evidence for this derived fill factor has been shown in the SED, high-resolution spectral inference, direct spectral detection, and TiO variability modelling.
@@
 
-One conceivable interpretation of the 67\% to 83\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere.
-The ambient hot photosphere would then be close to the equator, which could additionally be limb-darkened due to project effects.
-Local fingers of cool spots would reached down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
+The Pleiades serves as a slightly older sample of young stars possessing evidence for large coverage fraction of starspots.
+For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}.
+Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.
+However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
+LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation, therefore evading photometric modulation detection, but contributing to otherwise anomalous color offsets.
+
+The number of WTTS for which the areal filling factor of spots have been measured is relatively low.
+V 410 Tau shows up to 41\% coverage of spots \citep{petrov94}.
+Many more measurements exist for evolved giants and subgiants, with typical fill factors in the range 15$-$48\% \citep{berdyugina05}.
+The prototypical BY Dra source is consistent with 60\% coverage fraction of moderately cool ($\Delta \teff =400$) penumbra \citep{chugainov76}.
+By these comparisons, LkCa 4 seems on the high end of filling factor
+
+One conceivable interpretation of the 67\% to 83\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere, as described by \citet{donati14}.
+The ambient hot photosphere would then be close to the equator, which would be limb-darkened due to projection effects.
+Such limb darkening would cause a non-linear transformation between our observed fill factor $f_{\Omega}$, and the surface areal coverage fraction of spots.
+So it's conceivable, and probably likely that the reported $f_{\Omega}$ is and overestimate of the surface area actually covered by spots.
+In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
 \todo{Donati-- How does this compare to the reconstructed maps from ZDI in Donati et al.
@@
 
-Radial velocity (RV) planet searches in the infrared--where the modulation of RV signals is lessened \citep{prato08}-- could potentially reduce RV jitter by characterizing and constraining the effect of direct emission from starspots, in addition to the flux deficits imbued in optical line profiles.
+Radial velocity (RV) planet searches in the infrared--where the modulation of RV signals is lessened \citep[\emph{e.g.}][]{prato08}-- could potentially reduce RV jitter by characterizing and constraining the effect of direct emission from starspots, in addition to the flux deficits imbued in optical line profiles.
 Direct spectral emission from cool starspots is likely much weaker in sources with less starspot coverage than LkCa 4.

### 2016-08-16 document/ms.tex
Almost done with version 0.6... will send to co-authors soon.

@@
 
-\keywords{stars: fundamental parameters --- stars: individual (\name) ---  stars: low-mass -- stars: statistics}
+\keywords{stars: fundamental parameters --- stars: individual (LkCa 4) ---  stars: low-mass -- stars: statistics}
 
@@
 First we measured a single effective temperature to unique spectral orders in the optical (\S \ref{sec:ESP_starfish}) and near-IR (\S \ref{sec:IGR_starfish}).
-Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to the near-IR spectra (\S \ref{sec:two_tempIGRINS}), which should show greater starspot flux density than optical(\S \ref{sec:whyNearIR}).
+Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to a high grasp near-IR spectrum (\S \ref{sec:two_tempIGRINS}), which should show greater starspot flux density than optical.
 
@@
 The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
+The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of photosphere with equal areas (50\% filling factor) but different temperatures-- 2800 K and 4100 K for the starspot and ambient photosphere respectively.
+The black body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.
 
@@
 \caption{Predicted Photometric Range}
+\centering
 \label{tab:photrange}
@@
 
-Some overview?
+\todo{Some overview?}
 
@@
 
-\comm{From discussion with GJH about lifetime of spots:  Where to put the source on the observational HR diagram depends on what your assumptions for its evolutionary history are.}
-
-{\bf goes later?}
-
-Despite some evidence that LkCa 4 is an outlier, spots are likely broadly important in estimating the properties of young low-mass stars.
-As an example, the well-studied CTTS TW Hya has a $\sim 4000$ K photosphere measured from high resolution optical spectra \citep[e.g.][]{yang05}.
-However, the near-IR spectrum is consistent with $\sim M2$, when compared with main sequence dwarf stars \citep{vacca11}.
-\citet{debes13} reconciled this discrepancy by invoking spots, although the spectral contribution from continuum emission was uncertain.
-\citet{mcclure13} found that the TW Hya spectrum was well reproduced with near-IR spectra of stars with similar ($\sim$K7) optical spectral type, as long as the comparison spectra were young.
-\citet{herczeg14} found an intermediate spectral type for TW Hya and other TTSs by focusing on TiO bands at redder wavelengths than previous spectra, and also by using young stars as photospheric templates.
-The mismatch between near-IR spectra of dwarf stars and young stars, even with similar optical spectral types, is likely explained by the prevalence and importance of cool spots in low mass stars.
+As seen in Figures \ref{fig:PhotTime} and \ref{fig:PhotPhase}, the areal coverage of spots appears to wax and wane secularly through the observing seasons of the last 31 years.
+It is conceivable that LkCa 4 happens to be going through a short-lived episode of relatively high coverage of spots analogous to solar maximum.
+The intensity and duration of such episodes would further confound the interpretation of its instantaneous position on the HR diagram.
 
@@
 In reality, starspots are probably described by a range of effective temperatures like umbra, penumbra, and plages on the sun's surface.
-A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better.
+A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
 The fit-quality of the existing two-temperature fits seems fairly strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
@@
 These $K-$band orders could be examined for a penumbra-like temperature component.
-We suspect systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
-High-precision polychromatic planetary transit photometry could offer an avenue to measure the morphologies and temperatures of starspots for the subset of transiting exoplanet host stars.
+We caution that systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
+Space-based high-precision planetary transit spectrophotometry could offer an avenue to measure the morphologies and temperature distributions of starspots for the subset of transiting exoplanet host stars or eclipsing binaries.
 
 We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of LkCa 4, a young star that possesses a strong magnetic field \citep{donati14}.
-Cool sunspots are associated with heightened magnetic fields on the sun.
+Cool sunspots are associated with locally heightened magnetic fields on the sun, so synthetic spectral models employing negligible magnetic fields will fail to fit magnetic sensitive features.
 Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.
-The former effect will differentially impact lines with high magnetic sensitivity \citep{deen13}.
+The former effect will differentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.
 The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
-Our tacit assumptions have been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations.
+Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.
 We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
-Strong metal lines demonstrate large departures in their best fit $\Z$ due to Zeeman broadening.
+Strong metal lines demonstrate large departures in their best fit $\Z$, as the na\:ive fitting strategy futilely attempts to minimize the residuals from Zeeman-broadened lines.
 No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
 
-Uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
+Finally, uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
 Erroneous bulk opacities could be responsible for some of the scatter of fill factor distributions seen across different spectral orders, as in Figures \ref{fig:TwoTempResults} and \ref{fig:specPostageStamp}.
-The large number of spectral orders over which the fill factors are averaged offers some resilience against these anomalies.
+The large number of spectral orders over which the fill factors are averaged offers resilience against these anomalies.
 
@@
 \subsection{Is \name an extreme source?}
-LkCa 4 is an extreme source by several metrics.
-Mainly, its large amplitude of cyclical optical variability exceeds all other counterparts from long-term monitoring of WTTSs \citep{grankin08}.
-LkCa 4 has about 40 times the photometric amplitude of the typical young star towards Ophiuchus or Upper Sco (Gully-Santiago et al.
-in prep.).
+LkCa 4's large amplitude of cyclical optical variability exceeds all other counterparts from long-term monitoring of WTTSs \citep{grankin08}.
+From a statistical perspective, it might not be a surprise that the source with the largest photometric variability also posessess among the largest coverage fraction of cool spots.
+The large $\sim$1 kG toroidal component at equatorial latitudes makes LkCa 4 an outlier by this metric, when compared to other TTSs.
+
+Despite the evidence that LkCa 4 is an outlier, spots are likely broadly important in estimating the properties of young low-mass stars.
+As an example, the well-studied CTTS TW Hya has a $\sim 4000$ K photosphere measured from high resolution optical spectra \citep[e.g.][]{yang05}.
+However, the near-IR spectrum is consistent with $\sim M2$, when compared with main sequence dwarf stars \citep{vacca11}.
+\citet{debes13} reconciled this discrepancy by invoking spots, although the spectral contribution from continuum emission was uncertain.
+\citet{mcclure13} found that the TW Hya spectrum was well reproduced with near-IR spectra of stars with similar ($\sim$K7) optical spectral type, as long as the comparison spectra were young.
+\citet{herczeg14} found an intermediate spectral type for TW Hya and other TTSs by focusing on TiO bands at redder wavelengths than previous spectra, and also by using young stars as photospheric templates.
+The mismatch between near-IR spectra of dwarf stars and young stars, even with similar optical spectral types, is likely explained by the prevalence and importance of cool spots in low mass stars.
 
@@
 
+\section{Full table of IGRINS best fits}
+
+Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
+\LongTables
+\input{tables/tbl_order_results.tex}
+
 \section{Previous work}
@@
 \input{tables/tbl_history.tex}
-
-\section{Full table of IGRINS best fits}
-
-Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
-\comm{Update this with ``used/unused'' label and most recent values.}
-\input{tables/tbl_order_results.tex}
 
@@
 
-This research has made use of NASA's Astrophysics Data System.  
-Based on data from the OMC Archive at CAB (INTA-CSIC), pre-processed by ISDC.
+This work used the Immersion Grating Infrared Spectrograph (IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant ASTR1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.
+
+This research has made use of NASA's Astrophysics Data System.  The research is based on data from the OMC Archive at CAB (INTA-CSIC), pre-processed by ISDC.
 We acknowledge with thanks the variable star observations from the AAVSO International Database contributed by observers worldwide and used in this research.

### 2016-08-16 document/ms.tex
This is version 0.6 of the paper, the one we will send to co-authors!

@@
 The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\Delta V=0.6$.
-\todo{Update with all available photometry or the derived multi-term fit} }
+}
 \label{fig:vband_spot}
 \end{figure*}
+%\todo{Update with all available photometry or the derived multi-term fit}
 
@@
 
-\todo{Some overview?}
+%\todo{Some overview?}
 
@@
 in the main sequence/pre-main sequence temperature scales because the pre-main 
-sequence $J-K$ color is redder at 4100 K and bluer at 2750 K {\bf GJH: (just redo for Pec13 young colors)}.  Based on this 
+sequence $J-K$ color is redder at 4100 K and bluer at 2750 K.  Based on this 
 analysis, an $A_V=0.3$ mag is adopted throughout this paper.
@@
 Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types, if spot coverage is also similar.
+Discrepancies in colors, spectral type/effective temperatures, and extinctions for LkCa 4, and perhaps more broadly for TTSs, are dominated by ignoring spots and are not caused by fundamental problems in either photospheric models or in spectral type-effective temperature scales.
 
@@
 The intensity and duration of such episodes would further confound the interpretation of its instantaneous position on the HR diagram.
-
-{\bf For the conclusions}
-
-Discrepancies in colors, spectral type/effective temperatures, and extinctions for LkCa 4, and perhaps more broadly for TTSs, are dominated by ignoring spots and are not caused by fundamental problems in either photospheric models or in spectral type-effective temperature scales.
-
-{\bf GJH TO DO:  revise plots;  TiO Table; more citations for colors}
-
-0 New
-
-Reply
 
@@
 In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
-\todo{Donati-- How does this compare to the reconstructed maps from ZDI in Donati et al.
+{\bf Donati-- How does this compare to the reconstructed maps from ZDI in Donati et al.
 2014?}.
@@
 Additionally, veiling from mid-IR excess in classical T-Tauri stars will be lessened in $H-$band.
+
+\section{Conclusions}
+{\bf TBD}
 
@@
 
-\todo{Verify that the final term possesses a $q$ and not a $q^2$ term.}
+%\todo{Verify that the final term possesses a $q$ and not a $q^2$ term.}
 

### 2016-08-24 document/ms.tex
add existing coauthors
A stab at the conclusions, and cite the new Fang paper

@@
 
-\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} et al.}
+\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2}, Garrett Somers\altaffilmark{2}, et al.}
 
 \altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
+\altaffiltext{2}{TBD}
 
@@
 \section{Conclusions}
-{\bf TBD}
+This paper has presented several complementary constraints on the photospheric properties of the weak-lined T-Tauri star LkCa 4, showing that this heavily spotted star was previously misplaced on the pre-main sequence HR diagram.
+New results from \citet{fang2016} show that large starspot coverage fractions of $50\%$ are common among stars in the Pleiades.
+LkCa 4 breaks the apparent trend of a ceiling at 50\% coverage fraction of cool starspots, though it is not yet clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.
+
+Coupled with the results of \citet{fang2016} and \citet{covey16}, the results shown here suggest that the contribution of starspots to pre-main sequence stellar evolution have been systematically underestimated.
+Large parts of the stellar surface are covered in spots that do not induce photometric modulation, either from circumpolar regions that always face towards our line-of-sight, longitudinally symmetric bands, or isotropic small spots.
+
+The spectral inference technique described in this paper lays the foundation for future studies that seek accurate constraints on multiple photospheric components.
+The near-IR has been shown to be the most sensitive region to search for cool emission from starspots.
+Starspots and disk or accretion veiling can be modeled in this framework, and combining the two will enable studies of the large number of classical T-Tauri stars.
+Applying this technique to large ensembles of T-Tauri stars across a wide range of mass and age will offer an observational picture of starspot evolution that can revise the current understanding of pre-main sequence stellar evolution.
 

### 2016-09-13 document/PKU_document/ms.tex
modify the latex file for the PKU postdoc report formatting

--- 2016-08-24 document/ms.tex
@@
-%\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
-\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
-%\documentclass[12pt,preprint]{aastex}
-
-%\usepackage{lineno}
-%\usepackage{blindtext}
-%\linenumbers
+\documentclass[12pt]{report}
+%\documentclass[dvipdfmx]{PostDocRep}
 
@@
 %\input{setup}
+\usepackage{amsmath,amsfonts,amsthm,amscd}
+\usepackage{amssymb}
+
+\usepackage{stylefiles/aastex_hack}
+\usepackage{stylefiles/deluxetable} 
+\usepackage{longtable}
+
+\usepackage[numbers]{natbib}
+\usepackage[nottoc]{tocbibind}
+\usepackage{makeidx}       	% Package to make an index.
+
 \input{mgs_setup}
@@
 
-\slugcomment{In preparation}
+%\shorttitle{Starspots on LkCa 4}
 
-\shorttitle{Starspots on LkCa 4}
-
-\shortauthors{Gully-Santiago et al.}
-
-\bibliographystyle{yahapj}
+%\bibliographystyle{yahapj}
 
@@
 
-\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2}, Garrett Somers\altaffilmark{2}, et al.}
+\author{Michael A. Gully-Santiago}
 
-\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
-\altaffiltext{2}{TBD}
+\maketitle
 
@@
 
-\keywords{stars: fundamental parameters --- stars: individual (LkCa 4) ---  stars: low-mass -- stars: statistics}
+%\keywords{stars: fundamental parameters --- stars: individual (LkCa 4) ---  stars: low-mass -- stars: statistics}
 
-\maketitle
+\tableofcontents
+% ±í¸ñÄ¿Â¼
+\listoftables
+% ²åÍ¼Ä¿Â¼
+\listoffigures
 
@@
 Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
-\LongTables
 \input{tables/tbl_order_results.tex}
@@
 
-\acknowledgements
-The authors thank Gregory N. Mace for carrying out the IGRINS observations.
-
-MG-S and GJH are supported by general grant 11473005 awarded by the National Science Foundation of China.
-The ESPaDOnS observations are supported by the contribution to the MATYSSE Large Project on CFHT obtained through the Telescope Access Program (TAP), which has been funded by the ``the Strategic Priority Research Program---The Emergence of Cosmological Structures'' of the Chinese Academy of Sciences (Grant No.11 XDB09000000) and the Special Fund for Astronomy from the Ministry of Finance.
-
-This work used the Immersion Grating Infrared Spectrograph (IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant ASTR1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.
-
-This research has made use of NASA's Astrophysics Data System.  The research is based on data from the OMC Archive at CAB (INTA-CSIC), pre-processed by ISDC.
-We acknowledge with thanks the variable star observations from the AAVSO International Database contributed by observers worldwide and used in this research.
-This publication makes use of data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
-
-{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}
-
-{\it Software: } 
- \project{pandas} \citep{mckinney10},
- \project{emcee} \citep{foreman13},
- \project{matplotlib} \citep{hunter07},
- \project{numpy} \citep{vanderwalt11},
- \project{scipy} \citep{jones01},
- \project{ipython} \citep{perez07},
- \project{gatspy} \citep{JakeVanderplas2015},
- \project{starfish} \citep{czekala15},
- \project{seaborn} \citep{waskom14}
-%\software{%
-% \project{pandas} \citep{mckinney10}
-%    \project{emcee} \citep{foreman13},
-% \project{matplotlib} \citep{hunter07},
-% \project{numpy} \citep{vanderwalt11},
-% \project{scipy} \citep{jones01},
-% \project{ipython} \citep{perez07},
-% \project{gatspy} \citep{JakeVanderplas2015},
-% \project{starfish} \citep{czekala15}}.
-
 \clearpage
 
+%\bibliographystyle{plainnat}
 \bibliographystyle{apj}

### 2016-09-13 document/ms.tex
Includes Ian comments-- closes Issue #39

@@
  \centering
- \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_01}
-
- \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_02}
-
- \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_03} 
- \caption{Examples of spectral features in the observed IGRINS spectrum (thick gray line) that are present only in the hot (blue line) photosphere model (top panel), only in the cool (red line) photosphere model (middle panel), or in a mixture of hot and cool models (bottom panel).
-The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel spectrum) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
-The right-most panels show the temperature-fill factor correlation for these spectral orders, with a straight-line fit (dashed black line) through all the samples.
-The location of the samples used to make the synthetic spectra to the left are shown as solid black symbols.}
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_04} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_01} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_05} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_06} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_02} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_03} 
+ \caption{Examples of spectral features in the observed IGRINS spectrum (thick gray line).
+The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel spectrum) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.}
  \label{fig:specPostageStamp}
@@
 
-\section{DISCUSSION or something}
+\section{Placing LkCa 4 on the HR diagram}
 
@@
 
-\subsection{Placing LkCa 4 on an HR Diagram}
+\subsection{Spot-corrected HR diagram placement}
 
@@
 
+\section{Discussion}
+
 \subsection{Addressing limitations of assumptions in the spectral inference methodology}
@@
 We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
-Strong metal lines demonstrate large departures in their best fit $\Z$, as the na\:ive fitting strategy futilely attempts to minimize the residuals from Zeeman-broadened lines.
+Strong metal lines demonstrate large departures in their best fit $\Z$, as the na\"{i}ve fitting strategy futilely attempts to minimize the residuals from Zeeman-broadened lines.
 No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
@@
 The prototypical BY Dra source is consistent with 60\% coverage fraction of moderately cool ($\Delta \teff =400$) penumbra \citep{chugainov76}.
-By these comparisons, LkCa 4 seems on the high end of filling factor
+By these comparisons, LkCa 4 seems on the high end of filling factor.
 

### 2016-09-16 document/PKU_document/ms.tex
Including some of Garrett comments, see Issue #40.  Also printed the PKU document as it is.

@@
 \usepackage{longtable}
+\usepackage{graphicx}
 
@@
 
-\maketitle
+%\maketitle
 
-\begin{abstract}
-Magnetic fields temporarily increase the opacity in stellar photospheres, impacting both their instantaneous stellar flux and the duration and efficiency of their convective energy transport during pre-main sequence stellar evolution.
+%\begin{abstract}
+%Magnetic fields temporarily increase the opacity in stellar photospheres, impacting both their instantaneous stellar flux and the duration and efficiency of their convective energy transport during pre-main sequence stellar evolution.
 The observational manifestation of local magnetic fields, starspots on young stars can cover a large fraction of the stellar surface, causing the incorrect assessment of both the effective temperature and the luminosity and therefore the placement of sources on HR diagrams.
@@
 Geometric considerations of spot coverage suggest that other heavily spotted young stars have been misplaced on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
-\end{abstract}
+%\end{abstract}
 
@@
 
-A low-resolution near-IR spectrum of LkCa 4 was obtained with APO/TripleSpec \citep{Wilson04} contemporaneous to the Palomar/DBSP optical spectrum.  {\bf Covey:  fill in reduction details.}
+A low-resolution near-IR spectrum of LkCa 4 was obtained with APO/TripleSpec \citep{Wilson04} contemporaneous to the Palomar/DBSP optical spectrum.
 
@@
  \includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
- \caption{Overview of \name $V-$band photometric monitoring from 1986$-$2016.
+ \caption[Overview of LkCa 4 $V-$band photometric monitoring from 1986$-$2016]{Overview of LkCa 4 $V-$band photometric monitoring from 1986$-$2016.
 The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DoubleSpec, and TripleSpec.
@@
  \includegraphics[width=0.95\textwidth]{figures/Vband_22s.pdf}
- \caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.
+ \caption[Phase-folded lightcurves assuming the same 3.375 day period for all observing seasons.]{Phase-folded lightcurves constructed assuming the same period for all observing seasons.
 The blue solid lines show a multi-term regularized periodic fit keeping the first $M_{\rm max}=4$ Fourier components.
@@
  \includegraphics[width=0.48\textwidth]{figures/single_Teff_v_order}
- \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
+ \caption[Effective temperature derived from spectral inference in 58 spectral orders]{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
 The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.
@@
  \includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
- \caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 48 IGRINS orders.
+ \caption[Results of two-temperature mixture model from 48 IGRINS orders]{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 48 IGRINS orders.
 Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=111$) consistent with negligible starspot emission, and others ($o=104, 102, 100$) showing tight constraints on the filling factor of starspots.
@@
  \includegraphics[width=0.80\textwidth]{figures/spectral_postage_stamp_03} 
- \caption{Examples of spectral features in the observed IGRINS spectrum (thick gray line) that are present only in the hot (blue line) photosphere model (top panel), only in the cool (red line) photosphere model (middle panel), or in a mixture of hot and cool models (bottom panel).
+ \caption[Examples of spectral features in the observed IGRINS spectrum]{Examples of spectral features in the observed IGRINS spectrum (thick gray line) that are present only in the hot (blue line) photosphere model (top panel), only in the cool (red line) photosphere model (middle panel), or in a mixture of hot and cool models (bottom panel).
 The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel spectrum) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
@@
  \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot_2750}
-\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
+\caption[The SED of LkCa 4]{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
 \label{fig:sed}
@@
  \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_2750k}
- \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
+ \caption[Flux-calibrated, low resolution spectra of LkCa 4]{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
 The inset shows that the 2750 K (red, 70\% fill factor) and 4100 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.
@@
  \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2750k}
-\caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
+\caption[Conversion of starspot coverage fraction to phase]{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
 The optical brightness depends mostly on the hot component.
@@
     \end{tabular}
-\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions from converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{kenyon95} (purple lines).}
+\caption[Polychromatic phase variation]{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions from converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{kenyon95} (purple lines).}
 \label{fig:colors}
@@
  \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{figures/lkca4_tio_forpaper}
- \caption{Variability in TiO bands measured with ESPaDOnS.
+ \caption[Variability in TiO bands measured with ESPaDOnS]{Variability in TiO bands measured with ESPaDOnS.
 The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
@@
  \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag}
- \caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.
+ \caption[Locations for LkCa 4 on an HR diagram]{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.
 The measured effective temperature and luminosity from this paper, based on the two-component fit and a median $V$-band magnitude, corresponds to the black asterisk.
@@
 This shift to lower temperature may also help to resolve some of the age discrepancies between intermediate mass and low mass young stars \citep[e.g.][]{herczeg15}.
-
-{\bf For Somers:  do we want a paragraph with a more explicit comparison to Somers \& Pinnsoneault (2015) and Feiden (2016)?}
 
@@
 In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
-{\bf Donati-- How does this compare to the reconstructed maps from ZDI in Donati et al.
-2014?}.
 
@@
  \includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
- \caption{IGRINS Orders 94 and $99-119$.
+ \caption[$H-$band IGRINS spectra]{IGRINS Orders 94 and $99-119$.
 Note that the $y-$axis is on a logarithmic scale.
@@
  \includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
- \caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  Cools are the same as Figure \ref{fig:Hband3x7}}
+ \caption[$K-$band IGRINS spectra]{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  Cools are the same as Figure \ref{fig:Hband3x7}}
  \label{fig:Kband3x7}
@@
 
-\section{Previous work}
-
-Table \ref{tbl_history} lists measurements of \name from previous studies.
-\input{tables/tbl_history.tex}
+%\section{Previous work}
+%Table \ref{tbl_history} lists measurements of \name from previous studies.
+%\input{tables/tbl_history.tex}
 

### 2016-09-16 document/ms.tex
Including some of Garrett comments, see Issue #40.  Also printed the PKU document as it is.

@@
 The singleton weak-lined T-Tauri star LkCa 4 shows exceptionally large photometric modulation attributable to star spots, making it an ideal testbed for measuring starspot properties.
-Infrared spectral features in high resolution IGRINS spectra indicate that 80\% of the surface is covered in $\teff \sim 2750$ K patches of cool photosphere at the epoch of the observation.
-The rest of the $20\%$ of the stellar surface can be thought of as either ambient photosphere or a hot spot of $\teff\sim4100$ K.
+Infrared spectral features in high resolution IGRINS spectra indicate that 80\% of the surface is covered in $\teffb \sim 2750$ K patches of cool photosphere at the epoch of the observation.
+The rest of the $20\%$ of the stellar surface can be thought of as either ambient photosphere or a hot spot of $\teffa \sim4100$ K.
 The spectral energy distribution, color variability, rotational modulation, and low-resolution optical/IR spectroscopy-- when registered to the filling factors at the epochs of their observations--strengthen the case for a large starspot filling factor and temperature contrast through time.
@@
 
-The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_b$ and $\Omega_a$, respectively.
+The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$, respectively.
 Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, and they share the same average intrinsic and extrinsic stellar parameters otherwise; that is $(\vsini, \logg, \Z, v_z)$ are identical for starspots and ambient photosphere.
@@
 \begin{eqnarray} \label{eqn:mix_M}
-S_{\mathrm{mix}} = \Omega_a B(\teffa)  + \Omega_b B(\teffb)
+S_{\mathrm{mix}} = \Omega_{\mathrm{amb}} B(\teffa)  + \Omega_{\mathrm{spot}} B(\teffb)
 \end{eqnarray}
@@
 \begin{eqnarray} \label{eqn:fill_factor}
-f_{\Omega} = \frac{\Omega_b}{\Omega_a + \Omega_b}
+f_{\Omega} = \frac{\Omega_{\mathrm{spot}}}{\Omega_{\mathrm{amb}} + \Omega_{\mathrm{spot}}}
 \end{eqnarray}
@@
 The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $f_{\Omega}$.
-The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in effective temperature.
+The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in $\teffa$, $\teffb$, and $f_{\Omega}$.
 This challenge motivated the second important change to the spectral inference framework, which involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
@@
 The MCMC samples generally had 5000 steps with 40 walkers.
-The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the effective temperature range was $\teffa, \teffb \in [2700, 4500]$.
+The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the \PHOENIX\ model spectrum temperature range\footnote{The \PHOENIX\ model spectra are indexed by $\teff$, but this term carries a different meaning for spotted stars than non-spotted stars.} was $\teffa, \teffb \in [2700, 4500]$.
 $H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$ km/s.
@@
 The IGRINS spectrum demonstrates some features that are reproduced only in the hot photosphere model, or only in the cool photosphere model.
-Figure \ref{fig:specPostageStamp} shows a selection of such spectral features for a range of fill factors.
-The temperature-sensitivity for the whole-order spectral fit is shown as a function of fill factor in the rightmost panels.
-The unshown portion of the spectral order dilutes the temperature-sensitivity of these distinctive features, but overall the fill factor correlates with effective temperature in order to reproduce the observed line-depth ratio.
+Figure \ref{fig:specPostageStamp} shows a selection of six such spectral features for a range of plausible fill factors.
 In some cases, featureless cool photosphere spectra veil isolated spectral lines predicted in the hot photosphere models.
 In other cases, the hot photosphere model veils sequences of shallow spectral features predicted in the cool photosphere model.
-The cool photosphere models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotationally broadening.
+The cool photosphere models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening.
 This line blanketing has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
-One such feature has been previously identified in the near-IR: the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines, although the \PHOENIX\ models predict a non-negligible hot star contribution to the middle line at our range of effective temperatures.
+One such feature has been previously identified in the near-IR: the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines, although the \PHOENIX\ models predict a non-negligible hot star contribution to the middle line for our range of ambient and spot temperatures.
 In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
@@
 
-{\bf For Somers:  do we want a paragraph with a more explicit comparison to Somers \& Pinnsoneault (2015) and Feiden (2016)?}
+The IGRINS and ESPaDOnS spectra indicate indicate $\vsini\sim$ 28 km~s$^{-1}$ and a rotation period of 3.375 days.
+Combining these numbers gives $R\sin{i} \sim 1.87 R_{\odot}$.
+Our HR diagram analysis gives $R \sim 2.3R_{\odot}$.
+These numbers are consistent for $\sin{i} \sim 0.813$, or an inclination of about 35$^{\circ}$ from edge on.
+These values show broad consistency between rotational properties, spectral fitting values, and our interpretation of a tilted star revealing a circumpolar region with large areal coverage of starspots.
+While this is obviously not proof of anything, the fact that all our different angles agree nicely would be a fun tidbit to point out.
 
@@
 The spectral inference method assumed only two temperature components present in the photosphere.
-In reality, starspots are probably described by a range of effective temperatures like umbra, penumbra, and plages on the sun's surface.
+In reality, starspots are probably described by a range of spot temperatures like umbra, penumbra, and plages on the sun's surface.
 A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
@@
 The evidence for this derived fill factor has been shown in the SED, high-resolution spectral inference, direct spectral detection, and TiO variability modelling.
-Perhaps the strongest evidence for the large fill factor of cool photosphere is the large amplitude of $V-$band modulation, which cannot be explained with small spots, even if an effective temperature of absolute zero is assigned to the cool regions.
+Perhaps the strongest evidence for the large fill factor of cool photosphere is the large amplitude of $V-$band modulation, which cannot be explained with small spots, even if a spot temperature of absolute zero is assigned to the cool regions.
 
@@
 The choice to standardize fluxes makes no difference for modeling a single photospheric component.
-But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $f_{\Omega} \equiv \Omega_b/(\Omega_a+\Omega_b)$.
+But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $f_{\Omega} \equiv \Omega_{\mathrm{spot}}/(\Omega_{\mathrm{amb}}+\Omega_{\mathrm{spot}})$.
 So we scale the mixture model in the following way:
@@
 \begin{eqnarray} \label{eqn:norm_scaling}
-f_{\lambda, \mathrm{mix}} &=& f_{\mathrm{a}} \bar f_{\lambda, \mathrm{a}} \times \Omega_a + f_{\mathrm{b}} \bar f_{\lambda, \mathrm{b}} \times \Omega_b \\
-q &=& q(\vt_{\ast})\equiv \frac{f_{\mathrm{b}}(\teffb, ...)}{f_{\mathrm{a}}(\teffa, ...)} \\
-f_{\lambda, \mathrm{mix}}^{\prime} &=& \bar f_{\lambda, \mathrm{a}} \times \Omega_a + q \bar f_{\lambda, \mathrm{b}} \times \Omega_b
+f_{\lambda, \mathrm{mix}} &=& f_{\mathrm{amb}} \bar f_{\lambda, \mathrm{amb}} \times \Omega_{\mathrm{amb}} + f_{\mathrm{spot}} \bar f_{\lambda, \mathrm{spot}} \times \Omega_{\mathrm{spot}} \\
+q &=& q(\vt_{\ast})\equiv \frac{f_{\mathrm{spot}}(\teffb, ...)}{f_{\mathrm{amb}}(\teffa, ...)} \\
+f_{\lambda, \mathrm{mix}}^{\prime} &=& \bar f_{\lambda, \mathrm{amb}} \times \Omega_{\mathrm{amb}} + q \bar f_{\lambda, \mathrm{spot}} \times \Omega_{\mathrm{spot}}
 \end{eqnarray}
@@
 The mixture model is a linear operation with all the same stellar extrinsic parameters, so we can re-use all the same post-processed eigenspectra $\widetilde{\mathbf{\Xi}}$, mean spectrum $\widetilde{\xi}_\mu$, and variance spectrum $\widetilde{\xi}_\sigma$, with the tildes representing all post processing \emph{except} the $\Omega$ scaling.
-We calulate \emph{two} sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{a}, \mathrm{b})}$, and their associated mean and covariances following the Appendix of \iancze, and yielding:
+We calulate \emph{two} sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{amb}, \mathrm{spot})}$, and their associated mean and covariances following the Appendix of \iancze, and yielding:
 
 \begin{equation}
-  \mathsf{M}_{\mathrm{mix}}^\prime = \Omega_a (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{a}}) + q \Omega_b (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{b}})
+  \mathsf{M}_{\mathrm{mix}}^\prime = \Omega_{\mathrm{amb}} (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{amb}}) + q \Omega_{\mathrm{spot}} (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{spot}})
 \end{equation}
@@
 \begin{equation}
-  \mathsf{C}_{\mathrm{mix}}^\prime = \Omega_a^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{a}} \mathbf{X}^T + q \Omega_b^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{b}} \mathbf{X}^T + \mathsf{C}
+  \mathsf{C}_{\mathrm{mix}}^\prime = \Omega_{\mathrm{amb}}^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{amb}} \mathbf{X}^T + q \Omega_{\mathrm{spot}}^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{spot}} \mathbf{X}^T + \mathsf{C}
   \label{eqn:modC}

### 2016-09-16 document/ms.tex
Last of comments from Garrett that I could do without others

@@
 No attempt was made to downweight spectral-line outliers using local kernels.
+
+This two-temperature mixture model for starspots requires single stars, or at least double stars with extremely large (>100) luminosity ratios or wide separations.
+Unresolved single-lined or double-lined binaries could mimic a signal that would be misattributed to starspots.
+As pointed out earlier, LkCa 4 has no detected companion from direct imaging, and its RV variations are consistent with starspot modulation, so any binary companion would have to have exceptionally large luminosity or mass ratios, rendering it undetectable with our spectral inference methodology with the finite signal to noise available in the IGRINS data.
+The absense of a mid-IR excess emission attributable to a disk also means that the spectral modeling requires no further parameters like veiling or accretion.
 
@@
 This shift to lower temperature may also help to resolve some of the age discrepancies between intermediate mass and low mass young stars \citep[e.g.][]{herczeg15}.
+The corrected placement of spotted stars on the HR diagram reflects the accurate luminosity, radius, and effective temperature, but evolutionary models are not yet equipped to interpret such heavily spotted stars \citep{somers15}.
 
@@
 
+\subsection{Comparison to studies of ensembles}
+
+%Introduce
+The number of WTTS for which the areal filling factor of spots have been measured is relatively low.  Recently there have been many new estimates.
+
+% Grankin
+V 410 Tau shows up to 41\% coverage of spots \citep{petrov94}.
+Many more measurements exist for evolved giants and subgiants, with typical fill factors in the range 15$-$48\% \citep{berdyugina05}.
+The prototypical BY Dra source is consistent with 60\% coverage fraction of moderately cool ($\Delta \teff =400$) penumbra \citep{chugainov76}.
+By these comparisons, LkCa 4 seems on the high end of filling factor.
+
+% Covey
+The Pleiades serves as a slightly older sample of young stars possessing evidence for large coverage fraction of starspots.
+For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}.
+Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.
+However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
+LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation, therefore evading photometric modulation detection, but contributing to otherwise anomalous color offsets.
+
+% Venuti
+WTTSs observed towards NGC2264 show photometric variations similar to--but of lower average amplitude than-- LkCa 4 \citep{venuti15}.
+Modeling of polychromatic photometric monitoring of the locus of WTTSs indicates a lower limit to the true coverage fraction $f_{\mathrm{eq}}\sim10-30\%$ and a difference $\teffa-\teffb\sim500$ K.
+
+% Fang
+\textbf{Insert Fang info here.}
+
 \subsection{Interpretation of the large filling factor of cool starspots}
@@
 
-The Pleiades serves as a slightly older sample of young stars possessing evidence for large coverage fraction of starspots.
-For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}.
-Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.
-However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
-LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation, therefore evading photometric modulation detection, but contributing to otherwise anomalous color offsets.
-
-The number of WTTS for which the areal filling factor of spots have been measured is relatively low.
-V 410 Tau shows up to 41\% coverage of spots \citep{petrov94}.
-Many more measurements exist for evolved giants and subgiants, with typical fill factors in the range 15$-$48\% \citep{berdyugina05}.
-The prototypical BY Dra source is consistent with 60\% coverage fraction of moderately cool ($\Delta \teff =400$) penumbra \citep{chugainov76}.
-By these comparisons, LkCa 4 seems on the high end of filling factor.
-
 One conceivable interpretation of the 67\% to 83\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere, as described by \citet{donati14}.
@@
 In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
-{\bf Donati-- How does this compare to the reconstructed maps from ZDI in Donati et al.
-2014?}.
+
+The starspot geometry is also consistent with morphologies observed in interferometric maps of $\Zeta$ Andromedae: large areal coverage of permanent polar spots, and smaller, transient networks of varying darkness which thread across the whole surface \citep{roettenbacher16}.
+
+%\subsection{Possibility of third temperature or multiple temperatures}
 

### 2016-09-16 document/ms.tex
Include some comments from K. Grankin

@@
 
-The WTTS \name \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep[\emph{e.g.}][]{hartigan95} or mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15}, and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
+The WTTS LkCa 4 \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep[\emph{e.g.}][]{hartigan95} or mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15}, and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
 LkCa 4 has no evidence for a close companion from both direct imaging searches\citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}} and RV searches \citep{nguyen12,donati14}.
@@
 
-LkCa 4 has recently been examined with ZDI \citep{donati14}, revealing a dark spot over the magnetic pole and a bright region at mid-latitudes.
-Unanswered questions about the large disagreement ($\Delta \teff \sim$ 500 K) in LkCa 4's effective temperature \citep{herczeg14, donati14} remain.
+LkCa 4 has recently been examined with ZDI \citep{donati14}, revealing a complex distribution of cool and warm spots in brightness map reconstructions.
+Dark polar spots extend to about $30^\circ$ from the pole, with about 5 appendages reaching down to about $60^\circ$ from the pole.
+There is also evidence for a hot spot in the reconstructed ZDI map.
+Still, unanswered questions about the large disagreement ($\Delta \teff \sim$ 500 K) in LkCa 4's effective temperature \citep{herczeg14, donati14} remain.
 
@@
 We model this rotational modulation using the main sequence colors \citep[compiled by][]{pecaut13}, which should have less contribution from spots than  pre-main sequence colors.
-The Cousins $R$ photometry from \citet{pecaut13} is converted to Johnson $R$ for comparison with the \citet{grankin08} photometry, following the color transformation prescribed by \citet{landolt82} and applied by Grankin et al.
+The Cousins $R$ photometry from \citet{pecaut13} is converted to Johnson $R$ for comparison with the \citet{grankin08} photometry, following the color transformation prescribed by \citet{landolt83} and applied by Grankin et al.
 Photometry from synthetic spectra produced by Phoenix and BT-Settl models cannot be used here because the predicted $B-V$ colors are much bluer than observed.
@@
 
+There are several WTTS in the Taurus-Auriga star-forming region that demonstrate the highest amplitudes of periodic light variations, achieving $0.4−0.8$ mag in the $V-$band: LkCa 4, V410 Tau, V836 Tau, LkCa 7, V827 Tau, V830 Tau, and V819 Tau \citep{grankin08}.
+Such large amplitudes of the light variation indicate the existence of very extended spotted regions on the stellar surface.
+To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, V830 Tau, and V836 Tau \citep{1998AstL...24..497G,1999AstL...25..526G}.
+For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500−1400$ K lower than the ambient photosphere.
+An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
+nonuniformity, which is defined as the difference of spot coverage in the visible hemispheres of the star at maximum and minimum light.
+As the amplitude increases from 0.39 to 0.63mag, the degree of nonuniformity in the spot distribution increases from 21 to 37\%.
+Besides the high amplitude of variability, these objects show the phenomenon of long-term stability of a brightness minimum in the interval from 5 to 19 years.
+To all appearances, this group of stars has the similar nature of stellar activity which
+should be investigated in the future.
+
 % Covey
@@
 
-The starspot geometry is also consistent with morphologies observed in interferometric maps of $\Zeta$ Andromedae: large areal coverage of permanent polar spots, and smaller, transient networks of varying darkness which thread across the whole surface \citep{roettenbacher16}.
+The starspot geometry is also consistent with morphologies observed in interferometric maps of $\zeta$ Andromedae: large areal coverage of permanent polar spots, and smaller, transient networks of varying darkness which thread across the whole surface \citep{roettenbacher16}.
 

### 2016-09-18 document/ms.tex
Incorporate feedback from K. Grankin, closes Issue # 41

@@
  \centering
+  \includegraphics[width=0.45\textwidth]{figures/v_v-r_Grankin} 
  \begin{tabular}{ll}
@@
     \end{tabular}
-\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions from converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{kenyon95} (purple lines).}
+\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions.  
+\emph{Top}: Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.
+The purple line represents a two component photometric model  described by \citet{grankin08}, comprising a photospheric temperature of 4040K (for K7), and a temperature of spotted area of 3030K (for an M5).
+In this model, the spot coverage of the observed hemisphere varies from $\sim36\%$ at maximum brightness, and $\sim82\%$ at minimum brightness.
+\emph{Bottom:}  The model is constructed instead by converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{pecaut13} (purple lines).}
 \label{fig:colors}
@@
 
-There are several WTTS in the Taurus-Auriga star-forming region that demonstrate the highest amplitudes of periodic light variations, achieving $0.4−0.8$ mag in the $V-$band: LkCa 4, V410 Tau, V836 Tau, LkCa 7, V827 Tau, V830 Tau, and V819 Tau \citep{grankin08}.
+There are several WTTS in the Taurus-Auriga star-forming region that demonstrate the highest amplitudes of periodic light variations, achieving $0.4-0.8$ mag in the $V-$band: LkCa 4, V410 Tau, V836 Tau, LkCa 7, V827 Tau, V830 Tau, and V819 Tau \citep{grankin08}.
 Such large amplitudes of the light variation indicate the existence of very extended spotted regions on the stellar surface.
 To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, V830 Tau, and V836 Tau \citep{1998AstL...24..497G,1999AstL...25..526G}.
-For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500−1400$ K lower than the ambient photosphere.
+For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500-1400$ K lower than the ambient photosphere.
 An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
@@
 From a statistical perspective, it might not be a surprise that the source with the largest photometric variability also posessess among the largest coverage fraction of cool spots.
-The large $\sim$1 kG toroidal component at equatorial latitudes makes LkCa 4 an outlier by this metric, when compared to other TTSs.
 

### 2016-09-18 document/ms.tex
Include comments from Greg Mace.  Closes Issue $42.

@@
 Telluric correction was performed by dividing the spectrum of \name by a spectrum of HR 1237, an A0V star observed immediately before \name, both at airmass 1.1.
-The broad hydrogen lines in the A0V star produced broad flux excesses in the spectrum of LkCa 4.
-No effort was made to remove these flux excesses, which affect several spectral orders.
+The broad hydrogen lines in the A0V star produced broad flux excess residuals in the spectrum of LkCa 4.
+No effort was made to mitigate these flux excess residuals, which affect several spectral orders.
 
@@
 As pointed out earlier, LkCa 4 has no detected companion from direct imaging, and its RV variations are consistent with starspot modulation, so any binary companion would have to have exceptionally large luminosity or mass ratios, rendering it undetectable with our spectral inference methodology with the finite signal to noise available in the IGRINS data.
-The absense of a mid-IR excess emission attributable to a disk also means that the spectral modeling requires no further parameters like veiling or accretion.
+LkCa 4's absense of mid-IR excess emission attributable to a disk also means that the spectral modeling requires no further parameters like veiling or accretion.
 
@@
  \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_03} 
- \caption{Examples of spectral features in the observed IGRINS spectrum (thick gray line).
-The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel spectrum) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.}
+ \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).
+The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
+The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\Omega}$ for individual spectral orders.}
  \label{fig:specPostageStamp}
@@
 \subsection{Evidence for intra-spectrum RV jitter}
-Starspots cause significant jitter in radial velocity surveys for young planets \citep[e.g.][]{donati14, robertson14}.
+Starspots cause significant jitter in radial velocity (RV) surveys for young planets \citep[e.g.][]{donati14, robertson14}.
 The two-temperature model assumed that the hot and cool components shared the same $\vsini$ and $v_z$.
@@
 LkCa 4 has clear optical line-profile variations \citep{nguyen12, donati14}.
-Accordingly, we should be able to detect anticorrelation between lines attributable to hot photosphere, and lines attributable to cool photosphere, since there is a zero-sum competition for solid-angle on the recessional and advancing stellar limbs.
+We should be able to detect \emph{anticorrelation} between the line center positions of spectral lines arising from ambient photosphere, and lines arising from cool starspots, since there is a zero-sum competition for solid-angle on the recessional and advancing stellar limbs.
 We found tentative, albeit weak, evidence for such anticorrelation in $v_z$ across spectral orders dominated by cool photosphere and those dominated by hot photosphere.
 For example, the cool-photosphere dominated spectral orders $o = 100, 102, 104$ show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
+An independent analysis of the RV of the IGRINS spectrum yields a barycentric RV of $14.6\pm0.2$ km~s$^{-1}$.
+The direct emission of starspots could constitute a heretofore unaccounted source of correlations in conventional RV signal processing.
 
@@
 Direct spectral emission from cool starspots is likely much weaker in sources with less starspot coverage than LkCa 4.
+Still, the characterization and modeling of direct emission from starspots should, in principle, decrease RV jitter attributable to starspots in the near-IR spectra of any spotted star as demands on RV precision increase.
 
@@
 \acknowledgements
-The authors thank Gregory N. Mace for carrying out the IGRINS observations.
 

### 2016-09-18 document/ms.tex
Include comments from IGRINS internal referee process-- Closes Issue #43

@@
  \includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
- \caption{Violin plot of marginalized samples for $\teffa$, $\teffb$, and fill factor $f_{\Omega}$, derived independently from full-spectrum fitting to 48 IGRINS orders.
-Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=111$) consistent with negligible starspot emission, and others ($o=104, 102, 100$) showing tight constraints on the filling factor of starspots.
+ \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\Omega}$ (yellow shade).
+The stellar parameters are derived independently in each spectral order.
+Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.
 The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.
-$K-$band orders show lower estimates for the ambient photosphere, though some of these estimates are unreliable due to spectral line outliers}
+$K-$band orders show lower estimates for the ambient photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
  \label{fig:TwoTempResults}
@@
 
-The IGRINS spectrum demonstrates some features that are reproduced only in the hot photosphere model, or only in the cool photosphere model.
+The IGRINS spectrum demonstrates some features that are present only in the ambient photosphere model, and some features that are present only in the starspot model.
 Figure \ref{fig:specPostageStamp} shows a selection of six such spectral features for a range of plausible fill factors.
-In some cases, featureless cool photosphere spectra veil isolated spectral lines predicted in the hot photosphere models.
-In other cases, the hot photosphere model veils sequences of shallow spectral features predicted in the cool photosphere model.
-The cool photosphere models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening.
+In some cases, featureless starspot spectra veil isolated spectral lines predicted in the ambient photosphere models.
+In other cases, the ambient photosphere model veils sequences of shallow spectral features predicted in the starspot model.
+The starspot spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening.
 This line blanketing has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
-One such feature has been previously identified in the near-IR: the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines, although the \PHOENIX\ models predict a non-negligible hot star contribution to the middle line for our range of ambient and spot temperatures.
+One such feature has been previously identified in the near-IR: the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines, although the \PHOENIX\ models predict a non-negligible ambient photosphere contribution to the middle line for our range of ambient and spot temperatures.
 In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
@@
 Photometry from synthetic spectra produced by Phoenix and BT-Settl models cannot be used here because the predicted $B-V$ colors are much bluer than observed.
-Offsets between model and observed colors are attributed to extinction and are discussed in \S 5.1.
+Offsets between model and observed colors are at least in part attributed to extinction and are discussed in \S 5.1.
+
+Limb darkening effects also become important if starspots are distributed in a finite number of large patches, not many small patches.
+The variations in the mean projection angle cause confounding color trends in the photometric modulations.
 

### 2016-09-18 document/ms.tex
Closes #44 : Feedback from the ASASSN team.  Still need to format the coauthors and affiliations though.

@@
 
-\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2}, Garrett Somers\altaffilmark{2}, et al.}
+\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2}, Garrett Somers\altaffilmark{3}, et al.}
+
+%%% Coauthors:
+
+%%% Konstantin Grankin
+%CrAO
+
+%%% Donati
+% CNRS
+
+%%% Covey
+% WWU
+
+%%% Greg Mace
+%UT Austin
+
+%%% TODO: Fill in more here as I go through the emails and feedback
+
+%%%T.~W.-S.~Holoien\altafifilmark{3}
+%- Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA
+%- Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA
+
+%%% Ben Shappee
+%Hubble, Carnegie-Princeton Fellow
+%Observatories of the Carnegie Institution for Science
+%813 Santa Barbara Street
+%Pasadena, CA  91101
+%USA
 
 \altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
-\altaffiltext{2}{TBD}
+\altaffiltext{2}{Stanford University, Palo Alto, CA}
+\altaffiltext{3}{Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center, Nashville, TN, 37235, USA}
 
@@
 Magnetic fields temporarily increase the opacity in stellar photospheres, impacting both their instantaneous stellar flux and the duration and efficiency of their convective energy transport during pre-main sequence stellar evolution.
-The observational manifestation of local magnetic fields, starspots on young stars can cover a large fraction of the stellar surface, causing the incorrect assessment of both the effective temperature and the luminosity and therefore the placement of sources on HR diagrams.
-The singleton weak-lined T-Tauri star LkCa 4 shows exceptionally large photometric modulation attributable to star spots, making it an ideal testbed for measuring starspot properties.
+The observational manifestation of local magnetic fields, starspots can cover a large fraction of the stellar surface, biasing estimates of both the effective temperature and the luminosity and therefore the placement of sources on HR diagrams.
+The weak-lined T-Tauri star LkCa 4 shows exceptionally large photometric modulations of 0.5-0.8 $\Delta V$ mag attributable to star spots, making it an ideal testbed for measuring starspot properties.
 Infrared spectral features in high resolution IGRINS spectra indicate that 80\% of the surface is covered in $\teffb \sim 2750$ K patches of cool photosphere at the epoch of the observation.
@@
 The spectral energy distribution, color variability, rotational modulation, and low-resolution optical/IR spectroscopy-- when registered to the filling factors at the epochs of their observations--strengthen the case for a large starspot filling factor and temperature contrast through time.
-The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger when placed on a pre-main sequence HR diagram, compared to previous estimates based only on optical spectroscopy and not taking into account the large coverage fraction of cool spots.
-The derived starspot properties explain the extreme $V-$band photometric amplitude of 0.5$-$0.8 magnitudes.
-Geometric considerations of spot coverage suggest that other heavily spotted young stars have been misplaced on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
+The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based only on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
+The derived starspot properties explain the extreme $V-$band photometric variability.
+Emission from polar starspots viewed at moderate inclination has likely caused the misplacement of heavily spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
 \end{abstract}
@@
 Observationally, \citet{hartmann01} and \citet{slesnick08} argue that measurement uncertainties may mask any real differences in ages within a cluster.
-In models, \citet{hartmann97} and \citet{baraffe09} describe how non-static accretion histories change the stellar contraction at early times.
+In models, \citet{hartmann97} and \citet{baraffe09} describe how variable accretion histories change the stellar contraction and hence luminosities at early times.
 Contraction rates also depend on the prescription for convection, which may vary with mass.
@@
 Magnetic activity is a likely source of significant uncertainty in both the models and observations of young low-mass stars.
-Convection at these young ages generates strong magnetic fields, as measured in Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}.
+Convection at these young ages generates strong magnetic fields, as measured by Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}.
 Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (\citet{somers15}, \citet{feiden16}; see also \citet{baraffe15} for an updated treatment of convection without introducing magnetic fields).
-Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with derived masses biased towards lower masses \citep{somers15}.
+Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with standard mass estimates being biased towards lower masses \citep{somers15}.
 Starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
-For example, effective temperatures for 3493 young stars measured using the APOGEE spectrograph \citep[$1.5-1.70 \;\mu$m at $R=22,500$][]{wilson10} are offset by 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) relative to previous measurements, usually from optical \citep{cottaar14}.
+For example, the effective temperatures for 3493 young stars measured using the APOGEE spectrograph \citep[$1.5-1.70 \;\mu$m at $R=22,500$][]{wilson10} are offset by 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) relative to previous, usually optical, measurements \citep{cottaar14}.
 
@@
 Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep[\emph{e.g}][]{harrison11,davenport15}.
-Monochromatic photometric monitoring cannot separate the relative areas and temperatures of the emitting regions, and therefore cannot yield estimates for the areal fill factor of spots without making assumptions about the relative temperature contrast.
-Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{petrov94,bouvier95,grankin07,cody14} can break the degeneracy between starspot areal filling factor and starspot temperature, but these measurements are still limited to detecting large longitudinally asymmetric starspots.
+The single band light curves from such surveys cannot separate the relative areas and temperatures of the emitting regions, and therefore cannot yield estimates for the filling factor of spots without making assumptions about the relative temperature contrast.
+Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{petrov94,bouvier95,grankin07,cody14} can break the degeneracy between starspot filling factor and starspot temperature but these measurements are still limited to detecting large longitudinally asymmetric starspots.
 Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups, but the number of such transiting systems and demands of high photometric precision limit wider application.
@@
 
-Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 22 observing seasons and phase-folded by period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
+Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 22 observing seasons and phase-folded by the period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
 The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-The estimated $BVR$ magnitudes at the time of the spectral observations are determined from regularized multiterm fits \citep{vanderplas15a} shown as the solid blue lines in Figure \ref{fig:PhotPhase}.
+The estimated $BVR$ magnitudes at the time of the spectral observations are determined from regularized multiterm fits \citep[\emph{i.e.} Fourier series truncated to the first $\sim 4$ components]{vanderplas15a} shown as the solid blue lines in Figure \ref{fig:PhotPhase}.
 Table \ref{tbl_estimated_V} lists the estimated $BVR$ photometry and the observing epoch for data from IGRINS, ESPaDOnS, 2MASS \citep{skrutskie06}, DoubleSpec, and TripleSpec.
@@
  \includegraphics[width=0.95\textwidth]{figures/Vband_22s.pdf}
- \caption{Phase-folded lightcurves constructed assuming the same period for all observing seasons.
-The blue solid lines show a multi-term regularized periodic fit keeping the first $M_{\rm max}=4$ Fourier components.
-The vertical lines show the epochs of observations for ancillary data, with the same line styles and colors as Figure \ref{fig:PhotTime}.
-The unchanged vertical and horizontal scales highlight the secular drift of the light curve amplitude and morphology.}
+ \caption{Phase-folded lightcurves constructed assuming $P=3.375$ days for all 22 observing seasons.
+The blue solid lines show a ``multiterm'' regularized periodic fit, that is, keeping the first $M_{\rm max}=4$ Fourier components \citep{vanderplas15a}.
+The vertical lines show the epochs at which spectra or ancillary photometry were obtained, with the same line styles and colors as Figure \ref{fig:PhotTime}.
+LkCa 4 shows secular changess in its light curve morphology.}
  \label{fig:PhotPhase}
@@
 The apparent veiling of the lines and their respective temperature dependences can be combined to solve for the starspot and ambient photosphere temperatures and relative areal coverages.
-The line depth ratio method suffers from the need to identify portions of the spectrum that possess such strong lines, and also suffers from the need to assemble large atlases of observed spectral templates to which the spotted star spectrum can be compared.
-In this section, we introduce a generalization of line depth ratio analysis which employs pixel-by-pixel modeling of spectral orders.
-By leveraging all the channels present in a spectrum, this strategy has the power to constrain starspot properties at relatively low fill-factors and identify weak lines that originate from the starspot.
+This line depth ratio method suffers from the need to identify portions of the spectrum that possess such strong lines, and from the need to assemble large atlases of observed spectral templates to which the spotted star spectrum can be compared.
+In this section, we introduce a generalization of the line depth ratio analysis which employs pixel-by-pixel modeling of all spectral orders.
+By using all the spectral data, this strategy has the power to constrain starspot properties at relatively low filling factors and to identify weak lines that originate from the starspots.
 
 We took two approaches to characterizing the effective temperature response from a spotted-star spectrum.
-First we measured a single effective temperature to unique spectral orders in the optical (\S \ref{sec:ESP_starfish}) and near-IR (\S \ref{sec:IGR_starfish}).
-Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to a high grasp near-IR spectrum (\S \ref{sec:two_tempIGRINS}), which should show greater starspot flux density than optical.
+First we measured a single unique effective temperature to each spectral order in the optical (\S \ref{sec:ESP_starfish}) and near-IR (\S \ref{sec:IGR_starfish}).
+Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to a near-IR echelle spectrum (\S \ref{sec:two_tempIGRINS}), which should show greater starspot flux density than optical.
 
@@
 The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}} to infer stellar properties from high resolution spectra.
-The \iancze\ technique forward models observed spectra with synthetic spectral from pre-computed model grids.
-The intra-grid-point spectra are emulated, taking into account the information loss attributable to the coarsely sampled stellar intrinsic parameters.
+The \iancze\ technique forward models observed spectra with synthetic spectra from pre-computed model grids.
+The intra-grid-point spectra are ``emulated'' in a process similar but superior to interpolation, since it seemlessly quantifies the uncertainty attributable to the coarsely sampled stellar intrinsic parameters (see Appendix of \iancze).
 The forward model includes calibration parameters, line spread functions, and a Gaussian process noise model to account for correlations in the residual spectrum.
-We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
+We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which span a wide range of wavelengths at high spectral resolution with a sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
 The modular framework was altered to accommodate starspot measurements in two ways.
 First, the single photospheric component was updated to include a starspot spectrum.
-Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added in the starspot model.
+Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added by the starspot model.
 
-The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$, respectively.
-Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, and they share the same average intrinsic and extrinsic stellar parameters otherwise; that is $(\vsini, \logg, \Z, v_z)$ are identical for starspots and ambient photosphere.
-The composite mixture model for observed flux density can be written down as:
-
+The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$, respectively\footnote{For flux calibrated spectra, the total solid angle $\Omega$ can be constrained, but for typical echelle spectrographs only relative values of $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$ can be inferred.}.
+Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, but otherwise share the same average intrinsic and extrinsic stellar parameters $(\vsini, \logg, \Z, v_z)$.
+The composite mixture model for observed flux density is:
 \begin{eqnarray} \label{eqn:mix_M}
@@
 \end{eqnarray}
-
-where $B$ is the spectral radiance from emulated model spectra.  The observed filling factor of starspots $f_{\Omega}$ is simply the ratio:
-
+where $B(T)$ is the spectral radiance from model spectra.  The filling factor of the starspots is:
 \begin{eqnarray} \label{eqn:fill_factor}
@@
 The ESPaDOnS observations are supported by the contribution to the MATYSSE Large Project on CFHT obtained through the Telescope Access Program (TAP), which has been funded by the ``the Strategic Priority Research Program---The Emergence of Cosmological Structures'' of the Chinese Academy of Sciences (Grant No.11 XDB09000000) and the Special Fund for Astronomy from the Ministry of Finance.
+TW-SH is supported by the DOE Computational Science Graduate Fellowship, grant number DE-FG02-97ER25308.
 

### 2016-09-18 document/ms.tex
Closes #45 : MATYESSE team feedback

@@
 The weak-lined T-Tauri star LkCa 4 shows exceptionally large photometric modulations of 0.5-0.8 $\Delta V$ mag attributable to star spots, making it an ideal testbed for measuring starspot properties.
-Infrared spectral features in high resolution IGRINS spectra indicate that 80\% of the surface is covered in $\teffb \sim 2750$ K patches of cool photosphere at the epoch of the observation.
+Infrared spectral features in high resolution IGRINS spectra indicate that 80\% of the surface is covered in $\teffb \sim 2750$ K patches of starspots at the epoch of the observation.
 The rest of the $20\%$ of the stellar surface can be thought of as either ambient photosphere or a hot spot of $\teffa \sim4100$ K.
@@
 No effort was made to mitigate these flux excess residuals, which affect several spectral orders.
+These orders were ultimately excluded from further analyses.
 
@@
 First we measured a single unique effective temperature to each spectral order in the optical (\S \ref{sec:ESP_starfish}) and near-IR (\S \ref{sec:IGR_starfish}).
-Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to a near-IR echelle spectrum (\S \ref{sec:two_tempIGRINS}), which should show greater starspot flux density than optical.
+Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to a near-IR echelle spectrum (\S \ref{sec:two_tempIGRINS}).
+The near-IR was preferred over the optical, since the cool starspots emit most of their flux in the near-IR, enhancing the likelihood of direct detection of emission from the starspots.
 
@@
 
-We performed spectral fitting on the ESPaDOnS spectrum acquired on 2014 January 11, the fourth ESPaDOnS spectrum from Table \ref{tbl_estimated_V}.
+We performed spectral fitting on an ESPaDOnS spectrum\footnote{The fourth ESPaDOnS spectrum from Table \ref{tbl_estimated_V} was arbitrarily chosen.} acquired on 2014 January 11.
 The spectrum was apportioned into subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
@@
 Overall the 26 sets of point estimates for stellar parameters show relatively good agreement, with exceptions.
-We have little constraint on $\logg$ and $\Z$ since full-spectrum fitting tends to wash out the weak signal contained in line wings for spectra with a finite level of random noise and systematic error.
-Meanwhile, strong metal lines can bias estimates of $\Z$ at the expense of estimates for $\teff$.
-Estimates for $v_z \sim 15.6 \pm 0.6$ km/s and $\vsini \sim 28.0 \pm 0.9$ km/s are consistent across all orders with the exception of two spectral orders at $6920 <\lambda \;(\mathrm{nm})< 7057$ and $8473 < \lambda \;(\mathrm{nm}) < 8706$ due to numerous large spectral outliers.
-The more-well-behaved spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
+The best-fitting spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
 Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each spectral order.
@@
 The effective temperature peaks at values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
-The $K-$band shows even lower derived effective temperatures of $\sim3300$ K, or 700 K cooloer than estimated from optical.
+The $K-$band shows even lower derived effective temperatures of $\sim3300$ K, or 700 K cooler than estimated from optical.
 No single temperature can describe all the spectral lines present in the high resolution optical and IR spectra.
-This discrepancy is circumstantial evidence for the detection of spectral features attributable to starspots.
+Sources with such discrepancies have been seen previously, for example in Figures 4 and 5 in \citet{bouvier92}.
+These discrepancies are circumstantial evidence for the detection of spectral features attributable to starspots.
 
@@
 Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.
-These spectra have comparable albeit different estimated $V-$band magnitudes of 12.90 and 12.83 for the ESPaDOnS and IGRINS spectra respectively.
-Assuming the areal coverage fraction of spots was the same or greater during the ESPaDOnS spectrum acquisition, the optical bands and short-wavelength end of $H$-band are relatively insensitive to the spectral signatures of starspots in this system.
+The particular ESPaDOnS spectrum used in Section \ref{sec:ESP_starfish} has an estimated $V-$band magnitude of 12.90 while the IGRINS spectrum has 12.83.
+The fainter magnitude during the ESPaDOnS spectrum acquisition implies a greater coverage fraction than during the IGRINS spectrum.
+The $\teff$ derived in the optical bands and short-wavelength end of $H$-band yield similar values of $\sim 4100$ K, suggesting the \emph{bulk}\footnote{The bulk appearance and disappearance of spectral lines is mostly controlled by the temperature of the emitting region of the local photosphere.
+In other words, most of the variance in a spectrum is attributable to temperature, assuming near-solar metallicity.
+Starspots imbue dearths of flux in the line profiles of optical spectra, but these are secondary to the mere presence of temperature-sensitive lines.} spectral features are broadly consistent with a emission from a single temperature component.
+A single ESPaDOnS order surrounding the TiO bands shows an exceptionally low estimated $\teff$.
 The long wavelength portion of $H-$band and all of $K-$band are more sensitive to starspot spectral signatures than the shorter wavelength portions.
@@
 The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
-Starspots are cooler than their surrounding photosphere and will, therefore, have a longer wavelength of peak emission, according to Wein's displacement law.
+Starspots are cooler than their surrounding photosphere and will, therefore, have a longer wavelength of peak emission.
 The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
@@
 The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
-Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere, and the two temperature photosphere that best fit the IGRINS spectrum.
+Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere (red), and the two temperature photosphere (pink) that best fits the IGRINS spectrum.
 The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
@@
 The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
-The $3500$ K component hotter component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
+The $3500$ K component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
 A two temperature photosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
@@
 Figure~\ref{fig:vband_spot} shows the 2015--2016 ASAS-SN lightcurve, converted into a cool spot filling factor.
-In this epochs, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
+In this epoch, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
 Since 1992 the $V$ band photometry has been as bright as $12.3$ mag, which corresponds to a cool component fill factor of $65\%$, and as faint as $13.2$ mag, or a cool component fill factor of $87\%$.
@@
  \caption{Variability in TiO bands measured with ESPaDOnS.
-The V-band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
-The main panel shows a correlation between V-band magnitude and the TiO-7140 index, while the inset shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
+The $V-$band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
+The bottom left panel shows a correlation between $V-$band magnitude and the TiO-7140 index, while the bottom right shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
  \label{fig:tiovar}
@@
 Low mass young stars are redder than expected in the near-IR, when compared with expectations from optical spectral types \citep[e.g.][]{tottle15}.
-For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $1.04$ mag for a 4200 K photosphere and \citep{pecaut13} colors.
+For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $1.04$ mag for a 4200 K photosphere and \citet{pecaut13} colors.
 This extinction is consistent with the color and SED analysis of \citet{furlan06}, which adopted a K7 spectral type, and is significantly higher than extinctions of $A_V=0.69$ measured from optical photometry \citep{kenyon95} and $0.35$ mag measured by comparing optical spectra to young spectral templates \citep{herczeg14}.
@@
 Such large amplitudes of the light variation indicate the existence of very extended spotted regions on the stellar surface.
-To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, V830 Tau, and V836 Tau \citep{1998AstL...24..497G,1999AstL...25..526G}.
+To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, V830 Tau, and V836 Tau \citep{grankin98,grankin99}.
 For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500-1400$ K lower than the ambient photosphere.
@@
 However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
-LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation, therefore evading photometric modulation detection, but contributing to otherwise anomalous color offsets.
+LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation.
+The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.
 

### 2016-09-19 document/ms.tex
Add a section about the absolute lower limit and upper limit of filling factor and temperature.

@@
 \input{tables/tbl_estV_atObsEpoch.tex}
+
+\subsection{Absolute lower limit of starspot filling factor}
+
+A lower limit to the starspot filling factor can be set by the size of a black spot that can induce such large $\Delta V$.
+
+Consider the following extremely conservative assumptions:  \begin{enumerate}
+  \item The starspot emits \emph{zero flux}.  This statement is equivalent to the starspot being at \emph{absolute zero}.
+  \item The stellar disk shows no starspots at maximum brightness.
+  \item The starspot transits the center of the stellar disk.
+\end{enumerate}
+
+If \emph{any} these assumptions is relaxed, the minimum fill factor \emph{increases}.
+
+For LkCa 4 in 2015 the $\Delta V\sim 0.5$ mag amplitude corresponds to an absolute minimum fill factor $f>0.37$.
+At least 37\% of the stellar is covered in starspots at minimum light.
+In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
+
+\subsection{Absolute upper limit of starspot temperature}
+
+Consider relaxing assumption 1 from above to better match reality: a starspot is not at absolute zero temperature, it has a finite temperature and therefore emits a finite amount of radiation.
+Increasing the temperature a little means that the starspot size has to increase to cause the same flux difference.
+The starspot cannot occupy more than 100\% of the projected stellar hemisphere, so there is an upper limit for the temperature of the starspot that yields a given $\Delta V$.
+The starspot temperature upper limit for $\Delta V=0.5$ is 3650 K.
+In the 2004 season, the starspot temperature upper limit was 3410 K.
+
+In reality, the star will have some patches of starspots that always face toward the observer, like polar spots, bands of spots, multiple finitie-sized patches of starspots, or homogenuously distributed small spots.
+Dark spots on extreme latitudes on inclined stars might only pass over the limb of the stellar disk, reducing the diminution $V-$band flux for a given projected surface area.
+All of these effect mean that real starspot filling factors are likely to be larger than the filling factor lower limit, and cooler than the temperature upper limit.
 

### 2016-09-20 document/ms.tex
Relates to Issue #46-- K. Covey feedback.  Overhaul the abstract, include Triplespec description

@@
 
+%%% Covey
+% WWU
+
 %%% Donati
@@
 
-%%% Covey
-% WWU
+%%% Sylvia Alencar
+
+%%% Gaitee Hussein
+
+%%% Ben Shappee
+%Hubble, Carnegie-Princeton Fellow
+%Observatories of the Carnegie Institution for Science
+%813 Santa Barbara Street
+%Pasadena, CA  91101
+%USA
 
 %%% Greg Mace
+%UT Austin
+
+%%% Jae-Joon Lee
 %UT Austin
@@
 
-%%% Ben Shappee
-%Hubble, Carnegie-Princeton Fellow
-%Observatories of the Carnegie Institution for Science
-%813 Santa Barbara Street
-%Pasadena, CA  91101
-%USA
-
 \altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
@@
 \begin{abstract}
-Magnetic fields temporarily increase the opacity in stellar photospheres, impacting both their instantaneous stellar flux and the duration and efficiency of their convective energy transport during pre-main sequence stellar evolution.
-The observational manifestation of local magnetic fields, starspots can cover a large fraction of the stellar surface, biasing estimates of both the effective temperature and the luminosity and therefore the placement of sources on HR diagrams.
-The weak-lined T-Tauri star LkCa 4 shows exceptionally large photometric modulations of 0.5-0.8 $\Delta V$ mag attributable to star spots, making it an ideal testbed for measuring starspot properties.
-Infrared spectral features in high resolution IGRINS spectra indicate that 80\% of the surface is covered in $\teffb \sim 2750$ K patches of starspots at the epoch of the observation.
-The rest of the $20\%$ of the stellar surface can be thought of as either ambient photosphere or a hot spot of $\teffa \sim4100$ K.
+\emph{Context.}  Ages and masses of young stars can be estimated by comparing observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks.
+Nonstandard physics like magnetic fields and starspots confound interpretations of pre-main sequence HR diagrams and their age and mass estimates.
+
+\emph{Aims.} We characterize the fundamental properties of the spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for signatures of the emergent radiation originating from the starspot or starspot groups.
+The spectral and photometric properties of this radiation can be used to constrain both the starspot filling factor and the starspot temperature.
+
+\emph{Methods.} A generalization of line depth ratio analysis is developed and applied to a high-resolution near-IR IGRINS spectrum.
+The IGRINS spectrum is forward modeled with pre-computed \PHOENIX\ synthetic spectra using the open source spectral inference framework \texttt{Starfish} extended to include a two component mixture model comprised of ambient photosphere and starspot emission.
+
+\emph{Results.} Spectral features attributable to both ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2750$ K are detected in the IGRINS spectrum.
+In some spectral regions, the starspot emission acts merely as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
+The filling factor of starspots is consistently large ($>50\%$) across all IGRINS spectral orders, with a best fit filling factor of $80\%$ starspots.
+The interpretation of the 20\% ambient photosphere as a ``hot spot'' is also possible, though there is no physical motivation for such a distinction.
 The spectral energy distribution, color variability, rotational modulation, and low-resolution optical/IR spectroscopy-- when registered to the filling factors at the epochs of their observations--strengthen the case for a large starspot filling factor and temperature contrast through time.
 The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based only on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
-The derived starspot properties explain the extreme $V-$band photometric variability.
-Emission from polar starspots viewed at moderate inclination has likely caused the misplacement of heavily spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
+
+\emph{Conclusions.} Emission from longitudinally symmetric starspots has likely caused the misplacement of spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
 \end{abstract}
@@
 
-A flux-calibrated low-resolution optical spectrum of LkCa 4 was obtained using Palomar/DBSP \citep{Oke1982} on 30 Dec.
+A flux-calibrated low-resolution optical spectrum of LkCa 4 was obtained using Palomar/DBSP \citep{oke82} on 30 Dec.
 2008.
@@
 
-A low-resolution near-IR spectrum of LkCa 4 was obtained with APO/TripleSpec \citep{Wilson04} contemporaneous to the Palomar/DBSP optical spectrum.  {\bf Covey:  fill in reduction details.}
+Near-infrared spectra of LkCa 4 were obtained at ~01:30 UT on Dec.
+30, 2008, using the TripleSpec spectrograph on the Astrophysical Research Consortium (ARC) 3.5 meter telescope at Apache Point Observatory in Sunspot, New Mexico.
+LkCa 4 was observed for a total integration time of 90s using an ABBA dither sequence along the slit to remove sky emission by differencing sequential exposures.
+With the 1.1$\arcsec$ slit used for these observations, TripleSpec provides nearly contiguous coverage from 0.95 to 2.46 $\mu$m at a resolution of  R $\sim$3200 \citep{wilson04}.
+Spectra were reduced with a variant of the SpeXTool pipeline, originally developed by \citet{cushing04} and modified for use with TripleSpec data.
+Spectra were differenced, flattened, extracted, and wavelength calibrated prior to telluric correction and flux calibration; the latter two corrections were performed using the XTELLCOR IDL package \citep{vacca03} and a spectrum of HD 25175, a nearby A0V star observed directly after LkCa 4 at a similar airmass.
 
@@
 These values show broad consistency between rotational properties, spectral fitting values, and our interpretation of a tilted star revealing a circumpolar region with large areal coverage of starspots.
-While this is obviously not proof of anything, the fact that all our different angles agree nicely would be a fun tidbit to point out.
 

### 2016-09-20 document/ms.tex
Relates to Issue #46: nearly done with K. Covey comments.

@@
 In some spectral regions, the starspot emission acts merely as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
-The filling factor of starspots is consistently large ($>50\%$) across all IGRINS spectral orders, with a best fit filling factor of $80\%$ starspots.
-The interpretation of the 20\% ambient photosphere as a ``hot spot'' is also possible, though there is no physical motivation for such a distinction.
+The filling factor of of starspots at minimum light $\Delta V = 0.5$must be $>37\%$, and is likely much larger based on geometry and temperature considerations.
+The IGRINS spectra yield consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f=80\%$ starspots at the epoch of spectrum acquisition.
+The interpretation of the 20\% ambient photosphere as a ``hot spot'' is also possible, but then all previous studies have misclassified the K7 spectral type from an unseen persistent hot spot spectrum.
 The spectral energy distribution, color variability, rotational modulation, and low-resolution optical/IR spectroscopy-- when registered to the filling factors at the epochs of their observations--strengthen the case for a large starspot filling factor and temperature contrast through time.
-The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based only on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
 
-\emph{Conclusions.} Emission from longitudinally symmetric starspots has likely caused the misplacement of spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
+\emph{Conclusions.} The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based only on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
+Emission from longitudinally symmetric starspots has likely caused the misplacement of spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
 \end{abstract}
@@
 Systematic uncertainties in ages of pre-main sequence stars lead to uncertainties in dissipation timescales of envelopes and protoplanetary disks as evaluated in global studies.
-All clusters have large spreads in luminosity at any given temperature \citep[e.g.][]{reggiani11}, which frustrates the interpretation of individual star/disk properties as related to age.
+Young clusters also have large spreads in luminosity at any given temperature \citep[e.g.][]{reggiani11}, which further frustrate the interpretation of individual star/disk properties as related to age.
 
@@
 Starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
-For example, the effective temperatures for 3493 young stars measured using the APOGEE spectrograph \citep[$1.5-1.70 \;\mu$m at $R=22,500$][]{wilson10} are offset by 200$-$500 K ($\sim$0.02$-$0.05 dex) and as high as 1000 K ($\sim$0.1 dex) relative to previous, usually optical, measurements \citep{cottaar14}.
+For example, the effective temperatures for 3493 young stars measured using the APOGEE spectrograph \citep[$1.5-1.70 \;\mu$m at $R=22,500$][]{wilson10} exhibit systematic offsets from prior measurements predominantly that were predominantly made at optical wavelengths.
+Typical offsets range from $-400-400$ K, with a systematic dependence on $\teff$, with some offsets as large as 1000 K \citep{cottaar14}.
 
@@
 There is also evidence for a hot spot in the reconstructed ZDI map.
-Still, unanswered questions about the large disagreement ($\Delta \teff \sim$ 500 K) in LkCa 4's effective temperature \citep{herczeg14, donati14} remain.
+Still, unanswered questions about the large disagreement in LkCa 4's effective temperature remain, with 4100 K measured from holistic analysis of ESPaDOnS spectra yielding $\teff=4100$K \citep{donati14}, and analysis of the TiO bands of the same spectra yielding $\teff=3600$ K \citep{herczeg14}.
 
-In this work, we constrain the starspot properties of \name with 4 complementary techniques.
-Section \ref{sec:obs} quantifies the optical variability of \name over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
-Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution panchromatic near-IR spectrum of \name in Section \ref{sec:two_tempIGRINS} .
+In this work, we constrain the starspot properties of LkCa 4 with four complementary techniques.
+Section \ref{sec:obs} quantifies the optical variability of LkCa 4 over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
+Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution $H$ and $K$ near-IR spectrum of LkCa 4 in Section \ref{sec:two_tempIGRINS}.
 Section \ref{sec:GJHsection4} shows results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
-All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.
+All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of LkCa 4, and what can be understood about pre-MS stellar evolution from this exemplar.
 
@@
 The vertical lines show the epochs at which spectra or ancillary photometry were obtained, with the same line styles and colors as Figure \ref{fig:PhotTime}.
-LkCa 4 shows secular changess in its light curve morphology.}
+LkCa 4 shows secular changess in its light curve morphology.
+The IGRINS spectrum was acquired near the median flux level, not the extrema.}
  \label{fig:PhotPhase}
@@
 We took two approaches to characterizing the effective temperature response from a spotted-star spectrum.
+
+Using the spectral fitting approach introduced in Section 3.1 \ref{sec:methods}, we first first separately fit the optical (ESPaDOnS) and near-IR (IGRINS) spectra with distinct, single $\teff$ models; these fits are described in Sections \ref{sec:ESP_starfish} and \ref{sec:IGR_starfish} respectively.
+We then use a two temperature mixture model to perform a fit to the near-IR spectra in Section \ref{sec:two_tempIGRINS}.
+
 First we measured a single unique effective temperature to each spectral order in the optical (\S \ref{sec:ESP_starfish}) and near-IR (\S \ref{sec:IGR_starfish}).
@@
 The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$, respectively\footnote{For flux calibrated spectra, the total solid angle $\Omega$ can be constrained, but for typical echelle spectrographs only relative values of $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$ can be inferred.}.
-Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, but otherwise share the same average intrinsic and extrinsic stellar parameters $(\vsini, \logg, \Z, v_z)$.
+Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, but otherwise share the same average intrinsic and extrinsic stellar parameters $\vsini, \logg, \Z, v_z$.
 The composite mixture model for observed flux density is:
@@
 This challenge motivated the second important change to the spectral inference framework, which involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
-The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling.
+The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling \citep{}.
 The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order, making stellar parameter estimates $\vt_{o}$ unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
@@
 For the other 26 spectral orders, the number of samples was generally much longer than the estimated integrated autocorrelation length.
-Overlays of models with observed spectra show modest agreement, with the exception of conspicuous spectral line outliers.
+Overlays of models with observed spectra showed conspicuous spectral line outliers, but the bulk of spectral lines were replicated in the synethic spectral model fits.
 
@@
 The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.
-The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.}
+The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.
+The cluster of $H-$band orders at 1.7 $\mu$m correspond to a local peak in flux density of cool starspots.}
  \label{fig:SingleTeffvsOrder}
@@
 
-We performed full-spectrum fitting on 32 of the 54 available IGRINS spectral orders, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $o$.
+We selected a subset of 32 of the 54 available IGRINS spectral orders\footnote{The finite computational cost limited running all the spectral orders.} with the low telluric absorption artifacts.
+We performed full-spectrum fitting, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $o$.
 We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
@@
 In other words, most of the variance in a spectrum is attributable to temperature, assuming near-solar metallicity.
-Starspots imbue dearths of flux in the line profiles of optical spectra, but these are secondary to the mere presence of temperature-sensitive lines.} spectral features are broadly consistent with a emission from a single temperature component.
+Starspots imbue dearths of flux in the line profiles of optical spectra, but these are secondary to the mere presence of temperature-sensitive lines, despite carrying useful information about the longitudinal distribution of the spots.} spectral features are broadly consistent with a emission from a single temperature component.
 A single ESPaDOnS order surrounding the TiO bands shows an exceptionally low estimated $\teff$.
@@
 
-Full-spectrum fitting was performed for 48 of the 54 available IGRINS spectral orders as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.
+Full-spectrum fitting was performed for 48 of the 54 available IGRINS spectral orders, omitting only the orders with the most pathological telluric spectral artifacts.
+We applied the mixture model as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.
 The MCMC samples generally had 5000 steps with 40 walkers.
@@
 Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.
-What's left were the most informative orders relatively devoid of spectral line outliers, referred to hereafter as the Reliable Order subset.
-Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\Omega}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the Reliable Orders shown in bold.
+The remaining orders are rerelatively devoid of spectral line outliers and include the most information rich portion of the spectrum.
+Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\Omega}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the reliable order subset shown in bold.
 The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.
@@
 The starspot spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening.
+Any feature of interest will be biased to non-zero veiling.
 This line blanketing has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
@@
 In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
-Similar forward-modelling strategies have successfully identified patterns of metal lines in the line-blanketed spectra of low metallicity stars \citep{kirby11,kirby15}.
+The level of veiling of ambient photospheric lines is set by the starspot filling factor and temperature, while the level of veiling of the starspot lines is set by the filling factor and temperature of the ambient photosphere lines.
+Similar forward-modelling strategies have successfully identified patterns of weak metal lines in the line-blanketed spectra of low metallicity stars \citep{kirby11,kirby15}.
 Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
@@
  \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).
-The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
+The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
 The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\Omega}$ for individual spectral orders.}
@@
  \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
-The inset shows that the 2750 K (red, 70\% fill factor) and 4100 K (blue, 30\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.
+The inset shows that the 2750 K (red, 80\% fill factor) and 4100 K (blue, 20\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.
 The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
@@
 We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface.
-The IGRINS spectrum occurred when LkCa 4 had an estimated brightness of $V=12.84$ mag.
-These parameters are selected without any adjustments to attempt to improve fits to the SED or broadband spectra.
+The IGRINS spectrum was obtained when LkCa 4 had an estimated brightness of $V=12.84$ mag.
+The starspot and ambient temperatures and the filling factor are adopted without any adjustments to attempt to improve fits to the SED or broadband spectra.
 
@@
 
-The  $V$-band brightness corresponds to the filling factor of the cool and hot components.
+The  $V$-band brightness reflects the instantaneous filling factor of the cool and hot components.
 In the two-temperature photosphere, the $V$-band emission is dominated by the hotter component and is therefore a good proxy for the visible surface area of the hot component.
 Figure~\ref{fig:vband_spot} shows the 2015--2016 ASAS-SN lightcurve, converted into a cool spot filling factor.
-In this epoch, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
+During this period, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
 Since 1992 the $V$ band photometry has been as bright as $12.3$ mag, which corresponds to a cool component fill factor of $65\%$, and as faint as $13.2$ mag, or a cool component fill factor of $87\%$.
@@
 Our simple model predicts that the correlation should be much weaker than is measured.
-Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ could could be reproduced with some contribution from intermediate temperature.
+Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ could be reproduced with some contribution from intermediate temperature.
 
@@
 
-The improved characterization of the photospheric emission and radius of LkCa 4 is supposed to lead to more accurate estimates of mass and age from pre-main sequence tracks.
+The improved characterization of the photospheric emission and radius of LkCa 4 would ideally lead to more accurate estimates of mass and age from pre-main sequence tracks.
 However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
@@
 As a result, the surface is cooler and releases less radiation, slowing the contraction rate.
-LkCa 4 then appears more luminous and cooler than expected from evolutionary tracks that do not consider magnetic fields.
+LkCa 4 then appears more luminous and cooler than expected for a star of its genuine age from evolutionary tracks that do not consider magnetic fields.
 This shift to lower temperature may also help to resolve some of the age discrepancies between intermediate mass and low mass young stars \citep[e.g.][]{herczeg15}.
@@
 As seen in Figures \ref{fig:PhotTime} and \ref{fig:PhotPhase}, the areal coverage of spots appears to wax and wane secularly through the observing seasons of the last 31 years.
+Notably, it appears to be in a relatively faint phase currently, 0.2 mag fainter in $V$ than it was through much of the late 1980's and early 1990's.
 It is conceivable that LkCa 4 happens to be going through a short-lived episode of relatively high coverage of spots analogous to solar maximum.
@@
 
-\section{Examples of full spectrum fitting}
-
-Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} show spectra from 42 IGRINS orders.
-
-\begin{figure*}
- \centering
- \includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
- \caption{IGRINS Orders 94 and $99-119$.
-Note that the $y-$axis is on a logarithmic scale.
-The red line is the cool photosphere while the blue line is the hot photosphere.
-The purple line is the composite mixture model.}
- \label{fig:Hband3x7}
-\end{figure*}
-
-\begin{figure*}
- \centering
- \includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
- \caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  Cools are the same as Figure \ref{fig:Hband3x7}}
- \label{fig:Kband3x7}
-\end{figure*}
-
 \section{Methodological details}
@@
 %\todo{Verify that the final term possesses a $q$ and not a $q^2$ term.}
+
+\section{Examples of full spectrum fitting}
+
+Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} show spectra from 42 IGRINS orders.
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
+ \caption{IGRINS Orders 94 and $99-119$.
+Note that the $y-$axis is on a logarithmic scale.
+The red line is the cool photosphere while the blue line is the hot photosphere.
+The purple line is the composite mixture model.}
+ \label{fig:Hband3x7}
+\end{figure*}
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
+ \caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  Cools are the same as Figure \ref{fig:Hband3x7}}
+ \label{fig:Kband3x7}
+\end{figure*}
 

### 2016-09-20 document/ms.tex
Relates to Issue: #47-- GJH feedback.  Also, include all coauthors, but need to fill in the affiliations.

@@
 
-\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2}, Garrett Somers\altaffilmark{3}, et al.}
-
-%%% Coauthors:
-
-%%% Konstantin Grankin
-%CrAO
-
-%%% Covey
-% WWU
-
-%%% Donati
-% CNRS
-
-%%% Sylvia Alencar
-
-%%% Gaitee Hussein
-
-%%% Ben Shappee
-%Hubble, Carnegie-Princeton Fellow
-%Observatories of the Carnegie Institution for Science
-%813 Santa Barbara Street
-%Pasadena, CA  91101
-%USA
-
-%%% Greg Mace
-%UT Austin
-
-%%% Jae-Joon Lee
-%UT Austin
-
-%%% TODO: Fill in more here as I go through the emails and feedback
-
-%%%T.~W.-S.~Holoien\altafifilmark{3}
-%- Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA
-%- Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA
+\author{Michael A.
+Gully-Santiago,\altaffilmark{1} Gregory J.
+Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin Covey,\altaffilmark{5} J.F.
+Donati,\altaffilmark{6} Sylvia Alencar,\altaffilmark{7}, Gaitee Hussein,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
 
@@
 \altaffiltext{3}{Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center, Nashville, TN, 37235, USA}
+\altaffiltext{4}{TBD--Grankin}
+\altaffiltext{5}{TBD--Covey}
+\altaffiltext{6}{TBD--Donati}
+\altaffiltext{7}{TBD--Alencar}
+\altaffiltext{8}{TBD--Hussein}
+\altaffiltext{9}{TBD--Shappee}
+\altaffiltext{10}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway St, Austin, TX, USA}
+\altaffiltext{11}{TBD--Lee}
+\altaffiltext{12}{Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
+\altaffiltext{13}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
+\altaffiltext{15}{TBD--Liu}
 
 \begin{abstract}
-\emph{Context.}  Ages and masses of young stars can be estimated by comparing observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks.
+Ages and masses of young stars can be estimated by comparing observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks.
 Nonstandard physics like magnetic fields and starspots confound interpretations of pre-main sequence HR diagrams and their age and mass estimates.
-
-\emph{Aims.} We characterize the fundamental properties of the spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for signatures of the emergent radiation originating from the starspot or starspot groups.
+We characterize the fundamental properties of the spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for signatures of the emergent radiation originating from the starspot or starspot groups.
 The spectral and photometric properties of this radiation can be used to constrain both the starspot filling factor and the starspot temperature.
-
-\emph{Methods.} A generalization of line depth ratio analysis is developed and applied to a high-resolution near-IR IGRINS spectrum.
+A generalization of line depth ratio analysis is developed and applied to a high-resolution near-IR IGRINS spectrum.
 The IGRINS spectrum is forward modeled with pre-computed \PHOENIX\ synthetic spectra using the open source spectral inference framework \texttt{Starfish} extended to include a two component mixture model comprised of ambient photosphere and starspot emission.
-
-\emph{Results.} Spectral features attributable to both ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2750$ K are detected in the IGRINS spectrum.
+Spectral features attributable to both ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2700-3000$ K are detected in the IGRINS spectrum.
 In some spectral regions, the starspot emission acts merely as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
 The filling factor of of starspots at minimum light $\Delta V = 0.5$must be $>37\%$, and is likely much larger based on geometry and temperature considerations.
-The IGRINS spectra yield consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f=80\%$ starspots at the epoch of spectrum acquisition.
-The interpretation of the 20\% ambient photosphere as a ``hot spot'' is also possible, but then all previous studies have misclassified the K7 spectral type from an unseen persistent hot spot spectrum.
-The spectral energy distribution, color variability, rotational modulation, and low-resolution optical/IR spectroscopy-- when registered to the filling factors at the epochs of their observations--strengthen the case for a large starspot filling factor and temperature contrast through time.
-
-\emph{Conclusions.} The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based only on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
+The IGRINS spectra yield consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f\sim80\%$ starspots at the epoch of spectrum acquisition.
+The interpretation of the $\sim20\%$ ambient photosphere as a persistent ``hot spot'' is also possible.
+The spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy show broad support for the starspot parameter estimates derived separately from IGRINS, strengthening the case for a large albeit secularly changing starspot filling factor and temperature contrast through time.
+The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
 Emission from longitudinally symmetric starspots has likely caused the misplacement of spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
@@
 
-%\subsection{Pre Main Sequence HR diagram spread}
-
-Pre-main sequence stellar evolution is an unsolved problem \citep[see review by][]{soderblom14}.
-Systematic uncertainties in ages of pre-main sequence stars lead to uncertainties in dissipation timescales of envelopes and protoplanetary disks as evaluated in global studies.
-Young clusters also have large spreads in luminosity at any given temperature \citep[e.g.][]{reggiani11}, which further frustrate the interpretation of individual star/disk properties as related to age.
-
 The causes of global age uncertainties and of large luminosity spreads in individual clusters are controversial.
@@
 Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (\citet{somers15}, \citet{feiden16}; see also \citet{baraffe15} for an updated treatment of convection without introducing magnetic fields).
-Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with standard mass estimates being biased towards lower masses \citep{somers15}.
+Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with standard mass estimates being biased towards lower masses \citep{somers15,feiden16}.
 Starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
@@
 
-In this work, we constrain the starspot properties of LkCa 4 with four complementary techniques.
+In this work, we measure the starspot properties of LkCa 4 with four complementary techniques.
 Section \ref{sec:obs} quantifies the optical variability of LkCa 4 over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
@@
 \subsection{IGRINS Spectroscopy}\label{sec:igrins} 
-We acquired observations with the Immersion Grating Infrared Spectrograph, IGRINS \citep{park14} on the Harlan J.
+We acquired observations of LkCa 4 with the Immersion Grating Infrared Spectrograph, IGRINS \citep{park14} on the Harlan J.
 Smith Telescope at McDonald Observatory on 2015-11-18 $09^h$ UTC.
@@
 \subsection{ESPaDOnS Spectroscopy}
-We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MATYSSE Large Program.
+We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MaTYSSE Large Program.
 These spectra cover 3900$-$10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.
@@
 
-We performed spectral fitting on an ESPaDOnS spectrum\footnote{The fourth ESPaDOnS spectrum from Table \ref{tbl_estimated_V} was arbitrarily chosen.} acquired on 2014 January 11.
-The spectrum was apportioned into subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
-Full-spectrum fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
+We performed spectral fitting on an ESPaDOnS spectrum acquired on 2014 January 11.
+The spectrum was split into subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
+Fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
 The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and $\teff \in [3500, 4200]$.
 
-The Metropolis-Hastings step sizes were tuned with several iterations of burn-in procedure and the final chains were visually checked for convergence.
-Nine of the 35 available spectral orders failed to converge, due to numerical artifacts arising from poor model fits.
-For the other 26 spectral orders, the number of samples was generally much longer than the estimated integrated autocorrelation length.
-Overlays of models with observed spectra showed conspicuous spectral line outliers, but the bulk of spectral lines were replicated in the synethic spectral model fits.
-
+The Metropolis-Hastings step sizes were tuned with several iterations of burn-in procedure and the final chains were visually checked for convergence, dropping 9 orders that failed to converge for numerical reasons.
 We computed the median value and 5$^{th}$ and $95^{th}$ percentiles of burned-in subsets of the MCMC samples described above.
@@
 We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
-For the IGRINS $K-$band, we employed an expanded search range for the effective temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.
+For the IGRINS $K-$band, we employed an expanded search range for the temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.
 
@@
 The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of photosphere with equal areas (50\% filling factor) but different temperatures-- 2800 K and 4100 K for the starspot and ambient photosphere respectively.
-The black body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.
+The black-body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.
 
@@
 
-Marginalized distributions were computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
-The fit quality was first assessed by examining the consistency of the point estimates of $v_z$ and $\vsini$ across the spectral orders.
+Marginalized distributions are computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
+The fit quality is first assessed by examining the consistency of the point estimates of $v_z$ and $\vsini$ across the spectral orders.
 The distribution of $v_z$ and $\vsini$ exposed extremely poor fits in two orders ($o=91$ and $94$), with all other orders demonstrating $v_z = 12.4 \pm 2.6$ km/s and $\vsini = 28.8 \pm 2.0$ km/s.
@@
 Fitting defects were conspicuous.
-Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, were all excluded from our final stellar parameter compilation.
+Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, are all excluded from our final stellar parameter compilation.
 Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.
 For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
-These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \citep{deen13}.
+These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \citep{johnskrull07,deen13}.
 Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.
@@
 Figure \ref{fig:specPostageStamp} shows a selection of six such spectral features for a range of plausible fill factors.
-In some cases, featureless starspot spectra veil isolated spectral lines predicted in the ambient photosphere models.
-In other cases, the ambient photosphere model veils sequences of shallow spectral features predicted in the starspot model.
+In some cases (\emph{e.g.} the top two panels), featureless starspot spectra veil isolated spectral lines predicted in the ambient photosphere models.
+In other cases (\emph{e.g.} the middle row and lower left panel), the ambient photosphere model veils sequences of shallow spectral features predicted in the starspot model.
 The starspot spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening.
 Any feature of interest will be biased to non-zero veiling.
-This line blanketing has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
+
+The combination of line blanketing and high $\vsini$ has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
 One such feature has been previously identified in the near-IR: the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines, although the \PHOENIX\ models predict a non-negligible ambient photosphere contribution to the middle line for our range of ambient and spot temperatures.
@@
 Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.
-Remarkably, the filling factor of starspots exceeds 50\% with a best fit value of $f_{\Omega}=80\pm 5 \% $.
+Remarkably, the filling factor of starspots exceeds 50\%, with a best fit value of $f_{\Omega}=80\pm 5 \% $.
 
@@
 The synthetic models match the full spectrum reasonably well.
-When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (bottom panels of Figure \ref{fig:lores}).
-However, single temperature photospheres fail to reproduce large spectral features.
+When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (bottom panels of Figure \ref{fig:lores}), while single temperature photospheres fail to reproduce large spectral features.
 The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
@@
 
-The spectral features should be rotationally modulated as the filling factors of the hot and cool components change.
+These spectral features should be rotationally modulated as the filling factors of the hot and cool components change.
 In \S 4.1, we first use our fit to the IGRINS spectrum to convert the $V$-band brightness to the filling factor of the two components.
@@
 Figure~\ref{fig:vband_spot} shows the 2015--2016 ASAS-SN lightcurve, converted into a cool spot filling factor.
-During this period, the brightest and coolest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
+During this period, the brightest and faintest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
 Since 1992 the $V$ band photometry has been as bright as $12.3$ mag, which corresponds to a cool component fill factor of $65\%$, and as faint as $13.2$ mag, or a cool component fill factor of $87\%$.
@@
 Our simple model predicts that the correlation should be much weaker than is measured.
-Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ could be reproduced with some contribution from intermediate temperature.
+Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ color could be reproduced with some contribution from intermediate temperature.
 
@@
 In a 2-temperature photosphere cool enough for molecules to form, the depth of observed TiO bands will depend on the fractional coverage of the components.
-In this subsection, we demonstrate that the TiO band depths vary with spot coverage using 12 epochs of CFHT/ESPaDOnS spectra obtained over 14 days ($\sim 4$ rotation periods) by \citet{donati14}.
+The TiO band depths vary with spot coverage using 12 epochs of CFHT/ESPaDOnS spectra obtained over 14 days ($\sim 4$ rotation periods) by \citet{donati14}.
 
@@
 Small but significant changes are seen in the TiO bands.
-The blue spectrum does not change.
+On the other hand, the blue spectrum does not change.
 The TiO band depths in these spectra are measured from spectral indices as described in \citet{herczeg14}.
@@
 Decreasing the cool spot size to 74\% increases the effective temperature to 3440 K, while increasing the spot size to 86\% decreases to the effective temperature to 3200 K.
-This wide range of possible observed effective temperatures at any single epoch, when accounting for the visible contributions of both hot and cool components, underscores the difficulty in placing young stars on HR diagrams.
-Since the Hayashi tracks are nearly vertical at this temperature and age, this range in effective temperatures corresponds to a mass range of $\sim 0.2-0.3$ $M_\odot$.
-Our IGRINS analysis is also consistent with a cool component of 3000 K instead of 2750 K, which would increase the effective temperature by $\sim 200$ K.
+When accounting for the visible contributions of both hot and cool components, this wide range of possible observed effective temperatures at any single epoch underscores the difficulty in placing young stars on HR diagrams.
+Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.2-0.3$ $M_\odot$.
+Our IGRINS analysis is also consistent with a cool component of 3000 K instead of 2750 K, which would increase the effective temperature by $\sim 200$ K, and mass by 0.1 $M_\odot$.
 
-The discrepancies in temperature are even larger when spectral type/temperature estimates focus on features in either blue-optical or $H$ or $K$-band spectra, and may explain the severe differences in effective temperature between APOGEE and other (optical) methods \citep{cottaar14}.
+The discrepancies in temperature are even larger when spectral type/temperature estimates focus on features only in either blue-optical or $H$ or $K$-band spectra, and may explain the severe differences in effective temperature between APOGEE and other (optical) methods \citep{cottaar14}.
+
+The INfrared Spectra of Young Nebulous Clusters (IN-SYNC) project \citep{cottaar14} employs APOGEE, which has a $15100-17000$ \AA\ bandwidth.
+The long-wavelength cutoff prevents APOGEE from detecting the most conspicuous cool star emission we detected in IGRINS spectral orders $o = 100, 101, 104$ at $17075-17990 \;\AA$.
+These IGRINS spectral orders that APOGEE misses can be thought of as a ``sweet spot'' where the cool star spectrum is putting out ample flux, has relatively conspicuous features, and is far-enough away from the $K-$band where problems like magnetic field-sensitive lines, and enhanced telluric absorption complicate the spectra.
+Additionally, veiling from mid-IR excess in classical T-Tauri stars will be lessened in $H-$band.
+
 On the other hand, GAIA-ESO spectra \citep{frasca15} cover only a narrow wavelength around H$\alpha$ and would yield an effective temperature of 4000 K.
@@
 The improved characterization of the photospheric emission and radius of LkCa 4 would ideally lead to more accurate estimates of mass and age from pre-main sequence tracks.
-However, our effective temperature and luminosity yield a mass of 0.33 $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
+However, our effective temperature and luminosity yield a mass of $0.2-0.3$ $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
 This age is uncomfortably young and this mass is uncomfortably low.
@@
 The spectral inference method assumed only two temperature components present in the photosphere.
-In reality, starspots are probably described by a range of spot temperatures like umbra, penumbra, and plages on the sun's surface.
+In reality, starspots are probably described by a range of spot temperatures analogous to umbra, penumbra, and plages on the solar surface.
 A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
@@
 Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.
-Most of these orders were flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.
-But some orders just showed mediocre fits where no permutation of hot and cool two-temperature models could describe all of the variance in the spectrum.
+Most of these orders are flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.
+A few orders just show mediocre fits where no permutation of hot and cool two-temperature models could describe all of the variance in the spectrum.
 These $K-$band orders could be examined for a penumbra-like temperature component.
@@
 Cool sunspots are associated with locally heightened magnetic fields on the sun, so synthetic spectral models employing negligible magnetic fields will fail to fit magnetic sensitive features.
-Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.
-The former effect will differentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.
+Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into the photosphere in the line wings than in the line center.
+The former effect will preferentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.
 The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
@@
 % Covey
-The Pleiades serves as a slightly older sample of young stars possessing evidence for large coverage fraction of starspots.
+The Pleiades serves as an older age sample of young stars possessing evidence for large coverage fraction of starspots.
 For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}.
 Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.
-However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
+However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude at the precision of the PTF data, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
 LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation.
@@
 \subsection{Interpretation of the large filling factor of cool starspots}
-We have shown that LkCa 4 exposes between 67\% and 83\% cool photosphere towards our viewing direction in 2015-2016, the most recent season for which there is data.
+We have shown that LkCa 4 exposes between 74\% and 86\% cool photosphere towards our viewing direction in 2015-2016, the most recent season for which there is data.
 In previous seasons, like Fall 2004 (\emph{c.f.} Figures \ref{fig:PhotPhase} and \ref{fig:vband_spot}), the filling factor of cool spots could have exceeded 90\%.
@@
 
-One conceivable interpretation of the 67\% to 83\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere, as described by \citet{donati14}.
+One conceivable interpretation of the 74\% to 86\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere, as described by \citet{donati14}.
 The ambient hot photosphere would then be close to the equator, which would be limb-darkened due to projection effects.
 Such limb darkening would cause a non-linear transformation between our observed fill factor $f_{\Omega}$, and the surface areal coverage fraction of spots.
-So it's conceivable, and probably likely that the reported $f_{\Omega}$ is and overestimate of the surface area actually covered by spots.
+It is conceivable, and probably likely, that the value we report for $f_{\Omega}$ is an overestimate of the surface area actually covered by spots.
 In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
@@
 \subsection{Is \name an extreme source?}
-LkCa 4's large amplitude of cyclical optical variability exceeds all other counterparts from long-term monitoring of WTTSs \citep{grankin08}.
+The large amplitude of cyclical optical variability of LkCa 4 exceeds all other counterparts from long-term monitoring of WTTSs \citep{grankin08}.
 From a statistical perspective, it might not be a surprise that the source with the largest photometric variability also posessess among the largest coverage fraction of cool spots.
@@
 However, the near-IR spectrum is consistent with $\sim M2$, when compared with main sequence dwarf stars \citep{vacca11}.
-\citet{debes13} reconciled this discrepancy by invoking spots, although the spectral contribution from continuum emission was uncertain.
+\citet{debes13} reconciled this discrepancy by invoking spots, although the spectral contribution from accretion and disk continuum emission was uncertain.
 \citet{mcclure13} found that the TW Hya spectrum was well reproduced with near-IR spectra of stars with similar ($\sim$K7) optical spectral type, as long as the comparison spectra were young.
@@
 Still, the characterization and modeling of direct emission from starspots should, in principle, decrease RV jitter attributable to starspots in the near-IR spectra of any spotted star as demands on RV precision increase.
-
-\subsection{Comparison with APOGEE/IN-SYNC}
-The INfrared Spectra of Young Nebulous Clusters (IN-SYNC) project \citep{cottaar14} employs APOGEE, which has a $15100-17000$ \AA\ bandwidth.
-The long-wavelength cutoff prevents APOGEE from detecting the most conspicuous cool star emission we detected in IGRINS spectral orders $o = 100, 101, 104$ at $17075-17990 \;\AA$.
-These spectral orders can be thought of as a ``sweet spot'' where the cool star spectrum is putting out ample flux, but still far-enough away from the $K-$band where problems like magnetic field-sensitive lines, and enhanced telluric absorption complicate the spectra.
-Additionally, veiling from mid-IR excess in classical T-Tauri stars will be lessened in $H-$band.
 
@@
 We are then tasked with computing an estimator, $\hat f(\vt_{\ast})$, for estimating the scale factor $q$ in-between model gridpoints.
-The Right Thing to Do would be to follow \iancze\ by training a Gaussian process on the $f(\{\vt_{\ast}\}^\textrm{grid})$.
-What We Actually Did was linearly interpolate between the model grid-points.
+One robust approach would be to follow \iancze\ by training a Gaussian process on the $f(\{\vt_{\ast}\}^\textrm{grid})$.
+Instead, we simply linearly interpolated between the model grid-points.
 Interpolation can cause pile-up near model grid-points, as noted in \citet{cottaar14}, which motivated the spectral emulation procedure in \iancze.
@@
  \includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
- \caption{IGRINS Orders 94 and $99-119$.
-Note that the $y-$axis is on a logarithmic scale.
+ \caption{IGRINS Orders $122-100$, with panels arranged with the shortest wavelength in the upper left corner with central wavelenth decreasing toward the bottom of the leftmost column, then decreasing through the subsequent columns.
+The $y-$axis is on a logarithmic scale.
 The red line is the cool photosphere while the blue line is the hot photosphere.
@@
  \includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
- \caption{IGRINS Orders $73-93$.  Note that the $y-$axis is on a logarithmic scale.  Cools are the same as Figure \ref{fig:Hband3x7}}
+ \caption{IGRINS Orders $93-73$, with the same layout, ordering, and colors as Figure \ref{fig:Hband3x7}. The $y-$axis is on a logarithmic scale.}
  \label{fig:Kband3x7}
@@
 MG-S and GJH are supported by general grant 11473005 awarded by the National Science Foundation of China.
-The ESPaDOnS observations are supported by the contribution to the MATYSSE Large Project on CFHT obtained through the Telescope Access Program (TAP), which has been funded by the ``the Strategic Priority Research Program---The Emergence of Cosmological Structures'' of the Chinese Academy of Sciences (Grant No.11 XDB09000000) and the Special Fund for Astronomy from the Ministry of Finance.
+The ESPaDOnS observations are supported by the contribution to the MaTYSSE Large Project on CFHT obtained through the Telescope Access Program (TAP), which has been funded by the ``the Strategic Priority Research Program---The Emergence of Cosmological Structures'' of the Chinese Academy of Sciences (Grant No.11 XDB09000000) and the Special Fund for Astronomy from the Ministry of Finance.
 TW-SH is supported by the DOE Computational Science Graduate Fellowship, grant number DE-FG02-97ER25308.

### 2016-09-20 document/ms.tex
Relates to Issue #47-- feedback from GJH, new h2o jump feature figure added, some rearranging.

@@
 Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin Covey,\altaffilmark{5} J.F.
-Donati,\altaffilmark{6} Sylvia Alencar,\altaffilmark{7}, Gaitee Hussein,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
+Donati,\altaffilmark{6} Sylvia Alencar,\altaffilmark{7} Gaitee Hussein,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
 
@@
 \input{tables/tbl_estV_atObsEpoch.tex}
-
-\subsection{Absolute lower limit of starspot filling factor}
-
-A lower limit to the starspot filling factor can be set by the size of a black spot that can induce such large $\Delta V$.
-
-Consider the following extremely conservative assumptions:  \begin{enumerate}
-  \item The starspot emits \emph{zero flux}.  This statement is equivalent to the starspot being at \emph{absolute zero}.
-  \item The stellar disk shows no starspots at maximum brightness.
-  \item The starspot transits the center of the stellar disk.
-\end{enumerate}
-
-If \emph{any} these assumptions is relaxed, the minimum fill factor \emph{increases}.
-
-For LkCa 4 in 2015 the $\Delta V\sim 0.5$ mag amplitude corresponds to an absolute minimum fill factor $f>0.37$.
-At least 37\% of the stellar is covered in starspots at minimum light.
-In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
-
-\subsection{Absolute upper limit of starspot temperature}
-
-Consider relaxing assumption 1 from above to better match reality: a starspot is not at absolute zero temperature, it has a finite temperature and therefore emits a finite amount of radiation.
-Increasing the temperature a little means that the starspot size has to increase to cause the same flux difference.
-The starspot cannot occupy more than 100\% of the projected stellar hemisphere, so there is an upper limit for the temperature of the starspot that yields a given $\Delta V$.
-The starspot temperature upper limit for $\Delta V=0.5$ is 3650 K.
-In the 2004 season, the starspot temperature upper limit was 3410 K.
-
-In reality, the star will have some patches of starspots that always face toward the observer, like polar spots, bands of spots, multiple finitie-sized patches of starspots, or homogenuously distributed small spots.
-Dark spots on extreme latitudes on inclined stars might only pass over the limb of the stellar disk, reducing the diminution $V-$band flux for a given projected surface area.
-All of these effect mean that real starspot filling factors are likely to be larger than the filling factor lower limit, and cooler than the temperature upper limit.
 
@@
  \centering
-  \includegraphics[width=0.45\textwidth]{figures/v_v-r_Grankin} 
  \begin{tabular}{ll}
@@
 \caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions.
-\emph{Top}: Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.
-The purple line represents a two component photometric model  described by \citet{grankin08}, comprising a photospheric temperature of 4040K (for K7), and a temperature of spotted area of 3030K (for an M5).
-In this model, the spot coverage of the observed hemisphere varies from $\sim36\%$ at maximum brightness, and $\sim82\%$ at minimum brightness.
-\emph{Bottom:}  The model is constructed instead by converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{pecaut13} (purple lines).}
+The model is constructed instead by converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{pecaut13} (purple lines).}
 \label{fig:colors}
@@
 The $V-R_J$ color excess leads to $A_V=0.48$ mag, which should be less affected by gravity (based on $V-I_C$ colors in Pecaut et al.) but is likely to be overestimated because the cool component contributes to the $R_J$-band emission, as seen in Fig.~\ref{fig:colors}.
-In the near-IR, the estimated $V=12.61$ mag at the time of the 2MASS observations leads to a template (main sequence) color 
+In the near-IR, the estimated $V=12.61$ mag at the time of the 2MASS observations leads to a spot-weighted template (main sequence) color 
 $J-K_s=0.87$ mag, with a range of $\sim 0.05$ mag for acceptable solutions with other 
@@
 The spectrum of LkCa 4 is well reproduced by a cool component of $2750$ K covering 80\% of the surface and a $4100$ K component covering 20\% of the surface.
-Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=0.17$, adopting $A_V=0.3$ mag and a distance of 131 pc for the parallax distance of the nearest Taurus member \citep{torres12}.
+Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=0.17$, adopting $A_V=0.3$ mag and a distance of $131 \pm 2$ pc$^x$ based on the range of parallaxes of nearby Taurus members measured by \citet{torres12}\footnote{This distance is consistent with the Gaia distance of $130 \pm4$ pc measured to the nearby Taurus members V410 Tau, V773 Tau, and BP Tau \citep{gaia2016dr}.}.
 The effective temperature of these two components is 3330 K, as calculated from the average surface flux at the median $V$ band magnitude.
@@
 
-\subsection{Addressing limitations of assumptions in the spectral inference methodology}
+\subsection{Limitations of assumptions in the spectral inference methodology}
 
@@
 
-Finally, uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
+Uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
 Erroneous bulk opacities could be responsible for some of the scatter of fill factor distributions seen across different spectral orders, as in Figures \ref{fig:TwoTempResults} and \ref{fig:specPostageStamp}.
 The large number of spectral orders over which the fill factors are averaged offers resilience against these anomalies.
+
+\begin{figure*}
+ \centering
+\includegraphics[width=0.45\textwidth]{figures/v_v-r_Grankin} 
+\caption{Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.
+The purple line represents a two component photometric model  described by \citet{grankin08}, comprising a photospheric temperature of 4040K (for K7), and a temperature of spotted area of 3030K (for an M5).
+In this model, the spot coverage of the observed hemisphere varies from $\sim36\%$ at maximum brightness, and $\sim82\%$ at minimum brightness.}
+ \label{fig:grankin_vr}
+\end{figure*}
+
+Analyses of optical emission also suggest that a two-temperature model may be an oversimplification.
+Figure \ref{fig:grankin_vr} shows that the $V-R$ colors from \citet{grankin} are better reproduced if the cooler component is $\sim 3050$ K, thereby contributing more flux at optical wavelengths.
+The ZDI imaging of \citet{donati14} also indicate a complex structure of spots that are hotter than what is interpreted here as the ambient photosphere, while also reproducing the optical photometry.
+Despite the need for more complicated emission structures to simultaneously reproduce all observations, the broadband SED, spectral shape, and rotational modulation of spectral indices are reasonably well fit with the two components presented here.
+Moreover, the high and low-resolution near-IR spectra require a cool (2700--3000 K) component while the global photometry requires a large covering fraction for this cool component.
+
+The need for the cool component to have a large covering fraction and $<3000$ K is also demonstrated by the size of the H$_2$O band absorption between the $J$ and $H$ bands (see Figure~\ref{fig:h2ojump}).
+Assuming that the hotter component is 4100 K, the H$_2$O opacity is only sufficient if $T_{spot}<3000$ K, with a high spot coverage.
+
+\begin{figure*}
+ \centering
+ %\includegraphics[width=0.65\textwidth]{}
+ \includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.65\textwidth]{figures/jbandjump}
+ \caption{The constraint on the size and temperature of the cool spot from the H$_2$O absorption band depth between $J$ and $H$-bands.
+The contours show the flux ratio between 1.30 and 1.34 $\mu$m (shaded yellow region in inset plot), as produced by the Phoenix models.
+The solid and hatched purple lines show the best fit and range of acceptable contours from the APO/TripleSpec spectrum, which was obtained when the cool spot fraction was $\sim 84$\%.
+The range of acceptable contour is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption.
+}
+ \label{fig:h2ojump}
+\end{figure*}
+
+\subsection{Absolute lower limit of starspot filling factor}
+
+A lower limit to the starspot filling factor can be set by the size of a black spot that can induce such large $\Delta V$.
+
+Consider the following extremely conservative assumptions:  \begin{enumerate}
+  \item The starspot emits \emph{zero flux}.  This statement is equivalent to the starspot being at \emph{absolute zero}.
+  \item The stellar disk shows no starspots at maximum brightness.
+  \item The starspot transits the center of the stellar disk.
+\end{enumerate}
+
+If \emph{any} these assumptions is relaxed, the minimum fill factor \emph{increases}.
+
+For LkCa 4 in 2015 the $\Delta V\sim 0.5$ mag amplitude corresponds to an absolute minimum fill factor $f>0.37$.
+At least 37\% of the stellar is covered in starspots at minimum light.
+In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
+
+%\subsection{Absolute upper limit of starspot temperature}
+
+%Consider relaxing assumption 1 from above to better match reality: a starspot is not at absolute zero temperature, it has a finite temperature and therefore emits a finite amount of radiation.
+Increasing the temperature a little means that the starspot size has to increase to cause the same flux difference.
+The starspot cannot occupy more than 100\% of the projected stellar hemisphere, so there is an upper limit for the temperature of the starspot that yields a given $\Delta V$.
+The starspot temperature upper limit for $\Delta V=0.5$ is 3650 K.
+In the 2004 season, the starspot temperature upper limit was 3410 K.
+
+%In reality, the star will have some patches of starspots that always face toward the observer, like polar spots, bands of spots, multiple finitie-sized patches of starspots, or homogenuously distributed small spots.
+Dark spots on extreme latitudes on inclined stars might only pass over the limb of the stellar disk, reducing the diminution $V-$band flux for a given projected surface area.
+All of these effect mean that real starspot filling factors are likely to be larger than the filling factor lower limit, and cooler than the temperature upper limit.
 
@@
 % Fang
-\textbf{Insert Fang info here.}
+%\textbf{Insert Fang info here.}
 
@@
 
-{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}
+{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}, \facility{Gaia}
 

### 2016-09-20 document/ms.tex
Relates to Issue #47: re-arrange the figures

@@
 
-An archive of 1216 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
-Published data targeting \name is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
-ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002$-$2004.
-Integral-OMC obtained 138 $V-$band measurements from 2006$-$2008 \citep{garzon12}.
-The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.
-Unpublished data from the ASAS-SN survey \citep{shappee14} were obtained from 2012 January -- 2016 March in 186 visits.
-Finally, recent photometry from the ongoing Crimean Astrophysical Observatory (CrAO) ROTOR project \citep{grankin08} is presented here for the first time.
-The CrAO data includes 43 $BVR$ visits from August 2015 - March 2016.
-Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1985-2016.
-HJD, BJD, and JD are simply referred to as JD, which is accurate to the precision of available data.
-
 \begin{figure*}
@@
 \end{figure*}
-
-Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 22 observing seasons and phase-folded by the period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
-The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
-The estimated $BVR$ magnitudes at the time of the spectral observations are determined from regularized multiterm fits \citep[\emph{i.e.} Fourier series truncated to the first $\sim 4$ components]{vanderplas15a} shown as the solid blue lines in Figure \ref{fig:PhotPhase}.
-Table \ref{tbl_estimated_V} lists the estimated $BVR$ photometry and the observing epoch for data from IGRINS, ESPaDOnS, 2MASS \citep{skrutskie06}, DoubleSpec, and TripleSpec.
 
@@
 
+An archive of 1216 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
+Published data targeting \name is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
+ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002$-$2004.
+Integral-OMC obtained 138 $V-$band measurements from 2006$-$2008 \citep{garzon12}.
+The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.
+Unpublished data from the ASAS-SN survey \citep{shappee14} were obtained from 2012 January -- 2016 March in 186 visits.
+Finally, recent photometry from the ongoing Crimean Astrophysical Observatory (CrAO) ROTOR project \citep{grankin08} is presented here for the first time.
+The CrAO data includes 43 $BVR$ visits from August 2015 - March 2016.
+Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1985-2016.
+HJD, BJD, and JD are simply referred to as JD, which is accurate to the precision of available data.
+
+Figure \ref{fig:PhotPhase} shows all available $V-$band data grouped by the 22 observing seasons and phase-folded by the period $P=3.375$ days obtained from multiterm Lomb-Scargle periodograms \citep{ivezic14}.
+The general appearance of the phase-folded lightcurves does not change with perturbations to the period on the scale of 0.003 days.
+The estimated $BVR$ magnitudes at the time of the spectral observations are determined from regularized multiterm fits \citep[\emph{i.e.} Fourier series truncated to the first $\sim 4$ components]{vanderplas15a} shown as the solid blue lines in Figure \ref{fig:PhotPhase}.
+Table \ref{tbl_estimated_V} lists the estimated $BVR$ photometry and the observing epoch for data from IGRINS, ESPaDOnS, 2MASS \citep{skrutskie06}, DoubleSpec, and TripleSpec.
+
 \input{tables/tbl_estV_atObsEpoch.tex}
@@
 \section{FITS TO HIGH RESOLUTION SPECTRA}\label{sec:Starfish}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.48\textwidth]{figures/single_Teff_v_order}
+ \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
+The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.
+The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.
+The cluster of $H-$band orders at 1.7 $\mu$m correspond to a local peak in flux density of cool starspots.}
+ \label{fig:SingleTeffvsOrder}
+\end{figure}
 
@@
 \citet[hereafter \iancze]{czekala15} developed a modular framework\footnote{The open source codebase and its full revision history is available at \url{https://github.com/iancze/Starfish}.
-The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}} to infer stellar properties from high resolution spectra.
+The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}.
+} to infer stellar properties from high resolution spectra.
 The \iancze\ technique forward models observed spectra with synthetic spectra from pre-computed model grids.
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=0.48\textwidth]{figures/single_Teff_v_order}
- \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
-The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.
-The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.
-The cluster of $H-$band orders at 1.7 $\mu$m correspond to a local peak in flux density of cool starspots.}
- \label{fig:SingleTeffvsOrder}
-\end{figure}
-
 \subsection{Single temperature fitting to the IGRINS spectrum}\label{sec:IGR_starfish}
@@
 
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_04} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_01} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_05} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_06} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_02} 
+ \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_03} 
+ \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).
+The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
+The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\Omega}$ for individual spectral orders.}
+ \label{fig:specPostageStamp}
+\end{figure*}
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
+ \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\Omega}$ (yellow shade).
+The stellar parameters are derived independently in each spectral order.
+Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.
+The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.
+$K-$band orders show lower estimates for the ambient photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
+ \label{fig:TwoTempResults}
+\end{figure*}
+
 Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.
@@
 In other words, most of the variance in a spectrum is attributable to temperature, assuming near-solar metallicity.
-Starspots imbue dearths of flux in the line profiles of optical spectra, but these are secondary to the mere presence of temperature-sensitive lines, despite carrying useful information about the longitudinal distribution of the spots.} spectral features are broadly consistent with a emission from a single temperature component.
+Starspots imbue dearths of flux in the line profiles of optical spectra, but these are secondary to the mere presence of temperature-sensitive lines.} spectral features are broadly consistent with a emission from a single temperature component.
 A single ESPaDOnS order surrounding the TiO bands shows an exceptionally low estimated $\teff$.
@@
 The remaining orders are rerelatively devoid of spectral line outliers and include the most information rich portion of the spectrum.
-Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\Omega}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the reliable order subset shown in bold.
-The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.
-
-\begin{figure*}
- \centering
- \includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
- \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\Omega}$ (yellow shade).
-The stellar parameters are derived independently in each spectral order.
-Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.
-The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.
-$K-$band orders show lower estimates for the ambient photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
- \label{fig:TwoTempResults}
-\end{figure*}
 
@@
 
-\begin{figure*}
- \centering
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_04} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_01} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_05} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_06} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_02} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_03} 
- \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).
-The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
-The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\Omega}$ for individual spectral orders.}
- \label{fig:specPostageStamp}
-\end{figure*}
+Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\Omega}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the reliable order subset shown in bold.
+The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.
 
@@
 
+\begin{figure*}
+ \centering
+ \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{figures/lkca4_tio_forpaper}
+ \caption{Variability in TiO bands measured with ESPaDOnS.
+The $V-$band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
+The bottom left panel shows a correlation between $V-$band magnitude and the TiO-7140 index, while the bottom right shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
+ \label{fig:tiovar}
+\end{figure*}
+
 The depths of TiO and other molecular bands are common diagnostics of spectral type and therefore temperature in optical spectra \citep[e.g.][]{kirkpatrick91}.
@@
 When the hotter component has a larger filling fraction, the TiO bands are veiled by the hotter component and are therefore not as deep.
-
-\begin{figure*}
- \centering
- \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{figures/lkca4_tio_forpaper}
- \caption{Variability in TiO bands measured with ESPaDOnS.
-The $V-$band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
-The bottom left panel shows a correlation between $V-$band magnitude and the TiO-7140 index, while the bottom right shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
- \label{fig:tiovar}
-\end{figure*}
 
@@
 
-Analyses of optical emission also suggest that a two-temperature model may be an oversimplification.
-Figure \ref{fig:grankin_vr} shows that the $V-R$ colors from \citet{grankin} are better reproduced if the cooler component is $\sim 3050$ K, thereby contributing more flux at optical wavelengths.
-The ZDI imaging of \citet{donati14} also indicate a complex structure of spots that are hotter than what is interpreted here as the ambient photosphere, while also reproducing the optical photometry.
-Despite the need for more complicated emission structures to simultaneously reproduce all observations, the broadband SED, spectral shape, and rotational modulation of spectral indices are reasonably well fit with the two components presented here.
-Moreover, the high and low-resolution near-IR spectra require a cool (2700--3000 K) component while the global photometry requires a large covering fraction for this cool component.
-
-The need for the cool component to have a large covering fraction and $<3000$ K is also demonstrated by the size of the H$_2$O band absorption between the $J$ and $H$ bands (see Figure~\ref{fig:h2ojump}).
-Assuming that the hotter component is 4100 K, the H$_2$O opacity is only sufficient if $T_{spot}<3000$ K, with a high spot coverage.
-
 \begin{figure*}
@@
 \end{figure*}
+
+Analyses of optical emission also suggest that a two-temperature model may be an oversimplification.
+Figure \ref{fig:grankin_vr} shows that the $V-R$ colors from \citet{grankin} are better reproduced if the cooler component is $\sim 3050$ K, thereby contributing more flux at optical wavelengths.
+The ZDI imaging of \citet{donati14} also indicate a complex structure of spots that are hotter than what is interpreted here as the ambient photosphere, while also reproducing the optical photometry.
+Despite the need for more complicated emission structures to simultaneously reproduce all observations, the broadband SED, spectral shape, and rotational modulation of spectral indices are reasonably well fit with the two components presented here.
+Moreover, the high and low-resolution near-IR spectra require a cool (2700--3000 K) component while the global photometry requires a large covering fraction for this cool component.
+
+The need for the cool component to have a large covering fraction and $<3000$ K is also demonstrated by the size of the H$_2$O band absorption between the $J$ and $H$ bands (see Figure~\ref{fig:h2ojump}).
+Assuming that the hotter component is 4100 K, the H$_2$O opacity is only sufficient if $T_{spot}<3000$ K, with a high spot coverage.
 
@@
 In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
-
-%\subsection{Absolute upper limit of starspot temperature}
-
-%Consider relaxing assumption 1 from above to better match reality: a starspot is not at absolute zero temperature, it has a finite temperature and therefore emits a finite amount of radiation.
-Increasing the temperature a little means that the starspot size has to increase to cause the same flux difference.
-The starspot cannot occupy more than 100\% of the projected stellar hemisphere, so there is an upper limit for the temperature of the starspot that yields a given $\Delta V$.
-The starspot temperature upper limit for $\Delta V=0.5$ is 3650 K.
-In the 2004 season, the starspot temperature upper limit was 3410 K.
-
-%In reality, the star will have some patches of starspots that always face toward the observer, like polar spots, bands of spots, multiple finitie-sized patches of starspots, or homogenuously distributed small spots.
-Dark spots on extreme latitudes on inclined stars might only pass over the limb of the stellar disk, reducing the diminution $V-$band flux for a given projected surface area.
-All of these effect mean that real starspot filling factors are likely to be larger than the filling factor lower limit, and cooler than the temperature upper limit.
 
@@
 
-\section{Methodological details}
+\section{Further methodological details}
 \label{methods-details}
 
-\subsection{Addressing absolute flux calibration}
-If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.
+If the synthetic stellar models used in \texttt{Starfish} are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.
 However \iancze\ employ \emph{standardized} $\flam$ when constructing the forward model $\vM$:
-
 \begin{eqnarray} \label{eqn:normalization}
@@
 
-\section{Examples of full spectrum fitting}
+\section{Further examples of full spectrum fitting}
 
@@
 
-Table \ref{tbl_history} lists measurements of \name from previous studies.
+Table \ref{tbl_history} lists measurements of \name from previous studies, compared to this work.
 \input{tables/tbl_history.tex}
@@
 \acknowledgements
+
+Portions of the data, Python code, Jupyter notebooks, Starfish configuration files, MCMC samples, and revision history of this manuscript are available on the project's GitHub repository at \url{https://github.com/BrownDwarf/welter}.
 

### 2016-09-20 document/ms.tex
Version 0.7-- the last version I am sending to collaborators before submission.

@@
 Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin Covey,\altaffilmark{5} J.F.
-Donati,\altaffilmark{6} Sylvia Alencar,\altaffilmark{7} Gaitee Hussein,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
+Donati,\altaffilmark{6} Sylvia Alencar,\altaffilmark{7} Gaitee Hussein,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose,\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
 
@@
 
-We selected a subset of 32 of the 54 available IGRINS spectral orders\footnote{The finite computational cost limited running all the spectral orders.} with the low telluric absorption artifacts.
+We selected a subset of 32 of the 54 available IGRINS spectral orders\footnote{The prohibitive computational cost limited us from running all the spectral orders.} with low telluric absorption artifacts.
 We performed full-spectrum fitting, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $o$.
@@
 In other words, most of the variance in a spectrum is attributable to temperature, assuming near-solar metallicity.
-Starspots imbue dearths of flux in the line profiles of optical spectra, but these are secondary to the mere presence of temperature-sensitive lines.} spectral features are broadly consistent with a emission from a single temperature component.
+Starspots imbue dearths of flux in the line profiles of optical spectra, but these are secondary to the mere presence of temperature-sensitive lines.} spectral features are broadly consistent with emission from a single temperature component.
 A single ESPaDOnS order surrounding the TiO bands shows an exceptionally low estimated $\teff$.
@@
 
-If \emph{any} these assumptions is relaxed, the minimum fill factor \emph{increases}.
+For LkCa 4 in 2015 the $\Delta V\sim 0.5$ mag amplitude corresponds to an absolute minimum fill factor $f>0.37$.
+At least 37\% of the stellar disk is covered in starspots at minimum light.
+In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
 
-For LkCa 4 in 2015 the $\Delta V\sim 0.5$ mag amplitude corresponds to an absolute minimum fill factor $f>0.37$.
-At least 37\% of the stellar is covered in starspots at minimum light.
-In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
+If \emph{any} of these assumptions is relaxed, the minimum fill factor \emph{increases}.
 

### 2016-09-20 document/ms.tex
correct coauthor names

@@
 Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin Covey,\altaffilmark{5} J.F.
-Donati,\altaffilmark{6} Sylvia Alencar,\altaffilmark{7} Gaitee Hussein,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose,\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
+Donati,\altaffilmark{6} Silvia Alencar,\altaffilmark{7} Gaitee Hussain,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose,\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
 

### 2016-09-23 document/ms.tex
update to abstract from Garrett

@@
 \begin{abstract}
-Ages and masses of young stars can be estimated by comparing observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks.
+%Ages and masses of young stars can be estimated by comparing observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks.
 Nonstandard physics like magnetic fields and starspots confound interpretations of pre-main sequence HR diagrams and their age and mass estimates.
-We characterize the fundamental properties of the spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for signatures of the emergent radiation originating from the starspot or starspot groups.
+%We characterize the fundamental properties of the spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for signatures of the emergent radiation originating from the starspot or starspot groups.
 The spectral and photometric properties of this radiation can be used to constrain both the starspot filling factor and the starspot temperature.
-A generalization of line depth ratio analysis is developed and applied to a high-resolution near-IR IGRINS spectrum.
+%A generalization of line depth ratio analysis is developed and applied to a high-resolution near-IR IGRINS spectrum.
 The IGRINS spectrum is forward modeled with pre-computed \PHOENIX\ synthetic spectra using the open source spectral inference framework \texttt{Starfish} extended to include a two component mixture model comprised of ambient photosphere and starspot emission.
-Spectral features attributable to both ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2700-3000$ K are detected in the IGRINS spectrum.
+%Spectral features attributable to both ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2700-3000$ K are detected in the IGRINS spectrum.
 In some spectral regions, the starspot emission acts merely as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
 The filling factor of of starspots at minimum light $\Delta V = 0.5$must be $>37\%$, and is likely much larger based on geometry and temperature considerations.
-The IGRINS spectra yield consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f\sim80\%$ starspots at the epoch of spectrum acquisition.
-The interpretation of the $\sim20\%$ ambient photosphere as a persistent ``hot spot'' is also possible.
+The IGRINS spectra yield consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f\sim80$\% starspots at the epoch of spectrum acquisition.
+The interpretation of the $\sim20$\% ambient photosphere as a persistent ``hot spot'' is also possible.
 The spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy show broad support for the starspot parameter estimates derived separately from IGRINS, strengthening the case for a large albeit secularly changing starspot filling factor and temperature contrast through time.
-The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
+%The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
 Emission from longitudinally symmetric starspots has likely caused the misplacement of spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
+
+Ages and masses of young stars can be estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process.
+In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.
+To do this, we introduce new methodology for constraining both the starspot filling factor and the typical spot temperature, which involves fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
+We detect spectral features attributable to both an ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2700-3000$ K, and derive consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f\sim80$\% starspots at the epoch of spectrum acquisition.
+These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively provide broad support for the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time.
+A persistent hotspot covering $\sim20$\% of the surface is a plausible alternative explanation.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous measurements, a bias likely afflicting most young, heavily spotted stars, and which may contribute to observed age spreads in open clusters.
+We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
+
 \end{abstract}

### 2016-09-25 document/ms.tex
Version on Overleaf that Greg edited on the plane to LAX.

@@
 Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin Covey,\altaffilmark{5} J.F.
-Donati,\altaffilmark{6} Silvia Alencar,\altaffilmark{7} Gaitee Hussain,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose,\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
+Donati,\altaffilmark{6,7} Silvia Alencar,\altaffilmark{8} Gaitee Hussain,\altaffilmark{9} Benjamin J.
+Shappee,\altaffilmark{10,11} Gregory Mace,\altaffilmark{12} Jae-Joon Lee\altaffilmark{13} T.~W.-S.~Holoien,\altaffilmark{14,15} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{16}}
 
 \altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
-\altaffiltext{2}{Stanford University, Palo Alto, CA}
+\altaffiltext{2}{KIPAC, Physics and Astronomy, Stanford University, Stanford, CA}
 \altaffiltext{3}{Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center, Nashville, TN, 37235, USA}
@@
 \altaffiltext{5}{TBD--Covey}
-\altaffiltext{6}{TBD--Donati}
-\altaffiltext{7}{TBD--Alencar}
-\altaffiltext{8}{TBD--Hussein}
-\altaffiltext{9}{TBD--Shappee}
-\altaffiltext{10}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway St, Austin, TX, USA}
-\altaffiltext{11}{TBD--Lee}
-\altaffiltext{12}{Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
-\altaffiltext{13}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
-\altaffiltext{15}{TBD--Liu}
+\altaffiltext{6}{CNRS, IRAP / UMR 5277, Toulouse, 14 avenue E. Belin, F– 31400 France}
+\altaffiltext{7}{Universit\`e de Toulouse, UPS-OMP, IRAP, 14 avenue E. Belin, Toulouse, F–31400 France}
+\altaffiltext{8}{TBD--Alencar}
+\altaffiltext{9}{TBD--Hussain ESO and IRAP}
+\altaffiltext{10}{Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}
+\altaffiltext{11}{Hubble and Carnegie-Princeton Fellow}
+\altaffiltext{12}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway St, Austin, TX, USA}
+\altaffiltext{13}{TBD--Lee}
+\altaffiltext{14}{Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
+\altaffiltext{15}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
+\altaffiltext{16}{Institute of Astronomy and Astrophysics, Academia Sinica (ASIAA), P.O. Box 23-141, Taipei 10641, Taiwan}
 
@@
 In some spectral regions, the starspot emission acts merely as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
-The filling factor of of starspots at minimum light $\Delta V = 0.5$must be $>37\%$, and is likely much larger based on geometry and temperature considerations.
+The filling factor of starspots at minimum light $\Delta V = 0.5$must be $>37\%$, and is likely much larger based on geometry and temperature considerations.
 The IGRINS spectra yield consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f\sim80$\% starspots at the epoch of spectrum acquisition.
@@
 TW-SH is supported by the DOE Computational Science Graduate Fellowship, grant number DE-FG02-97ER25308.
+We thank LCOGT and its staff for their continued support of ASAS-SN.
+ASAS-SN is supported by NSF grant AST-1515927.
+Development of ASAS-SN has been supported by NSF grant AST-0908816, the Center for Cosmology and AstroParticle Physics at the Ohio State University, the Mt.
+Cuba Astronomical Foundation, and by George Skestos.
+
+BJS is supported by NASA through Hubble Fellowship grant HST-HF-51348.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
 

### 2016-09-26 document/ms.tex
Update all affiliations, except Grankin--emailed him for update.  Correct some errant citations and formatting, fix a table comment placeholder

--- 2016-09-23 document/ms.tex
@@
 Gully-Santiago,\altaffilmark{1} Gregory J.
-Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin Covey,\altaffilmark{5} J.F.
-Donati,\altaffilmark{6} Silvia Alencar,\altaffilmark{7} Gaitee Hussain,\altaffilmark{8} Ben Shappee,\altaffilmark{9} Greg Mace,\altaffilmark{10} Jae-Joon Lee\altaffilmark{11} T.~W.-S.~Holoien,\altaffilmark{12,13} Jessy Jose,\altaffilmark{1} Jimmy Liu\altaffilmark{15}}
+Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin R.
+Covey,\altaffilmark{5} J.F.
+Donati,\altaffilmark{6,7} Silvia H.
+P.
+Alencar,\altaffilmark{8} Gaitee A.J.
+Hussain,\altaffilmark{9,10} Benjamin J.
+Shappee,\altaffilmark{11,12} Gregory N.
+Mace,\altaffilmark{13} Jae-Joon Lee\altaffilmark{14} T.~W.-S.~Holoien,\altaffilmark{15,16} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{17,1}}
 
-\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Beijing, China}
-\altaffiltext{2}{Stanford University, Palo Alto, CA}
+\altaffiltext{1}{Kavli Institute for Astronomy and Astrophysics, Peking University, Yi He Yuan Lu 5, Haidian Qu, 100871 Beijing, People's Republic of China}
+\altaffiltext{2}{KIPAC, Physics and Astronomy, Stanford University, Stanford, CA}
 \altaffiltext{3}{Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center, Nashville, TN, 37235, USA}
 \altaffiltext{4}{TBD--Grankin}
-\altaffiltext{5}{TBD--Covey}
-\altaffiltext{6}{TBD--Donati}
-\altaffiltext{7}{TBD--Alencar}
-\altaffiltext{8}{TBD--Hussein}
-\altaffiltext{9}{TBD--Shappee}
-\altaffiltext{10}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway St, Austin, TX, USA}
-\altaffiltext{11}{TBD--Lee}
-\altaffiltext{12}{Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
-\altaffiltext{13}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
-\altaffiltext{15}{TBD--Liu}
+\altaffiltext{5}{Department of Physics \& Astronomy, Western Washington University, Bellingham WA 98225-9164, USA}
+\altaffiltext{6}{CNRS, IRAP / UMR 5277, Toulouse, 14 avenue E. Belin, F– 31400 France}
+\altaffiltext{7}{Université de Toulouse, UPS-OMP, IRAP, 14 avenue E. Belin, Toulouse, F–31400 France}
+\altaffiltext{8}{Departamento de F\`{\i}sica -- ICEx -- UFMG, Av. Ant\^onio Carlos, 6627, 30270-901 Belo Horizonte, MG, Brazil}
+\altaffiltext{9}{European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching bei M\"unchen, Germany}
+\altaffiltext{10}{Institut de Recherche en Astrophysique et Plan\'etologie, Universit\'e de Toulouse, UPS-OMP, F-31400 Toulouse, France}
+\altaffiltext{11}{Carnegie Observatories, 813 Santa Barbara Street,
+  Pasadena, CA 91101, USA}
+\altaffiltext{12}{Hubble, Carnegie-Princeton Fellow}
+\altaffiltext{13}{Department of Astronomy, The University of Texas at Austin, 2515 Speedway St, Austin, TX, USA}
+\altaffiltext{14}{Korea Astronomy and Space Science Institute, 776 Daedeok-daero, Yuseong-gu, Daejeon 305-348, Korea.}
+\altaffiltext{15}{Department of Astronomy, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
+\altaffiltext{16}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
+\altaffiltext{17}{Institute of Astronomy and Astrophysics, Academia Sinica
+(ASIAA), P.O. Box 23-141, Taipei 10641, Taiwan}
 
@@
 
-Ages and masses of young stars can be estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process.
+Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process.
 In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.
-To do this, we introduce new methodology for constraining both the starspot filling factor and the typical spot temperature, which involves fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
-We detect spectral features attributable to both an ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2700-3000$ K, and derive consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f\sim80$\% starspots at the epoch of spectrum acquisition.
-These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively provide broad support for the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time.
+We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
+Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which have
+%a consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with 
+a best fit filling factor of $f\sim80$\% starspots at the time of the observation.
+These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time.
 A persistent hotspot covering $\sim20$\% of the surface is a plausible alternative explanation.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous measurements, a bias likely afflicting most young, heavily spotted stars, and which may contribute to observed age spreads in open clusters.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous measurements, a bias likely afflicting most young, heavily spotted stars, and which likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
 We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
@@
 In models, \citet{hartmann97} and \citet{baraffe09} describe how variable accretion histories change the stellar contraction and hence luminosities at early times.
-Contraction rates also depend on the prescription for convection, which may vary with mass.
+Contraction rates also depend on the interior stellar structure and convective efficiency.
 
@@
 Convection at these young ages generates strong magnetic fields, as measured by Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}.
-Evolutionary models are just now starting to implement new prescriptions for convection with magnetic fields (\citet{somers15}, \citet{feiden16}; see also \citet{baraffe15} for an updated treatment of convection without introducing magnetic fields).
-Stellar evolution models including the effect of starspots can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with standard mass estimates being biased towards lower masses \citep{somers15,feiden16}.
-Starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
-For example, the effective temperatures for 3493 young stars measured using the APOGEE spectrograph \citep[$1.5-1.70 \;\mu$m at $R=22,500$][]{wilson10} exhibit systematic offsets from prior measurements predominantly that were predominantly made at optical wavelengths.
-Typical offsets range from $-400-400$ K, with a systematic dependence on $\teff$, with some offsets as large as 1000 K \citep{cottaar14}.
+Evolutionary models are just now starting to implement prescriptions for how spots and magnetic fields affect the interior structure \citep{jackson14a,somers15,feiden16}.
+Stellar evolution models that includes these effects can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with standard mass estimates being biased towards lower masses.
+Observationally, starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
+For example, the effective temperatures for 3493 young stars measured using the APOGEE spectrograph \citep[$1.5-1.70 \;\mu$m at $R=22,500$][]{wilson10} are offset from and usually cooler than prior measurements made at optical wavelengths \citep{cottaar14}.
+Similarly, near-IR spectral types of young stars have sometimes been evaluated as later than optical spectral types \citep{bouvier92,vacca11}.
 
@@
 Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups, but the number of such transiting systems and demands of high photometric precision limit wider application.
-Zeeman Doppler Imaging \citep[ZDI]{donati14} suffers from similar longitudinal asymmetry limitations as photometry, but can yield some information on the latitudinal distribution of starspots in reconstructed brightness maps based on models for spectro-polarimetric line shapes.
+Zeeman Doppler Imaging \citep[ZDI]{donati14} produces the latitudinal and longitudinal distribution of starspots in reconstructed brightness maps based on models for spectro-polarimetric line shapes, but would be unable to identify uniform distributions of small spots.
 All of these techniques would tend to underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots, or stars with an isotropic distribution of small starspots.
@@
 Spectroscopic strategies have the power to measure both the starspot areal coverage and temperature in any geometric configuration.
-At low resolution, SED modeling \citep{wolk96} has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).
-At high resolution, line depth ratio analysis has been demonstrated mostly on evolved stars in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.
-Past spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
+For weak-lined T Tauri stars (WTTSs), SED modeling \citep{wolk96} indicated the presence of cool spots, while \citet{grankin98} and \citet{venuti15} estimated spot temperature and coverage from rotational modulation of optical colors.
+The TiO bands in optical spectra have been used to measure spots on WTTSs \citep{petrov94}, stars in the Pleiades \citep{fang2016}, and evolved stars \citep[e.g.][]{neff95,oneal01,oneal04}.
+Recent spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
 
-The WTTS LkCa 4 \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any veiling \citep[\emph{e.g.}][]{hartigan95} or mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15}, and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
+The WTTS LkCa 4 \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15} and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
 LkCa 4 has no evidence for a close companion from both direct imaging searches\citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}} and RV searches \citep{nguyen12,donati14}.
@@
 There is also evidence for a hot spot in the reconstructed ZDI map.
-Still, unanswered questions about the large disagreement in LkCa 4's effective temperature remain, with 4100 K measured from holistic analysis of ESPaDOnS spectra yielding $\teff=4100$K \citep{donati14}, and analysis of the TiO bands of the same spectra yielding $\teff=3600$ K \citep{herczeg14}.
+These spot maps demonstrate that multiple temperature components contribute to the broadband emission from the star, which may explain the large differences between the 4100 K effective temperature measurement obtained from high resolution optical spectra \citep{donati14} compared with 3600 K obtained from an analysis dominated by TiO bands \citep{herczeg14}.
 
@@
 Telluric correction was performed by dividing the spectrum of \name by a spectrum of HR 1237, an A0V star observed immediately before \name, both at airmass 1.1.
-The broad hydrogen lines in the A0V star produced broad flux excess residuals in the spectrum of LkCa 4.
+The broad hydrogen lines in the A0V star produced excess residuals in the spectrum of LkCa 4.
 No effort was made to mitigate these flux excess residuals, which affect several spectral orders.
@@
 
-A flux-calibrated low-resolution optical spectrum of LkCa 4 was obtained using Palomar/DBSP \citep{oke82} on 30 Dec.
-2008.
+A flux-calibrated low-resolution optical spectrum of LkCa 4 was obtained using Palomar/DBSP \citep[DBSP,][]{oke82} on 30 Dec.
+2008 at 06:30 UT.
 These spectra cover 3200--8700 \AA\ at a spectral resolution $R\sim 500$.
@@
 Near-infrared spectra of LkCa 4 were obtained at ~01:30 UT on Dec.
-30, 2008, using the TripleSpec spectrograph on the Astrophysical Research Consortium (ARC) 3.5 meter telescope at Apache Point Observatory in Sunspot, New Mexico.
+30, 2008, a few hours earlier than the DBSP spectra, using the TripleSpec spectrograph on the Astrophysical Research Consortium (ARC) 3.5 meter telescope at Apache Point Observatory in Sunspot, New Mexico.
 LkCa 4 was observed for a total integration time of 90s using an ABBA dither sequence along the slit to remove sky emission by differencing sequential exposures.
@@
  \caption{Overview of \name $V-$band photometric monitoring from 1986$-$2016.
-The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DoubleSpec, and TripleSpec.
-The near contemporaneous DoubleSpec and TripleSpec epochs lay on top of each other on this scale, as do the 12 ESPaDOnS epochs.
+The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DBSP, and TripleSpec.
+The near contemporaneous DBSP and TripleSpec epochs lay on top of each other on this scale, as do the 12 ESPaDOnS epochs.
 The abscissa range is equal to the current lifespan of the first author of this paper.}
@@
 The estimated $BVR$ magnitudes at the time of the spectral observations are determined from regularized multiterm fits \citep[\emph{i.e.} Fourier series truncated to the first $\sim 4$ components]{vanderplas15a} shown as the solid blue lines in Figure \ref{fig:PhotPhase}.
-Table \ref{tbl_estimated_V} lists the estimated $BVR$ photometry and the observing epoch for data from IGRINS, ESPaDOnS, 2MASS \citep{skrutskie06}, DoubleSpec, and TripleSpec.
+Table \ref{tbl_estimated_V} lists the estimated $BVR$ photometry and the observing epoch for data from IGRINS, ESPaDOnS, 2MASS \citep{skrutskie06}, DBSP, and TripleSpec.
 
@@
 We then use a two temperature mixture model to perform a fit to the near-IR spectra in Section \ref{sec:two_tempIGRINS}.
-
-First we measured a single unique effective temperature to each spectral order in the optical (\S \ref{sec:ESP_starfish}) and near-IR (\S \ref{sec:IGR_starfish}).
-Second we fit a two-temperature mixture model (\S \ref{sec:methods}) to a near-IR echelle spectrum (\S \ref{sec:two_tempIGRINS}).
-The near-IR was preferred over the optical, since the cool starspots emit most of their flux in the near-IR, enhancing the likelihood of direct detection of emission from the starspots.
+In general, the near-IR is preferred over the optical, since the cool starspots emit most of their flux in the near-IR, enhancing the likelihood of direct detection of emission from the starspots.
 
@@
 As pointed out earlier, LkCa 4 has no detected companion from direct imaging, and its RV variations are consistent with starspot modulation, so any binary companion would have to have exceptionally large luminosity or mass ratios, rendering it undetectable with our spectral inference methodology with the finite signal to noise available in the IGRINS data.
-LkCa 4's absense of mid-IR excess emission attributable to a disk also means that the spectral modeling requires no further parameters like veiling or accretion.
+The absence of a detectable disk around LkCa 4
+LkCa 4 means that the spectral modeling requires no further parameters like veiling or accretion.
 
@@
 We selected a subset of 32 of the 54 available IGRINS spectral orders\footnote{The prohibitive computational cost limited us from running all the spectral orders.} with low telluric absorption artifacts.
-We performed full-spectrum fitting, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $o$.
+We performed full-spectrum fitting, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order.
 We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
@@
 The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
-Starspots are cooler than their surrounding photosphere and will, therefore, have a longer wavelength of peak emission.
+Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission.
 The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
@@
 
-Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders performed better than others in assessing stellar properties.
+Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders perform better than others in assessing stellar properties.
 This model comparison is performed by sorting the 8000 samples by their fill factor estimates and examining random draws of the cool spectrum, hot spectrum, and composite spectrum, excluding the Gaussian process coveriance and white noise steps.
@@
 Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.
-For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
+For example, orders 79 and 81 overfit Ca~I and Na~I lines and orders $74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
 These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \citep{johnskrull07,deen13}.
@@
 The combination of line blanketing and high $\vsini$ has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
-One such feature has been previously identified in the near-IR: the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines, although the \PHOENIX\ models predict a non-negligible ambient photosphere contribution to the middle line for our range of ambient and spot temperatures.
+One such feature, the OH 1.563 $\mu$m line noted by \citet{oneal01}, shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines.
+The \PHOENIX\ models predict a non-negligible ambient photosphere contribution to the middle line for our range of ambient and spot temperatures.
 In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
@@
 
+\begin{figure}
+ \centering
+ %\includegraphics[width=0.65\textwidth]{}
+% \includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.65\textwidth]{figures/jbandjump}
+\includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.48\textwidth]{figures/jbandjump}
+\caption{The constraint on the size and temperature of the cool spot from the H$_2$O absorption band depth between $J$ and $H$-bands.
+The contours show the flux ratio between 1.30 and 1.34 $\mu$m (shaded yellow region in inset plot), as produced by the Phoenix models.
+The solid and hatched purple lines show the best fit and range of acceptable contours from the APO/TripleSpec spectrum, which was obtained when the cool spot fraction was $\sim 84$\%.
+The range of acceptable contour is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption.
+}
+ \label{fig:h2ojump}
+\end{figure}
+
 In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.
-In this section, we use testable predictions from this fit to demonstrate that the fit reasonably matches spectral features and their rotational modulation.
-We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface.
-The IGRINS spectrum was obtained when LkCa 4 had an estimated brightness of $V=12.84$ mag.
-The starspot and ambient temperatures and the filling factor are adopted without any adjustments to attempt to improve fits to the SED or broadband spectra.
+In this section, we test fit by comparing the combined spectrum to observed spectral features and rotational modulation.
+We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface, obtained when LkCa 4 had an estimated brightness of $V=12.84$ mag.
+The starspot and ambient temperatures and the filling factor are blindly adopted without any adjustments to attempt to improve fits to the SED or broadband spectra.
 
@@
 The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum (see \S 5.1-5.2).
-The optical-IR SED is obtained from estimating photometry from \citet{grankin08} during the 2MASS epoch, with $V\sim12.61$ mag.
+The optical-IR SED is obtained by estimating photometry from \citet{grankin08} during the 2MASS epoch, with $V\sim12.61$ mag (see Table~1).
 The SED also includes mid-IR photometry from Spitzer/IRAC \citep{hartmann05}, without adjusting for epoch.
 In the spectroscopic comparison, some minor discrepancies between the optical and near-IR spectra may be introduced because the spot coverage changed in the $\sim 5$ hrs between observations ($\Delta V=0.08$ mag).
-The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) for calculating the bolometric luminosity.
+The synthetic spectrum is obtained from the Phoenix models, as in \S 3, and is extended beyond the longest wavelength (5 $\mu$m) to calculate the bolometric luminosity.
 
@@
 When scaled separately to the red-optical and near-IR spectra, the synthetic models match even better (bottom panels of Figure \ref{fig:lores}), while single temperature photospheres fail to reproduce large spectral features.
-The $3900$ K component fits the TiO bands reasonably well at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
+The $3900$ K component fits the TiO bands at $<7400$ \AA\ but fails to reproduce molecular bands at longer wavelengths.
 The $3500$ K component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
@@
 
-Multi-temperature photospheres may resolve some of the long-standing problems related to discrepancies between observed and model colors of young stars.
-Low mass young stars are redder than expected in the near-IR, when compared with expectations from optical spectral types \citep[e.g.][]{tottle15}.
-For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $1.04$ mag for a 4200 K photosphere and \citet{pecaut13} colors.
-This extinction is consistent with the color and SED analysis of \citet{furlan06}, which adopted a K7 spectral type, and is significantly higher than extinctions of $A_V=0.69$ measured from optical photometry \citep{kenyon95} and $0.35$ mag measured by comparing optical spectra to young spectral templates \citep{herczeg14}.
-
 An accurate extinction estimate from the full SED is challenging because of a strong dependence on the areal distribution of temperatures in the photosphere, which in our work is simplified to a two temperature fit.
@@
 The near-IR extinctions of LkCa 4, and perhaps other TTSs, will be overestimated if emission is generated from a multi-temperature spectrum but template colors are based on only the hotter component.
-This mismatch likely explains why near-IR extinctions are often higher than optical extinctions for young stars \citep[see analysis in][]{herczeg14}.
+This mismatch likely explains why near-IR extinctions are often higher than optical extinctions for young stars \citep{herczeg14} and IR colors that are often redder than expected from models \citep{tottle15}.
+For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $0.84$ mag for a 4100 K photosphere and \citet{pecaut13} pre-main sequence colors.
+This extinction is consistent with the color and SED analysis of \citet{furlan06}, where a K7 spectral type was adopted, and is higher than extinctions of $A_V=0.69$ measured from optical photometry \citep{kenyon95} and $0.35$ mag measured by comparing optical spectra to young spectral templates \citep{herczeg14}.
+
 Our results tentatively support the lower extinctions obtained at optical wavelengths, although the template colors used to calculate extinction are uncertain and will need revision.
@@
  \centering
- \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag}
+ \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag_paper2}
  \caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.
@@
 The spectrum of LkCa 4 is well reproduced by a cool component of $2750$ K covering 80\% of the surface and a $4100$ K component covering 20\% of the surface.
-Scaling this composite spectrum for LkCa 4 to the observed $K$-band photometry yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=0.17$, adopting $A_V=0.3$ mag and a distance of $131 \pm 2$ pc$^x$ based on the range of parallaxes of nearby Taurus members measured by \citet{torres12}\footnote{This distance is consistent with the Gaia distance of $130 \pm4$ pc measured to the nearby Taurus members V410 Tau, V773 Tau, and BP Tau \citep{gaia2016dr}.}.
-The effective temperature of these two components is 3330 K, as calculated from the average surface flux at the median $V$ band magnitude.
+Scaling this composite spectrum for LkCa 4 to the observed 2MASS photometry ($\sim 74\%$ spot covering fraction) yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=-0.20$, adopting $A_V=0.3$ mag and a distance of $131 \pm 2$ pc$^x$ based on the range of parallaxes of nearby Taurus members measured by \citet{torres12}\footnote{This distance is consistent with the Gaia distance of $130 \pm4$ pc measured to the nearby Taurus members V410 Tau, V773 Tau, and BP Tau \citep{gaia2016dr}.}.
+At the median 80\% spot covering fraction from 2015, the luminosity would be $\log L/L_\odot=-0.26$.
+
+The effective temperature $T_{\rm eff}$ of these two components may be calculated as
+\begin{equation}
+T_{\rm eff}=[T_{\rm amb}^4(1-f_{\Omega})+T_{spot}^4f_{\Omega}]^{0.25}.
+\end{equation}
+For the median fill factor of 80\%, the observed effective temperature would be 3180 K, with a range of 3070--3280 for 86\% and 74\% spot fill factors.
+If the cool spot is 3000 K, at the limit of the acceptable temperature range, then these values would increase by 150 K.
+The apparent effective temperature in any single epoch depends on the relative fractions of the hot and cool spot.
+When accounting for the visible contributions of both hot and cool components, this wide range of possible observed effective temperatures at any single epoch underscores the difficulty in placing young stars on HR diagrams.
+
 Figure~\ref{fig:hrdiag} and Table~4 shows that this effective temperature is much cooler than previous measurements from optical spectra, which are clustered around 4000 K.
 The luminosity does not change significantly because the broadband SED yields similar luminosities, independent of temperature.
+Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.15-0.3$ $M_\odot$ from standard evolutionary tracks \citep{baraffe15}.
 
-The apparent effective temperature in any single epoch depends on the relative fractions of the hot and cool spot.
-Decreasing the cool spot size to 74\% increases the effective temperature to 3440 K, while increasing the spot size to 86\% decreases to the effective temperature to 3200 K.
-When accounting for the visible contributions of both hot and cool components, this wide range of possible observed effective temperatures at any single epoch underscores the difficulty in placing young stars on HR diagrams.
-Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.2-0.3$ $M_\odot$.
-Our IGRINS analysis is also consistent with a cool component of 3000 K instead of 2750 K, which would increase the effective temperature by $\sim 200$ K, and mass by 0.1 $M_\odot$.
-
-The discrepancies in temperature are even larger when spectral type/temperature estimates focus on features only in either blue-optical or $H$ or $K$-band spectra, and may explain the severe differences in effective temperature between APOGEE and other (optical) methods \citep{cottaar14}.
-
-The INfrared Spectra of Young Nebulous Clusters (IN-SYNC) project \citep{cottaar14} employs APOGEE, which has a $15100-17000$ \AA\ bandwidth.
-The long-wavelength cutoff prevents APOGEE from detecting the most conspicuous cool star emission we detected in IGRINS spectral orders $o = 100, 101, 104$ at $17075-17990 \;\AA$.
-These IGRINS spectral orders that APOGEE misses can be thought of as a ``sweet spot'' where the cool star spectrum is putting out ample flux, has relatively conspicuous features, and is far-enough away from the $K-$band where problems like magnetic field-sensitive lines, and enhanced telluric absorption complicate the spectra.
-Additionally, veiling from mid-IR excess in classical T-Tauri stars will be lessened in $H-$band.
-
-On the other hand, GAIA-ESO spectra \citep{frasca15} cover only a narrow wavelength around H$\alpha$ and would yield an effective temperature of 4000 K.
+When the photosphere is assumed to be a single temperature, the effective temperature depends on the wavelength where the measurement is made.
+For LkCa 4, the $K$-band temperature  is closest to the effective temperature of the entire photosphere.
+These discrepancies may also explain the large temperature, systematic offsets identified when comparing temperatures from $H$-band APOGEE \footnote{The APOGEE spectra have a long wavelength cutoff at 1.70 $\mu$m, just short of an IGRINS ``sweet spot'' from $17075-17990 \;\AA$ (orders 100, 101, and 104), which have conspicuous hot and cool features, is far-enough away from the $K-$band where problems like magnetic field-sensitive lines, enhanced telluric absorption, and veiling by disks may complicate the spectra.} spectra to those obtained from other (usually optical) methods \citep{cottaar14}.
+On the other hand, GAIA-ESO spectra \citep{frasca15} cover only a narrow wavelength around H$\alpha$ and would yield an effective temperature of $\sim 4000$ K.
 Spectral types and effective temperatures measured from TiO depths \citep{herczeg14} are lower than those from blue spectra but still overestimate the effective temperature.
@@
 LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
-Dynamical measurements of masses of young stars with similar optical properties suggest that LkCa 4 should have a mass of $\sim 0.6-1.0$ M$_\odot$ \citep[e.g.][]{guilloteau14,czekala16,rizzuto16}.
+Dynamical measurements of masses of young stars with similar optical properties suggest that LkCa 4 should have a mass of $\sim 0.7-1.0$ M$_\odot$ \citep[e.g.][]{guilloteau14,czekala16,rizzuto16}.
 Even though LkCa 4 is only a single data point, the inferred age and low mass may be evidence that strong magnetic fields are inhibiting convection in LkCa 4.
@@
 
-\subsection{Limitations of assumptions in the spectral inference methodology}
+%\subsection{Absolute lower limit of starspot filling factor}
 
-The spectral inference method assumed only two temperature components present in the photosphere.
-In reality, starspots are probably described by a range of spot temperatures analogous to umbra, penumbra, and plages on the solar surface.
-A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
-The fit-quality of the existing two-temperature fits seems fairly strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
-Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.
-Most of these orders are flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.
-A few orders just show mediocre fits where no permutation of hot and cool two-temperature models could describe all of the variance in the spectrum.
-These $K-$band orders could be examined for a penumbra-like temperature component.
-We caution that systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
-Space-based high-precision planetary transit spectrophotometry could offer an avenue to measure the morphologies and temperature distributions of starspots for the subset of transiting exoplanet host stars or eclipsing binaries.
+In this paper, we have demonstrated that IGRINS spectra of LkCa 4 is well modeled with two temperatures, an ambient photosphere of 4100 K and large cool spots of 2700--3000 K that cover 80\% of the stellar surface.
+This solution reproduces the high-resolution HK spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.
+Such a high covering fraction for a spot is extraordinary.
+In this section, we describe that this type of cool spot is robust, despite some simplifying limitations of our spectral inference technique, discuss how such a large spot could be interpreted, and suggest that, while LkCa 4 appears extreme, other young sources have similar characteristics.
 
-We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of LkCa 4, a young star that possesses a strong magnetic field \citep{donati14}.
-Cool sunspots are associated with locally heightened magnetic fields on the sun, so synthetic spectral models employing negligible magnetic fields will fail to fit magnetic sensitive features.
-Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into the photosphere in the line wings than in the line center.
-The former effect will preferentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.
-The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
-Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.
-We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
-Strong metal lines demonstrate large departures in their best fit $\Z$, as the na\"{i}ve fitting strategy futilely attempts to minimize the residuals from Zeeman-broadened lines.
-No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
+\subsection{An absolute lower limit of starspot filling factor}
 
-Uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
-Erroneous bulk opacities could be responsible for some of the scatter of fill factor distributions seen across different spectral orders, as in Figures \ref{fig:TwoTempResults} and \ref{fig:specPostageStamp}.
-The large number of spectral orders over which the fill factors are averaged offers resilience against these anomalies.
-
-\begin{figure*}
- \centering
-\includegraphics[width=0.45\textwidth]{figures/v_v-r_Grankin} 
-\caption{Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.
-The purple line represents a two component photometric model  described by \citet{grankin08}, comprising a photospheric temperature of 4040K (for K7), and a temperature of spotted area of 3030K (for an M5).
-In this model, the spot coverage of the observed hemisphere varies from $\sim36\%$ at maximum brightness, and $\sim82\%$ at minimum brightness.}
- \label{fig:grankin_vr}
-\end{figure*}
-
-\begin{figure*}
- \centering
- %\includegraphics[width=0.65\textwidth]{}
- \includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.65\textwidth]{figures/jbandjump}
- \caption{The constraint on the size and temperature of the cool spot from the H$_2$O absorption band depth between $J$ and $H$-bands.
-The contours show the flux ratio between 1.30 and 1.34 $\mu$m (shaded yellow region in inset plot), as produced by the Phoenix models.
-The solid and hatched purple lines show the best fit and range of acceptable contours from the APO/TripleSpec spectrum, which was obtained when the cool spot fraction was $\sim 84$\%.
-The range of acceptable contour is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption.
-}
- \label{fig:h2ojump}
-\end{figure*}
-
-Analyses of optical emission also suggest that a two-temperature model may be an oversimplification.
-Figure \ref{fig:grankin_vr} shows that the $V-R$ colors from \citet{grankin} are better reproduced if the cooler component is $\sim 3050$ K, thereby contributing more flux at optical wavelengths.
-The ZDI imaging of \citet{donati14} also indicate a complex structure of spots that are hotter than what is interpreted here as the ambient photosphere, while also reproducing the optical photometry.
-Despite the need for more complicated emission structures to simultaneously reproduce all observations, the broadband SED, spectral shape, and rotational modulation of spectral indices are reasonably well fit with the two components presented here.
-Moreover, the high and low-resolution near-IR spectra require a cool (2700--3000 K) component while the global photometry requires a large covering fraction for this cool component.
-
-The need for the cool component to have a large covering fraction and $<3000$ K is also demonstrated by the size of the H$_2$O band absorption between the $J$ and $H$ bands (see Figure~\ref{fig:h2ojump}).
-Assuming that the hotter component is 4100 K, the H$_2$O opacity is only sufficient if $T_{spot}<3000$ K, with a high spot coverage.
-
-\subsection{Absolute lower limit of starspot filling factor}
-
+This simple thought experiment demonstrates that the high starspot filling factor must be approximately correct.
 A lower limit to the starspot filling factor can be set by the size of a black spot that can induce such large $\Delta V$.
-
 Consider the following extremely conservative assumptions:  \begin{enumerate}
@@
 In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
-
 If \emph{any} of these assumptions is relaxed, the minimum fill factor \emph{increases}.
 
-\subsection{Comparison to studies of ensembles}
-
-%Introduce
-The number of WTTS for which the areal filling factor of spots have been measured is relatively low.  Recently there have been many new estimates.
-
-% Grankin
-V 410 Tau shows up to 41\% coverage of spots \citep{petrov94}.
-Many more measurements exist for evolved giants and subgiants, with typical fill factors in the range 15$-$48\% \citep{berdyugina05}.
-The prototypical BY Dra source is consistent with 60\% coverage fraction of moderately cool ($\Delta \teff =400$) penumbra \citep{chugainov76}.
-By these comparisons, LkCa 4 seems on the high end of filling factor.
-
-There are several WTTS in the Taurus-Auriga star-forming region that demonstrate the highest amplitudes of periodic light variations, achieving $0.4-0.8$ mag in the $V-$band: LkCa 4, V410 Tau, V836 Tau, LkCa 7, V827 Tau, V830 Tau, and V819 Tau \citep{grankin08}.
-Such large amplitudes of the light variation indicate the existence of very extended spotted regions on the stellar surface.
-To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, V830 Tau, and V836 Tau \citep{grankin98,grankin99}.
-For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500-1400$ K lower than the ambient photosphere.
-An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
-nonuniformity, which is defined as the difference of spot coverage in the visible hemispheres of the star at maximum and minimum light.
-As the amplitude increases from 0.39 to 0.63mag, the degree of nonuniformity in the spot distribution increases from 21 to 37\%.
-Besides the high amplitude of variability, these objects show the phenomenon of long-term stability of a brightness minimum in the interval from 5 to 19 years.
-To all appearances, this group of stars has the similar nature of stellar activity which
-should be investigated in the future.
-
-% Covey
-The Pleiades serves as an older age sample of young stars possessing evidence for large coverage fraction of starspots.
-For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}.
-Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.
-However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude at the precision of the PTF data, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
-LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation.
-The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.
-
-% Venuti
-WTTSs observed towards NGC2264 show photometric variations similar to--but of lower average amplitude than-- LkCa 4 \citep{venuti15}.
-Modeling of polychromatic photometric monitoring of the locus of WTTSs indicates a lower limit to the true coverage fraction $f_{\mathrm{eq}}\sim10-30\%$ and a difference $\teffa-\teffb\sim500$ K.
-
-% Fang
-%\textbf{Insert Fang info here.}
+\begin{figure}
+ \centering
+\includegraphics[width=0.45\textwidth]{figures/v_v-r_Grankin} 
+\caption{Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.
+The purple line represents a two component photometric model  described by \citet{grankin08}, comprising a photospheric temperature of 4040K (for K7), and a temperature of spotted area of 3030K (for an M5).
+In this model, the spot coverage of the observed hemisphere varies from $\sim36\%$ at maximum brightness, and $\sim82\%$ at minimum brightness.}
+ \label{fig:grankin_vr}
+\end{figure}
 
@@
 
-%\subsection{Possibility of third temperature or multiple temperatures}
-
 \subsection{Is \name an extreme source?}
@@
 From a statistical perspective, it might not be a surprise that the source with the largest photometric variability also posessess among the largest coverage fraction of cool spots.
+When compared with spot covering fractions of 15--60\% for evolved giants and subgiants \citep{chugainov76,berdyugina05}, the 80\% spot coverage of LkCa 4 seems high.
+However, many other young stars with similar spectral type also have large spot covering fractions.
 
-Despite the evidence that LkCa 4 is an outlier, spots are likely broadly important in estimating the properties of young low-mass stars.
-As an example, the well-studied CTTS TW Hya has a $\sim 4000$ K photosphere measured from high resolution optical spectra \citep[e.g.][]{yang05}.
+Several WTTS in the Taurus-Auriga star-forming region have large amplitudes in periodic light variations, achieving $0.4-0.8$ mag in the $V-$band: LkCa 4, V410 Tau, LkCa 7, V827 Tau, V830 Tau, and V819 Tau \citep{grankin08}.
+In a sample that is not biased to variable stars,
+WTTSs observed in NGC 2264 show photometric variations similar to--but of lower average amplitude than-- LkCa 4 \citep{cody14,venuti15}.
+Modeling of polychromatic photometric monitoring of the locus of WTTSs indicates a lower limit to the true coverage fraction $f_{\mathrm{eq}}\sim10-30\%$ and a difference $\teffa-\teffb\sim500$ K.
+
+Large amplitudes of the light variation indicate the existence of very extended spotted regions on the stellar surface.
+To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, and V830 Tau \citep{grankin98,grankin99}.
+For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500-1400$ K lower than the ambient photosphere.
+An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
+nonuniformity, which is defined as the difference of spot coverage in the visible hemispheres of the star at maximum and minimum light.
+As the amplitude increases from 0.39 to 0.63 mag, the degree of nonuniformity in the spot distribution increases from 21 to 37\%.
+An alternative analysis of TiO bands indicate a spot coverage of $\sim 41$\% for V410 Tau \citep{petrov94}.
+Besides the high amplitude of variability, these objects show the phenomenon of long-term stability of a brightness minimum in the interval from 5 to 19 years.
+To all appearances, this group of stars has the similar nature of stellar activity which should be investigated in the future.
+%The stars all have similar optical spectral types \citep[e.g.][]{kenyon95,herczeg14}.
+
+%The number of WTTS for which the areal filling factor of spots have been measured is relatively low.  
+%Recently there have been many new estimates.
+
+% Grankin
+
+% Covey
+The Pleiades serves as an older age sample of young stars possessing evidence for large coverage fraction of starspots.
+For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}, while LAMOST spectra of the TiO band indicates that $\sim 30$\% spot coverages may be common for 3500--5000 K stars \citep{fang2016}.
+Recent photometric monitoring of the Pleiades indicates that the anomalous colors scale with rotation rate, strengthing the case for magnetic-field induced starspots as the cause of the anomaly \citep{covey16}.
+However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude at the precision of the PTF data, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
+LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation.
+The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.
+
+% Venuti
+
+% Fang
+%\textbf{Insert Fang info here.}
+
+Spots are also likely important in estimating the properties of generic low-mass young stars.
+As an example, the well-studied CTTS TW Hya has a $\sim 4100$ K photosphere measured from high resolution optical spectra \citep[e.g.][]{yang05}.
 However, the near-IR spectrum is consistent with $\sim M2$, when compared with main sequence dwarf stars \citep{vacca11}.
@@
 \citet{herczeg14} found an intermediate spectral type for TW Hya and other TTSs by focusing on TiO bands at redder wavelengths than previous spectra, and also by using young stars as photospheric templates.
-The mismatch between near-IR spectra of dwarf stars and young stars, even with similar optical spectral types, is likely explained by the prevalence and importance of cool spots in low mass stars.
+The mismatch between near-IR spectra of dwarf stars and young stars (along with some of the color discrepancies, see Section 5.1) is likely explained by the prevalence and importance of cool spots in low mass stars.
+
+%\subsection{Possibility of third temperature or multiple temperatures}
+
+\subsection{The limitation of a two-temperature model}
+
+We assume only two temperature components present in the photosphere.
+In reality, starspots are probably described by a range of spot temperatures analogous to umbra, penumbra, and plages on the solar surface.
+A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
+The fit-quality of the existing two-temperature fits seems fairly strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
+Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.
+Most of these orders are flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.
+A few orders just show mediocre fits where no permutation of hot and cool two-temperature models could describe all of the variance in the spectrum.
+These $K-$band orders could be examined for a penumbra-like temperature component.
+We caution that systematic errors in the models would ultimately limit the interpretability of models with more than two temperature components.
+Space-based high-precision planetary transit spectrophotometry could offer an avenue to measure the morphologies and temperature distributions of starspots for the subset of transiting exoplanet host stars or eclipsing binaries.
+
+Analyses of optical emission also suggest that a two-temperature model may be an oversimplification.
+Figure \ref{fig:grankin_vr} shows that the $V-R$ colors from \citet{grankin08} are better reproduced if the cooler component is $\sim 3050$ K, thereby contributing more flux at optical wavelengths.
+The ZDI imaging of \citet{donati14} also indicate a complex structure of spots that are hotter than what is interpreted here as the ambient photosphere, while also reproducing the optical photometry.
+Despite the need for more complicated emission structures to simultaneously reproduce all observations, the broadband SED, spectral shape, and rotational modulation of spectral indices are reasonably well fit with the two components presented here.
+The high and low-resolution near-IR spectra, including the H$_2$O band absorption between the $J$ and $H$ bands (see Figure~\ref{fig:h2ojump}), require a cool (2700--3000 K) component while the global photometry requires a large covering fraction for this cool component.
+
+%Assuming that the hotter component is 4100 K, the H$_2$O opacity is only sufficient if $T_{spot}<3000$ K, with a high spot coverage.
+
+\subsection{Limitations of assumptions in the spectral inference methodology}
+
+We assumed that the \PHOENIX\ synthetic spectra are a good representation of the observed IGRINS spectrum of LkCa 4, a young star that possesses a strong magnetic field \citep{donati14}.
+Cool sunspots are associated with locally heightened magnetic fields on the sun, so synthetic spectral models employing negligible magnetic fields will fail to fit magnetic sensitive features.
+Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into the photosphere in the line wings than in the line center.
+The former effect will preferentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.
+The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
+Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.
+We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
+Strong metal lines demonstrate large departures in their best fit $\Z$, as the na\"{i}ve fitting strategy futilely attempts to minimize the residuals from Zeeman-broadened lines.
+No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
+
+Uncertainties in the \PHOENIX\ synthetic spectra continuum opacity flow down to uncertainties in the absolute value of the fill factor.
+Erroneous bulk opacities could be responsible for some of the scatter of fill factor distributions seen across different spectral orders, as in Figures \ref{fig:TwoTempResults} and \ref{fig:specPostageStamp}.
+The large number of spectral orders over which the fill factors are averaged offers resilience against these anomalies.
+
+%Introduce
 
@@
 We found tentative, albeit weak, evidence for such anticorrelation in $v_z$ across spectral orders dominated by cool photosphere and those dominated by hot photosphere.
-For example, the cool-photosphere dominated spectral orders $o = 100, 102, 104$ show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
+For example, the cool-photosphere dominated spectral orders $100, 102, 104$ ($1.7$--$1.8$ $\mu$m) show the largest median $v_z\sim14.5-17.0$ km/s, while the other orders that possess a mix of primarily hot- and some cool- photosphere features demonstrate $v_z\sim9-13$ km/s.
 An independent analysis of the RV of the IGRINS spectrum yields a barycentric RV of $14.6\pm0.2$ km~s$^{-1}$.
@@
 Direct spectral emission from cool starspots is likely much weaker in sources with less starspot coverage than LkCa 4.
-Still, the characterization and modeling of direct emission from starspots should, in principle, decrease RV jitter attributable to starspots in the near-IR spectra of any spotted star as demands on RV precision increase.
+As demands on RV precision increase, the characterization and modeling of direct emission from starspots should in principle decrease RV jitter attributable to starspots in the near-IR spectra of any spotted star.
 
 \section{Conclusions}
-This paper has presented several complementary constraints on the photospheric properties of the weak-lined T-Tauri star LkCa 4, showing that this heavily spotted star was previously misplaced on the pre-main sequence HR diagram.
-New results from \citet{fang2016} show that large starspot coverage fractions of $50\%$ are common among stars in the Pleiades.
-LkCa 4 breaks the apparent trend of a ceiling at 50\% coverage fraction of cool starspots, though it is not yet clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.
+This paper establishes that the optical+near-IR spectrum of the weak-lined T Tauri star LkCa 4 includes multiple components.
+When fit with two temperatures, the ambient photosphere of 4100 K covers 20\% of the stellar surface while the cool spot of 2700--3000 K covers 80\% of the stellar surface.
+The previously-established $V$-band brightness variability of $0.8$ mag is interpreted as the rotational modulation of the covering fraction of the hot spot.
+This spectral modelling leads to an improved effective temperature measurement of LkCa 4.
+
+New results from \citet{fang2016} show that large starspot coverage fractions of $50\%$ are common even among stars in the Pleiades, which at $\sim 120$ Myr are much older than the 1--10 Myr old stars in the Taurus Molecular Cloud.
+LkCa 4 breaks the apparent ceiling at 50\% coverage fraction of cool starspots, though it is not yet clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.
 
@@
 Large parts of the stellar surface are covered in spots that do not induce photometric modulation, either from circumpolar regions that always face towards our line-of-sight, longitudinally symmetric bands, or isotropic small spots.
+Some cool stars in the Pleaides have a large excess in Li abundance, some have inflated radii, some are fast rotators, and some have spots \citep[e.g.][]{somers15b}.
+While the source overlap for these properties is unclear, these anomalies may all be explained if the pre-main sequence evolution of some stars is strongly affected by spots \citep{somers15}.
+LkCa 4 and other young stars with similar properties may help to connect the properties of anomalous Pleiades stars with earlier starges of stellar evolution.
 
@@
 
+We thank Chris Kochanek for valuable comments on the draft.  MG-S and GJH also thank Steve Saar and GJH thanks Lynne Hillenbrand for valuable discussions about spots.
+
 Portions of the data, Python code, Jupyter notebooks, Starfish configuration files, MCMC samples, and revision history of this manuscript are available on the project's GitHub repository at \url{https://github.com/BrownDwarf/welter}.
@@
 TW-SH is supported by the DOE Computational Science Graduate Fellowship, grant number DE-FG02-97ER25308.
+
+We thank LCOGT and its staff for their continued support of ASAS-SN.
+ASAS-SN is supported by NSF grant AST-1515927.
+Development of ASAS-SN has been supported by NSF grant AST-0908816, the Center for Cosmology and AstroParticle Physics at the Ohio State University, the Mt.
+Cuba Astronomical Foundation, and by George Skestos.
+
+BJS is supported by NASA through Hubble Fellowship grant HST-HF-51348.001 awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.
 

### 2016-09-27 document/ms.tex
Grankin affiliation, etc.

@@
 \altaffiltext{3}{Department of Physics and Astronomy, Vanderbilt University, 6301 Stevenson Center, Nashville, TN, 37235, USA}
-\altaffiltext{4}{TBD--Grankin}
+\altaffiltext{4}{Crimean Astrophysical Observatory, Nauchny, Crimea 298409, Russia}
 \altaffiltext{5}{Department of Physics \& Astronomy, Western Washington University, Bellingham WA 98225-9164, USA}
@@
 We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
-Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which have
+Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which imply
 %a consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with 
@@
 Convection at these young ages generates strong magnetic fields, as measured by Zeeman broadening and polarimetry \citep[e.g.][]{johnskrull07,donati09} and as seen in starspots \citep[e.g.][]{stauffer03,grankin08}.
-Evolutionary models are just now starting to implement prescriptions for how spots and magnetic fields affect the interior structure \citep{jackson14a,somers15,feiden16}.
+Evolutionary models are just now starting to implement prescriptions for how spots and magnetic fields affect the interior structure \citep{macdonald13,jackson14a,somers15,feiden16}.
 Stellar evolution models that includes these effects can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with standard mass estimates being biased towards lower masses.

### 2016-09-27 document/ms.tex
Include content from GJH from overleaf

@@
 Zeeman Doppler Imaging \citep[ZDI]{donati14} produces the latitudinal and longitudinal distribution of starspots in reconstructed brightness maps based on models for spectro-polarimetric line shapes, but would be unable to identify uniform distributions of small spots.
-All of these techniques would tend to underestimate the starspot areal coverage of pole-on stars, stars with longitudinally symmetric bands of starspots, or stars with an isotropic distribution of small starspots.
+All of these techniques would tend to underestimate the starspot areal coverage on stars with an isotropic distribution of small starspots, or pole-on stars or stars with longitudinally symmetric bands of starspots.
 
@@
 
-Rotational modulation is expected to lead to much smaller brightness changes at near-IR wavelengths than at optical wavelengths (see Table~\ref{tab:photrange}).
+Rotational modulation is expected to lead to much smaller brightness changes at near-IR wavelengths, with amplitudes of 0.15--0.2 mag, than the 0.6--0.8 mag amplitudes seen at optical wavelengths.
 The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
@@
 
-\begin{table}
-\caption{Predicted Photometric Range}
-\centering
-\label{tab:photrange}
-\begin{tabular}{cccc}
-\hline
-Band & Low Spot & High Spot & Range\\
-Cool Spot & 68\% & 83\% &\\
-\hline
-\multicolumn{4}{c}{Based on $V$, need to adapt for $A_V$}\\
-$B$ & 13.80 & 14.48 & 0.68\\
-$V$ & 12.56 & 13.23 & 0.67\\
-$R$ & 11.53 & 12.17 & 0.64 \\
-$I$ & 10.80 & 11.38 & 0.58\\
-$J$ & 9.79 & 10.00 & 0.21\\
-$K$ & 8.89 & 9.04 & 0.15\\
-\hline
-\end{tabular}
-\end{table}
+%\begin{table}
+%\caption{Predicted Photometric Range}
+%\centering
+%\label{tab:photrange}
+%\begin{tabular}{cccc}
+%\hline
+%Band & Low Spot & High Spot & Range\\
+%Cool Spot & 68\% & 83\% &\\
+%\hline
+%\multicolumn{4}{c}{Based on $V$, need to adapt for $A_V$}\\
+%$B$ & 13.80 & 14.48 & 0.68\\
+%$V$ & 12.56 & 13.23 & 0.67\\
+%$R$ & 11.53 & 12.17 & 0.64 \\
+%$I$ & 10.80 & 11.38 & 0.58\\
+%$J$ & 9.79 & 10.00 & 0.21\\
+%$K$ & 8.89 & 9.04 & 0.15\\
+%\hline
+%\end{tabular}
+%\end{table}
 
@@
 
-%\subsection{Absolute lower limit of starspot filling factor}
-
 In this paper, we have demonstrated that IGRINS spectra of LkCa 4 is well modeled with two temperatures, an ambient photosphere of 4100 K and large cool spots of 2700--3000 K that cover 80\% of the stellar surface.
@@
   \item The starspot transits the center of the stellar disk.
+  \item The star shows no feature brighter than the quiet photosphere at the visible surface
 \end{enumerate}
@@
 In the 2004 season, LkCa 4 exhibited $\Delta V\sim 0.8$, corresponding to a minimum fill factor of $f=0.52$.
-If \emph{any} of these assumptions is relaxed, the minimum fill factor \emph{increases}.
+If any of assumptions 1-3 is relaxed, the minimum fill factor \emph{increases}.
+If assumption 4 is relaxed, the minimum fill factor decreases.
+The large amplitude photometric variations in LkCa 4 are therefore evidence for either a hot spot in excess of the ambient photosphere, or a large coverage fraction of cool starspots.
 
@@
 In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
+This scenario would have to be consistent with the inclination derived from relating $\vsini$, rotation period, and estimates for the stellar radius.
+Such estimates are limited by estimates of the radius, since uncertainties in effective temperature and luminosity cause a wide range of radius estimates.
 
@@
 Cool sunspots are associated with locally heightened magnetic fields on the sun, so synthetic spectral models employing negligible magnetic fields will fail to fit magnetic sensitive features.
-Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into the photosphere in the line wings than in the line center.
+Magnetic fields will have a few effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into the photosphere in the line wings than in the line center.
 The former effect will preferentially impact lines with high magnetic sensitivity \citep[\emph{e.g.}][]{johnskrull99,deen13}.
 The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants \citep{oneal96}.
+Zeeman amplification can also be present \citep{basri92}.
 Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.
@@
 
-Radial velocity (RV) planet searches in the infrared--where the modulation of RV signals is lessened \citep[\emph{e.g.}][]{prato08}-- could potentially reduce RV jitter by characterizing and constraining the effect of direct emission from starspots, in addition to the flux deficits imbued in optical line profiles.
+Radial velocity (RV) planet searches in the infrared--where the modulation of RV signals is lessened \citep[\emph{e.g.}][]{prato08,crockett12}-- could potentially reduce RV jitter by characterizing and constraining the effect of direct emission from starspots, in addition to the flux deficits imbued in optical line profiles.
 Direct spectral emission from cool starspots is likely much weaker in sources with less starspot coverage than LkCa 4.
@@
 
-We thank Chris Kochanek for valuable comments on the draft.  MG-S and GJH also thank Steve Saar and GJH thanks Lynne Hillenbrand for valuable discussions about spots.
+We thank Chris Kochanek and Daniel T. Jaffe for valuable comments on the draft.  MG-S and GJH also thank Steve Saar and GJH thanks Lynne Hillenbrand for valuable discussions about spots.
 

### 2016-09-27 document/submission/ms.tex
Submitted version of the paper.

--- 2016-09-27 document/ms.tex
@@
 Shappee,\altaffilmark{11,12} Gregory N.
-Mace,\altaffilmark{13} Jae-Joon Lee\altaffilmark{14} T.~W.-S.~Holoien,\altaffilmark{15,16} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{17,1}}
+Mace,\altaffilmark{13} Jae-Joon Lee,\altaffilmark{14} T.~W.-S.~Holoien,\altaffilmark{15,16} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{17,1}}
 
@@
 We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
-Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which imply
-%a consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with 
-a best fit filling factor of $f\sim80$\% starspots at the time of the observation.
+Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which imply a best fit filling factor of $f\sim80$\% starspots at the time of the observation.
 These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time.
@@
  \centering
- \includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
+ \includegraphics[width=0.98\textwidth]{LkCa4_phot1986-2016.pdf}
  \caption{Overview of \name $V-$band photometric monitoring from 1986$-$2016.
@@
  \centering
- \includegraphics[width=0.95\textwidth]{figures/Vband_22s.pdf}
+ \includegraphics[width=0.95\textwidth]{Vband_22s.pdf}
  \caption{Phase-folded lightcurves constructed assuming $P=3.375$ days for all 22 observing seasons.
@@
 
-\input{tables/tbl_estV_atObsEpoch.tex}
+\input{tbl_estV_atObsEpoch.tex}
 
@@
  \centering
- \includegraphics[width=0.48\textwidth]{figures/single_Teff_v_order}
+ \includegraphics[width=0.48\textwidth]{single_Teff_v_order}
  \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
@@
  \centering
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_04} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_01} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_05} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_06} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_02} 
- \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_03} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_04} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_01} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_05} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_06} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_02} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_03} 
  \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).
@@
  \centering
- \includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
+ \includegraphics[width=0.95\textwidth]{violin_Teff_fill_order} 
  \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\Omega}$ (yellow shade).
@@
 
-\input{tables/tbl_best_fit.tex}
+\input{tbl_best_fit.tex}
 
@@
  \centering
- \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot_2750}
+ \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{phot_2750}
 \caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
@@
  \centering
- \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_2750k}
+ \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{lores_panels_2750k}
  \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
@@
  %\includegraphics[width=0.65\textwidth]{}
-% \includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.65\textwidth]{figures/jbandjump}
-\includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.48\textwidth]{figures/jbandjump}
+% \includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.65\textwidth]{jbandjump}
+\includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.48\textwidth]{jbandjump}
 \caption{The constraint on the size and temperature of the cool spot from the H$_2$O absorption band depth between $J$ and $H$-bands.
@@
  \centering
- \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2750k}
+ \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{vband_spot_2750k}
 \caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
@@
  \begin{tabular}{ll}
- \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{figures/bv_pec13} 
+ \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{bv_pec13} 
     &
-   \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{figures/vr_pec13}
+   \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{vr_pec13}
     \end{tabular}
@@
  \centering
- \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{figures/lkca4_tio_forpaper}
+ \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{lkca4_tio_forpaper}
  \caption{Variability in TiO bands measured with ESPaDOnS.
@@
  \centering
- \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag_paper2}
+ \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{lkca4_hrdiag_paper2}
  \caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.
@@
  \centering
-\includegraphics[width=0.45\textwidth]{figures/v_v-r_Grankin} 
+\includegraphics[width=0.45\textwidth]{v_v-r_Grankin} 
 \caption{Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.
@@
  \centering
- \includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
+ \includegraphics[width=0.95\textwidth]{H_band_spectra_3x7}
  \caption{IGRINS Orders $122-100$, with panels arranged with the shortest wavelength in the upper left corner with central wavelenth decreasing toward the bottom of the leftmost column, then decreasing through the subsequent columns.
@@
  \centering
- \includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
+ \includegraphics[width=0.95\textwidth]{K_band_spectra_3x7}
  \caption{IGRINS Orders $93-73$, with the same layout, ordering, and colors as Figure \ref{fig:Hband3x7}. The $y-$axis is on a logarithmic scale.}
@@
 \LongTables
-\input{tables/tbl_order_results.tex}
+\input{tbl_order_results.tex}
 
@@
 Table \ref{tbl_history} lists measurements of \name from previous studies, compared to this work.
-\input{tables/tbl_history.tex}
+\input{tbl_history.tex}
 

### 2016-12-06 document/submission/ms.tex
Working on the referee report in the submitted version of the manuscript

@@
 
-\slugcomment{In preparation}
+\slugcomment{Submitted}
 
@@
 \begin{abstract}
-%Ages and masses of young stars can be estimated by comparing observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks.
-Nonstandard physics like magnetic fields and starspots confound interpretations of pre-main sequence HR diagrams and their age and mass estimates.
-%We characterize the fundamental properties of the spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for signatures of the emergent radiation originating from the starspot or starspot groups.
-The spectral and photometric properties of this radiation can be used to constrain both the starspot filling factor and the starspot temperature.
-%A generalization of line depth ratio analysis is developed and applied to a high-resolution near-IR IGRINS spectrum.
-The IGRINS spectrum is forward modeled with pre-computed \PHOENIX\ synthetic spectra using the open source spectral inference framework \texttt{Starfish} extended to include a two component mixture model comprised of ambient photosphere and starspot emission.
-%Spectral features attributable to both ambient photosphere $\teffa\sim4100$ K and cool starspots $\teffb\sim2700-3000$ K are detected in the IGRINS spectrum.
-In some spectral regions, the starspot emission acts merely as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
-The filling factor of of starspots at minimum light $\Delta V = 0.5$must be $>37\%$, and is likely much larger based on geometry and temperature considerations.
-The IGRINS spectra yield consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with a best fit filling factor of $f\sim80$\% starspots at the epoch of spectrum acquisition.
-The interpretation of the $\sim20$\% ambient photosphere as a persistent ``hot spot'' is also possible.
-The spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy show broad support for the starspot parameter estimates derived separately from IGRINS, strengthening the case for a large albeit secularly changing starspot filling factor and temperature contrast through time.
-%The revised effective temperature and luminosity make LkCa 4 appear much lower mass and much younger compared to previous estimates based on optical spectroscopy and not taking into account the large covering fraction of the cool spots.
-Emission from longitudinally symmetric starspots has likely caused the misplacement of spotted young stars on the observational HR diagram, leading to incorrect estimates for ages and masses and contributing, in part, to the apparent age spread observed towards young clusters.
 
@@
 The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.
-The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.
-The cluster of $H-$band orders at 1.7 $\mu$m correspond to a local peak in flux density of cool starspots.}
+The increasing flux density from the cool photospheric component compared to the flux from hot photospheric components can explain the observed trend in derived photospheric temperature.}
  \label{fig:SingleTeffvsOrder}
@@
 
-Starspot line depth ratio analysis has traditionally been limited to isolated portions of spectrum that possess spectral lines attributable only to starspots and spectral lines attributable only to ambient photosphere \citep[\emph{e.g.}][]{neff95, oneal01}.
-The apparent veiling of the lines and their respective temperature dependences can be combined to solve for the starspot and ambient photosphere temperatures and relative areal coverages.
-This line depth ratio method suffers from the need to identify portions of the spectrum that possess such strong lines, and from the need to assemble large atlases of observed spectral templates to which the spotted star spectrum can be compared.
+Starspot line depth ratio analysis has traditionally been limited to isolated portions of spectrum that possess spectral lines attributable only to cool photospheric components and spectral lines arising from the warmer ambient photosphere \citep[\emph{e.g.}][]{neff95, oneal01}.
+The apparent veiling of the lines and their respective temperature dependences can be combined to solve for the cool photosphere and ambient photosphere temperatures and relative areal coverages.
+This line depth ratio method suffers from the need to identify portions of the spectrum that possess easily identifiable strong lines, and from the need to assemble large atlases of observed spotless spectral templates to which the spotted star spectrum can be compared.
 In this section, we introduce a generalization of the line depth ratio analysis which employs pixel-by-pixel modeling of all spectral orders.
-By using all the spectral data, this strategy has the power to constrain starspot properties at relatively low filling factors and to identify weak lines that originate from the starspots.
+By using all the spectral data, this strategy has the power to constrain starspot properties at relatively low filling factors and to identify weak lines that originate from the cool photosphere.
 
@@
 
-Using the spectral fitting approach introduced in Section 3.1 \ref{sec:methods}, we first first separately fit the optical (ESPaDOnS) and near-IR (IGRINS) spectra with distinct, single $\teff$ models; these fits are described in Sections \ref{sec:ESP_starfish} and \ref{sec:IGR_starfish} respectively.
+Using the spectral fitting approach introduced in Section 3.1 \ref{sec:methods}, we first first separately fit the optical (ESPaDOnS) and near-IR (IGRINS) spectra with distinct, single photospheric component models; these fits are described in Sections \ref{sec:ESP_starfish} and \ref{sec:IGR_starfish} respectively.
 We then use a two temperature mixture model to perform a fit to the near-IR spectra in Section \ref{sec:two_tempIGRINS}.
-In general, the near-IR is preferred over the optical, since the cool starspots emit most of their flux in the near-IR, enhancing the likelihood of direct detection of emission from the starspots.
+The near-IR spectral range is preferred over the optical, since the cool photosphere emits most of its flux in the near-IR, enhancing the likelihood of direct detection of emission from the cool component.
 
@@
 
-The stellar photosphere is characterized as two photospheric components with a starspot temperature $\teffb$ and ambient photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$, respectively\footnote{For flux calibrated spectra, the total solid angle $\Omega$ can be constrained, but for typical echelle spectrographs only relative values of $\Omega_{\mathrm{spot}}$ and $\Omega_{\mathrm{amb}}$ can be inferred.}.
-Starspots (or spot groups) are assumed to be cooler than the ambient photosphere, but otherwise share the same average intrinsic and extrinsic stellar parameters $\vsini, \logg, \Z, v_z$.
-The composite mixture model for observed flux density is:
+The stellar photosphere is characterized as two photospheric components with a cool photosphere temperature $\teffb$ and hot photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$, respectively\footnote{For flux calibrated spectra, the total solid angle $\Omega$ can be constrained, but for typical echelle spectrographs only relative values of $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$ can be inferred.}.
+
+The choice of nomenclature depends on the physical origin of the emission region.
+In general, the emission region's physical origin is not directly observable without ancillary information.
+For many applications, it could be reasonably assumed that the cool photospheric component corresponds to a sunspot or sunspot group, and the hot component corresponds to the ambient photosphere.
+However, a cool ambient photosphere possessing localized hot spots---like plages on the sun---could yield the same or similar two-temperature composite spectrum.
+In principle the physical origin could be assessed with detailed comparision of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.
+We made no effort to make such an assessment in this work, and therefore index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.
+
+The two photospheric components share the same average intrinsic and extrinsic stellar parameters $\vsini, \logg, \Z, v_z$.  The composite mixture model for observed flux density is:
 \begin{eqnarray} \label{eqn:mix_M}
-S_{\mathrm{mix}} = \Omega_{\mathrm{amb}} B(\teffa)  + \Omega_{\mathrm{spot}} B(\teffb)
+S_{\mathrm{mix}} = \Omega_{\mathrm{hot}} B(\teffa)  + \Omega_{\mathrm{cool}} B(\teffb)
 \end{eqnarray}
@@
 \begin{eqnarray} \label{eqn:fill_factor}
-f_{\Omega} = \frac{\Omega_{\mathrm{spot}}}{\Omega_{\mathrm{amb}} + \Omega_{\mathrm{spot}}}
+f_{\mathrm{cool}} = \frac{\Omega_{\mathrm{cool}}}{\Omega_{\mathrm{hot}} + \Omega_{\mathrm{cool}}}
 \end{eqnarray}
 
-The term $f_{\Omega}$ represents an instantaneous, observational fill factor seen on one projected hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
-In the limit of homogenously distributed spots, $f_{\Omega}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\Omega}$ can vary cyclically through rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
+The term $f_{\mathrm{cool}}$ represents an instantaneous, observational fill factor seen on one projected hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
+In the limit of homogenously distributed starspots and assuming the cool photosphere arises from starspots, $f_{\mathrm{cool}}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\mathrm{cool}}$ can vary cyclically through rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
 
-The starspot model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $f_{\Omega}$.
-The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the starspot and ambient photosphere are nearly degenerate over small changes in $\teffa$, $\teffb$, and $f_{\Omega}$.
+The two component mixture model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $f_{\mathrm{cool}}$.
+The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the two photospheric components are nearly degenerate over small changes in $\teffa$, $\teffb$, and $f_{\mathrm{cool}}$.
 This challenge motivated the second important change to the spectral inference framework, which involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
-The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling \citep{}.
+The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling \citep{foreman13}.
 The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order, making stellar parameter estimates $\vt_{o}$ unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
@@
 The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
-The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\Omega}$ for individual spectral orders.}
+The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\mathrm{cool}}$ for individual spectral orders.}
  \label{fig:specPostageStamp}
@@
  \includegraphics[width=0.95\textwidth]{violin_Teff_fill_order} 
- \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\Omega}$ (yellow shade).
+ \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\mathrm{cool}}$ (yellow shade).
 The stellar parameters are derived independently in each spectral order.
@@
 
-Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\Omega}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the reliable order subset shown in bold.
+Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\mathrm{cool}}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the reliable order subset shown in bold.
 The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.
@@
 Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.
-Remarkably, the filling factor of starspots exceeds 50\%, with a best fit value of $f_{\Omega}=80\pm 5 \% $.
+Remarkably, the filling factor of starspots exceeds 50\%, with a best fit value of $f_{\mathrm{cool}}=80\pm 5 \% $.
 
@@
 \begin{equation}
-T_{\rm eff}=[T_{\rm amb}^4(1-f_{\Omega})+T_{spot}^4f_{\Omega}]^{0.25}.
+T_{\rm eff}=[T_{\rm amb}^4(1-f_{\mathrm{cool}})+T_{spot}^4f_{\mathrm{cool}}]^{0.25}.
 \end{equation}
@@
 The ambient hot photosphere would then be close to the equator, which would be limb-darkened due to projection effects.
-Such limb darkening would cause a non-linear transformation between our observed fill factor $f_{\Omega}$, and the surface areal coverage fraction of spots.
-It is conceivable, and probably likely, that the value we report for $f_{\Omega}$ is an overestimate of the surface area actually covered by spots.
+Such limb darkening would cause a non-linear transformation between our observed fill factor $f_{\mathrm{cool}}$, and the surface areal coverage fraction of spots.
+It is conceivable, and probably likely, that the value we report for $f_{\mathrm{cool}}$ is an overestimate of the surface area actually covered by spots.
 In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
@@
 The choice to standardize fluxes makes no difference for modeling a single photospheric component.
-But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $f_{\Omega} \equiv \Omega_{\mathrm{spot}}/(\Omega_{\mathrm{amb}}+\Omega_{\mathrm{spot}})$.
+But for two-component photosphere models, the relative flux of the two model spectra needs to be accounted for to get an accurate estimate of the areal coverage fraction of the cool spots, $f_{\mathrm{cool}} \equiv \Omega_{\mathrm{cool}}/(\Omega_{\mathrm{hot}}+\Omega_{\mathrm{cool}})$.
 So we scale the mixture model in the following way:
@@
 \begin{eqnarray} \label{eqn:norm_scaling}
-f_{\lambda, \mathrm{mix}} &=& f_{\mathrm{amb}} \bar f_{\lambda, \mathrm{amb}} \times \Omega_{\mathrm{amb}} + f_{\mathrm{spot}} \bar f_{\lambda, \mathrm{spot}} \times \Omega_{\mathrm{spot}} \\
-q &=& q(\vt_{\ast})\equiv \frac{f_{\mathrm{spot}}(\teffb, ...)}{f_{\mathrm{amb}}(\teffa, ...)} \\
-f_{\lambda, \mathrm{mix}}^{\prime} &=& \bar f_{\lambda, \mathrm{amb}} \times \Omega_{\mathrm{amb}} + q \bar f_{\lambda, \mathrm{spot}} \times \Omega_{\mathrm{spot}}
+f_{\lambda, \mathrm{mix}} &=& f_{\mathrm{hot}} \bar f_{\lambda, \mathrm{hot}} \times \Omega_{\mathrm{hot}} + f_{\mathrm{cool}} \bar f_{\lambda, \mathrm{cool}} \times \Omega_{\mathrm{cool}} \\
+q &=& q(\vt_{\ast})\equiv \frac{f_{\mathrm{cool}}(\teffb, ...)}{f_{\mathrm{hot}}(\teffa, ...)} \\
+f_{\lambda, \mathrm{mix}}^{\prime} &=& \bar f_{\lambda, \mathrm{hot}} \times \Omega_{\mathrm{hot}} + q \bar f_{\lambda, \mathrm{cool}} \times \Omega_{\mathrm{cool}}
 \end{eqnarray}
@@
 Interpolation can cause pile-up near model grid-points, as noted in \citet{cottaar14}, which motivated the spectral emulation procedure in \iancze.
-We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable as kinks in the distribution of samples in the starspot coverage fraction $f_{\Omega}$.
-One drawback of our estimator method compared to the Gaussian Process regression method is that we do not propagate the uncertainty associated with the absolute flux ratio interpolation into our estimate of $f_{\Omega}$.
+We assume the interpolation of $\hat f$ is smooth enough that we will not see such pileups and if even we did see pileups, they would mostly be discernable as kinks in the distribution of samples in the starspot coverage fraction $f_{\mathrm{cool}}$.
+One drawback of our estimator method compared to the Gaussian Process regression method is that we do not propagate the uncertainty associated with the absolute flux ratio interpolation into our estimate of $f_{\mathrm{cool}}$.
 We assume this uncertainty is relatively small and can be ignored.
@@
 The mixture model is a linear operation with all the same stellar extrinsic parameters, so we can re-use all the same post-processed eigenspectra $\widetilde{\mathbf{\Xi}}$, mean spectrum $\widetilde{\xi}_\mu$, and variance spectrum $\widetilde{\xi}_\sigma$, with the tildes representing all post processing \emph{except} the $\Omega$ scaling.
-We calulate \emph{two} sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{amb}, \mathrm{spot})}$, and their associated mean and covariances following the Appendix of \iancze, and yielding:
+We calulate \emph{two} sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{hot}, \mathrm{cool})}$, and their associated mean and covariances following the Appendix of \iancze, and yielding:
 
 \begin{equation}
-  \mathsf{M}_{\mathrm{mix}}^\prime = \Omega_{\mathrm{amb}} (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{amb}}) + q \Omega_{\mathrm{spot}} (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{spot}})
+  \mathsf{M}_{\mathrm{mix}}^\prime = \Omega_{\mathrm{hot}} (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{hot}}) + q \Omega_{\mathrm{cool}} (\widetilde{\xi}_\mu + \mathbf{X} \mathbf{\mu}_{\mathbf{w}, \mathrm{cool}})
 \end{equation}
@@
 \begin{equation}
-  \mathsf{C}_{\mathrm{mix}}^\prime = \Omega_{\mathrm{amb}}^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{amb}} \mathbf{X}^T + q \Omega_{\mathrm{spot}}^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{spot}} \mathbf{X}^T + \mathsf{C}
+  \mathsf{C}_{\mathrm{mix}}^\prime = \Omega_{\mathrm{hot}}^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{hot}} \mathbf{X}^T + q \Omega_{\mathrm{cool}}^2 \mathbf{X} \mathbf{\Sigma}_\mathbf{w, \mathrm{cool}} \mathbf{X}^T + \mathsf{C}
   \label{eqn:modC}

### 2016-12-06 document/submission/ms.tex
Global replace all the ambient with hot photosphere, and starspot with cool photosphere.

@@
 We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
-Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which imply a best fit filling factor of $f\sim80$\% starspots at the time of the observation.
-These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time.
-A persistent hotspot covering $\sim20$\% of the surface is a plausible alternative explanation.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous measurements, a bias likely afflicting most young, heavily spotted stars, and which likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
+Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, which imply a best fit filling factor of cool photosphere of $f_{\mathrm{cool}}\sim80$\% at the time of the observation.
+These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of either an extremely heavily spotted star or a hotspot covering $\sim20$\% of the surface.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.
+Biases from starspots likely afflict most young, heavily spotted stars, and likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
 We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
@@
 Approaches like ZDI and line-bisector analysis \citep[\emph{e.g.}][]{prato08, donati14} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.
-In contrast, the technique described in this Section detects and measures the emergent spectrum originating from cool starspots.
+In contrast, the technique described in this Section detects and measures the emergent spectrum originating from patches of cool starspots.
 
@@
 However, a cool ambient photosphere possessing localized hot spots---like plages on the sun---could yield the same or similar two-temperature composite spectrum.
-In principle the physical origin could be assessed with detailed comparision of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.
+In principle, the physical origin could be assessed with detailed comparision of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.
 We made no effort to make such an assessment in this work, and therefore index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.
@@
 The stellar parameters are derived independently in each spectral order.
-Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.
+Spectral orders show differing levels of constraint on the cool photosphere and hot photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.
 The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.
-$K-$band orders show lower estimates for the ambient photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
+$K-$band orders show lower estimates for the hot photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
  \label{fig:TwoTempResults}
@@
 The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
-The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of photosphere with equal areas (50\% filling factor) but different temperatures-- 2800 K and 4100 K for the starspot and ambient photosphere respectively.
+The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of photosphere with equal areas (50\% filling factor) but different temperatures-- 2800 K and 4100 K for the cool and hot photosphere respectively.
 The black-body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.
@@
 
-The IGRINS spectrum demonstrates some features that are present only in the ambient photosphere model, and some features that are present only in the starspot model.
+The IGRINS spectrum demonstrates some features that are present only in the hot photosphere model, and some features that are present only in the cool photosphere model.
 Figure \ref{fig:specPostageStamp} shows a selection of six such spectral features for a range of plausible fill factors.
-In some cases (\emph{e.g.} the top two panels), featureless starspot spectra veil isolated spectral lines predicted in the ambient photosphere models.
-In other cases (\emph{e.g.} the middle row and lower left panel), the ambient photosphere model veils sequences of shallow spectral features predicted in the starspot model.
-The starspot spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening.
-Any feature of interest will be biased to non-zero veiling.
+In some cases (\emph{e.g.} the top two panels), featureless cool photosphere spectra veil isolated spectral lines predicted in the hot photosphere models.
+In other cases (\emph{e.g.} the middle row and lower left panel), the hot photosphere model veils sequences of shallow spectral features predicted in the cool photosphere model.
+The cool spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening; any feature of interest will be biased to non-zero veiling.
 
@@
 One such feature, the OH 1.563 $\mu$m line noted by \citet{oneal01}, shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines.
-The \PHOENIX\ models predict a non-negligible ambient photosphere contribution to the middle line for our range of ambient and spot temperatures.
+The \PHOENIX\ models predict a non-negligible hot photosphere contribution to the middle line for our range of hot and cool temperatures.
 In comparison, the forward-modeling technique described in this work thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.
-The level of veiling of ambient photospheric lines is set by the starspot filling factor and temperature, while the level of veiling of the starspot lines is set by the filling factor and temperature of the ambient photosphere lines.
+The level of veiling of hot photospheric lines is set by the cool photosphere filling factor and temperature, while the level of veiling of the cool lines is set by the filling factor and temperature of the hot photosphere lines.
 Similar forward-modelling strategies have successfully identified patterns of weak metal lines in the line-blanketed spectra of low metallicity stars \citep{kirby11,kirby15}.
@@
 
-Best fit values for the stellar parameters summarized are listed in Table \ref{tbl_adopted_props}.
-Remarkably, the filling factor of starspots exceeds 50\%, with a best fit value of $f_{\mathrm{cool}}=80\pm 5 \% $.
+Best fit values for the stellar parameters are listed in Table \ref{tbl_adopted_props}.
+Remarkably, the filling factor of cool photosphere exceeds 50\%, with a best fit value of $f_{\mathrm{cool}}=80\pm 5 \% $.
 
@@
 In the previous section, we established that the high resolution optical and near-IR spectra of LkCa 4 may be explained by a two-temperature photosphere.
-In this section, we test fit by comparing the combined spectrum to observed spectral features and rotational modulation.
+In this section, we test the two component fit by comparing the combined spectrum to observed spectral features and rotational modulation.
 We adopt the best-fit two temperature model to the IGRINS spectrum, with components of 2750 K covering 80\% of the visible stellar surface and 4100 K covering 20\% of the stellar surface, obtained when LkCa 4 had an estimated brightness of $V=12.84$ mag.
-The starspot and ambient temperatures and the filling factor are blindly adopted without any adjustments to attempt to improve fits to the SED or broadband spectra.
+The cool and hot temperatures and the filling factor are blindly adopted without any adjustments to attempt to improve fits to the SED or broadband spectra.
 
-Figures~\ref{fig:sed}-\ref{fig:lores} compares synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
+Figures~\ref{fig:sed}-\ref{fig:lores} compare synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
 The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum (see \S 5.1-5.2).
@@
 The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
-
-%Furlan:  K7, V-IC=1.92, E(V-I)=1.6 => 0.85 mag;  close enough to their 1.1 mag
-%V-K = 4.18  ; MS colors:  3.16 (KH95) => Av=1.1 mag
-
-%V-J:  2.8-3.8
-%J-K:  0.9-1.0
-
-%\begin{table}
-%\caption{Predicted Photometric Range}
-%\centering
-%\label{tab:photrange}
-%\begin{tabular}{cccc}
-%\hline
-%Band & Low Spot & High Spot & Range\\
-%Cool Spot & 68\% & 83\% &\\
-%\hline
-%\multicolumn{4}{c}{Based on $V$, need to adapt for $A_V$}\\
-%$B$ & 13.80 & 14.48 & 0.68\\
-%$V$ & 12.56 & 13.23 & 0.67\\
-%$R$ & 11.53 & 12.17 & 0.64 \\
-%$I$ & 10.80 & 11.38 & 0.58\\
-%$J$ & 9.79 & 10.00 & 0.21\\
-%$K$ & 8.89 & 9.04 & 0.15\\
-%\hline
-%\end{tabular}
-%\end{table}
 
@@
 
-In this paper, we have demonstrated that IGRINS spectra of LkCa 4 is well modeled with two temperatures, an ambient photosphere of 4100 K and large cool spots of 2700--3000 K that cover 80\% of the stellar surface.
+In this paper, we have demonstrated that IGRINS spectra of LkCa 4 is well modeled with two temperatures, a hot photosphere of 4100 K and large cool patches of 2700--3000 K that cover 80\% of the stellar surface.
 This solution reproduces the high-resolution HK spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.
@@
 To estimate the total area and mean temperature of the spots in the visible stellar hemisphere Grankin used a simple non-parametric model for analysis of V410 Tau, V819 Tau, V827 Tau, and V830 Tau \citep{grankin98,grankin99}.
-For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the spots is $500-1400$ K lower than the ambient photosphere.
+For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the cool regions is $500-1400$ K lower than the ambient photosphere.
 An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
@@
 Besides the high amplitude of variability, these objects show the phenomenon of long-term stability of a brightness minimum in the interval from 5 to 19 years.
-To all appearances, this group of stars has the similar nature of stellar activity which should be investigated in the future.
-%The stars all have similar optical spectral types \citep[e.g.][]{kenyon95,herczeg14}.
 
-%The number of WTTS for which the areal filling factor of spots have been measured is relatively low.  
-%Recently there have been many new estimates.
-
-% Grankin
-
-% Covey
 The Pleiades serves as an older age sample of young stars possessing evidence for large coverage fraction of starspots.
@@
 The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.
-
-% Venuti
 
@@
 In reality, starspots are probably described by a range of spot temperatures analogous to umbra, penumbra, and plages on the solar surface.
-A model possessing three unique temperatures and two unique fill factors might better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
-The fit-quality of the existing two-temperature fits seems fairly strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
+A model possessing three unique temperatures and two unique fill factors would better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
+The fit-quality of the existing two-temperature fits seems strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
 Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.
@@
 \section{Conclusions}
-This paper establishes that the optical+near-IR spectrum of the weak-lined T Tauri star LkCa 4 includes multiple components.
-When fit with two temperatures, the ambient photosphere of 4100 K covers 20\% of the stellar surface while the cool spot of 2700--3000 K covers 80\% of the stellar surface.
-The previously-established $V$-band brightness variability of $0.8$ mag is interpreted as the rotational modulation of the covering fraction of the hot spot.
+This paper establishes that the optical and near-IR spectra of the weak-lined T Tauri star LkCa 4 include multiple components.
+When fit with two temperatures, the hot photosphere of 4100 K covers 20\% of the stellar surface while the cool photospheric component of 2700--3000 K covers 80\% of the stellar surface.
+The previously-established $V$-band brightness variability of $0.8$ mag is interpreted as the rotational modulation of the covering fraction of the hot photospheric component.
 This spectral modelling leads to an improved effective temperature measurement of LkCa 4.

### 2016-12-07 document/submission/ms.tex
put in caveats about effective temperature and photospheric temperature, change some language regarding the indexing

@@
 
-We took two approaches to characterizing the effective temperature response from a spotted-star spectrum.
+We took two approaches to characterizing the photospheric temperature from a spotted-star spectrum.
 
@@
 The forward model includes calibration parameters, line spread functions, and a Gaussian process noise model to account for correlations in the residual spectrum.
-We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which span a wide range of wavelengths at high spectral resolution with a sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.
+We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which span a wide range of wavelengths at high spectral resolution with a sampling of 100 K in stellar photospheric temperature\footnote{Single component \PHOENIX\ photospheres are indexed by the label ``effective temperature'', or $\teff$, which presupposes that the emergent spectrum is comprised of only a single photospheric component.
+In this work we avoid labeling the photospheric components by $\teff$, and instead refer to them as simply ``photospheric temperatures''.} in our range of interest \citep{husser13}.
 The modular framework was altered to accommodate starspot measurements in two ways.
-First, the single photospheric component was updated to include a starspot spectrum.
-Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added by the starspot model.
+First, the single photospheric component was updated to include a two photospheric components.
+Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added by the two component model.
 
@@
 Fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
-The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and $\teff \in [3500, 4200]$.
+The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and photospheric temperatures $\in [3500, 4200]$.
 
@@
 Overall the 26 sets of point estimates for stellar parameters show relatively good agreement, with exceptions.
-The best-fitting spectral orders show effective temperature point estimates in the range $\teff=4000\pm130$ K.
-Figure \ref{fig:SingleTeffvsOrder} displays the $\teff$ point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each spectral order.
+The best-fitting spectral orders show photospheric temperature point estimates in the range $4000\pm130$ K.
+Figure \ref{fig:SingleTeffvsOrder} displays the point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each spectral order.
 
@@
 We find a larger dispersion in the point estimates for the stellar parameters derived from the IGRINS data than those derived in optical.
-The most conspicuous trend is in the derived effective temperature as a function of wavelength shown in Figure \ref{fig:SingleTeffvsOrder}.
-The effective temperature peaks at values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
-The $K-$band shows even lower derived effective temperatures of $\sim3300$ K, or 700 K cooler than estimated from optical.
+The most conspicuous trend is in the derived photospheric temperature as a function of wavelength shown in Figure \ref{fig:SingleTeffvsOrder}.
+The photospheric temperature peaks at values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
+The $K-$band shows even lower derived photospheric temperatures of $\sim3300$ K, or 700 K cooler than estimated from optical.
 No single temperature can describe all the spectral lines present in the high resolution optical and IR spectra.
 Sources with such discrepancies have been seen previously, for example in Figures 4 and 5 in \citet{bouvier92}.
-  These discrepancies are circumstantial evidence for the detection of spectral features attributable to starspots.
+These discrepancies are circumstantial evidence for the detection of spectral features attributable to a second photospheric component.
 
@@
 The measured effective temperature and luminosity from this paper, based on the two-component fit and a median $V$-band magnitude, corresponds to the black asterisk.
-The yellow shaded region corresponds to the range of apparent effective temperatures that are would be measured as the hot component rotates into and out of our view.
+The yellow shaded region corresponds to the range of apparent effective temperatures that would be measured as the hot component rotates into and out of our view.
 The blue circle corresponds to the measurement at blue-optical wavelengths by \citet{donati14}, the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to]{herczeg14}, while the red diamond corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
@@
 \begin{equation}
-T_{\rm eff}=[T_{\rm amb}^4(1-f_{\mathrm{cool}})+T_{spot}^4f_{\mathrm{cool}}]^{0.25}.
+T_{\rm eff}=[T_{\rm hot}^4(1-f_{\mathrm{cool}})+T_{\mathrm{cool}}^4 f_{\mathrm{cool}}]^{0.25}.
 \end{equation}
@@
 For LkCa 4, the $K$-band temperature  is closest to the effective temperature of the entire photosphere.
-These discrepancies may also explain the large temperature, systematic offsets identified when comparing temperatures from $H$-band APOGEE \footnote{The APOGEE spectra have a long wavelength cutoff at 1.70 $\mu$m, just short of an IGRINS ``sweet spot'' from $17075-17990 \;\AA$ (orders 100, 101, and 104), which have conspicuous hot and cool features, is far-enough away from the $K-$band where problems like magnetic field-sensitive lines, enhanced telluric absorption, and veiling by disks may complicate the spectra.} spectra to those obtained from other (usually optical) methods \citep{cottaar14}.
+These discrepancies may also explain the large temperature, systematic offsets identified when comparing temperatures from $H$-band APOGEE spectra to those obtained from other (usually optical) methods \citep{cottaar14}.
+Two component photopheres would also explain deriving different spectral types in the optical and infrared for the same source.
 On the other hand, GAIA-ESO spectra \citep{frasca15} cover only a narrow wavelength around H$\alpha$ and would yield an effective temperature of $\sim 4000$ K.

### 2016-12-07 document/submission/ms.tex
Massive reduction in statistical jargon, as recommended by the anonymous referee.  Almost all detail about the MCMC sampling has been deleted.

@@
 In principle, the physical origin could be assessed with detailed comparision of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.
-We made no effort to make such an assessment in this work, and therefore index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.
+For now we index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.
 
@@
 The two component mixture model includes two more free parameters than the standard \iancze\ model, namely $\teffb$ and $f_{\mathrm{cool}}$.
-The addition of these two parameters makes the MCMC sampling much more correlated than it was before because the relative contribution of the two photospheric components are nearly degenerate over small changes in $\teffa$, $\teffb$, and $f_{\mathrm{cool}}$.
-This challenge motivated the second important change to the spectral inference framework, which involves technical aspects of switching from sampling the nuisance and stellar parameters separately in a blocked Gibbs framework to ensemble sampling using \texttt{emcee} \citep{foreman13}.
-The affine-invariant \texttt{emcee} ensemble sampler is more resilient to correlations among stellar temperatures and fill factor than the Metropolis-Hastings sampler used in Gibbs sampling \citep{foreman13}.
+The addition of these two parameters makes the MCMC sampling much more correlated than it was for single component models.
+This challenge motivated a second technical change to the spectral inference framework, switching from Gibbs sampling (\emph{c.f.} \iancze) to ensemble sampling using \texttt{emcee} \citep{foreman13}.
 The practical effect of this switch is that all 14 stellar and nuisance parameters are fit simultaneously in a single spectral order, making stellar parameter estimates $\vt_{o}$ unique for each spectral order $o$, whereas the \iancze\ strategy had the power to provide a single set of stellar parameters $\vt$ that was based on all $N_{\rm ord}$ spectral orders.
-The $N_{\rm ord}$ sets of inferences on $\vt_{o}$ are combined by weighted averaging point estimates of results from reliable orders, which offers resilience to flagrant calibration artifacts or conspicuous model mismatches.
-This process can be thought of as a coarse approximation to the much more sophisticated spectral line outlier rejection described in \iancze.
-No attempt was made to downweight spectral-line outliers using local kernels.
 
-This two-temperature mixture model for starspots requires single stars, or at least double stars with extremely large (>100) luminosity ratios or wide separations.
+Interpreting the two two-temperature mixture model as arising from the same photosphere requires single stars, or at least double stars with extremely large (>100) luminosity ratios or wide separations.
 Unresolved single-lined or double-lined binaries could mimic a signal that would be misattributed to starspots.
 As pointed out earlier, LkCa 4 has no detected companion from direct imaging, and its RV variations are consistent with starspot modulation, so any binary companion would have to have exceptionally large luminosity or mass ratios, rendering it undetectable with our spectral inference methodology with the finite signal to noise available in the IGRINS data.
-The absence of a detectable disk around LkCa 4
-LkCa 4 means that the spectral modeling requires no further parameters like veiling or accretion.
+The absence of a detectable disk around LkCa 4 means that the spectral modeling requires no further parameters like veiling or accretion.
 
@@
 We performed spectral fitting on an ESPaDOnS spectrum acquired on 2014 January 11.
-The spectrum was split into subsets of $N=35$ chunks, corresponding approximately to spectral order boundaries.
-Fitting was performed separately on each of 35 spectral orders following the Metropolis-Hasting MCMC sampling procedure described in \iancze.
-The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and photospheric temperatures $\in [3500, 4200]$.
+The spectrum was split into subsets of $N=26$ chunks, corresponding approximately to spectral order boundaries.
+Fitting was performed separately on each spectral chunk.
+The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and photospheric temperatures $\in [3500, 4200]$ K.
 
-The Metropolis-Hastings step sizes were tuned with several iterations of burn-in procedure and the final chains were visually checked for convergence, dropping 9 orders that failed to converge for numerical reasons.
-We computed the median value and 5$^{th}$ and $95^{th}$ percentiles of burned-in subsets of the MCMC samples described above.
-Overall the 26 sets of point estimates for stellar parameters show relatively good agreement, with exceptions.
-The best-fitting spectral orders show photospheric temperature point estimates in the range $4000\pm130$ K.
-Figure \ref{fig:SingleTeffvsOrder} displays the point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each spectral order.
+Standard MCMC convergence criteria were assessed.
+Typical spectral chunks show photospheric temperature point estimates in the range $4000\pm130$ K.
+Figure \ref{fig:SingleTeffvsOrder} displays the point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each spectral chunk.
+The spectral chunk from 8473$-$8707 \AA\ was an outlier, showing an estimated photospheric temperature of $\sim3500$ K.
 
@@
 We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
-For the IGRINS $K-$band, we employed an expanded search range for the temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.
+For the IGRINS $K-$band, we employed an expanded search range for the photosperic temperature, $\teff \in [3000, 4200]$ K.
 
@@
 We applied the mixture model as described in Section \ref{sec:methods} and Appendix \ref{methods-details}.
-The MCMC samples generally had 5000 steps with 40 walkers.
-The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the \PHOENIX\ model spectrum temperature range\footnote{The \PHOENIX\ model spectra are indexed by $\teff$, but this term carries a different meaning for spotted stars than non-spotted stars.} was $\teffa, \teffb \in [2700, 4500]$.
+Standard MCMC convergence tests were evaluated.
+The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the \PHOENIX\ model spectrum temperature range\footnote{The \PHOENIX\ model spectra are indexed by $\teff$, but this term carries a different meaning for two-component photospheres.} was $\teffa, \teffb \in [2700, 4500]$.
 $H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$ km/s.
-The MCMC chains all appeared to converge after about 1500 steps.
 
-Marginalized distributions are computed for all 14 stellar and nuisance parameters by selecting the final 200 $\times$ 40 walkers = 8000 samples, and point estimates were obtained by computing the median, $5^{th}$ and $95^{th}$ percentiles of the marginal distributions.
 The fit quality is first assessed by examining the consistency of the point estimates of $v_z$ and $\vsini$ across the spectral orders.
@@
 Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders perform better than others in assessing stellar properties.
-This model comparison is performed by sorting the 8000 samples by their fill factor estimates and examining random draws of the cool spectrum, hot spectrum, and composite spectrum, excluding the Gaussian process coveriance and white noise steps.
-Fitting defects were conspicuous.
+When present, fitting defects were conspicuous.
 Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, are all excluded from our final stellar parameter compilation.
-Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.
+Notably, several orders in $K-$band were rejected due to overfitting of orders possessing deep metal lines.
 For example, orders 79 and 81 overfit Ca~I and Na~I lines and orders $74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
-These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \citep{johnskrull07,deen13}.
-Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.
-The remaining orders are rerelatively devoid of spectral line outliers and include the most information rich portion of the spectrum.
+These and other metal lines can also be biased by Zeeman broadening, which could explain poorer fit quality with wavelength \citep{johnskrull07,deen13}.
+Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were discarded.
+The remaining orders are relatively devoid of spectral line outliers and include the most information rich portion of the spectrum.
 

### 2016-12-08 document/submission/ms.tex
Working on Issue #53-- on to the vsini discussion.

@@
 
-% Theory of starspots
-% Jackson \& Jeffries 2014ab needs to go somewhere.
-
-Starspots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep[\emph{e.g}][]{harrison11,davenport15}.
+Rotational modulation from starspots has been understood as the cause of cyclic variations in weak-lined T Tauri stars (WTTSs) and some classical T Tauri stars \citep{vrba86,herbst94}.
+Spots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep[\emph{e.g}][]{harrison11,davenport15}.
 The single band light curves from such surveys cannot separate the relative areas and temperatures of the emitting regions, and therefore cannot yield estimates for the filling factor of spots without making assumptions about the relative temperature contrast.
-Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{petrov94,bouvier95,grankin07,cody14} can break the degeneracy between starspot filling factor and starspot temperature but these measurements are still limited to detecting large longitudinally asymmetric starspots.
+Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{herbst94,petrov94,bouvier95,grankin07,cody14} can break the degeneracy between starspot filling factor and starspot temperature but these measurements are still limited to detecting large longitudinally asymmetric starspots.
 Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups, but the number of such transiting systems and demands of high photometric precision limit wider application.
@@
 Spectroscopic strategies have the power to measure both the starspot areal coverage and temperature in any geometric configuration.
-For weak-lined T Tauri stars (WTTSs), SED modeling \citep{wolk96} indicated the presence of cool spots, while \citet{grankin98} and \citet{venuti15} estimated spot temperature and coverage from rotational modulation of optical colors.
+For WTTSs, SED modeling \citep{wolk96} indicated the presence of cool spots, while \citet{grankin98} and \citet{venuti15} estimated spot temperature and coverage from rotational modulation of optical colors.
 The TiO bands in optical spectra have been used to measure spots on WTTSs \citep{petrov94}, stars in the Pleiades \citep{fang2016}, and evolved stars \citep[e.g.][]{neff95,oneal01,oneal04}.
@@
 
-Several WTTS in the Taurus-Auriga star-forming region have large amplitudes in periodic light variations, achieving $0.4-0.8$ mag in the $V-$band: LkCa 4, V410 Tau, LkCa 7, V827 Tau, V830 Tau, and V819 Tau \citep{grankin08}.
-In a sample that is not biased to variable stars,
-WTTSs observed in NGC 2264 show photometric variations similar to--but of lower average amplitude than-- LkCa 4 \citep{cody14,venuti15}.
+Several WTTS in the Taurus-Auriga star-forming region have large amplitudes in periodic light variations, achieving $0.4-0.8$ mag in the $V-$band: LkCa 4, V410 Tau \citep{herbst89}, LkCa 7, V827 Tau, V830 Tau, and V819 Tau \citep{grankin08}.
+In a sample that is not biased to variable stars, WTTSs observed in NGC 2264 show photometric variations similar to--but of lower average amplitude than-- LkCa 4 \citep{cody14,venuti15}.
 Modeling of polychromatic photometric monitoring of the locus of WTTSs indicates a lower limit to the true coverage fraction $f_{\mathrm{eq}}\sim10-30\%$ and a difference $\teffa-\teffb\sim500$ K.
@@
 
-%\todo{Verify that the final term possesses a $q$ and not a $q^2$ term.}
-
 \section{Further examples of full spectrum fitting}

### 2017-01-03 document/submission/ms.tex
GJH comments, changes bolded

@@
 We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
-Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, which imply a best fit filling factor of cool photosphere of $f_{\mathrm{cool}}\sim80$\% at the time of the observation.
-These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of either an extremely heavily spotted star or a hotspot covering $\sim20$\% of the surface.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.
-Biases from starspots likely afflict most young, heavily spotted stars, and likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
-We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
+Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, {\bf with a best-fit filling factor of $\sim80$\%  for the cool photosphere at the time of the observation.} {\bf These results are supported by comparisons of this mix of hot and cool photospheric temperatures by analyses of the spectral energy distribution, rotational modulation of colors and of TiO band strengths, and low-resolution optical/near-IR spectroscopy.
+LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.}  The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.
+Biases from starspots likely afflict most {\bf fully convective} young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
+We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra, {\bf and anti-correlations expected in the velocity jitter of the warm and cool components.
+I put this in cause I think it's interesting, but delete if you do not want to highlight this in the abstract.}
 
@@
 
-The causes of global age uncertainties and of large luminosity spreads in individual clusters are controversial.
-Observationally, \citet{hartmann01} and \citet{slesnick08} argue that measurement uncertainties may mask any real differences in ages within a cluster.
-In models, \citet{hartmann97} and \citet{baraffe09} describe how variable accretion histories change the stellar contraction and hence luminosities at early times.
-Contraction rates also depend on the interior stellar structure and convective efficiency.
+{\bf The causes of age uncertainties and of large luminosity spreads in young clusters are controversial \citep[see reviews by][]{preibisch12,soderblom14}.
+Absolute ages are usually inferred from comparisons between observed stellar properties and pre-main sequence evolutionary models, which are sensitive to stellar birthlines and the input physics that controls the contraction and internal heating.
+Within clusters, any real differences in ages between stars may be masked by observational uncertainties in temperature and luminosity measurements \citep[e.g.][]{hartmann01,slesnick08}.}
 
@@
 Evolutionary models are just now starting to implement prescriptions for how spots and magnetic fields affect the interior structure \citep{macdonald13,jackson14a,somers15,feiden16}.
-Stellar evolution models that includes these effects can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr, with standard mass estimates being biased towards lower masses.
+Stellar evolution models that include these effects can make a coeval 10 Myr population exhibit apparent age spreads of 3$-$10 Myr.
+Mass estimates may also be biased to lower masses, as measured for some eclipsing binaries \citep[e.g.][]{stassun14,rizzuto16}.
 Observationally, starspots may also be responsible for biases in stellar effective temperatures derived by different methods.
@@
 
-Rotational modulation from starspots has been understood as the cause of cyclic variations in weak-lined T Tauri stars (WTTSs) and some classical T Tauri stars \citep{vrba86,herbst94}.
+Rotational modulation from starspots is understood as the cause of cyclic variations in weak-lined T Tauri stars (WTTSs) and some classical T Tauri stars \citep[e.g.][]{vrba86,herbst94}.
 Spots have recently been observed with exceptional photometric precision from monitoring surveys targeting exoplanet transits \citep[\emph{e.g}][]{harrison11,davenport15}.
@@
 Zeeman Doppler Imaging \citep[ZDI]{donati14} produces the latitudinal and longitudinal distribution of starspots in reconstructed brightness maps based on models for spectro-polarimetric line shapes, but would be unable to identify uniform distributions of small spots.
-All of these techniques would tend to underestimate the starspot areal coverage on stars with an isotropic distribution of small starspots, or pole-on stars or stars with longitudinally symmetric bands of starspots.
+All of these techniques would tend to underestimate the fractional coverage of starspots distributed isotropically on the surface, stars viewed pole-on, or stars with longitudinally symmetric bands of starspots.
 
 Spectroscopic strategies have the power to measure both the starspot areal coverage and temperature in any geometric configuration.
-For WTTSs, SED modeling \citep{wolk96} indicated the presence of cool spots, while \citet{grankin98} and \citet{venuti15} estimated spot temperature and coverage from rotational modulation of optical colors.
+For WTTSs, SED modeling indicated the presence of cool spots \citep{wolk96}, while spot temperatures have been estimated from rotational modulation of optical colors \citep[e.g.][]{grankin98,venuti15,koen16}.
 The TiO bands in optical spectra have been used to measure spots on WTTSs \citep{petrov94}, stars in the Pleiades \citep{fang2016}, and evolved stars \citep[e.g.][]{neff95,oneal01,oneal04}.
@@
 
-The WTTS LkCa 4 \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15} and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
-LkCa 4 has no evidence for a close companion from both direct imaging searches\citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}} and RV searches \citep{nguyen12,donati14}.
+The star LkCa 4, a WTTS member of the Taurus Molecular Cloud \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15} and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
+LkCa 4 has no evidence for a close companion from either direct imaging searches \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}} or from RV searches \citep{nguyen12,donati14}.
 This single star demonstrates a large amplitude of sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}.
-The variability amplitude cannot arise from eclipsing binarity, since the large RV variations would have been seen in spectroscopic monitoring.
-All of these observations indicate that the spectrum of \name should be devoid of complicating factors like near-IR excess veiling, accretion excess, or close binaries.
+The variability amplitude cannot arise from an eclipsing binary, since the large RV variations would have been seen in spectroscopic monitoring.
+All of these observations indicate that the spectrum of \name should be devoid of complicating factors like near-IR excess veiling, accretion excess, or close binarity.
 
@@
 
-In this work, we measure the starspot properties of LkCa 4 with four complementary techniques.
-Section \ref{sec:obs} quantifies the optical variability of LkCa 4 over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
-Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution $H$ and $K$ near-IR spectrum of LkCa 4 in Section \ref{sec:two_tempIGRINS}.
+In this work, we measure the starspot properties of LkCa 4 with four complementary techniques.  Section \ref{sec:obs} describes the full spectroscopic and photometric dataset and 
+quantifies the optical variability of LkCa 4 over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
+Section 3 and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution $H$ and $K$ near-IR spectrum of LkCa 4 in Section \ref{sec:two_tempIGRINS}.
 Section \ref{sec:GJHsection4} shows results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.
-All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of LkCa 4, and what can be understood about pre-MS stellar evolution from this exemplar.
+All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of LkCa 4.
+{\bf Section 5 describes how the two-temperature fit affects the placement of LkCa 4 on the HR diagram and what can be understood about pre-main sequence stellar evolution from this exemplar.
+Finally, Section 6 describes how our results should be interpreted, the implications for analyses of spots in high-resolution spectra, and methodological limitations.}
 
@@
 LkCa 4 shows secular changess in its light curve morphology.
-The IGRINS spectrum was acquired near the median flux level, not the extrema.}
+The IGRINS spectrum was acquired near the median flux level of the season.}
  \label{fig:PhotPhase}
@@
 
-An archive of 1216 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
+Photometry in $B$, $V$, and/or $R$-bands in 1216 distinct epochs was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.
 Published data targeting \name is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.
@@
  \includegraphics[width=0.48\textwidth]{single_Teff_v_order}
- \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.
-The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.
-The increasing flux density from the cool photospheric component compared to the flux from hot photospheric components can explain the observed trend in derived photospheric temperature.}
+ \caption{Top panel:  the best-fit temperature measured from our full spectrum fitting to each of 58 spectral orders in the optical and infrared portions of the spectrum,  assuming a single component photosphere.
+The best-fit temperature measured in the $K-$band is about 800 K lower than that derived in optical.
+Bottom panel:  The flux ratio between the cool and hot components increases to the near-IR, which explains the observed trend in the best-fit temperature.}
  \label{fig:SingleTeffvsOrder}
@@
 Approaches like ZDI and line-bisector analysis \citep[\emph{e.g.}][]{prato08, donati14} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.
-In contrast, the technique described in this Section detects and measures the emergent spectrum originating from patches of cool starspots.
+In contrast, the technique described in this Section measures the spectrum that emerges from {\bf both the hot and the cool surfaces of the photosphere.}
 
-Starspot line depth ratio analysis has traditionally been limited to isolated portions of spectrum that possess spectral lines attributable only to cool photospheric components and spectral lines arising from the warmer ambient photosphere \citep[\emph{e.g.}][]{neff95, oneal01}.
+Starspot line depth ratio analysis has traditionally been limited to isolated portions of spectrum that possess absorption lines attributable only to cool photospheric components and spectral lines arising from the warmer ambient photosphere \citep[\emph{e.g.}][]{neff95, oneal01}.
 The apparent veiling of the lines and their respective temperature dependences can be combined to solve for the cool photosphere and ambient photosphere temperatures and relative areal coverages.
@@
 
-We took two approaches to characterizing the photospheric temperature from a spotted-star spectrum.
-
-Using the spectral fitting approach introduced in Section 3.1 \ref{sec:methods}, we first first separately fit the optical (ESPaDOnS) and near-IR (IGRINS) spectra with distinct, single photospheric component models; these fits are described in Sections \ref{sec:ESP_starfish} and \ref{sec:IGR_starfish} respectively.
-We then use a two temperature mixture model to perform a fit to the near-IR spectra in Section \ref{sec:two_tempIGRINS}.
+We took two approaches to characterizing the photospheric temperature from a spotted-star spectrum.  First, 
+using the spectral fitting approach introduced in Section 3.1 \ref{sec:methods}, we separately fit the optical (ESPaDOnS) and near-IR (IGRINS) spectra with distinct, single photospheric component models; these fits are described in Sections \ref{sec:ESP_starfish} and \ref{sec:IGR_starfish} respectively, and then compared in \ref{sec:whyNearIR}.
+Second, we use a two temperature mixture model to perform a fit to the near-IR spectra in Section \ref{sec:two_tempIGRINS}.
 The near-IR spectral range is preferred over the optical, since the cool photosphere emits most of its flux in the near-IR, enhancing the likelihood of direct detection of emission from the cool component.
@@
 The modular framework was altered to accommodate starspot measurements in two ways.
-First, the single photospheric component was updated to include a two photospheric components.
+First, the single photospheric component was updated to include two photospheric components.
 Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added by the two component model.
@@
 The stellar photosphere is characterized as two photospheric components with a cool photosphere temperature $\teffb$ and hot photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$, respectively\footnote{For flux calibrated spectra, the total solid angle $\Omega$ can be constrained, but for typical echelle spectrographs only relative values of $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$ can be inferred.}.
-
 The choice of nomenclature depends on the physical origin of the emission region.
@@
 
-Interpreting the two two-temperature mixture model as arising from the same photosphere requires single stars, or at least double stars with extremely large (>100) luminosity ratios or wide separations.
+Interpreting the two-temperature mixture model as arising from the same photosphere requires single stars, or at least double stars with extremely large (>100) luminosity ratios or wide separations.
 Unresolved single-lined or double-lined binaries could mimic a signal that would be misattributed to starspots.
@@
 
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_04} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_01} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_05} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_06} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_02} 
+ \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_03} 
+ \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).
+The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
+The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no attention to magnetic field, which may bias estimates of $\teffa$ and/or $f_{\mathrm{cool}}$ for individual spectral orders.}
+ \label{fig:specPostageStamp}
+\end{figure*}
+
 \subsection{Single temperature fitting to the ESPaDOnS spectrum}\label{sec:ESP_starfish}
 
-We performed spectral fitting on an ESPaDOnS spectrum acquired on 2014 January 11.
+We performed spectral fitting on an ESPaDOnS spectrum acquired on 2014 January 11 (JD 2456668.9).
 The spectrum was split into subsets of $N=26$ chunks, corresponding approximately to spectral order boundaries.
@@
 We selected a subset of 32 of the 54 available IGRINS spectral orders\footnote{The prohibitive computational cost limited us from running all the spectral orders.} with low telluric absorption artifacts.
-We performed full-spectrum fitting, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order.
+We performed unique spectral fitting on each order, with free stellar parameters $\vt = (\teff, \logg, \Z)$.
 We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
@@
 
-We find a larger dispersion in the point estimates for the stellar parameters derived from the IGRINS data than those derived in optical.
+We find a larger dispersion in the point estimates for the stellar parameters derived from the IGRINS data than those derived in the optical spectrum.
 The most conspicuous trend is in the derived photospheric temperature as a function of wavelength shown in Figure \ref{fig:SingleTeffvsOrder}.
-The photospheric temperature peaks at values of $\sim4200$K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
+The photospheric temperature peaks at values of $\sim4200$~K in the short wavelength end of $H-$band and saturates at $<3500$ K at the long wavelength end of $H-$band.
 The $K-$band shows even lower derived photospheric temperatures of $\sim3300$ K, or 700 K cooler than estimated from optical.
@@
 
-\subsection{Heightened sensitivity to starspot spectral lines in the infrared}\label{sec:whyNearIR}
-
-\begin{figure*}
- \centering
- \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_04} 
- \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_01} 
- \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_05} 
- \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_06} 
- \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_02} 
- \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_03} 
- \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).
-The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.
-The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\mathrm{cool}}$ for individual spectral orders.}
- \label{fig:specPostageStamp}
-\end{figure*}
-
 \begin{figure*}
@@
  \includegraphics[width=0.95\textwidth]{violin_Teff_fill_order} 
- \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\mathrm{cool}}$ (yellow shade).
+ \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade in the top panel), $\teffb$ (red shade, top), and fill factor $f_{\mathrm{cool}}$ (yellow shade, bottom).
 The stellar parameters are derived independently in each spectral order.
-Spectral orders show differing levels of constraint on the cool photosphere and hot photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.
+Spectral orders show differing levels of constraint on the cool photosphere and hot photosphere properties, including some orders ($o=104, 102, 100, 88, 83$) that yield especially tight cool spot filling factors.
 The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.
-$K-$band orders show lower estimates for the hot photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
+Many of the $K-$band orders that show lower estimates for the hot photosphere are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
  \label{fig:TwoTempResults}
@@
 
+\subsection{Heightened sensitivity to starspot spectral lines in the infrared}\label{sec:whyNearIR}
+
+{\bf reordered to place main result first}
+
+The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
+Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission.
+The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptotically approaching a fixed value on the Rayleigh-Jeans tail \citep{wolk96}.
+The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of 2800 K and 4100 K photospheres with equal areas (50\% filling factor).
+The black-body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.
+The visible portion of the spectrum will be dominated by the warm patches.
+The infrared spectrum will have a lower overall spot contrast, and will have more net starspot flux than optical.
+
 Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.
-The particular ESPaDOnS spectrum used in Section \ref{sec:ESP_starfish} has an estimated $V-$band magnitude of 12.90 while the IGRINS spectrum has 12.83.
+The particular ESPaDOnS spectrum used in Section \ref{sec:ESP_starfish} was obtained when LkCa 4 ahd an estimated $V-$band brightness of 12.94 mag, compared with 12.84 mag at the time of the IGRINS spectrum.
 The fainter magnitude during the ESPaDOnS spectrum acquisition implies a greater coverage fraction than during the IGRINS spectrum.
@@
 
-The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
-Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission.
-The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptoting to a fixed value in the Rayleigh-Jeans tail \citep{wolk96}.
-The bottom panel of Figure \ref{fig:SingleTeffvsOrder} shows the flux density ratio for patches of photosphere with equal areas (50\% filling factor) but different temperatures-- 2800 K and 4100 K for the cool and hot photosphere respectively.
-The black-body ratios predict smooth flux ratio increases with wavelength, while the ratio of \PHOENIX\ models shows wavelength regions with heightened sensitivity to starspot fluxes, for example in $J-$band.
-
-In summary, the visible portion of the spectrum will be dominated by the warm patches.
-The infrared spectrum will have a lower overall spot contrast, and will have more net starspot flux than optical.
+\input{tbl_best_fit.tex}[!b]
 
@@
 Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders perform better than others in assessing stellar properties.
-When present, fitting defects were conspicuous.
 Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, are all excluded from our final stellar parameter compilation.
-Notably, several orders in $K-$band were rejected due to overfitting of orders possessing deep metal lines.
-For example, orders 79 and 81 overfit Ca~I and Na~I lines and orders $74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
+Several orders in $K-$band were rejected due to poor spectral fits influenced by deep metal lines.
+For example, orders 79 and 81 {\bf I'm not really sure what {\it overfit} means} overfit Ca~I and Na~I lines and orders $74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
 These and other metal lines can also be biased by Zeeman broadening, which could explain poorer fit quality with wavelength \citep{johnskrull07,deen13}.
@@
 The combination of line blanketing and high $\vsini$ has probably hampered efforts to identify isolated spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.
-One such feature, the OH 1.563 $\mu$m line noted by \citet{oneal01}, shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines.
+One such feature, the OH 1.563 $\mu$m line analyzed by \citet{oneal01}, shows a clear pattern of 3 lines in our data, with the central line exceeding the depth of the adjacent two lines.
 The \PHOENIX\ models predict a non-negligible hot photosphere contribution to the middle line for our range of hot and cool temperatures.
@@
 
-\input{tbl_best_fit.tex}
-
 \section{The Two Temperature Fit to the SED and Stellar Rotation}\label{sec:GJHsection4}
@@
  \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{phot_2750}
-\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
+\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black), scaled to $A_V=0.3$ and $\log L/L_\odot=0.20$ at the epoch of the 2MASS observation (see \S 5n).}
 \label{fig:sed}
@@
  \centering
- \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{lores_panels_2750k}
- \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
+ \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{lores_panels_paper_new}
+ \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (4100 K with 20\% fill factor and 2750 K with 80\% fill factor, reddened by $A_V=0.3$ mag; purple lines), a 3900 K spectrum reddened by 1.3 mag (blue lines), and a 3500 K spectrum with no reddening.
+All synthetic spectra are fit to the $J$-band spectrum of LkCa 4.
+The observations in gray and the single temperature photospheres are scaled by factors of 3 and 9 for visual purposes.
+ Bottom:  Same as the top panel, but the synthetic spectra are 
+scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
+Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.
+Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
+The two temperature photosphere accurately fits spectral features in both optical and near-IR wavelengths.}
+ \label{fig:lores}
+\end{figure*}
+
+%\caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
 The inset shows that the 2750 K (red, 80\% fill factor) and 4100 K (blue, 20\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.
-The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum.
+The synthetic spectrum is reddened by $A_V=0.3$ mag and scaled to the observed $J$-band spectrum.
 Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere (red), and the two temperature photosphere (pink) that best fits the IGRINS spectrum.
@@
 Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
-The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
- \label{fig:lores}
-\end{figure*}
+The two temperature photosphere accurately fits spectral features in both optical and near-IR wavelengths.}
 
@@
 \caption{The constraint on the size and temperature of the cool spot from the H$_2$O absorption band depth between $J$ and $H$-bands.
-The contours show the flux ratio between 1.30 and 1.34 $\mu$m (shaded yellow region in inset plot), as produced by the Phoenix models.
-The solid and hatched purple lines show the best fit and range of acceptable contours from the APO/TripleSpec spectrum, which was obtained when the cool spot fraction was $\sim 84$\%.
-The range of acceptable contour is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption.
+The contours show the flux ratio at 1.30 and 1.34 $\mu$m from the Phoenix models.
+Comparisons to the APO/TripleSpec spectrum yield best-fit solutions (solid purple line) and the range of acceptable fits (shaded cyan region, with contours of flux ratio in dashed black lines) for an epoch when  the cool spot fraction was $\sim 84$\%.
+The range of acceptable fits is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption.
 }
@@
 
-Figures~\ref{fig:sed}-\ref{fig:lores} compare synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
-The only free parameters in this comparison are the luminosity and extinction, which are both scaled to match the spectrum (see \S 5.1-5.2).
+Figures~\ref{fig:sed}--\ref{fig:lores} compare synthetic spectra from the two-component photosphere to the SED and flux-calibrated spectra of LkCa 4.
+The only free parameters in this comparison, the luminosity and extinction, are both scaled to match the spectrum (see \S 5.1-5.2).
 The optical-IR SED is obtained by estimating photometry from \citet{grankin08} during the 2MASS epoch, with $V\sim12.61$ mag (see Table~1).
@@
 The $3500$ K component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
-A two temperature photosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
+The two temperaturephotosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
+{\bf This latter feature is caused by H$_2$O opacity in H$_2$O bands and is only seen when the fraction of emission from the cool component is high (Figure \ref{fig:h2ojump}).}
 
-These spectral features should be rotationally modulated as the filling factors of the hot and cool components change.
+These spectral features should be rotationally modulated as the filling factors of the visible hot and cool components change.
 In \S 4.1, we first use our fit to the IGRINS spectrum to convert the $V$-band brightness to the filling factor of the two components.
@@
  \centering
- \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{vband_spot_2750k}
+ \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{vband_spot_master}
 \caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.
@@
     \end{tabular}
-\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions.
+\caption{The observed optical colors of LkCa 4, mostly from \citet{grankin08}, compared with predictions from the rotation of a two-temperature photosphere model.
 The model is constructed instead by converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{pecaut13} (purple lines).}
@@
 
-The relative contributions from the hot and cool components change as LkCa 4 rotates, leading to rotational modulation of colors.
+The relative contributions from the hot and cool components change as LkCa 4 rotates, leading to color changes.
 We model this rotational modulation using the main sequence colors \citep[compiled by][]{pecaut13}, which should have less contribution from spots than  pre-main sequence colors.
@@
 Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, which is consistent with expectations for a single hot component with no contributions from the cooler component.
-The standard deviation of 0.03 mag in $B-V$ color, which includes a $\sim 0.01$ mag uncertainty in both $V$ and $B$, indicates that the spot temperature is stable to $\lesssim 50$ K.
-The stability of this temperature implies that this hotter component may be the ambient temperature of the photosphere.
+The standard deviation of 0.03 mag in $B-V$ color (which includes a $\sim 0.01$ mag uncertainty in both $V$ and $B$) indicates that the spot temperature is stable to $\lesssim 50$ K over decades.
+The stability of this temperature implies that the hotter component may be the ambient temperature of the photosphere.
 
@@
 Our simple model predicts that the correlation should be much weaker than is measured.
-Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ color could be reproduced with some contribution from intermediate temperature.
+Most likely, our two temperature model for the photosphere is overly simplistic, since the $V-R$ color could be reproduced with some contribution from intermediate temperatures.
 
-Rotational modulation is expected to lead to much smaller brightness changes at near-IR wavelengths, with amplitudes of 0.15--0.2 mag, than the 0.6--0.8 mag amplitudes seen at optical wavelengths.
+Rotational modulation is expected to lead to much smaller brightness changes at near-IR wavelengths, with amplitudes of $0.15-0.2$ mag, than the $0.6-0.8$ mag amplitudes seen at optical wavelengths.
 The smaller amplitude of near-IR brightness is also seen in a few spotted stars in the optical/IR monitoring of NGC 2264 \citep{cody14}, although those stars have a much smaller $V$ band amplitude than LkCa 4.
 
-\subsection{Rotational Modulation of TiO Depth}\label{sec:RotTiO}
+\subsection{Rotational Modulation of TiO Band Depths}\label{sec:RotTiO}
 
@@
  \centering
- \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{lkca4_tio_forpaper}
- \caption{Variability in TiO bands measured with ESPaDOnS.
+ \includegraphics[trim=3.2cm 3.3cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{lkca4_tio_forpaper2}
+ \caption{Variability in TiO bands measured with ESPaDOnS spectra.
+The top panel compares spectra between when LkCa 4 was bright (blue) and faint (red).
 The $V-$band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.
-The bottom left panel shows a correlation between $V-$band magnitude and the TiO-7140 index, while the bottom right shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
+The bottom left and middle panels show correlations between $V-$band magnitude and individual TiO band indices, while the bottom right panel shows a similar correlation with the average of the TiO-6200, CaH-6800, TiO-7140, TiO-7600, and TiO-8500 indices.}
  \label{fig:tiovar}
@@
 
-Both the raw TiO 7140 index and this combined TiO index correlate strongly with the optical brightness.
-In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).
-These results are consistent with expectations from the rotational modulation of the hot spot.
-The TiO bands trace the cool component.
-When the hotter component has a larger filling fraction, the TiO bands are veiled by the hotter component and are therefore not as deep.
+The TiO bands trace the cool component.  When the hotter component has a larger filling fraction, the TiO bands are veiled by the hotter component and should therefore be shallower. As expected, 
+the TiO indices all correlate strongly with the optical brightness.
+{\bf The TiO-7140 band depths are accurately reproduced by varying the two-temperature fit with rotation.
+Other bands have small offsets, likely caused by either contributions from intermediate temperatures or by small errors in the synthetic spectra.}  In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).
 
@@
 
-An accurate extinction estimate from the full SED is challenging because of a strong dependence on the areal distribution of temperatures in the photosphere, which in our work is simplified to a two temperature fit.
+An accurate extinction estimate from the full SED is challenging because of a strong dependence on the  distribution of temperatures in the photosphere, which in our work is simplified to a two temperature fit.
 However, isolating specific colors constrains the possible range of extinctions.
+{\bf Based on the following analysis, an $A_V=0.3$ mag is adopted throughout this paper, although some uncertainty is introduced by confusion in the choice of template colors.}
+
 The $B-V$ color is stable and not affected by cooler components, and may therefore be compared with the expected colors for the hotter (4100 K) temperature.  
@@
 The $B-V$ color 
-excess leads to an extinction $A_V=0.28\pm0.15$ mag, or $0.62\pm0.15$ mag relative to 
+excess leads to an extinction $A_V=0.28\pm0.15$ mag relative to main sequence colors, or $0.62\pm0.15$ mag relative to 
 pre-main sequence colors.   The listed uncertainties are calculated from extinction estimates relative to colors of 4000 and 4200 K photospheres.
@@
 in the main sequence/pre-main sequence temperature scales because the pre-main 
-sequence $J-K$ color is redder at 4100 K and bluer at 2750 K.  Based on this 
-analysis, an $A_V=0.3$ mag is adopted throughout this paper.
+sequence $J-K$ color is redder at 4100 K and bluer at 2750 K.
 
-The near-IR extinctions of LkCa 4, and perhaps other TTSs, will be overestimated if emission is generated from a multi-temperature spectrum but template colors are based on only the hotter component.
-This mismatch likely explains why near-IR extinctions are often higher than optical extinctions for young stars \citep{herczeg14} and IR colors that are often redder than expected from models \citep{tottle15}.
+The near-IR extinction to LkCa 4, and perhaps to other TTSs, will be overestimated if emission is generated from a multi-temperature spectrum but template colors are based on only the hotter component.
+This mismatch likely explains why near-IR extinctions are often higher than optical extinctions for young stars \citep{herczeg14}, IR colors that are often redder than expected from models \citep{tottle15}, and general challenges in near-IR templates of T Tauri stars \citep[e.g.][]{espaillat10,fischer11}.
 For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $0.84$ mag for a 4100 K photosphere and \citet{pecaut13} pre-main sequence colors.
@@
 Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types, if spot coverage is also similar.
-Discrepancies in colors, spectral type/effective temperatures, and extinctions for LkCa 4, and perhaps more broadly for TTSs, are dominated by ignoring spots and are not caused by fundamental problems in either photospheric models or in spectral type-effective temperature scales.
+Discrepancies in colors, spectral type/effective temperatures, and extinctions for LkCa 4, and perhaps more broadly for TTSs, are dominated by ignoring spots and not by spectral type-effective temperature scales.
+{\bf Fundamental problems in molecular opacities and photospheric models are likely important secondary affects.}
 
@@
  \caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.
-The measured effective temperature and luminosity from this paper, based on the two-component fit and a median $V$-band magnitude, corresponds to the black asterisk.
-The yellow shaded region corresponds to the range of apparent effective temperatures that would be measured as the hot component rotates into and out of our view.
-The blue circle corresponds to the measurement at blue-optical wavelengths by \citet{donati14}, the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to]{herczeg14}, while the red diamond corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
+The measured effective temperature and luminosity from this paper, based on the two-component fit and a median $V$-band magnitude, is shown as the black asterisk.
+The yellow shaded region corresponds to the range of apparent effective temperatures that would be measured as the hot component rotates into and out of our view for a cool temperature of 2750 K, while the green shaded region shows the same range for a cool temperature of 3000 K.
+The blue circles correspond to the measurement at blue-optical wavelengths (the large circle and error bar is from \citet{donati14}), the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to TiO bands]{herczeg14}, while the red diamond corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
  \label{fig:hrdiag}
@@
 The spectrum of LkCa 4 is well reproduced by a cool component of $2750$ K covering 80\% of the surface and a $4100$ K component covering 20\% of the surface.
-Scaling this composite spectrum for LkCa 4 to the observed 2MASS photometry ($\sim 74\%$ spot covering fraction) yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=-0.20$, adopting $A_V=0.3$ mag and a distance of $131 \pm 2$ pc$^x$ based on the range of parallaxes of nearby Taurus members measured by \citet{torres12}\footnote{This distance is consistent with the Gaia distance of $130 \pm4$ pc measured to the nearby Taurus members V410 Tau, V773 Tau, and BP Tau \citep{gaia2016dr}.}.
+Scaling this composite spectrum of LkCa 4 to the observed 2MASS photometry ($\sim 74\%$ spot covering fraction) yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=-0.20$, adopting $A_V=0.3$ mag and a distance of $131 \pm 2$ pc\footnote{This distance is consistent with the Gaia distance of $130 \pm4$ pc measured to the nearby Taurus members V410 Tau, V773 Tau, and BP Tau \citep{gaia2016dr}.} based on the range of parallaxes of nearby Taurus members measured by \citet{torres12}.
 At the median 80\% spot covering fraction from 2015, the luminosity would be $\log L/L_\odot=-0.26$.
@@
 The apparent effective temperature in any single epoch depends on the relative fractions of the hot and cool spot.
-When accounting for the visible contributions of both hot and cool components, this wide range of possible observed effective temperatures at any single epoch underscores the difficulty in placing young stars on HR diagrams.
+When accounting for the visible contributions of both hot and cool components, this wide range of possible observed effective temperatures in any single epoch underscores the difficulty in placing young stars on HR diagrams.
 
 Figure~\ref{fig:hrdiag} and Table~4 shows that this effective temperature is much cooler than previous measurements from optical spectra, which are clustered around 4000 K.
-The luminosity does not change significantly because the broadband SED yields similar luminosities, independent of temperature.
+The luminosity does not change significantly because the broadband SED yields similar luminosities.
 Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.15-0.3$ $M_\odot$ from standard evolutionary tracks \citep{baraffe15}.
@@
 Two component photopheres would also explain deriving different spectral types in the optical and infrared for the same source.
-On the other hand, GAIA-ESO spectra \citep{frasca15} cover only a narrow wavelength around H$\alpha$ and would yield an effective temperature of $\sim 4000$ K.
+On the other hand, many GAIA-ESO spectra cover only a narrow wavelength around H$\alpha$ \citep[e.g.][]{jeffries14,frasca15}, which would yield an effective temperature of $\sim 4000$ K.
 Spectral types and effective temperatures measured from TiO depths \citep{herczeg14} are lower than those from blue spectra but still overestimate the effective temperature.
@@
 
-The improved characterization of the photospheric emission and radius of LkCa 4 would ideally lead to more accurate estimates of mass and age from pre-main sequence tracks.
+The improved characterization of the photospheric emission and radius of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
 However, our effective temperature and luminosity yield a mass of $0.2-0.3$ $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
 This age is uncomfortably young and this mass is uncomfortably low.
-LkCa 4 is not located deeply within a molecular cloud and is not associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
+LkCa 4 is not located deeply within a molecular cloud and is not directly associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
 Dynamical measurements of masses of young stars with similar optical properties suggest that LkCa 4 should have a mass of $\sim 0.7-1.0$ M$_\odot$ \citep[e.g.][]{guilloteau14,czekala16,rizzuto16}.
+
 Even though LkCa 4 is only a single data point, the inferred age and low mass may be evidence that strong magnetic fields are inhibiting convection in LkCa 4.
@@
 Combining these numbers gives $R\sin{i} \sim 1.87 R_{\odot}$.
-Our HR diagram analysis gives $R \sim 2.3R_{\odot}$.
-These numbers are consistent for $\sin{i} \sim 0.813$, or an inclination of about 35$^{\circ}$ from edge on.
+Our HR diagram analysis gives $R \sim 2.3R_{\odot}$, which suggests  $\sin{i} \sim 0.813$, or an inclination of about 35$^{\circ}$ from edge on.
 These values show broad consistency between rotational properties, spectral fitting values, and our interpretation of a tilted star revealing a circumpolar region with large areal coverage of starspots.
@@
 As seen in Figures \ref{fig:PhotTime} and \ref{fig:PhotPhase}, the areal coverage of spots appears to wax and wane secularly through the observing seasons of the last 31 years.
-Notably, it appears to be in a relatively faint phase currently, 0.2 mag fainter in $V$ than it was through much of the late 1980's and early 1990's.
+LkCa 4 is currently in a relatively faint phase, 0.2 mag fainter in $V$ than it was through much of the late 1980's and early 1990's.
 It is conceivable that LkCa 4 happens to be going through a short-lived episode of relatively high coverage of spots analogous to solar maximum.
@@
 
-In this paper, we have demonstrated that IGRINS spectra of LkCa 4 is well modeled with two temperatures, a hot photosphere of 4100 K and large cool patches of 2700--3000 K that cover 80\% of the stellar surface.
+In this paper, we have demonstrated that the IGRINS spectra of LkCa 4 is well fit with two temperatures, a hot photosphere of 4100 K and large cool patches of 2700--3000 K that cover 80\% of the stellar surface.
 This solution reproduces the high-resolution HK spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.
 Such a high covering fraction for a spot is extraordinary.
-In this section, we describe that this type of cool spot is robust, despite some simplifying limitations of our spectral inference technique, discuss how such a large spot could be interpreted, and suggest that, while LkCa 4 appears extreme, other young sources have similar characteristics.
+In this section, we describe that the need for a large cool spot is robust, despite some simplifying limitations of our spectral inference technique.
+We also discuss how such a large spot could be interpreted, and suggest that even though LkCa 4 appears extreme, other young sources have similar characteristics.
 
 \subsection{An absolute lower limit of starspot filling factor}
+
+{\bf just a note, I do really like this subsection, it's very simple.}
 
@@
 \subsection{Is \name an extreme source?}
-The large amplitude of cyclical optical variability of LkCa 4 exceeds all other counterparts from long-term monitoring of WTTSs \citep{grankin08}.
+The large amplitude of cyclical optical variability of LkCa 4 exceeds all other counterparts from the long-term monitoring of WTTSs by \citet{grankin08}.
 From a statistical perspective, it might not be a surprise that the source with the largest photometric variability also posessess among the largest coverage fraction of cool spots.
 When compared with spot covering fractions of 15--60\% for evolved giants and subgiants \citep{chugainov76,berdyugina05}, the 80\% spot coverage of LkCa 4 seems high.
-However, many other young stars with similar spectral type also have large spot covering fractions.
+However, photometric and spectroscopic evidence demonstrates that many other young low-mass stars also have large spot covering fractions.
 
@@
 
-The Pleiades serves as an older age sample of young stars possessing evidence for large coverage fraction of starspots.
+The Pleiades serves as an older {\bf \citep[$\sim125$ Myr][]{stauffer98}} sample of young stars, many of which have starspots that cover large fractions of the stellar surface.
 For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}, while LAMOST spectra of the TiO band indicates that $\sim 30$\% spot coverages may be common for 3500--5000 K stars \citep{fang2016}.
@@
 However, the \citet{covey16} Pleiades rotation rates do not scale with the $\Delta V$ photometric amplitude at the precision of the PTF data, suggesting that while the overall starspot coverage increases with rotation rate, the longitudinally asymmetric component does not.
-LkCa 4 represents an example of such an architecture, where more than 50\% of the stellar surface is covered in spots, regardless of the phase of observation.
+LkCa 4 represents an example of such an architecture, with more than  50\% of the visible stellar surface covered in spots at all observational phases.
 The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.
-
-% Fang
-%\textbf{Insert Fang info here.}
 
@@
 \citet{herczeg14} found an intermediate spectral type for TW Hya and other TTSs by focusing on TiO bands at redder wavelengths than previous spectra, and also by using young stars as photospheric templates.
-The mismatch between near-IR spectra of dwarf stars and young stars (along with some of the color discrepancies, see Section 5.1) is likely explained by the prevalence and importance of cool spots in low mass stars.
+{\bf Similar discrepancies have been found between optical and near-IR spectral types \citep[e.g.][]{bouvier92,bary14,cottaar14} and in comparisons of spectral types measurement based on TiO bands and those based on high resolution blue spectra \citep[see discussion in][]{herczeg14}.}
+
+{bf The mismatches between near-IR spectra of dwarf stars and young stars (along with some of the color discrepancies, see Section 5.1) is also likely explained by the prevalence and importance of cool spots in low mass stars.
+For classical T Tauri stars, the veiling at $\sim 1$ $\mu$m is usually larger than can be explained by either most accretion models\footnote{\citet{ingleby13} invoked multiple accretion flows with a range of densities to explain this red excess.} or warm disk emission \citep[e.g.][]{basri90,cieza05,fischer11,mcclure13}.
+Similarly, \citet{cottaar14} found that most cool stars in the Pleiades are veiled in the H-band, with no possibility for any disk or accretion emission.
+Differences in spot temperatures and coverages likely contribute to and may explain entirely this excess veiling.}
+
+%[though see][][for a fit with multi-component accretion flow]{
 
@@
 
-We assume only two temperature components present in the photosphere.
+We assume only two temperature components are present in the photosphere.
 In reality, starspots are probably described by a range of spot temperatures analogous to umbra, penumbra, and plages on the solar surface.
-A model possessing three unique temperatures and two unique fill factors would better approximate the minor constituents of the emergent spectrum than our two temperature model can, but would always fit the data better and could lead to the possibility of overfitting.
+A model possessing three unique temperatures and two unique fill factors would better approximate the minor constituents of the emergent spectrum than our two temperature model can, but additional components will always appear to fit data better while leading to possible overfitting.
 The fit-quality of the existing two-temperature fits seems strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
@@
 Zeeman amplification can also be present \citep{basri92}.
+
 Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.
@@
 \section{Conclusions}
-This paper establishes that the optical and near-IR spectra of the weak-lined T Tauri star LkCa 4 include multiple components.
-When fit with two temperatures, the hot photosphere of 4100 K covers 20\% of the stellar surface while the cool photospheric component of 2700--3000 K covers 80\% of the stellar surface.
-The previously-established $V$-band brightness variability of $0.8$ mag is interpreted as the rotational modulation of the covering fraction of the hot photospheric component.
-This spectral modelling leads to an improved effective temperature measurement of LkCa 4.
+{\bf rearranged a bit}
 
-New results from \citet{fang2016} show that large starspot coverage fractions of $50\%$ are common even among stars in the Pleiades, which at $\sim 120$ Myr are much older than the 1--10 Myr old stars in the Taurus Molecular Cloud.
+This paper establishes that the optical and near-IR spectra of the weak-lined T Tauri star LkCa 4 are produced by multiple temperature components.
+When the temperature distribution is simplified to two temperatures, the photospheric model that best fits the spectrum includes a hot (4100 K) photospheric region that covers 20\% of the stellar surface and a cool (2700--3000 K) photospheric that covers 80\% of the stellar surface.
+The previously-established $V$-band brightness variability of $0.8$ mag is caused by the rotational modulation of the covering fraction of the hot photospheric component.
+This spectral modeling leads to an improved effective temperature measurement of LkCa 4.
+{\bf For LkCa 4 and other young low-mass stars, the standard approach of inferring masses and ages of young stars is inappropriate and will lead to large uncertainties, both because effective temperatures are systematically too hot and because most models of pre-main sequence evolution neglect spots}.
+
+New results from \citet{fang2016} show that large starspot coverage fractions of $50\%$ are common even among stars in the Pleiades, which at $\sim 125$ Myr are much older than the 1--10 Myr old stars in the Taurus Molecular Cloud.
 LkCa 4 breaks the apparent ceiling at 50\% coverage fraction of cool starspots, though it is not yet clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.
+Large parts of the stellar surface are covered in spots that do not induce photometric modulation, either from circumpolar regions that always face towards our line-of-sight, longitudinally symmetric bands, or isotropic small spots.
 
 Coupled with the results of \citet{fang2016} and \citet{covey16}, the results shown here suggest that the contribution of starspots to pre-main sequence stellar evolution have been systematically underestimated.
-Large parts of the stellar surface are covered in spots that do not induce photometric modulation, either from circumpolar regions that always face towards our line-of-sight, longitudinally symmetric bands, or isotropic small spots.
 Some cool stars in the Pleaides have a large excess in Li abundance, some have inflated radii, some are fast rotators, and some have spots \citep[e.g.][]{somers15b}.
 While the source overlap for these properties is unclear, these anomalies may all be explained if the pre-main sequence evolution of some stars is strongly affected by spots \citep{somers15}.
-LkCa 4 and other young stars with similar properties may help to connect the properties of anomalous Pleiades stars with earlier starges of stellar evolution.
+LkCa 4 and other young stars with similar properties may help to connect the properties of anomalous Pleiades stars with earlier stages of stellar evolution.
 
@@
 
-If the synthetic stellar models used in \texttt{Starfish} are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.
+When the synthetic stellar models used in \texttt{Starfish} are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.
 However \iancze\ employ \emph{standardized} $\flam$ when constructing the forward model $\vM$:
@@
 The mixture model is a linear operation with all the same stellar extrinsic parameters, so we can re-use all the same post-processed eigenspectra $\widetilde{\mathbf{\Xi}}$, mean spectrum $\widetilde{\xi}_\mu$, and variance spectrum $\widetilde{\xi}_\sigma$, with the tildes representing all post processing \emph{except} the $\Omega$ scaling.
-We calulate \emph{two} sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{hot}, \mathrm{cool})}$, and their associated mean and covariances following the Appendix of \iancze, and yielding:
+We calculate \emph{two} sets of eigenspectra weights $\mathbf{w}_{\in (\mathrm{hot}, \mathrm{cool})}$, and their associated mean and covariances following the Appendix of \iancze, and yielding:
 
@@
  \includegraphics[width=0.95\textwidth]{H_band_spectra_3x7}
- \caption{IGRINS Orders $122-100$, with panels arranged with the shortest wavelength in the upper left corner with central wavelenth decreasing toward the bottom of the leftmost column, then decreasing through the subsequent columns.
+ \caption{IGRINS Orders $122-100$, with panels arranged with the shortest wavelength in the upper left corner with central wavelength decreasing toward the bottom of the leftmost column, then decreasing through the subsequent columns.
 The $y-$axis is on a logarithmic scale.

### 2017-01-03 document/submission/ms.tex
remove the bf comments from GJH

@@
 We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
-Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, {\bf with a best-fit filling factor of $\sim80$\%  for the cool photosphere at the time of the observation.} {\bf These results are supported by comparisons of this mix of hot and cool photospheric temperatures by analyses of the spectral energy distribution, rotational modulation of colors and of TiO band strengths, and low-resolution optical/near-IR spectroscopy.
-LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.}  The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.
-Biases from starspots likely afflict most {\bf fully convective} young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
-We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra, {\bf and anti-correlations expected in the velocity jitter of the warm and cool components.
-I put this in cause I think it's interesting, but delete if you do not want to highlight this in the abstract.}
+Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, with a best-fit filling factor of $\sim80$\%  for the cool photosphere at the time of the observation.
+These results are supported by comparisons of this mix of hot and cool photospheric temperatures by analyses of the spectral energy distribution, rotational modulation of colors and of TiO band strengths, and low-resolution optical/near-IR spectroscopy.
+LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.
+Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
+We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra, and anti-correlations expected in the velocity jitter of the warm and cool components.
 
@@
 
-{\bf The causes of age uncertainties and of large luminosity spreads in young clusters are controversial \citep[see reviews by][]{preibisch12,soderblom14}.
+The causes of age uncertainties and of large luminosity spreads in young clusters are controversial \citep[see reviews by][]{preibisch12,soderblom14}.
 Absolute ages are usually inferred from comparisons between observed stellar properties and pre-main sequence evolutionary models, which are sensitive to stellar birthlines and the input physics that controls the contraction and internal heating.
-Within clusters, any real differences in ages between stars may be masked by observational uncertainties in temperature and luminosity measurements \citep[e.g.][]{hartmann01,slesnick08}.}
+Within clusters, any real differences in ages between stars may be masked by observational uncertainties in temperature and luminosity measurements \citep[e.g.][]{hartmann01,slesnick08}.
 
@@
 All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of LkCa 4.
-{\bf Section 5 describes how the two-temperature fit affects the placement of LkCa 4 on the HR diagram and what can be understood about pre-main sequence stellar evolution from this exemplar.
-Finally, Section 6 describes how our results should be interpreted, the implications for analyses of spots in high-resolution spectra, and methodological limitations.}
+Section 5 describes how the two-temperature fit affects the placement of LkCa 4 on the HR diagram and what can be understood about pre-main sequence stellar evolution from this exemplar.
+Finally, Section 6 describes how our results should be interpreted, the implications for analyses of spots in high-resolution spectra, and methodological limitations.
 
@@
 Approaches like ZDI and line-bisector analysis \citep[\emph{e.g.}][]{prato08, donati14} target the modulation of stellar photospheric lines as starspots enter and exit the observable stellar disk.
-In contrast, the technique described in this Section measures the spectrum that emerges from {\bf both the hot and the cool surfaces of the photosphere.}
+In contrast, the technique described in this Section measures the spectrum that emerges from both the hot and the cool surfaces of the photosphere.
 
@@
 
-{\bf reordered to place main result first}
-
 The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
@@
 Several orders in $K-$band were rejected due to poor spectral fits influenced by deep metal lines.
-For example, orders 79 and 81 {\bf I'm not really sure what {\it overfit} means} overfit Ca~I and Na~I lines and orders $74-76$ overfit the CO lines, which are known for their gravity sensitivity \citep{rayner09}.
-These and other metal lines can also be biased by Zeeman broadening, which could explain poorer fit quality with wavelength \citep{johnskrull07,deen13}.
+Metal lines can be biased by Zeeman broadening, which could explain poorer fit quality with wavelength \citep{johnskrull07,deen13}.
 Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were discarded.
@@
 
-%\caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).
-The inset shows that the 2750 K (red, 80\% fill factor) and 4100 K (blue, 20\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.
-The synthetic spectrum is reddened by $A_V=0.3$ mag and scaled to the observed $J$-band spectrum.
-Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere (red), and the two temperature photosphere (pink) that best fits the IGRINS spectrum.
-The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.
-Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.
-Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.
-The two temperature photosphere accurately fits spectral features in both optical and near-IR wavelengths.}
-
 \begin{figure}
@@
 The two temperaturephotosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
-{\bf This latter feature is caused by H$_2$O opacity in H$_2$O bands and is only seen when the fraction of emission from the cool component is high (Figure \ref{fig:h2ojump}).}
+This latter feature is caused by H$_2$O opacity in H$_2$O bands and is only seen when the fraction of emission from the cool component is high (Figure \ref{fig:h2ojump}).
 
@@
 the TiO indices all correlate strongly with the optical brightness.
-{\bf The TiO-7140 band depths are accurately reproduced by varying the two-temperature fit with rotation.
-Other bands have small offsets, likely caused by either contributions from intermediate temperatures or by small errors in the synthetic spectra.}  In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).
+The TiO-7140 band depths are accurately reproduced by varying the two-temperature fit with rotation.
+Other bands have small offsets, likely caused by either contributions from intermediate temperatures or by small errors in the synthetic spectra.
+In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).
 
@@
 However, isolating specific colors constrains the possible range of extinctions.
-{\bf Based on the following analysis, an $A_V=0.3$ mag is adopted throughout this paper, although some uncertainty is introduced by confusion in the choice of template colors.}
+Based on the following analysis, an $A_V=0.3$ mag is adopted throughout this paper, although some uncertainty is introduced by confusion in the choice of template colors.
 
@@
 Discrepancies in colors, spectral type/effective temperatures, and extinctions for LkCa 4, and perhaps more broadly for TTSs, are dominated by ignoring spots and not by spectral type-effective temperature scales.
-{\bf Fundamental problems in molecular opacities and photospheric models are likely important secondary affects.}
+Fundamental problems in molecular opacities and photospheric models are likely important secondary affects.
 
@@
 
-{\bf just a note, I do really like this subsection, it's very simple.}
-
 This simple thought experiment demonstrates that the high starspot filling factor must be approximately correct.
@@
 
-The Pleiades serves as an older {\bf \citep[$\sim125$ Myr][]{stauffer98}} sample of young stars, many of which have starspots that cover large fractions of the stellar surface.
+The Pleiades serves as an older \citep[$\sim125$ Myr][]{stauffer98} sample of young stars, many of which have starspots that cover large fractions of the stellar surface.
 For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}, while LAMOST spectra of the TiO band indicates that $\sim 30$\% spot coverages may be common for 3500--5000 K stars \citep{fang2016}.
@@
 \citet{herczeg14} found an intermediate spectral type for TW Hya and other TTSs by focusing on TiO bands at redder wavelengths than previous spectra, and also by using young stars as photospheric templates.
-{\bf Similar discrepancies have been found between optical and near-IR spectral types \citep[e.g.][]{bouvier92,bary14,cottaar14} and in comparisons of spectral types measurement based on TiO bands and those based on high resolution blue spectra \citep[see discussion in][]{herczeg14}.}
+Similar discrepancies have been found between optical and near-IR spectral types \citep[e.g.][]{bouvier92,bary14,cottaar14} and in comparisons of spectral types measurement based on TiO bands and those based on high resolution blue spectra \citep[see discussion in][]{herczeg14}.
 
-{bf The mismatches between near-IR spectra of dwarf stars and young stars (along with some of the color discrepancies, see Section 5.1) is also likely explained by the prevalence and importance of cool spots in low mass stars.
+The mismatches between near-IR spectra of dwarf stars and young stars (along with some of the color discrepancies, see Section 5.1) is also likely explained by the prevalence and importance of cool spots in low mass stars.
 For classical T Tauri stars, the veiling at $\sim 1$ $\mu$m is usually larger than can be explained by either most accretion models\footnote{\citet{ingleby13} invoked multiple accretion flows with a range of densities to explain this red excess.} or warm disk emission \citep[e.g.][]{basri90,cieza05,fischer11,mcclure13}.
 Similarly, \citet{cottaar14} found that most cool stars in the Pleiades are veiled in the H-band, with no possibility for any disk or accretion emission.
-Differences in spot temperatures and coverages likely contribute to and may explain entirely this excess veiling.}
-
-%[though see][][for a fit with multi-component accretion flow]{
-
-%\subsection{Possibility of third temperature or multiple temperatures}
+Differences in spot temperatures and coverages likely contribute to and may explain entirely this excess veiling.
 
@@
 
-%Assuming that the hotter component is 4100 K, the H$_2$O opacity is only sufficient if $T_{spot}<3000$ K, with a high spot coverage.
-
 \subsection{Limitations of assumptions in the spectral inference methodology}
@@
 
-%Introduce
-
 \subsection{Evidence for intra-spectrum RV jitter}
@@
 \section{Conclusions}
-{\bf rearranged a bit}
 
@@
 This spectral modeling leads to an improved effective temperature measurement of LkCa 4.
-{\bf For LkCa 4 and other young low-mass stars, the standard approach of inferring masses and ages of young stars is inappropriate and will lead to large uncertainties, both because effective temperatures are systematically too hot and because most models of pre-main sequence evolution neglect spots}.
+For LkCa 4 and other young low-mass stars, the standard approach of inferring masses and ages of young stars is inappropriate and will lead to large uncertainties, both because effective temperatures are systematically too hot and because most models of pre-main sequence evolution neglect spots.
 

### 2017-01-04 document/submission/ms.tex
Addressing the referee comments

@@
 Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
-We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra, and anti-correlations expected in the velocity jitter of the warm and cool components.
-
+In some spectral regions starspots acts as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
+Evidence for anti-correlations in velocity of the the warm and cool components is found.
 \end{abstract}
@@
 \maketitle
-
 \section{Introduction}\label{sec:intro}
-
 The causes of age uncertainties and of large luminosity spreads in young clusters are controversial \citep[see reviews by][]{preibisch12,soderblom14}.
@@
 
-\input{tbl_best_fit.tex}[!b]
+\input{tbl_best_fit.tex}
 

### 2017-01-06 document/submission/ms.tex
Referee comments for abstract

@@
 
-Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process.
+Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but magnetic fields and starspots complicate this process.
 In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.
@@
 LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates and naively using the same model tracks.
-Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters.
-In some spectral regions starspots acts as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when improperly compared to previous estimates and with unspotted model tracks, motivating the production and adoption of spotted model tracks.
+Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large apparent age spreads of those clusters.
+In some spectral regions starspots act as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
 Evidence for anti-correlations in velocity of the the warm and cool components is found.
@@
 
-We thank Chris Kochanek and Daniel T. Jaffe for valuable comments on the draft.  MG-S and GJH also thank Steve Saar and GJH thanks Lynne Hillenbrand for valuable discussions about spots.
+We thank the anonymous referee, Chris Kochanek, and Daniel T.
+Jaffe for valuable comments on the draft.
+MG-S and GJH also thank Steve Saar and GJH thanks Lynne Hillenbrand for valuable discussions about spots.
 

### 2017-01-06 document/submission/ms.tex
Big caveats about comparing to non-spotted models.

@@
 LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when improperly compared to previous estimates and with unspotted model tracks, motivating the production and adoption of spotted model tracks.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates with the same unspotted stellar evolution models, motivating the production and adoption of spotted evolutionary models.
 Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large apparent age spreads of those clusters.
@@
 This line depth ratio method suffers from the need to identify portions of the spectrum that possess easily identifiable strong lines, and from the need to assemble large atlases of observed spotless spectral templates to which the spotted star spectrum can be compared.
-In this section, we introduce a generalization of the line depth ratio analysis which employs pixel-by-pixel modeling of all spectral orders.
+In this section, we introduce a generalization of the line depth ratio analysis which employs pixel-by-pixel modeling of all echelle spectral orders.
 By using all the spectral data, this strategy has the power to constrain starspot properties at relatively low filling factors and to identify weak lines that originate from the cool photosphere.
@@
 We took two approaches to characterizing the photospheric temperature from a spotted-star spectrum.  First, 
-using the spectral fitting approach introduced in Section 3.1 \ref{sec:methods}, we separately fit the optical (ESPaDOnS) and near-IR (IGRINS) spectra with distinct, single photospheric component models; these fits are described in Sections \ref{sec:ESP_starfish} and \ref{sec:IGR_starfish} respectively, and then compared in \ref{sec:whyNearIR}.
+using the spectral fitting approach introduced in Section \ref{sec:methods}, we separately fit the optical (ESPaDOnS) and near-IR (IGRINS) spectra with distinct, single photospheric component models; these fits are described in Sections \ref{sec:ESP_starfish} and \ref{sec:IGR_starfish} respectively, and then compared in \ref{sec:whyNearIR}.
 Second, we use a two temperature mixture model to perform a fit to the near-IR spectra in Section \ref{sec:two_tempIGRINS}.
@@
 Fitting was performed separately on each spectral chunk.
-The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and photospheric temperatures $\in [3500, 4200]$ K.
+The spectral emulator was trained on stellar parameters in the range $\logg \in [3.5, 4.0]$, $\Z \in [-0.5, 0.5]$, and photospheric temperatures $ T \in [3500, 4200]$ K.
 
@@
 We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
-For the IGRINS $K-$band, we employed an expanded search range for the photosperic temperature, $\teff \in [3000, 4200]$ K.
+For the IGRINS $K-$band, we employed an expanded search range for the photosperic temperature, $T \in [3000, 4200]$ K.
 
@@
 The $K-$band shows even lower derived photospheric temperatures of $\sim3300$ K, or 700 K cooler than estimated from optical.
-No single temperature can describe all the spectral lines present in the high resolution optical and IR spectra.
+No single photospheric temperature can describe all the spectral lines present in the high resolution optical and IR spectra.
 Sources with such discrepancies have been seen previously, for example in Figures 4 and 5 in \citet{bouvier92}.
@@
 Some care should be taken when directly comparing results between the ESPaDOnS and IGRINS spectra since they were not taken at the same time.
-The particular ESPaDOnS spectrum used in Section \ref{sec:ESP_starfish} was obtained when LkCa 4 ahd an estimated $V-$band brightness of 12.94 mag, compared with 12.84 mag at the time of the IGRINS spectrum.
-The fainter magnitude during the ESPaDOnS spectrum acquisition implies a greater coverage fraction than during the IGRINS spectrum.
-The $\teff$ derived in the optical bands and short-wavelength end of $H$-band yield similar values of $\sim 4100$ K, suggesting the \emph{bulk}\footnote{The bulk appearance and disappearance of spectral lines is mostly controlled by the temperature of the emitting region of the local photosphere.
+The particular ESPaDOnS spectrum used in Section \ref{sec:ESP_starfish} was obtained when LkCa 4 had an estimated $V-$band brightness of 12.94 mag, compared with 12.84 mag at the time of the IGRINS spectrum.
+The fainter magnitude during the ESPaDOnS spectrum acquisition implies a greater coverage fraction of cool material than during the IGRINS spectrum acquisition.
+The photospheric temperature derived in the optical bands and short-wavelength end of $H$-band yield similar values of $\sim 4100$ K, suggesting the \emph{bulk}\footnote{The bulk appearance and disappearance of spectral lines is mostly controlled by the temperature of the emitting region of the local photosphere.
 In other words, most of the variance in a spectrum is attributable to temperature, assuming near-solar metallicity.
@@
 Standard MCMC convergence tests were evaluated.
-The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the \PHOENIX\ model spectrum temperature range\footnote{The \PHOENIX\ model spectra are indexed by $\teff$, but this term carries a different meaning for two-component photospheres.} was $\teffa, \teffb \in [2700, 4500]$.
+The stellar parameter ranges were $\logg \in [3.5, 4.0]$ and $\Z \in [-0.5, 0.5]$; the \PHOENIX\ model spectrum temperature range was $\teffa, \teffb \in [2700, 4500]$.
 $H-$band fits had normal distribution priors in place: solar metallicity to $\pm0.05$ dex, $logg=3.8\pm0.1$, and $\vsini=29\pm5$ km/s.
@@
 The luminosity does not change significantly because the broadband SED yields similar luminosities.
-Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.15-0.3$ $M_\odot$ from standard evolutionary tracks \citep{baraffe15}.
+Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.15-0.3$ $M_\odot$ from standard, \emph{unspotted} evolutionary tracks \citep{baraffe15}.
 
@@
 
-The improved characterization of the photospheric emission and radius of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
-However, our effective temperature and luminosity yield a mass of $0.2-0.3$ $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce some uncertainties when compared to results from the PHOENIX models used here.}.
-This age is uncomfortably young and this mass is uncomfortably low.
-LkCa 4 is not located deeply within a molecular cloud and is not directly associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
-Dynamical measurements of masses of young stars with similar optical properties suggest that LkCa 4 should have a mass of $\sim 0.7-1.0$ M$_\odot$ \citep[e.g.][]{guilloteau14,czekala16,rizzuto16}.
+In principle, the improved characterization of the photospheric emission and radius of LkCa 4 should lead to more accurate estimates of mass and age from pre-main sequence tracks.
+However, most standard pre-main sequence stellar evolution models do not take into account the effects of starspots, and those that do \citep{somers15} limit cool spot areal coverage fractions to less than 50\%.
+Comparison of LkCa 4 to \emph{unspotted} models is inherently flawed, but for the purposes of gauging the effect size of spots on derived parameters, our effective temperature and luminosity yield a mass of $0.2-0.3$ $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce minor uncertainties when compared to results from the PHOENIX models used here.}.
+This age is much younger and this mass is much lower than previous estimates made assuming the warm component solely accounted for the effective temperature.
 
-Even though LkCa 4 is only a single data point, the inferred age and low mass may be evidence that strong magnetic fields are inhibiting convection in LkCa 4.
+Even though LkCa 4 is only a single data point, the cool spot coverage fraction may be evidence that strong magnetic fields are inhibiting convection in LkCa 4.
 As a result, the surface is cooler and releases less radiation, slowing the contraction rate.
@@
 The corrected placement of spotted stars on the HR diagram reflects the accurate luminosity, radius, and effective temperature, but evolutionary models are not yet equipped to interpret such heavily spotted stars \citep{somers15}.
+In an HR digram, spotted evolutionary model tracks at a given mass and age shift to higher luminosity and lower effective temperature.
+Such a \emph{spot-corrected} HR diagram position would alter the age and mass estimates to $> 0.2-0.3$ $M_\odot$ and $\> 0.5$ Myr; in other words, back in the direction of previous na\"{i}ve estimates.
+However the full magnitude of the correction is an out-standing question.
+
+%LkCa 4 is not located deeply within a molecular cloud and is not directly associated with any nearby Class 0/1 stars, which would be expected for a 0.5 Myr star.
+Dynamical measurements of masses of young stars with similar optical properties suggest that LkCa 4 should have a mass of $\sim 0.7-1.0$ M$_\odot$ \citep[e.g.][]{guilloteau14,czekala16,rizzuto16}.
 

### 2017-01-06 document/submission/ms.tex
Closes Issue #53-- done with the referee report, but sending to GJH

@@
 The star LkCa 4, a WTTS member of the Taurus Molecular Cloud \citep{herbig86,strom89a,downes88,strom89b} is an ideal exemplar for a spotted pre-MS star because it does not have any mid-IR or mm excess \citep[\emph{e.g.}][]{andrews05,furlan06,buckle15} and is not actively accreting \citep[\emph{e.g.}][]{edwards06,cauley12}.
-LkCa 4 has no evidence for a close companion from either direct imaging searches \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}} or from RV searches \citep{nguyen12,donati14}.
+LkCa 4 has no evidence for a close companion from either direct imaging searches \citep{karr10,kraus11,daemgen15}\footnote{The status for wide companions is less clear; see \citet{stauffer91,itoh08,kraus09,kraus11,herczeg14}} or from RV searches \citep{nguyen12} and high-precision Zeeman Doppler Imaging \citep{donati14}.
 This single star demonstrates a large amplitude of sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}.
@@
 The \iancze\ technique forward models observed spectra with synthetic spectra from pre-computed model grids.
-The intra-grid-point spectra are ``emulated'' in a process similar but superior to interpolation, since it seemlessly quantifies the uncertainty attributable to the coarsely sampled stellar intrinsic parameters (see Appendix of \iancze).
+The intra-grid-point spectra are ``emulated'' in a process similar but superior to interpolation, since it seamlessly quantifies the uncertainty attributable to the coarsely sampled stellar intrinsic parameters (see Appendix of \iancze).
 The forward model includes calibration parameters, line spread functions, and a Gaussian process noise model to account for correlations in the residual spectrum.
@@
 The term $f_{\mathrm{cool}}$ represents an instantaneous, observational fill factor seen on one projected hemisphere, not $f_{\rm spot}$, the ``ratio of the spotted surface to the total surface areas'' \citep{somers15}.
-In the limit of homogenously distributed starspots and assuming the cool photosphere arises from starspots, $f_{\mathrm{cool}}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\mathrm{cool}}$ can vary cyclically through rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
+In the limit of homogeneously distributed starspots and assuming the cool photosphere arises from starspots, $f_{\mathrm{cool}}$ tends to $f_{\rm spot}$, but in general $f_{\rm spot}$ is not a direct observable since some circumpolar regions of inclined stars will always face away from Earth; $f_{\mathrm{cool}}$ can vary cyclically through rotational modulation, whereas $f_{\rm spot}$ changes secularly through starspot evolution that is not yet understood.
 
@@
 We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
-For the IGRINS $K-$band, we employed an expanded search range for the photosperic temperature, $T \in [3000, 4200]$ K.
+For the IGRINS $K-$band, we employed an expanded search range for the photospheric temperature, $T \in [3000, 4200]$ K.
 
@@
 The $3500$ K component suffers from the opposite problem, yielding molecular bands at short wavelengths that are too deep.
-The two temperaturephotosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
+The two temperature photosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
 This latter feature is caused by H$_2$O opacity in H$_2$O bands and is only seen when the fraction of emission from the cool component is high (Figure \ref{fig:h2ojump}).
@@
 \section{Placing LkCa 4 on the HR diagram}
-
-%\todo{Some overview?}
 
@@
 LkCa 4 is currently in a relatively faint phase, 0.2 mag fainter in $V$ than it was through much of the late 1980's and early 1990's.
-It is conceivable that LkCa 4 happens to be going through a short-lived episode of relatively high coverage of spots analogous to solar maximum.
+It is conceivable that LkCa 4 happens to be going through a short-lived episode of relatively high coverage of cool photosphere analogous to--- albeit distinct from---solar maximum.
 The intensity and duration of such episodes would further confound the interpretation of its instantaneous position on the HR diagram.
@@
 In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
-This scenario would have to be consistent with the inclination derived from relating $\vsini$, rotation period, and estimates for the stellar radius.
+This scenario is consistent with the inclination derived from relating $\vsini$, rotation period, and estimates for the stellar radius, as previously noted.
 Such estimates are limited by estimates of the radius, since uncertainties in effective temperature and luminosity cause a wide range of radius estimates.
@@
 Coupled with the results of \citet{fang2016} and \citet{covey16}, the results shown here suggest that the contribution of starspots to pre-main sequence stellar evolution have been systematically underestimated.
-Some cool stars in the Pleaides have a large excess in Li abundance, some have inflated radii, some are fast rotators, and some have spots \citep[e.g.][]{somers15b}.
+Some cool stars in the Pleiades have a large excess in Li abundance, some have inflated radii, some are fast rotators, and some have spots \citep[e.g.][]{somers15b}.
 While the source overlap for these properties is unclear, these anomalies may all be explained if the pre-main sequence evolution of some stars is strongly affected by spots \citep{somers15}.

### 2017-01-11 document/submission/ms.tex
GJH final comments before resubmission

@@
 \altaffiltext{5}{Department of Physics \& Astronomy, Western Washington University, Bellingham WA 98225-9164, USA}
-\altaffiltext{6}{CNRS, IRAP / UMR 5277, Toulouse, 14 avenue E. Belin, F– 31400 France}
+\altaffiltext{6}{CNRS, IRAP / UMR 5277, Toulouse, 14 avenue E. Belin, F- 31400 France}
 \altaffiltext{7}{Université de Toulouse, UPS-OMP, IRAP, 14 avenue E. Belin, Toulouse, F–31400 France}
@@
 LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates with the same unspotted stellar evolution models, motivating the production and adoption of spotted evolutionary models.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates with the same unspotted stellar evolution models, although appropriate comparisons require the
+production and adoption of spotted evolutionary models.
 Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large apparent age spreads of those clusters.
 In some spectral regions starspots act as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
-Evidence for anti-correlations in velocity of the the warm and cool components is found.
+Some evidence is also found for an anti-correlation between the velocities of the warm and cool components.
 \end{abstract}
@@
 The single band light curves from such surveys cannot separate the relative areas and temperatures of the emitting regions, and therefore cannot yield estimates for the filling factor of spots without making assumptions about the relative temperature contrast.
-Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{herbst94,petrov94,bouvier95,grankin07,cody14} can break the degeneracy between starspot filling factor and starspot temperature but these measurements are still limited to detecting large longitudinally asymmetric starspots.
+Contemporaneous or near-contemporaneous panchromatic photometric monitoring \citep{herbst94,petrov94,bouvier95,grankin07,cody14} can break the degeneracy between starspot filling factor and starspot temperature, but these measurements are still limited to detecting large longitudinally asymmetric starspots.
 Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups, but the number of such transiting systems and demands of high photometric precision limit wider application.
@@
 For WTTSs, SED modeling indicated the presence of cool spots \citep{wolk96}, while spot temperatures have been estimated from rotational modulation of optical colors \citep[e.g.][]{grankin98,venuti15,koen16}.
-The TiO bands in optical spectra have been used to measure spots on WTTSs \citep{petrov94}, stars in the Pleiades \citep{fang2016}, and evolved stars \citep[e.g.][]{neff95,oneal01,oneal04}.
+The TiO bands in optical spectra have been used to measure spots on WTTSs \citep{petrov94}, stars with ages of 125 Myr in the Pleiades \citep{fang2016}, and evolved stars \citep[e.g.][]{neff95,oneal01,oneal04}.
 Recent spectroscopic detections of spots on young stars have focused on TW Hya, an active accretor, and DQ Tau, a close binary in which both components are accreting \citep{debes13,bary14}.
@@
 
-In this work, we measure the starspot properties of LkCa 4 with four complementary techniques.  Section \ref{sec:obs} describes the full spectroscopic and photometric dataset and 
+In this work, we measure the starspot properties of LkCa 4 with four complementary techniques.\footnote{Some data, Python code, Starfish configuration files, and other documents related to this paper are available on the project's GitHub repository at \url{https://github.com/BrownDwarf/welter}}
+Section \ref{sec:obs} describes the full spectroscopic and photometric dataset and 
 quantifies the optical variability of LkCa 4 over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.
@@
 The best-fit temperature measured in the $K-$band is about 800 K lower than that derived in optical.
+The triangles in the $H$-band show upper limits with best fits near the edge of our grid.
 Bottom panel:  The flux ratio between the cool and hot components increases to the near-IR, which explains the observed trend in the best-fit temperature.}
@@
 The forward model includes calibration parameters, line spread functions, and a Gaussian process noise model to account for correlations in the residual spectrum.
-We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which span a wide range of wavelengths at high spectral resolution with a sampling of 100 K in stellar photospheric temperature\footnote{Single component \PHOENIX\ photospheres are indexed by the label ``effective temperature'', or $\teff$, which presupposes that the emergent spectrum is comprised of only a single photospheric component.
+We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which are provided at high spectral resolution over a wide wavelength range at 100 K intervals in stellar photospheric temperature\footnote{Single component \PHOENIX\ photospheres are indexed by the label ``effective temperature'', or $\teff$, which presupposes that the emergent spectrum is comprised of only a single photospheric component.
 In this work we avoid labeling the photospheric components by $\teff$, and instead refer to them as simply ``photospheric temperatures''.} in our range of interest \citep{husser13}.
@@
 
-The stellar photosphere is characterized as two photospheric components with a cool photosphere temperature $\teffb$ and hot photosphere temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$, respectively\footnote{For flux calibrated spectra, the total solid angle $\Omega$ can be constrained, but for typical echelle spectrographs only relative values of $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$ can be inferred.}.
-The choice of nomenclature depends on the physical origin of the emission region.
-In general, the emission region's physical origin is not directly observable without ancillary information.
+The stellar photosphere is characterized as two photospheric components with a cool temperature $\teffb$ and hot temperature $\teffa$, with scalar solid angular coverages $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$, respectively\footnote{For flux calibrated spectra, the total solid angle $\Omega$ can be constrained, but for typical echelle spectrographs only relative values of $\Omega_{\mathrm{cool}}$ and $\Omega_{\mathrm{hot}}$ can be inferred.}.
+The choice of nomenclature depends on the physical origin of the emission region, which is not directly observable without ancillary information.
 For many applications, it could be reasonably assumed that the cool photospheric component corresponds to a sunspot or sunspot group, and the hot component corresponds to the ambient photosphere.
@@
 Unresolved single-lined or double-lined binaries could mimic a signal that would be misattributed to starspots.
-As pointed out earlier, LkCa 4 has no detected companion from direct imaging, and its RV variations are consistent with starspot modulation, so any binary companion would have to have exceptionally large luminosity or mass ratios, rendering it undetectable with our spectral inference methodology with the finite signal to noise available in the IGRINS data.
+As pointed out earlier, LkCa 4 has no detected companion from direct imaging, and its RV variations are consistent with starspot modulation, so any binary companion would have to have an exceptionally large luminosity (or mass) ratio, rendering it undetectable with our spectral inference methodology with the finite signal to noise available in the IGRINS data.
 The absence of a detectable disk around LkCa 4 means that the spectral modeling requires no further parameters like veiling or accretion.
@@
 Figure \ref{fig:SingleTeffvsOrder} displays the point estimates with 5$^{th}$ and $95^{th}$ percentile error bars placed at the central wavelength of each spectral chunk.
-The spectral chunk from 8473$-$8707 \AA\ was an outlier, showing an estimated photospheric temperature of $\sim3500$ K.
+The spectral chunk from 8473$-$8707 \AA\ is an outlier, showing an estimated photospheric temperature of $\sim3500$ K.
 
@@
 We performed unique spectral fitting on each order, with free stellar parameters $\vt = (\teff, \logg, \Z)$.
-We used the same analysis procedure as described for the ESPaDOnS spectra, with one exception.
-For the IGRINS $K-$band, we employed an expanded search range for the photospheric temperature, $T \in [3000, 4200]$ K.
+The same analysis procedure described for the ESPaDOnS spectra is used here, though in the $K$-band the temperature search range is expanded to $T \in [3000, 4200]$ K.
 
@@
 The visible portion of the spectrum will be dominated by the warm patches.
-The infrared spectrum will have a lower overall spot contrast, and will have more net starspot flux than optical.
+The infrared spectrum will have a lower overall spot contrast, and will have more net starspot flux than optical emission.
 
@@
 Metal lines can be biased by Zeeman broadening, which could explain poorer fit quality with wavelength \citep{johnskrull07,deen13}.
-Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were discarded.
+Some orders were also discarded because their fits were mediocre or uninformative.
 The remaining orders are relatively devoid of spectral line outliers and include the most information rich portion of the spectrum.
@@
 The contours show the flux ratio at 1.30 and 1.34 $\mu$m from the Phoenix models.
-Comparisons to the APO/TripleSpec spectrum yield best-fit solutions (solid purple line) and the range of acceptable fits (shaded cyan region, with contours of flux ratio in dashed black lines) for an epoch when  the cool spot fraction was $\sim 84$\%.
+Comparisons to the APO/TripleSpec spectrum, shown in the inset and normalized at 1.4 $\mu$m, yield best-fit solutions (solid purple line) and the range of acceptable fits (shaded cyan region, with contours of flux ratio in dashed black lines) for an epoch when  the cool spot fraction was $\sim 84$\%.
 The range of acceptable fits is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption.
@@
 The two temperature photosphere with the parameters from the best-fit calculated in \S 3 reproduces the TiO bands, the hump in the $H$-band, and the jump in flux at the long-wavelength end of the $J$-band.
-This latter feature is caused by H$_2$O opacity in H$_2$O bands and is only seen when the fraction of emission from the cool component is high (Figure \ref{fig:h2ojump}).
+This latter feature is caused by opacity in H$_2$O bands and is only seen when the fraction of emission from the cool component is high (Figure \ref{fig:h2ojump}).
 
@@
 In the two-temperature photosphere, the $V$-band emission is dominated by the hotter component and is therefore a good proxy for the visible surface area of the hot component.
-Figure~\ref{fig:vband_spot} shows the 2015--2016 ASAS-SN lightcurve, converted into a cool spot filling factor.
+Figure~\ref{fig:vband_spot} shows the winter 2015--2016 ASAS-SN lightcurve, converted into a cool spot filling factor.
 During this period, the brightest and faintest phase corresponds to cool component fill factors of $74\%$ and $86\%$, respectively.
@@
 The TiO-7140 band depths are accurately reproduced by varying the two-temperature fit with rotation.
-Other bands have small offsets, likely caused by either contributions from intermediate temperatures or by small errors in the synthetic spectra.
+Other bands have small offsets (see middle panel of Figure~\ref{fig:tiovar}), likely caused by either contributions from intermediate temperatures or by small errors in the synthetic spectra.
 In the spectral type scheme derived by \citet{herczeg14}, the change in TiO-7140 index corresponds to a range from M1.5 (3640 K) to M2.2 (3530 K).
@@
 The template near-IR color is more robust than optical colors to differences 
-in the main sequence/pre-main sequence temperature scales because the pre-main 
+between the main sequence and pre-main sequence temperature scales because the pre-main 
 sequence $J-K$ color is redder at 4100 K and bluer at 2750 K.
@@
 For LkCa 4, the excess $E(J-K)$ color leads to an extinction of $0.84$ mag for a 4100 K photosphere and \citet{pecaut13} pre-main sequence colors.
-This extinction is consistent with the color and SED analysis of \citet{furlan06}, where a K7 spectral type was adopted, and is higher than extinctions of $A_V=0.69$ measured from optical photometry \citep{kenyon95} and $0.35$ mag measured by comparing optical spectra to young spectral templates \citep{herczeg14}.
+This extinction is consistent with the color and SED analysis of \citet{furlan06}, where a K7 spectral type was adopted, and is higher than extinctions of $A_V=0.69$ mag measured from optical photometry \citep{kenyon95} and $0.35$ mag measured by comparing optical spectra to young spectral templates \citep{herczeg14}.
 
-Our results tentatively support the lower extinctions obtained at optical wavelengths, although the template colors used to calculate extinction are uncertain and will need revision.
+Our results tentatively support the lower extinction obtained at optical wavelengths, although the template colors used to calculate extinction are uncertain and will need revision.
 Differences between main sequence and pre-main sequence temperature scales and colors in the \citet{pecaut13} tables are introduced by a combination of spots, in addition to any color differences caused by gravity differences.
@@
 The spectrum of LkCa 4 is well reproduced by a cool component of $2750$ K covering 80\% of the surface and a $4100$ K component covering 20\% of the surface.
-Scaling this composite spectrum of LkCa 4 to the observed 2MASS photometry ($\sim 74\%$ spot covering fraction) yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=-0.20$, adopting $A_V=0.3$ mag and a distance of $131 \pm 2$ pc\footnote{This distance is consistent with the Gaia distance of $130 \pm4$ pc measured to the nearby Taurus members V410 Tau, V773 Tau, and BP Tau \citep{gaia2016dr}.} based on the range of parallaxes of nearby Taurus members measured by \citet{torres12}.
+Scaling this composite spectrum of LkCa 4 to the observed 2MASS photometry ($\sim 74\%$ spot covering fraction) yields $R=2.3$ $R_\odot$ and $\log L/L_\odot=-0.20$, adopting $A_V=0.3$ mag and a distance of $131 \pm 2$ pc\footnote{This distance is consistent with the Gaia distance of $130 \pm4$ pc measured to the nearby Taurus members V410 Tau, V773 Tau, and BP Tau \citep{gaia2016dr}.} from the range of parallaxes of nearby Taurus members measured by \citet{torres12}.
 At the median 80\% spot covering fraction from 2015, the luminosity would be $\log L/L_\odot=-0.26$.
@@
 
-Figure~\ref{fig:hrdiag} and Table~4 shows that this effective temperature is much cooler than previous measurements from optical spectra, which are clustered around 4000 K.
+Figure~\ref{fig:hrdiag} and Table~4 show that this effective temperature is much cooler than previous measurements from optical spectra, which are clustered around 4000 K.
 The luminosity does not change significantly because the broadband SED yields similar luminosities.
-Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.15-0.3$ $M_\odot$ from standard, \emph{unspotted} evolutionary tracks \citep{baraffe15}.
-
+%Since the Hayashi tracks are nearly vertical at this temperature and age, the range in effective temperatures corresponds to a mass range from $\sim 0.15-0.3$ $M_\odot$ from standard, \emph{unspotted} evolutionary tracks \citep{baraffe15}.
 When the photosphere is assumed to be a single temperature, the effective temperature depends on the wavelength where the measurement is made.
@@
 On the other hand, many GAIA-ESO spectra cover only a narrow wavelength around H$\alpha$ \citep[e.g.][]{jeffries14,frasca15}, which would yield an effective temperature of $\sim 4000$ K.
-Spectral types and effective temperatures measured from TiO depths \citep{herczeg14} are lower than those from blue spectra but still overestimate the effective temperature.
+Spectral types and effective temperatures measured from TiO depths \citep[e.g.][]{herczeg14} are cooler than those estimated from blue spectra but still overestimate the effective temperature.
 Temperature uncertainties for young K and M dwarfs are larger than any formal uncertainties in individual measurements.
@@
 However, most standard pre-main sequence stellar evolution models do not take into account the effects of starspots, and those that do \citep{somers15} limit cool spot areal coverage fractions to less than 50\%.
-Comparison of LkCa 4 to \emph{unspotted} models is inherently flawed, but for the purposes of gauging the effect size of spots on derived parameters, our effective temperature and luminosity yield a mass of $0.2-0.3$ $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce minor uncertainties when compared to results from the PHOENIX models used here.}.
+Comparison of LkCa 4 to \emph{unspotted} models is inherently flawed, but for the purposes of gauging the effect size of spots on derived parameters, our effective temperature and luminosity yield a mass of $0.15-0.3$ $M_\odot$ and an age of $\sim 0.5$ Myr in the \citet{baraffe15} evolutionary models\footnote{The \citet{baraffe15} evolutionary tracks were calculated using BT-Settl photospheric spectra \citep{allard14}, which may introduce minor uncertainties when compared to results from the PHOENIX models used here.}.
 This age is much younger and this mass is much lower than previous estimates made assuming the warm component solely accounted for the effective temperature.
@@
 Such a \emph{spot-corrected} HR diagram position would alter the age and mass estimates to $> 0.2-0.3$ $M_\odot$ and $\> 0.5$ Myr; in other words, back in the direction of previous na\"{i}ve estimates.
-However the full magnitude of the correction is an out-standing question.
+However the full magnitude of the correction is an outstanding question.
 
@@
 It is conceivable that LkCa 4 happens to be going through a short-lived episode of relatively high coverage of cool photosphere analogous to--- albeit distinct from---solar maximum.
-The intensity and duration of such episodes would further confound the interpretation of its instantaneous position on the HR diagram.
+The intensity and duration of such episodes would further confound the interpretation of any instantaneous position on the HR diagram.
 
@@
 In this paper, we have demonstrated that the IGRINS spectra of LkCa 4 is well fit with two temperatures, a hot photosphere of 4100 K and large cool patches of 2700--3000 K that cover 80\% of the stellar surface.
-This solution reproduces the high-resolution HK spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.
-Such a high covering fraction for a spot is extraordinary.
+This solution reproduces the high-resolution $HK$-band spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.
+Such a high covering fraction for a spot seems extraordinary, but may be common among young stars.
 In this section, we describe that the need for a large cool spot is robust, despite some simplifying limitations of our spectral inference technique.
@@
 \subsection{Interpretation of the large filling factor of cool starspots}
-We have shown that LkCa 4 exposes between 74\% and 86\% cool photosphere towards our viewing direction in 2015-2016, the most recent season for which there is data.
-In previous seasons, like Fall 2004 (\emph{c.f.} Figures \ref{fig:PhotPhase} and \ref{fig:vband_spot}), the filling factor of cool spots could have exceeded 90\%.
+We have shown that LkCa 4 exposes between 74\% and 86\% cool photosphere towards our viewing direction in winter 2015-2016, the most recent season for which there is data.
+In previous seasons, like fall 2004 (\emph{c.f.} Figures \ref{fig:PhotPhase} and \ref{fig:vband_spot}), the filling factor of cool spots could have exceeded 90\%.
 This exceptionally large fraction of surface area covered by spots defies the conventional wisdom that starspots are the minority constituent of the stellar surface.
@@
 
-One conceivable interpretation of the 74\% to 86\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere, as described by \citet{donati14}.
+One conceivable interpretation of the 74\%--86\% coverage fraction of cool photosphere is a stellar axis inclined towards our observing direction, with a large circum-polar spot covering much of the observable hemisphere, as described by \citet{donati14}.
 The ambient hot photosphere would then be close to the equator, which would be limb-darkened due to projection effects.
@@
 For the stars with the highest light curve amplitudes, this model shows that the spotted regions cover from 17 to 73\% of the visible stellar hemisphere and that the mean temperature of the cool regions is $500-1400$ K lower than the ambient photosphere.
-An analysis of the calculated spot parameters of V410 Tau revealed that there is a real correlation between the amplitude of periodicity and the spot distribution
+An analysis of the calculated spot parameters of V410 Tau revealed a correlation between the amplitude of periodicity and the spot distribution
 nonuniformity, which is defined as the difference of spot coverage in the visible hemispheres of the star at maximum and minimum light.
@@
 
-The Pleiades serves as an older \citep[$\sim125$ Myr][]{stauffer98} sample of young stars, many of which have starspots that cover large fractions of the stellar surface.
+The Pleiades provides an older \citep[$\sim125$ Myr,][]{stauffer98} sample of young stars, many of which have starspots that cover large fractions of the stellar surface.
 For example, anomalous colors of K dwarfs in the Pleiades can be explained by $\sim$50\% fill factors of spots \citep{stauffer03}, while LAMOST spectra of the TiO band indicates that $\sim 30$\% spot coverages may be common for 3500--5000 K stars \citep{fang2016}.
@@
 As an example, the well-studied CTTS TW Hya has a $\sim 4100$ K photosphere measured from high resolution optical spectra \citep[e.g.][]{yang05}.
-However, the near-IR spectrum is consistent with $\sim M2$, when compared with main sequence dwarf stars \citep{vacca11}.
+However, the near-IR spectrum is consistent with $\sim$ M2, when compared with main sequence dwarf stars \citep{vacca11}.
 \citet{debes13} reconciled this discrepancy by invoking spots, although the spectral contribution from accretion and disk continuum emission was uncertain.
@@
 A model possessing three unique temperatures and two unique fill factors would better approximate the minor constituents of the emergent spectrum than our two temperature model can, but additional components will always appear to fit data better while leading to possible overfitting.
-The fit-quality of the existing two-temperature fits seems strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents must be relatively low.
-Interestingly, $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.
+The fit-quality of the existing two-temperature fits seems strong through much of $H-$band and many $K-$band orders, so the contribution of minor photospheric constituents is relatively low.
+Interestingly, the $K-$band has several spectral orders that converge towards hybrid temperatures in the vicinity of $\sim3500$ K.
 Most of these orders are flagged as erroneous due to strong metal line spectral outliers or uncorrected calibration artifacts.
@@
 
-Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) there exist many orders and lines that are not affected at all, and 3) the Gaussian process noise model fosters some resilience against unknown residual spectrum correlations induced by such under-fitting.
+Our tacit assumptions have been that these line-broadening effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures, 2) many orders and lines are not affected at all, and 3) the Gaussian process noise model provides some resilience against unknown residual spectrum correlations induced by such under-fitting.
 We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.
@@
 LkCa 4 has clear optical line-profile variations \citep{nguyen12, donati14}.
-We should be able to detect \emph{anticorrelation} between the line center positions of spectral lines arising from ambient photosphere, and lines arising from cool starspots, since there is a zero-sum competition for solid-angle on the recessional and advancing stellar limbs.
+We should be able to detect an \emph{anticorrelation} between the line center positions of spectral lines arising from the ambient photosphere and lines arising from cool starspots, since there is a zero-sum competition for solid-angle on the recessional and advancing stellar limbs.
 We found tentative, albeit weak, evidence for such anticorrelation in $v_z$ across spectral orders dominated by cool photosphere and those dominated by hot photosphere.
@@
 New results from \citet{fang2016} show that large starspot coverage fractions of $50\%$ are common even among stars in the Pleiades, which at $\sim 125$ Myr are much older than the 1--10 Myr old stars in the Taurus Molecular Cloud.
-LkCa 4 breaks the apparent ceiling at 50\% coverage fraction of cool starspots, though it is not yet clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.
-Large parts of the stellar surface are covered in spots that do not induce photometric modulation, either from circumpolar regions that always face towards our line-of-sight, longitudinally symmetric bands, or isotropic small spots.
+LkCa 4 breaks the apparent ceiling at 50\% coverage fraction of cool starspots, though it is not clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.
+A high fraction of the stellar surface may be covered in spots without inducing any photometric modulation, if the spoits are located in circumpolar regions that always face towards our line-of-sight, in longitudinally symmetric bands, or in many isotropic small spots.
 

### 2017-01-13 document/submission/ms.tex
Adjust the acknowledgements
Use grammarly on the draft to look for grammar and typos

@@
 LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates with the same unspotted stellar evolution models, although appropriate comparisons require the
-production and adoption of spotted evolutionary models.
+The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates with the same unspotted stellar evolution models, although appropriate comparisons require the production and adoption of spotted evolutionary models.
 Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large apparent age spreads of those clusters.
-In some spectral regions starspots act as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
+In some spectral regions, starspots act as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
 Some evidence is also found for an anti-correlation between the velocities of the warm and cool components.
@@
 Transiting planets or eclipsing binaries passing in front of starspots \citep{desert11} can break geometric degeneracies, providing estimates for the characteristic sizes and lifetimes of starspots or starspot groups, but the number of such transiting systems and demands of high photometric precision limit wider application.
-Zeeman Doppler Imaging \citep[ZDI]{donati14} produces the latitudinal and longitudinal distribution of starspots in reconstructed brightness maps based on models for spectro-polarimetric line shapes, but would be unable to identify uniform distributions of small spots.
+Zeeman Doppler Imaging \citep[ZDI]{donati14} produces the latitudinal and longitudinal distribution of starspots in reconstructed brightness maps based on models for spectro-polarimetric line shapes but would be unable to identify uniform distributions of small spots.
 All of these techniques would tend to underestimate the fractional coverage of starspots distributed isotropically on the surface, stars viewed pole-on, or stars with longitudinally symmetric bands of starspots.
@@
 This single star demonstrates a large amplitude of sinusoidal photometric variability indicative of large spots \citep{grankin08,xiao12}.
-The variability amplitude cannot arise from an eclipsing binary, since the large RV variations would have been seen in spectroscopic monitoring.
+The variability amplitude cannot arise from an eclipsing binary since the large RV variations would have been seen in spectroscopic monitoring.
 All of these observations indicate that the spectrum of \name should be devoid of complicating factors like near-IR excess veiling, accretion excess, or close binarity.
@@
 There is also evidence for a hot spot in the reconstructed ZDI map.
-These spot maps demonstrate that multiple temperature components contribute to the broadband emission from the star, which may explain the large differences between the 4100 K effective temperature measurement obtained from high resolution optical spectra \citep{donati14} compared with 3600 K obtained from an analysis dominated by TiO bands \citep{herczeg14}.
+These spot maps demonstrate that multiple temperature components contribute to the broadband emission from the star, which may explain the large differences between the 4100 K effective temperature measurement obtained from high-resolution optical spectra \citep{donati14} compared with 3600 K obtained from an analysis dominated by TiO bands \citep{herczeg14}.
 
@@
 \subsection{ESPaDOnS Spectroscopy}
-We used ESPaDOnS on CFHT to obtain twelve high resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MaTYSSE Large Program.
+We used ESPaDOnS on CFHT to obtain twelve high-resolution optical spectra of \name from 8-21 Jan.~2014 as part of the MaTYSSE Large Program.
 These spectra cover 3900$-$10000 \AA\ at $R\sim68,000$ and were obtained in spectropolarimetry mode.
@@
 To calculate TiO indices, the relative flux calibration was obtained from an approximate instrument sensitivity calculated from observations of 72 Tau.
-The spectral shapes match the flux calibrated low resolution spectra described in \S 2.3.
+The spectral shapes match the flux calibrated low-resolution spectra described in \S 2.3.
 
@@
 30, 2008, a few hours earlier than the DBSP spectra, using the TripleSpec spectrograph on the Astrophysical Research Consortium (ARC) 3.5 meter telescope at Apache Point Observatory in Sunspot, New Mexico.
-LkCa 4 was observed for a total integration time of 90s using an ABBA dither sequence along the slit to remove sky emission by differencing sequential exposures.
+LkCa 4 was observed for a total integration time of 90 s using an ABBA dither sequence along the slit to remove sky emission by differencing sequential exposures.
 With the 1.1$\arcsec$ slit used for these observations, TripleSpec provides nearly contiguous coverage from 0.95 to 2.46 $\mu$m at a resolution of  R $\sim$3200 \citep{wilson04}.
@@
 The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}.
-} to infer stellar properties from high resolution spectra.
+} to infer stellar properties from high-resolution spectra.
 The \iancze\ technique forward models observed spectra with synthetic spectra from pre-computed model grids.
-The intra-grid-point spectra are ``emulated'' in a process similar but superior to interpolation, since it seamlessly quantifies the uncertainty attributable to the coarsely sampled stellar intrinsic parameters (see Appendix of \iancze).
+The intra-grid-point spectra are ``emulated'' in a process similar but superior to interpolation since it seamlessly quantifies the uncertainty attributable to the coarsely sampled stellar intrinsic parameters (see Appendix of \iancze).
 The forward model includes calibration parameters, line spread functions, and a Gaussian process noise model to account for correlations in the residual spectrum.
 We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra, which are provided at high spectral resolution over a wide wavelength range at 100 K intervals in stellar photospheric temperature\footnote{Single component \PHOENIX\ photospheres are indexed by the label ``effective temperature'', or $\teff$, which presupposes that the emergent spectrum is comprised of only a single photospheric component.
-In this work we avoid labeling the photospheric components by $\teff$, and instead refer to them as simply ``photospheric temperatures''.} in our range of interest \citep{husser13}.
+In this work we avoid labeling the photospheric components by $\teff$, and instead, refer to them as simply ``photospheric temperatures''.} in our range of interest \citep{husser13}.
 The modular framework was altered to accommodate starspot measurements in two ways.
@@
 However, a cool ambient photosphere possessing localized hot spots---like plages on the sun---could yield the same or similar two-temperature composite spectrum.
-In principle, the physical origin could be assessed with detailed comparision of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.
-For now we index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.
+In principle, the physical origin could be assessed with detailed comparison of average surface magnetic field strengths through Zeeman line broadening or other magnetic-field sensitive techniques.
+For now, we index the two photospheric components in the most general way possible, simply \emph{cool} and \emph{hot}.
 
@@
 The heightened sensitivity to starspot spectral lines as a function of wavelength can be understood in the following way.
-Starspots are cooler than their surrounding photosphere and will therefore have a longer wavelength of peak emission.
+Starspots are cooler than their surrounding photosphere and will, therefore, have a longer wavelength of peak emission.
 The average ratio of flux density between starspot and bulk photosphere will increase with wavelength until asymptotically approaching a fixed value on the Rayleigh-Jeans tail \citep{wolk96}.
@@
 The visible portion of the spectrum will be dominated by the warm patches.
-The infrared spectrum will have a lower overall spot contrast, and will have more net starspot flux than optical emission.
+The infrared spectrum will have a lower overall spot contrast and will have more net starspot flux than optical emission.
 
@@
 In other cases (\emph{e.g.} the middle row and lower left panel), the hot photosphere model veils sequences of shallow spectral features predicted in the cool photosphere model.
-The cool spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotational broadening; any feature of interest will be biased to non-zero veiling.
+The cool spectral models predict shallow features because line blanketing from multiple indistinct molecular bands overlaps from rotational broadening; any feature of interest will be biased to non-zero veiling.
 
@@
 The  $V$-band brightness reflects the instantaneous filling factor of the cool and hot components.
-In the two-temperature photosphere, the $V$-band emission is dominated by the hotter component and is therefore a good proxy for the visible surface area of the hot component.
+In the two-temperature photosphere, the $V$-band emission is dominated by the hotter component and is, therefore, a good proxy for the visible surface area of the hot component.
 Figure~\ref{fig:vband_spot} shows the winter 2015--2016 ASAS-SN lightcurve, converted into a cool spot filling factor.
@@
 
-The optical emission is dominated by the hotter component while both components contribute equally to the infrared emission (see inset in top panel of Figure \ref{fig:lores}).
+The optical emission is dominated by the hotter component while both components contribute equally to the infrared emission (see inset in the top panel of Figure \ref{fig:lores}).
 Figure~\ref{fig:colors} demonstrates that the $B-V$ color from \citet{grankin08} does not depend on $V$, which is consistent with expectations for a single hot component with no contributions from the cooler component.
@@
 
-The TiO bands trace the cool component.  When the hotter component has a larger filling fraction, the TiO bands are veiled by the hotter component and should therefore be shallower. As expected, 
+The TiO bands trace the cool component.  When the hotter component has a larger filling fraction, the TiO bands are veiled by the hotter component and should, therefore, be shallower. As expected, 
 the TiO indices all correlate strongly with the optical brightness.
@@
 The average $B-V=1.41$ mag color from \citet{grankin08} has a color excess $E(B-V)=0.09$ mag relative to the empirical color expected for a main sequence star and $E(B-V)=0.20$ mag for colors of pre-main sequence stars, based on the temperature-color tables of \citep{pecaut13}.
-The main sequence colors are probably most
-appropriate in this analysis because they are more free of spots.  
-The $B-V$ color 
-excess leads to an extinction $A_V=0.28\pm0.15$ mag relative to main sequence colors, or $0.62\pm0.15$ mag relative to 
-pre-main sequence colors.   The listed uncertainties are calculated from extinction estimates relative to colors of 4000 and 4200 K photospheres.
+The main sequence colors are probably most appropriate in this analysis because they are freer of spots.
+The $B-V$ color excess leads to an extinction $A_V=0.28\pm0.15$ mag relative to main sequence colors, or $0.62\pm0.15$ mag relative to pre-main sequence colors.
+The listed uncertainties are calculated from extinction estimates relative to colors of 4000 and 4200 K photospheres.
 The $V-R_J$ color excess leads to $A_V=0.48$ mag, which should be less affected by gravity (based on $V-I_C$ colors in Pecaut et al.) but is likely to be overestimated because the cool component contributes to the $R_J$-band emission, as seen in Fig.~\ref{fig:colors}.
 In the near-IR, the estimated $V=12.61$ mag at the time of the 2MASS observations leads to a spot-weighted template (main sequence) color 
-$J-K_s=0.87$ mag, with a range of $\sim 0.05$ mag for acceptable solutions with other 
-temperatures and covering fractions. The observed $J-K=0.93$ mag leads to $A_V=0.35$ mag, 
+$J-K_s=0.87$ mag, with a range of $\sim 0.05$ mag for acceptable solutions with other temperatures and covering fractions. The observed $J-K=0.93$ mag leads to $A_V=0.35$ mag, 
 with a range of $0.29$ mag to account for the range of other acceptable photospheric solutions.  
-The template near-IR color is more robust than optical colors to differences 
-between the main sequence and pre-main sequence temperature scales because the pre-main 
-sequence $J-K$ color is redder at 4100 K and bluer at 2750 K.
+The template near-IR color is more robust than optical colors to differences between the main sequence and pre-main sequence temperature scales because the pre-main sequence $J-K$ color is redder at 4100 K and bluer at 2750 K.
 
@@
 Differences between main sequence and pre-main sequence temperature scales and colors in the \citet{pecaut13} tables are introduced by a combination of spots, in addition to any color differences caused by gravity differences.
-Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types, if spot coverage is also similar.
+Uncertainty in colors may be solved with self-consistent comparisons to young stars with similar spectral types if spot coverage is also similar.
 Discrepancies in colors, spectral type/effective temperatures, and extinctions for LkCa 4, and perhaps more broadly for TTSs, are dominated by ignoring spots and not by spectral type-effective temperature scales.
-Fundamental problems in molecular opacities and photospheric models are likely important secondary affects.
+Fundamental problems in molecular opacities and photospheric models are likely important secondary effects.
 
@@
 The corrected placement of spotted stars on the HR diagram reflects the accurate luminosity, radius, and effective temperature, but evolutionary models are not yet equipped to interpret such heavily spotted stars \citep{somers15}.
-In an HR digram, spotted evolutionary model tracks at a given mass and age shift to higher luminosity and lower effective temperature.
+In an HR diagram, spotted evolutionary model tracks at a given mass and age shift to higher luminosity and lower effective temperature.
 Such a \emph{spot-corrected} HR diagram position would alter the age and mass estimates to $> 0.2-0.3$ $M_\odot$ and $\> 0.5$ Myr; in other words, back in the direction of previous na\"{i}ve estimates.
-However the full magnitude of the correction is an outstanding question.
+However, the full magnitude of the correction is an outstanding question.
 
@@
 
-The IGRINS and ESPaDOnS spectra indicate indicate $\vsini\sim$ 28 km~s$^{-1}$ and a rotation period of 3.375 days.
+The IGRINS and ESPaDOnS spectra indicate $\vsini\sim$ 28 km~s$^{-1}$ and a rotation period of 3.375 days.
 Combining these numbers gives $R\sin{i} \sim 1.87 R_{\odot}$.
@@
 
-In this paper, we have demonstrated that the IGRINS spectra of LkCa 4 is well fit with two temperatures, a hot photosphere of 4100 K and large cool patches of 2700--3000 K that cover 80\% of the stellar surface.
+In this paper, we have demonstrated that the IGRINS spectra of LkCa 4 are well fit with two temperatures, a hot photosphere of 4100 K and large cool patches of 2700--3000 K that cover 80\% of the stellar surface.
 This solution reproduces the high-resolution $HK$-band spectra obtained with IGRINS, the broadband SED, and rotational modulation of spectral features.
@@
 If assumption 4 is relaxed, the minimum fill factor decreases.
-The large amplitude photometric variations in LkCa 4 are therefore evidence for either a hot spot in excess of the ambient photosphere, or a large coverage fraction of cool starspots.
+The large amplitude photometric variations in LkCa 4 are therefore evidence for either a hot spot in excess of the ambient photosphere or a large coverage fraction of cool starspots.
 
@@
 This exceptionally large fraction of surface area covered by spots defies the conventional wisdom that starspots are the minority constituent of the stellar surface.
-The evidence for this derived fill factor has been shown in the SED, high-resolution spectral inference, direct spectral detection, and TiO variability modelling.
+The evidence for this derived fill factor has been shown in the SED, high-resolution spectral inference, direct spectral detection, and TiO variability modeling.
 Perhaps the strongest evidence for the large fill factor of cool photosphere is the large amplitude of $V-$band modulation, which cannot be explained with small spots, even if a spot temperature of absolute zero is assigned to the cool regions.
@@
 It is conceivable, and probably likely, that the value we report for $f_{\mathrm{cool}}$ is an overestimate of the surface area actually covered by spots.
-In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out-of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
+In this circum-polar spot scenario, local fingers of cool spots could reach down to near the equator, entering into and out of the field of view and giving rise to the large amplitude photometric variation seen on LkCa 4.
 This scenario is consistent with the inclination derived from relating $\vsini$, rotation period, and estimates for the stellar radius, as previously noted.
-Such estimates are limited by estimates of the radius, since uncertainties in effective temperature and luminosity cause a wide range of radius estimates.
+Such estimates are limited by estimates of the radius since uncertainties in effective temperature and luminosity cause a wide range of radius estimates.
 
@@
 The large amplitude of cyclical optical variability of LkCa 4 exceeds all other counterparts from the long-term monitoring of WTTSs by \citet{grankin08}.
-From a statistical perspective, it might not be a surprise that the source with the largest photometric variability also posessess among the largest coverage fraction of cool spots.
+From a statistical perspective, it might not be a surprise that the source with the largest photometric variability also possesses among the largest coverage fraction of cool spots.
 When compared with spot covering fractions of 15--60\% for evolved giants and subgiants \citep{chugainov76,berdyugina05}, the 80\% spot coverage of LkCa 4 seems high.
@@
 LkCa 4 represents an example of such an architecture, with more than  50\% of the visible stellar surface covered in spots at all observational phases.
-The longitudinally symmetric component evades photometric modulation detection, but contributes to otherwise anomalous color offsets.
+The longitudinally symmetric component evades photometric modulation detection but contributes to otherwise anomalous color offsets.
 
 Spots are also likely important in estimating the properties of generic low-mass young stars.
-As an example, the well-studied CTTS TW Hya has a $\sim 4100$ K photosphere measured from high resolution optical spectra \citep[e.g.][]{yang05}.
+As an example, the well-studied CTTS TW Hya has a $\sim 4100$ K photosphere measured from high-resolution optical spectra \citep[e.g.][]{yang05}.
 However, the near-IR spectrum is consistent with $\sim$ M2, when compared with main sequence dwarf stars \citep{vacca11}.
@@
 \citet{herczeg14} found an intermediate spectral type for TW Hya and other TTSs by focusing on TiO bands at redder wavelengths than previous spectra, and also by using young stars as photospheric templates.
-Similar discrepancies have been found between optical and near-IR spectral types \citep[e.g.][]{bouvier92,bary14,cottaar14} and in comparisons of spectral types measurement based on TiO bands and those based on high resolution blue spectra \citep[see discussion in][]{herczeg14}.
+Similar discrepancies have been found between optical and near-IR spectral types \citep[e.g.][]{bouvier92,bary14,cottaar14} and in comparisons of spectral types measurement based on TiO bands and those based on high-resolution blue spectra \citep[see discussion in][]{herczeg14}.
 
@@
 Figure \ref{fig:grankin_vr} shows that the $V-R$ colors from \citet{grankin08} are better reproduced if the cooler component is $\sim 3050$ K, thereby contributing more flux at optical wavelengths.
-The ZDI imaging of \citet{donati14} also indicate a complex structure of spots that are hotter than what is interpreted here as the ambient photosphere, while also reproducing the optical photometry.
+The ZDI imaging of \citet{donati14} also indicates a complex structure of spots that are hotter than what is interpreted here as the ambient photosphere, while also reproducing the optical photometry.
 Despite the need for more complicated emission structures to simultaneously reproduce all observations, the broadband SED, spectral shape, and rotational modulation of spectral indices are reasonably well fit with the two components presented here.
@@
 LkCa 4 breaks the apparent ceiling at 50\% coverage fraction of cool starspots, though it is not clear how to classify stars for which the minority of the surface is purportedly the ambient photosphere.
-A high fraction of the stellar surface may be covered in spots without inducing any photometric modulation, if the spoits are located in circumpolar regions that always face towards our line-of-sight, in longitudinally symmetric bands, or in many isotropic small spots.
+A high fraction of the stellar surface may be covered in spots without inducing any photometric modulation, if the spots are located in circumpolar regions that always face towards our line-of-sight, in longitudinally symmetric bands, or in many isotropic small spots.
 
@@
 
-where the prime symbol in the final line indicates a re-standarized mixture model flux, where the relative fluxes of the model components are now correctly scaled.
+where the prime symbol in the final line indicates a re-standardized mixture model flux, where the relative fluxes of the model components are now correctly scaled.
 
@@
 Jaffe for valuable comments on the draft.
-MG-S and GJH also thank Steve Saar and GJH thanks Lynne Hillenbrand for valuable discussions about spots.
+MG-S and GJH also thank Steve Saar, Lisa Prato, and Lynne Hillenbrand for valuable discussions about spots.
 

### 2017-01-13 document/submission/ms.tex
GJH revised abstract, pretty much done, I think

@@
 
-Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but magnetic fields and starspots complicate this process.
-In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.
-We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
-Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, with a best-fit filling factor of $\sim80$\%  for the cool photosphere at the time of the observation.
-These results are supported by comparisons of this mix of hot and cool photospheric temperatures by analyses of the spectral energy distribution, rotational modulation of colors and of TiO band strengths, and low-resolution optical/near-IR spectroscopy.
-LkCa 4 has either a warm photosphere mostly covered in cool spots or is a very cool star with a small hot spot.
-The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous estimates with the same unspotted stellar evolution models, although appropriate comparisons require the production and adoption of spotted evolutionary models.
-Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in open cluster ages inferred from low-mass stars and in large apparent age spreads of those clusters.
-In some spectral regions, starspots act as a featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.
+Ages and masses of young stars are often estimated by comparing their luminosities and effective temperatures to pre-main sequence stellar evolution tracks, but magnetic fields and starspots complicate both the observations and evolution.
+To understand their influence, we study the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.
+We introduce a new methodology for constraining both the starspot filling factor and the spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.
+Clearly discernable spectral features arise from both a hot photospheric component $\teffa\sim4100$ K and to a cool component $\teffb\sim2700-3000$ K, which covers $\sim80\%$ of the visible surface.
+This mix of hot and cool emission is supported by analyses of the spectral energy distribution, rotational modulation of colors and of TiO band strengths, and features in low-resolution optical/near-IR spectroscopy.
+Although the revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass than previous estimates from unspotted stellar evolution models, appropriate estimates will require the production and adoption of spotted evolutionary models.
+Biases from starspots likely afflict most fully convective young stars and contribute to uncertainties in ages and age spreads of open clusters.
+In some spectral regions starspots act as a featureless ``veiling'' continuum owing to high rotational broadening and heavy line-blanketing in cool star spectra.
 Some evidence is also found for an anti-correlation between the velocities of the warm and cool components.

### 2017-01-19 document/submission/ms.tex
Small corrections and addition to the affiliations, per request by coauthors.

@@
 Gully-Santiago,\altaffilmark{1} Gregory J.
-Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin R.
+Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3,18} Konstantin Grankin,\altaffilmark{4} Kevin R.
 Covey,\altaffilmark{5} J.F.
@@
 \altaffiltext{16}{Center for Cosmology and AstroParticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH 43210, USA}
-\altaffiltext{17}{Institute of Astronomy and Astrophysics, Academia Sinica
-(ASIAA), P.O. Box 23-141, Taipei 10641, Taiwan}
+\altaffiltext{17}{Institute of Astronomy and Astrophysics, Academia Sinica (ASIAA), Taipei 10617, Taiwan}
+\altaffiltext{18}{VIDA Postdoctoral Fellow}
 
